### 2017-03-03 EmptyHomesV1.Rmd
First commit of the code used to create the excel template files

---
title: "Empty Homes V1"
author: "Jonathan Bourne"
date: "10 February 2017"
output: html_document
---

```{r}
packages <- c("tidyverse", "spdep", "igraph", "maptools")

#you could replace a lot of the packages with just tidyverse but some people have problems installing it.
new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

lapply(packages, library, character.only = TRUE)

#Set up file system to read the correct folders this switches between aws and windows mode
basewd <-"~/Dropbox/SSE/Empty Homes"

DataFolder <- file.path(basewd, "Data")
ShapeFiles <- file.path(basewd,"ShapeFiles/statistical-gis-boundaries-london/ESRI")
Figures <- file.path(basewd, "Figures")

select <-dplyr::select
```

```{r}
setwd(ShapeFiles)

wards.shp <- readShapeSpatial("London_Ward.shp")
coords <- coordinates(wards.shp)
WardsAdj <- poly2nb(wards.shp, queen= FALSE)
plot(wards.shp, border="grey")
plot(WardsAdj, coords, add=TRUE, col="red")

test <- (nb2mat(WardsAdj)>0)*1

g=graph.data.frame(WardsAdj)
get.adjacency(WardsAdj,sparse=FALSE)

```

### 2017-03-20 CreateExcelTemplates.Rmd
I haven't done an update in a while so all kinds of changes have been made. A lot of the changes are to do with making a map at ward level not lsoa level due to problems with getting data from the councils.

---
title: "Untitled"
author: "Jonathan Bourne"
date: "10 February 2017"
output: html_document
---

GEOGRAPHIC LESCENSING FROM ONS remember to use!
https://www.ons.gov.uk/methodology/geography/licences

The lookup to convert from Local authority code to name and region code and name is found here
http://ons.maps.arcgis.com/home/item.html?id=17a30c262cf44ad0b9780d97c5d4a856

Number of households of size x with bedrooms y
https://www.nomisweb.co.uk/census/2011/lc4405ew
```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")
```

Postocode look up data found at
http://ons.maps.arcgis.com/home/item.html?id=ef72efd6adf64b11a2228f7b3e95deea

Covered by open government licesence
```{r}

setwd(PostcodeLookups)

PstCdLSOA.raw <- read.csv("PCD11_OA11_LSOA11_MSOA11_LAD11_EW_LU_aligned_v2.csv", stringsAsFactors = FALSE)

templatefile<- "Convert Postcode to LSOA.xlsx"

lapply(unique(PstCdLSOA.raw$LAD1), function(LAD){ 
   PstCdLSOA <- PstCdLSOA.raw[PstCdLSOA.raw$LAD11NM == LAD,]

filename <- paste0(LAD,"LSOA.xlsx")
setwd(basewd)
wb <- loadWorkbook("Convert Postcode to LSOA.xlsx")
#input the LSOA lookup table
writeData(wb, sheet = "LSOAdata", PstCdLSOA, colNames = T)
#add in randomly sampled postcodes as an example
writeData(wb, sheet = "InpuNames and codes for administrative geographyt", sample(PstCdLSOA$PCD7, 6), 
          startCol = 2, startRow = 2,
          colNames = F)
setwd(ExcelLookups)
saveWorkbook(wb,filename ,overwrite = T)
  })

```

The data on ONS is old, so taking a current list of post codes is necessary.

https://www.freemaptools.com/download/outcode-postcodes/postcode-outcodes.csv

Need to check the lattitude and longitude and merge them with the LSOA they fall inside. to create a new list

The England and wales shape files can be downloaded here
http://geoportal.statistics.gov.uk/datasets/da831f80764346889837c72508f046fa_0

```{r}

setwd(ShapeFiles)
list.files(pattern = ".shp")

#load shape file
shape <- readOGR(dsn = "LSOA_2004_London_Low_Resolution.shp")

#Convert to Latitude and longitude
shape <- spTransform(shape, CRS("+init=epsg:4326"))

#read postcodes
# setwd(basewd)
# postcodes <-read.csv("ukpostcodes.csv")
# 
# #subset to souteast
# p2 <- postcodes[grepl("^SE",postcodes$postcode),]

#Plot using base this doesn't work I don't know why
# coordinates(p2) <- ~ latitude + longitude  # pts needs to be a data.frame for this to work
# proj4string(p2) <- proj4string(shape)
# 
# plot(shape)
# plot(p2, col="red" , add=TRUE)

#convert shape files to data frame
AG <- tidy(shape)

#Plot shape files as map of london with south east plotted over the top. this does work as expected.
ggplot()+ geom_polygon(data=AG, aes(long, lat, group = group), 
colour = alpha("darkred", 1/2), size = 0.7, fill = 'skyblue', alpha = .3) +geom_point(data= p2, aes(x = longitude, y= latitude))+
  ggtitle("London With SE postcodes overplotted")

#Subset map to a smaller area
AG2 <- AG %>% filter(long>-0.2, long<0.1, lat<51.55, lat>51.45)
#check that the points are aligned. They are.
ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group), 
colour = alpha("darkred", 1/2), size = 0.7, fill = 'skyblue', alpha = .3) + geom_point(data= p2, aes(x = longitude, y= latitude))

```

```{r}
p3 <- postcodes %>% filter(latitude<65)
#ensure that the points are converted to latitude and longitude
coordinates(p3) <- ~longitude + latitude
#set the projection of the data to longitude and latitude
proj4string(p3) <- CRS("+proj=longlat")
#I don't undertsand what is going on here
p3 <- spTransform(p3, proj4string(shape))
proj4string(p3) <- proj4string(shape)
z <- over(p3, shape)

PstCdLSOA.raw <- bind_cols(postcodes %>% filter(latitude<65), z)

PstCdLSOA.raw <- PstCdLSOA.raw %>% filter(!is.na(PstCdLSOA.raw$LSOA_CODE))

head(PstCdLSOA.raw,100)
```

```{r}
lapply(unique(PstCdLSOA.raw$LA_NAME), function(LAD){ 
   PstCdLSOA <- PstCdLSOA.raw[PstCdLSOA.raw$LA_NAME == LAD,]

filename <- paste0(LAD,"LSOA.xlsx")
setwd(basewd)
wb <- loadWorkbook("Convert Postcode to LSOA.xlsx")
#input the LSOA lookup table
writeData(wb, sheet = "LSOAdata", PstCdLSOA, colNames = T)
#add in randomly sampled postcodes as an example
writeData(wb, sheet = "Input", sample(PstCdLSOA$postcode, 6), 
          startCol = 2, startRow = 2,
          colNames = F)
setwd(ExcelLookups)
saveWorkbook(wb,filename ,overwrite = T)
  })
```

```{r}
#Read postcodes from the ONS folder of codes
setwd(ONSpostcodes)
list.files()
p2<- read.csv("se.csv", header = FALSE)
setwd(ONSpostcodeMeta)
names(p2) <- z <- read.csv("Code-Point_Open_Column_Headers.csv")[1,] %>%t

#Check that the shapes are using the same coordinate system
AG <- tidy(shape)
#Subset map to a smaller area
AG2 <- AG %>% filter(long>530000, long<550000, lat>170000, lat<185000)
#check that the points are aligned. They are.
ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group), 
colour = alpha("darkred", 1/2), size = 0.7, fill = 'skyblue', alpha = .3)+ geom_point(data= p2, aes(x = Eastings, y= Northings))

#set the Northings an eastings columns to be the coordinates
coordinates(p2) <- ~Eastings + Northings
#defines the coordinate system
proj4string(p2) <- CRS("+init=epsg:27700")
#converts the coordinate system from the one definded to the coordinate system of the shape file, this step is not neccesary in this case as both are using the Uk grid referencing system.
p2 <- spTransform(p2, proj4string(shape))

#check that the conversion has worked properly
plot(shape)
plot(p2, col="red" , add=TRUE)

#Check which LSOA each postcode falls within and bind it to the postcode data
PstCdLSOA.raw <- bind_cols(tidy(p2), over(p2, shape))

#remove any NA values
PstCdLSOA.raw <- PstCdLSOA.raw %>% filter(!is.na(PstCdLSOA.raw$LSOA_CODE))

```

This code block works smoothly using government data testing on the "se" postcodes. The next code chunk will perform the same operation for all postcodes. as a result it is computationally intense.

#Using only ONS data

Load the LSOA shape data for EW 
```{r}
setwd(LSOAshapedata)

shape <- readOGR(dsn = list.files(pattern = "shp"))

```

# Load Post code data

This chunk checks the exiatane of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup. Creating the lookup takes quite a lot of time so it is good to only have to do it once.
```{r}

if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
 PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
} else {
  source(file.path(CommonCode, "PostcodeLookup.R"))
}

```

Add in LAD names and Region, remove non-essential columns
```{r}
setwd(AddGeog)
list.files()

LADReg <- read.csv("LAD15_RGN15_EN_LU.csv", stringsAsFactors = FALSE   )
Wardnames <- read.csv("Ward_to_Local_Authority_District_to_County_to_Region_to_Country_December_2016_Lookup_in_United_Kingdom_V2.csv", stringsAsFactors = FALSE) %>%
  select(WD16CD, WD16NM)

PstCdLSOA <- PstCdLSOA.raw %>% mutate_if(., is.factor, as.character)

#There are a couple of errors is the region LSOA look up these are manually corrected here.
PstCdLSOA[PstCdLSOA$Postcode=="BN994AE", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="BN126BW", c(3,4,7)]

PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BA", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)] 
PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BB", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)]

PstCdLSOA <- PstCdLSOA %>% left_join(., LADReg, by = c("Admin_district_code"="LAD15CD")) %>%
  left_join(., Wardnames, c("Admin_ward_code" = "WD16CD")) %>% 
  select(Postcode, Country_code, Admin_district_code, 
                          Admin_ward_code, lsoa11cd, lsoa11nm, LAD15NM, 
                          RGN15CD, RGN15NM, WD16NM)

#Wales doesn't have any LAD for some reason, fix is to add in LSOA name subtracting the code

PstCdLSOA$LAD15NM[grepl("W", PstCdLSOA$Country_code)] <- gsub(' .*', '' , PstCdLSOA$lsoa11nm[grepl("W", PstCdLSOA$Country_code)])

#Make sure that Scotland and Wales are included in the regions.

PstCdLSOA[grepl("W", PstCdLSOA$Country_code),c("RGN15CD" , "RGN15NM" )] <- c("Wales", "Wales")

PstCdLSOA[grepl("S", PstCdLSOA$Country_code),c("RGN15CD" , "RGN15NM" )] <- c("Scotland", "Scotland")

#remove spaces from the the Postcodes

PstCdLSOA <- PstCdLSOA %>% mutate(Postcode = gsub(" ", "", Postcode))

```

Create a script that cycles through and creates a folder for each region and then generates the excel sheet for each LAD within each region. This allows the excel spreadsheet for different parts of the country to be found more easily.
```{r}

lapply(unique(PstCdLSOA$RGN15NM), function(n){
  title <- paste("Region", n)
  dir.create(file.path(Regions, title ), showWarnings = FALSE)
  #The inner loop creates the excel files for each LAD within each region
  PstCdLSOA.Reg <- PstCdLSOA %>% filter(RGN15NM == n)

  print(title)
  lapply(unique(PstCdLSOA.Reg$LAD15NM), function(LAD){

    PstCdLSOA.filt <- PstCdLSOA.Reg %>% filter(LAD15NM == LAD)
    print(paste(n, ":", LAD))
      ExemptionsFile <- paste0(LAD,"ExemptionsLSOA.xlsx")
      CTBandsFile <- paste0(LAD,"CTBandsLSOA.xlsx")
      setwd(basewd)
      wb <- loadWorkbook("Convert Postcode to LSOA.xlsx")
      #input the LSOA lookup table
      writeData(wb, sheet = "LSOAdata", PstCdLSOA.filt, colNames = T)
      #add in randomly sampled postcodes as an example
      writeData(wb, sheet = "Input", sample(PstCdLSOA.filt$Postcode, 6),
                startCol = 2, startRow = 2,
                colNames = F)
      setwd(file.path(Regions, title))
      saveWorkbook(wb,ExemptionsFile ,overwrite = T)
      saveWorkbook(wb,CTBandsFile ,overwrite = T)
    })
})

```

### 2017-03-20 EmptyHomesV1.Rmd
I haven't done an update in a while so all kinds of changes have been made. A lot of the changes are to do with making a map at ward level not lsoa level due to problems with getting data from the councils.

@@
 
+It would have been sensible to separate council and private housing
+
+```{r setup}
+setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
+source("Setup.R")
+```
+
+#Load completed data
+
 ```{r}
-packages <- c("tidyverse", "spdep", "igraph", "maptools")
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
+list.files()
 
-#you could replace a lot of the packages with just tidyverse but some people have problems installing it.
-new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
-if(length(new.packages)) install.packages(new.packages)
-
-lapply(packages, library, character.only = TRUE)
-
-#Set up file system to read the correct folders this switches between aws and windows mode
-basewd <-"~/Dropbox/SSE/Empty Homes"
-
-DataFolder <- file.path(basewd, "Data")
-ShapeFiles <- file.path(basewd,"ShapeFiles/statistical-gis-boundaries-london/ESRI")
-Figures <- file.path(basewd, "Figures")
-
-select <-dplyr::select
+test <- read.xlsx("SuttonExemptionsLSOA.xlsx")
+ken1 <- read.xlsx("Copy of Kensington and ChelseaCTBandsLSOA.xlsx" )
+ken2 <- read.xlsx("Copy of Kensington and ChelseaExemptionsLSOA (002).xlsx")
 ```
@@
 ```
+
+Council tax bands from VOA
+https://www.gov.uk/government/statistics/council-tax-stock-of-properties-2016
+
+```{r PopandHomes}
+setwd(DataFolder)
+
+CTtaxstock<- read_csv("Table_CTSOP1.1_2016.csv")
+
+pop <- read_csv("SAPE2.csv")
+
+EW <- inner_join(select(CTtaxstock, ECODE, ALL_PROPERTIES),select(pop, `Area Codes`, `All Ages`),
+          by=c("ECODE" = "Area Codes")) %>% setNames(c("ECODE", "Homes", "Pop")) 
+```
+
+#Padstow example
+```{r}
+test2 <- CTtaxstock 
+pop2 <- pop %>% filter(grepl("Cornwall 008",X3))
+
+#padstow
+pad <- left_join(select(test2, ECODE, ALL_PROPERTIES), select(pop2, `Area Codes`, `All Ages`),
+          by=c("ECODE" = "Area Codes")) %>% 
+  mutate(diff = ALL_PROPERTIES-`All Ages`, ratio = ALL_PROPERTIES/`All Ages`) %>% filter(complete.cases(.))
+
+```
+
+#Load the LSOA shape data for EW
+
+```{r}
+setwd(LSOAshapedata)
+
+shape <- readOGR(dsn = list.files(pattern = "shp"))
+
+```
+
+# Load Post code data
+
+This chunk checks the exiatane of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup.
+Creating the lookup takes quite a lot of time so it is good to only have to do it once.
+```{r}
+
+if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
+ PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
+} else {
+  source(file.path(CommonCode, "PostcodeLookup.R"))
+}
+
+```
+
+Bind the ward names and LAD names to the lsoa data
+```{r}
+setwd(PostcodeLookups)
+lsoa <- read_csv("PCD11_OA11_LSOA11_MSOA11_LAD11_EW_LU_aligned_v2.csv") %>%
+  select(LSOA11CD:LAD11NMW) %>% distinct(., LSOA11CD, .keep_all = TRUE)
+
+setwd(AddGeog)
+wardnames <- read_csv("Ward_to_Local_Authority_District_to_County_to_Region_to_Country_December_2016_Lookup_in_United_Kingdom_V2.csv") %>% setNames(c("Admin_ward_code", names(.)[-1]))
+
+#uses the dataframe from the CreateExceltemplates to get the ward names and the lsoa together
+wardlsoa <- PstCdLSOA.raw %>% distinct(lsoa11cd, .keep_all = TRUE) %>% 
+  select(lsoa11cd, Admin_ward_code)
+
+EW2 <- inner_join(EW, lsoa, by = c("ECODE" = "LSOA11CD") ) %>% 
+      left_join(., wardlsoa, by = c("ECODE"="lsoa11cd") ) %>% 
+  left_join(., select(wardnames, Admin_ward_code, WD16NM), by = "Admin_ward_code") %>%
+  group_by(Admin_ward_code) %>%
+  mutate(WardHomes = sum(Homes),  WardPop = sum(Pop)) %>% ungroup
+rm(wardlsoa)
+rm(wardnames)
+```
+
+Convert shape file to dataframe and join in the LSOA data
+```{r}
+setwd(LSOAshapedata)
+
+shape <- readOGR(dsn = list.files(pattern = "shp"))
+
+AG <- fortify(shape, region = "objectid")
+
+AG <- AG %>% mutate(id = as.integer(id)) %>% 
+  left_join(., shape@data, by = c("id" = "objectid")) %>% 
+  left_join(., EW2, by = c("lsoa11cd" = "ECODE"))
+
+```
+
+#I should probably join the homes and pop at the same time I join the council tax data
+
+other borough
+```{r}
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
+list.files()
+
+test <- read_excel("Copy of Haringey_Exemptions_Discounts_LSOA.xlsx")[,c(1,4:6)] %>% setNames(make.names(names(.)))
+
+test2 <- test %>% group_by(LSOA_CODE, Exemption.type) %>% summarise(Counts = n())
+
+test2b <- test %>% 
+  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
+  group_by(type2) %>% summarise(Counts = n())
+
+test2b <- test %>% 
+  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
+  group_by(type2, LSOA_CODE) %>% "Hammersmith.xls"  
+  summarise(Counts = n()) %>% 
+  spread(., type2, Counts, fill = 0)
+
+test3 <- test2b %>% left_join(., select(EW2, ECODE:Pop), by = c("LSOA_CODE" = "ECODE")) %>%
+   mutate(EmptPerc = Empty/Homes)
+
+```
+
+Load lambeth data
+```{r}
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
+list.files()
+
+test <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>% setNames(make.names(names(.)))
+
+test2b <- test %>% 
+  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
+  group_by(type2, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>% 
+  spread(., type2, Counts, fill = 0)
+
+test3 <- test2b %>% left_join(., select(EW2, ECODE:Pop), by = c("LSOA_CODE" = "ECODE")) %>%
+   mutate(EmptPerc = Empty/Homes)
+
+```
+
+Filter to lambeth and plot
+```{r}
+AG2 <- AG %>% filter(LAD11NM == "Lambeth") %>% 
+  left_join(., test2b, by = c("lsoa11cd" = "LSOA_CODE")) %>% mutate(EmptPerc = Empty/Homes)
+
+ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptPerc), 
+colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
+  ggtitle("Lambeth coloured by areas of highest % empty Homes")
+
+```
+
+Filter to RBKC
+```{r}
+
+AG2 <- AG %>% filter(LAD11NM == "Kensington and Chelsea")
+
+#manually map ward codes to empty and missing homes
+
+WardDat <- data.frame(Admin_ward_code = unique(AG2$Admin_ward_code), 
+           Wardname = c("Abingdon","Brompton and Hans Town", "Courtfield", "Stanley", "Campden", "Colville", "Earl's Court", 
+                      "Redcliffe", "Chelsea Riverside", "Kensal Green", "Golborne", "Royal Hospital", "Holland", "Notting Dale",
+                      "Norland", "St. Helen's", "Pembridge", "Queen's Gate", "Dalgarno"),
+           LowUse = c(744,1932,1060,593,664,330,572,587,371,0, 196, 829, 640,106,237, 149,331,846,87))
+
+Chelsea <- EW2 %>% filter(LAD11NM == "Kensington and Chelsea") %>% 
+  select(Admin_ward_code:WardPop) %>%
+  distinct(Admin_ward_code, .keep_all=TRUE) %>% 
+  left_join(., WardDat) %>% ungroup %>% mutate(PercEmpt = LowUse/WardHomes)
+
+AG2 <- AG2 %>% left_join(., WardDat, by = "Admin_ward_code") %>% 
+  filter(Wardname != "Kensal Green")
+
+ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = vallow), 
+colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() 
+```
+
+#get prices
+
+```{r}
+
+setwd(DataFolder)
+
+test <-read_csv("pp-2016.csv", col_names = FALSE )
+
+#quick and dirty loses half the sales due to missing the postcode
+test <- test %>% left_join(., PstCdLSOA.raw, by = c("X4"="Postcode")) %>% filter(!is.na(lsoa11cd))
+
+test2 <- test %>% group_by(Admin_ward_code) %>% summarise( MeanPrice = mean(X2), counts =n() )
+
+WardDat2 <- WardDat %>% left_join(., test2) %>% mutate(vallow = LowUse*MeanPrice) %>%
+  filter(!is.na(MeanPrice))
+
+sum(WardDat2$vallow)/sum(WardDat2$LowUse)
+
+Lest <- test %>% filter(X14 =="LEICESTERSHIRE")
+
+Lest %>% filter(X2<15000000) %>% ggplot(., aes(x= X2)) + geom_density()
+
+%>% group_by(X13) %>% summarise(mean = mean(X2))
+
+Melt <- test %>% filter(X13 == "MELTON")
+
+test %>% filter(grepl("chelsea", X13, ignore.case = TRUE)) %>%
+  filter(X2<3000000) %>% ggplot(., aes(x= X2)) + geom_density()
+
+```
+
+# Using the semi data
+
+```{r}
+#Lambeth
+
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
+
+Lambeth <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>% setNames(make.names(names(.))) %>% 
+  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
+  group_by(type2, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>% 
+  spread(., type2, Counts, fill = 0) %>% 
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
+  group_by(Admin_ward_code) %>% mutate(Empty = sum(Empty), LowUse = Empty) %>% ungroup
+
+LAMDAT <- AG %>% filter(LAD11NM == "Lambeth") %>% 
+  left_join(., select(Lambeth, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Sutton
+
+Sutton <- read_excel("SuttonExemptionsLSOA.xlsx"  )[,1:6]
+
+#ward folder
+setwd(SemiLondon)
+list.files()
+
+wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)
+
+test <- wardnames %>% filter(grepl("Kensington", LAD11NM))
+
+test <- EW2 %>% filter(LAD11NM == "Wandsworth")
+
+#Chelsea
+Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM))
+
+Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
+  mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(X.Ward) %>%
+  mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related., Empty..50..premium., Moorings , na.rm = TRUE),
+         LowUse = Empty + Second.Homes) %>% ungroup
+
+Chelsea[is.na(Chelsea)] <-0
+rm(Chelwards)
+
+CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
+  filter(WD16NM!= "Kensal Green")
+
+#Hackney has provided Census Wards I'm not sure how useable it is. 
+hackney <- read_csv("hackney.csv") %>% setNames(make.names(names(.))) %>% group_by(Exemption.Discount, Ward.Name) %>% summarise(counts = n()) %>% ungroup %>% spread(Exemption.Discount, counts, fill = 0)
+
+#Hammersmith 
+Hammersmith <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
+  bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
+  mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`)
+
+Hammersmith2 <- EW2 %>% filter(LAD11NM == "Hammersmith and Fulham") %>% left_join(., select(Hammersmith, Admin_ward_code, LowUse, Empty))
+
+HAMDAT <- AG %>% filter(LAD11NM == "Hammersmith and Fulham")%>% left_join(., select(Hammersmith, Admin_ward_code, LowUse, Empty))
+
+#Wandsworth
+
+wardnames %>% filter(LAD11NM == "Wandsworth")
+
+Wandsworth <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
+  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
+  arrange(`Ptc Wardname`) %>% 
+  filter(!is.na(`Ptc Wardname`)) %>% 
+  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
+              select(Admin_ward_code)) %>%
+  mutate(LowUse = Empty)
+
+Wandsworth2 <- EW2 %>% filter(LAD11NM == "Wandsworth") %>% left_join(., select(Wandsworth, Admin_ward_code, Empty))
+WANDAT <- AG %>% filter(LAD11NM == "Wandsworth")%>% left_join(., select(Wandsworth, Admin_ward_code, LowUse, Empty))
+
+#Merton
+wardnames %>% filter(LAD11NM == "Merton")
+Merton <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X) %>%
+  filter(X != "Norbury", X!="Nightingale", X !="Stonecot") %>% 
+    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
+              select(Admin_ward_code)) %>%
+  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home )
+
+MERDAT <- AG %>% filter(LAD11NM == "Merton")%>% left_join(., select(Merton, Admin_ward_code, LowUse, Empty))
+
+#Southwark
+
+test <- wardnames %>% filter(LAD11NM == "Southwark")
+
+Southwark <- read_excel("southwark.xlsx" , skip = 1) %>% setNames(make.names(names(.))) %>% 
+  filter(Ward.codes != "TOTALS") %>% select(-Ward.codes) %>%
+  mutate(WARDS= na.locf(WARDS)) %>% group_by(WARDS) %>%
+  summarise_all(sum, na.rm = TRUE) %>% ungroup %>%
+  arrange(WARDS) %>%
+    bind_cols(., wardnames %>% filter(LAD11NM == "Southwark") %>% 
+              select(Admin_ward_code)) %>%
+  mutate(Empty =   Unoccupied.and.furnished.lets....0.
++ Job.related.dwelling...50..discount + Second.Home...unoccupied.and.furnished...0.+Empty.and.unfurnished...0.
++ Levy.on.long.term.empty...50..Premium + Uninhabitable.Works.required....0., LowUse =  Empty )
+
+Wandsworth2 <- EW2 %>% filter(LAD11NM == "Southwark") %>% left_join(., select(Southwark, Admin_ward_code, Empty))
+
+SOUDAT <- AG %>% filter(LAD11NM == "Southwark")%>% left_join(., select(Southwark, Admin_ward_code, LowUse, Empty))
+
+#Harrow
+
+test <- read_excel("HarrowCTBandsLSOA. 3118795.xlsx"  )[1:4]%>% setNames(make.names(names(.)))
+
+#Kingston
+test <- wardnames %>% filter(grepl("Kingston upon Thames", LAD11NM))
+
+Kingston <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
+  arrange(X) %>% slice(1:16) %>%
+  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
+              select(Admin_ward_code)) %>%
+  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..)
+
+KINDAT <- AG %>% filter(LAD11NM == "Kingston upon Thames")%>% left_join(., select(Kingston, Admin_ward_code, LowUse, Empty))
+
+#TowerHamlets
+test <- wardnames %>% filter(grepl("Tower", LAD11NM))
+
+Tower <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
+  filter(!is.na(DiscClass)) %>%
+  group_by(Ward, DiscClass) %>%
+  summarise(count = n()) %>% ungroup %>%
+  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
+  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
+  slice(c(1:13, 15:17, 14, 18:20)) %>%
+   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM)))
+
+TOWDAT <- AG %>% filter(grepl("Tower", LAD11NM)) %>% left_join(., select(Tower, Admin_ward_code, LowUse, Empty))
+
+#Greenwhich
+list.files()
+wardnames %>% filter(grepl("Greenwich", LAD11NM))
+
+Greenwich <- read_excel( "FOI-3348 ctfoi35report.xlsx" ) %>%  
+  setNames(make.names(names(.))) %>%
+  filter(grepl("EMPTY",Exempt.Discount.Description)) %>% 
+  select(-Exempt.Code) %>%
+  spread(key= Exempt.Discount.Description, value = Total, fill = 0) %>%
+  mutate(Empty = rowSums(.[,-1]), LowUse = Empty) %>%
+   bind_cols(., wardnames %>% filter(grepl("Greenwich", LAD11NM)))
+
+GREDAT <- AG %>% filter(grepl("Greenwich", LAD11NM)) %>% left_join(., select(Greenwich, Admin_ward_code, LowUse, Empty))
+
+```
+
+Plot Map
+```{r}
+AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
+                 SOUDAT, KINDAT, TOWDAT, GREDAT) %>% 
+  mutate(LowUsePerc = LowUse/WardHomes, 
+         EmptyPerc = Empty/WardHomes,
+         EmptyPercRank = percent_rank(Empty/WardHomes))
+
+ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptyPerc), 
+colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
+  labs(title = "All Boroughs Percentage Empty") +
+  theme(plot.title = element_text(hjust = 0.5))
+
+AG2 %>% 
+  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =sqrt(EmptyPerc)), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+
+ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = LowUse/WardHomes), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+
+#single borough
+GREDAT %>%
+  mutate(LowUsePerc = LowUse/WardHomes, 
+         EmptyPerc = Empty/WardHomes,
+         EmptyPercRank = percent_rank(Empty/WardHomes)) %>%
+ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = EmptyPerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+
+```
+
+#Proper data Barrow
+
+```{r}
+setwd(file.path(RegionsComp, "Region North West"))
+
+list.files()
+
+test <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1) %>% setNames(make.names(names(.))) %>% .[,1:4] %>% filter(Current.Discount.Type.Code !="SINGLE") %>% group_by(LSOA_CODE) %>%
+  summarise(Empty = n())
+
+Barrow2 <- test %>% left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)
+
+test2 <- test %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd")) %>% mutate(EmptyPerc = Empty/Homes)
+
+ggplot()+ geom_polygon(data=test2, aes(long, lat, group = group, fill = EmptyPerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")
+```

### 2017-03-20 SubCode/Setup.R

@@ -1,0 +1,31 @@
+##This code is used to setup the project it is common to both the empty homes doc and also the template creation doc.
+
+
+packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "zoo")
+
+new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
+if(length(new.packages)) install.packages(new.packages)
+
+
+lapply(packages, library, character.only = TRUE)
+
+
+#Set up file system to read the correct folders this switches between aws and windows mode
+basewd <-"~/Dropbox/SSE/Empty Homes"
+
+DataFolder <- file.path(basewd, "Data")
+ShapeFiles <- file.path(basewd,"ShapeFiles/statistical-gis-boundaries-london/ESRI")
+Figures <- file.path(basewd, "Figures")
+PostcodeLookups <- file.path(DataFolder, "PostcodeLookups")
+ExcelLookups <- file.path(basewd, "ExcelLookups")
+ONSpostcodes <- file.path(basewd, "ONS postcodes", "CSV")
+ONSpostcodeMeta <- file.path(basewd, "ONS postcodes", "Doc")
+LSOAshapedata <- file.path(basewd,"ShapeFiles",
+                           "Lower_Layer_Super_Output_Areas_December_2011_Generalised_Clipped__Boundaries_in_England_and_Wales")
+AddGeog <- file.path(basewd, "AdditionalGeographies")
+#The regions folder is for the excel templates of each region of the UK
+Regions <- file.path(basewd, "Regions")
+RegionsComp <- file.path(basewd, "Regions-Complete")
+CommonCode <- file.path(basewd, "EmptyHomesCode", "SubCode")
+SemiLondon <- file.path(basewd, "semi-data-london")
+select <-dplyr::select

### 2017-03-21 CreateExcelTemplates.Rmd
Cleaned up the code to prevent AG from needed to be built every time.
Added in the cornwall data and map at LSOA level.

@@
 https://www.nomisweb.co.uk/census/2011/lc4405ew
+
 ```{r setup}

### 2017-03-21 EmptyHomesV1.Rmd
Cleaned up the code to prevent AG from needed to be built every time.
Added in the cornwall data and map at LSOA level.

@@
 It would have been sensible to separate council and private housing
+
+#Telegraph article on pensioners requireing mortgages
+http://www.telegraph.co.uk/personal-banking/mortgages/pensioner-mortgages-boom-britains-broken-housing-market/
 
@@
 ken1 <- read.xlsx("Copy of Kensington and ChelseaCTBandsLSOA.xlsx" )
-ken2 <- read.xlsx("Copy of Kensington and ChelseaExemptionsLSOA (002).xlsx")
+ken2 <- read.xlsx("NewhamExemptionsLSOA.XLSX")[,1:4]
 ```
@@
 
+#VOA data
+
 Council tax bands from VOA
@@
           by=c("ECODE" = "Area Codes")) %>% setNames(c("ECODE", "Homes", "Pop")) 
-```
-
-#Padstow example
-```{r}
-test2 <- CTtaxstock 
-pop2 <- pop %>% filter(grepl("Cornwall 008",X3))
-
-#padstow
-pad <- left_join(select(test2, ECODE, ALL_PROPERTIES), select(pop2, `Area Codes`, `All Ages`),
-          by=c("ECODE" = "Area Codes")) %>% 
-  mutate(diff = ALL_PROPERTIES-`All Ages`, ratio = ALL_PROPERTIES/`All Ages`) %>% filter(complete.cases(.))
-
 ```
@@
 Bind the ward names and LAD names to the lsoa data
-```{r}
+```{r LAD/WARD data}
 setwd(PostcodeLookups)
@@
 ```{r}
+
+if(file.exists(file.path(DataFolder,"shapeframe.rds"))){
+ PstCdLSOA.raw <- readRDS(file.path(DataFolder,"shapeframe.rds"))
+} else{
     setwd(LSOAshapedata)
@@
     left_join(., EW2, by = c("lsoa11cd" = "ECODE"))
+
+    saveRDS(AG, file.path(DataFolder,"shapeframe.rds"))
+    }
 
@@
 colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
-  ggtitle("Lambeth coloured by areas of highest % empty Homes")
+  ggtitle("Lambeth coloured by areas of highest % empty Homes")+
+  theme(plot.title = element_text(hjust = 0.5))
 
@@
 
-AG2 <- AG2 %>% left_join(., WardDat, by = "Admin_ward_code") %>% 
-  filter(Wardname != "Kensal Green")
+AG2 <-AG2 %>% left_join(., WardDat, by = "Admin_ward_code") %>% 
+  filter(Wardname != "Kensal Green")%>% mutate(PercEmpt = LowUse/WardHomes)
 
-ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = vallow), 
-colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() 
+ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = PercEmpt), 
+colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
+  ggtitle("Kensington and Chelsea low use property")+
+  theme(plot.title = element_text(hjust = 0.5))
+
 ```
@@
 
-test <-read_csv("pp-2016.csv", col_names = FALSE )
+prices <-read_csv("pp-2016.csv", col_names = FALSE )
 
 #quick and dirty loses half the sales due to missing the postcode
-test <- test %>% left_join(., PstCdLSOA.raw, by = c("X4"="Postcode")) %>% filter(!is.na(lsoa11cd))
+test <- prices %>% mutate(X4 = gsub(" ", "", X4)) %>% left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), by = c("X4"="Postcode")) %>% filter(!is.na(lsoa11cd))
 
-test2 <- test %>% group_by(Admin_ward_code) %>% summarise( MeanPrice = mean(X2), counts =n() )
+MeanWardPrice <- test %>% group_by(Admin_ward_code) %>% summarise( MeanPrice = mean(X2), counts =n() )
 
-WardDat2 <- WardDat %>% left_join(., test2) %>% mutate(vallow = LowUse*MeanPrice) %>%
+MeanWardPrice %>% ggplot(., aes(x= counts)) +geom_density()
+
+WardDat2 <- WardDat %>% left_join(., MeanWardPrice) %>% mutate(vallow = LowUse*MeanPrice) %>%
   filter(!is.na(MeanPrice))
@@
 ```
+
+```{r}
+test <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% mutate(Empty = rowSums(.[,2:9])) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)
+
+test2 <- test %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))
+
+```
+
+#Cornwall
+
+```{r}
+
+setwd(file.path(RegionsComp, "Region South West"))
+
+list.files()
+
+Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+  mutate(LowUse = rowSums(.[,c(FALSE,!grepl("exempt",(names(.)[-1])))])) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup
+
+Cornwall <- Cornwall %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+Cornwall %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
+  ggplot(.)+ 
+  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall Empty and second Homes %")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+ Cornwall %>% filter(Admin_ward_code !="E05009195") %>% summarise(x =cor(MeanPrice, WardLowUsePerc, use = 'complete.obs'))
+
+ Cornwall %>% ggplot(., aes(y=MeanPrice, x= WardLowUsePerc )) + geom_point() +
+   labs(title = "Relationshibetween LowUse Percentage and Mean Price in Ward")+
+  theme(plot.title = element_text(hjust = 0.5))
+
+```

### 2017-03-28 EmptyHomesV1.Rmd
Removed the initial borough plotting. Added in the rural boroughs. Added in code for creating a single borough plot using the XXXDAT format

@@
 
+PCLB0 is second homes, PCLC0 is long term empty, PCLC100 is empty and unfurnished up to six months and PCLD100 is undergoing major repairs up to 12 months.
+
 #Telegraph article on pensioners requireing mortgages
 http://www.telegraph.co.uk/personal-banking/mortgages/pensioner-mortgages-boom-britains-broken-housing-market/
+
+Mean household income 31920
+https://www.ons.gov.uk/peoplepopulationandcommunity/personalandhouseholdfinances/incomeandwealth/datasets/nowcastinghouseholdincomeintheuk
 
@@
 ```{r}
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
+
+setwd(file.path(RegionsComp, "Region East of England"))
 list.files()
 
-test <- read.xlsx("SuttonExemptionsLSOA.xlsx")
-ken1 <- read.xlsx("Copy of Kensington and ChelseaCTBandsLSOA.xlsx" )
-ken2 <- read.xlsx("NewhamExemptionsLSOA.XLSX")[,1:4]
+test <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")
+
+unique(test$Exemption.type)
+
 ```
@@
 ```{r}
-setwd(ShapeFiles)
-
-wards.shp <- readShapeSpatial("London_Ward.shp")
-coords <- coordinates(wards.shp)
-WardsAdj <- poly2nb(wards.shp, queen= FALSE)
-plot(wards.shp, border="grey")
-plot(WardsAdj, coords, add=TRUE, col="red")
-
-test <- (nb2mat(WardsAdj)>0)*1
-
-g=graph.data.frame(WardsAdj)
-get.adjacency(WardsAdj,sparse=FALSE)
+# setwd(ShapeFiles)
+# 
+# wards.shp <- readShapeSpatial("London_Ward.shp")
+# coords <- coordinates(wards.shp)
+# WardsAdj <- poly2nb(wards.shp, queen= FALSE)
+# plot(wards.shp, border="grey")
+# plot(WardsAdj, coords, add=TRUE, col="red")
+# 
+# test <- (nb2mat(WardsAdj)>0)*1
+# 
+# 
+# g=graph.data.frame(WardsAdj)
+# get.adjacency(WardsAdj,sparse=FALSE)
 
@@
 if(file.exists(file.path(DataFolder,"shapeframe.rds"))){
- PstCdLSOA.raw <- readRDS(file.path(DataFolder,"shapeframe.rds"))
+ AG<- readRDS(file.path(DataFolder,"shapeframe.rds"))
 } else{
@@
 
-other borough
-```{r}
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
-list.files()
-
-test <- read_excel("Copy of Haringey_Exemptions_Discounts_LSOA.xlsx")[,c(1,4:6)] %>% setNames(make.names(names(.)))
-
-test2 <- test %>% group_by(LSOA_CODE, Exemption.type) %>% summarise(Counts = n())
-
-test2b <- test %>% 
-  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
-  group_by(type2) %>% summarise(Counts = n())
-
-test2b <- test %>% 
-  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
-  group_by(type2, LSOA_CODE) %>% "Hammersmith.xls"  
-  summarise(Counts = n()) %>% 
-  spread(., type2, Counts, fill = 0)
-
-test3 <- test2b %>% left_join(., select(EW2, ECODE:Pop), by = c("LSOA_CODE" = "ECODE")) %>%
-   mutate(EmptPerc = Empty/Homes)
-
-```
-
-Load lambeth data
-```{r}
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
-list.files()
-
-test <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>% setNames(make.names(names(.)))
-
-test2b <- test %>% 
-  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
-  group_by(type2, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>% 
-  spread(., type2, Counts, fill = 0)
-
-test3 <- test2b %>% left_join(., select(EW2, ECODE:Pop), by = c("LSOA_CODE" = "ECODE")) %>%
-   mutate(EmptPerc = Empty/Homes)
-
-```
-
-Filter to lambeth and plot
-```{r}
-AG2 <- AG %>% filter(LAD11NM == "Lambeth") %>% 
-  left_join(., test2b, by = c("lsoa11cd" = "LSOA_CODE")) %>% mutate(EmptPerc = Empty/Homes)
-
-ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptPerc), 
-colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
-  ggtitle("Lambeth coloured by areas of highest % empty Homes")+
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
-Filter to RBKC
-```{r}
-
-AG2 <- AG %>% filter(LAD11NM == "Kensington and Chelsea")
-
-#manually map ward codes to empty and missing homes
-
-WardDat <- data.frame(Admin_ward_code = unique(AG2$Admin_ward_code), 
-           Wardname = c("Abingdon","Brompton and Hans Town", "Courtfield", "Stanley", "Campden", "Colville", "Earl's Court", 
-                      "Redcliffe", "Chelsea Riverside", "Kensal Green", "Golborne", "Royal Hospital", "Holland", "Notting Dale",
-                      "Norland", "St. Helen's", "Pembridge", "Queen's Gate", "Dalgarno"),
-           LowUse = c(744,1932,1060,593,664,330,572,587,371,0, 196, 829, 640,106,237, 149,331,846,87))
-
-Chelsea <- EW2 %>% filter(LAD11NM == "Kensington and Chelsea") %>% 
-  select(Admin_ward_code:WardPop) %>%
-  distinct(Admin_ward_code, .keep_all=TRUE) %>% 
-  left_join(., WardDat) %>% ungroup %>% mutate(PercEmpt = LowUse/WardHomes)
-
-AG2 <-AG2 %>% left_join(., WardDat, by = "Admin_ward_code") %>% 
-  filter(Wardname != "Kensal Green")%>% mutate(PercEmpt = LowUse/WardHomes)
-
-ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = PercEmpt), 
-colour = alpha("darkred", 1/2), size = 0.7) + scale_colour_gradient2() +
-  ggtitle("Kensington and Chelsea low use property")+
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
 #get prices
@@
 
-prices <-read_csv("pp-2016.csv", col_names = FALSE )
+prices <-read_csv("pp-2016.csv", col_names = FALSE ) %>% 
+  mutate(X4 = gsub(" ", "", X4)) %>% 
+  left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), 
+            by = c("X4"="Postcode")) %>% 
+  filter(!is.na(lsoa11cd)) %>% mutate(Prime = X2>1e6, SuperPrime = X2>1e7)
 
-#quick and dirty loses half the sales due to missing the postcode
-test <- prices %>% mutate(X4 = gsub(" ", "", X4)) %>% left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), by = c("X4"="Postcode")) %>% filter(!is.na(lsoa11cd))
+MeanWardPrice <- prices %>% 
+  group_by(Admin_ward_code) %>% 
+  summarise( MeanPrice = mean(X2), 
+             MedianPrice = median(X2),counts =n(),  
+             Prime = sum(Prime), 
+             SuperPrime = sum(SuperPrime)) %>% 
+  mutate(TotPrime = Prime/sum(Prime), TotSupPrime = SuperPrime/sum(SuperPrime),
+         PrimePerc = Prime/counts, SuperPrimePerc = SuperPrime/counts)
 
-MeanWardPrice <- test %>% group_by(Admin_ward_code) %>% summarise( MeanPrice = mean(X2), counts =n() )
-
-MeanWardPrice %>% ggplot(., aes(x= counts)) +geom_density()
+MeanWardPrice %>% ggplot(., aes(x= counts)) + geom_density()
 
@@
 
-sum(WardDat2$vallow)/sum(WardDat2$LowUse)
+setwd(DataFolder)
+list.files()
 
-Lest <- test %>% filter(X14 =="LEICESTERSHIRE")
+#Unnfordability at EW level salery 2014-2015
+mean(prices$X2)/31920
 
-Lest %>% filter(X2<15000000) %>% ggplot(., aes(x= X2)) + geom_density()
+#is mean income estimates
+IncomeEst <- read_excel("1smallareaincomeestimatesdataupdate.xls", sheet = 4, skip = 4) %>%
+  setNames(make.names(names(.)) %>% 
+             gsub("\\.(?=\\.*$)", "", ., perl=TRUE)) #removes trailing full stop.
 
-%>% group_by(X13) %>% summarise(mean = mean(X2))
+test2 <- prices %>% left_join(., select(EW2, ECODE, MSOA11CD), 
+                              by =c("lsoa11cd"="ECODE")) %>%
+  group_by(MSOA11CD) %>%
+  summarise(MeanPrice = mean(X2), counts = n()) %>%
+  left_join(., IncomeEst, by=c("MSOA11CD"= "MSOA.code")) %>%
+  mutate(Yearly.income= 52 * Total.weekly.income, ratio = MeanPrice/Yearly.income)
 
-Melt <- test %>% filter(X13 == "MELTON")
+test2 %>% ggplot(.,aes(x=ratio)) +geom_density()
 
-test %>% filter(grepl("chelsea", X13, ignore.case = TRUE)) %>%
-  filter(X2<3000000) %>% ggplot(., aes(x= X2)) + geom_density()
+sum(test2$ratio>6)/nrow(test2)  #about 50% EW
+test2 %>% filter(Region.name == "London") %>% mutate(HighRatio = ratio>10) %>%
+  summarise(total = sum(HighRatio)/n())
 
@@
 
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/Regions-Complete/Region London")
+setwd(file.path(RegionsComp, "Region London"))
 
-Lambeth <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>% setNames(make.names(names(.))) %>% 
-  mutate(type2 = ifelse(grepl("Empty", Exemption.type), "Empty", Exemption.type)) %>%
-  group_by(type2, LSOA_CODE) %>% 
+Lambeth <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%
+  setNames(make.names(names(.))) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% 
   summarise(Counts = n()) %>% 
-  spread(., type2, Counts, fill = 0) %>% 
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
-  group_by(Admin_ward_code) %>% mutate(Empty = sum(Empty), LowUse = Empty) %>% ungroup
+  spread(., Exemption.type, Counts, fill = 0) %>%
+    setNames(make.names(names(.))) %>%
+  mutate(LowUse = rowSums(.[,c(2:5, 24:25)]), Empty = LowUse - Empty.Class.A-Empty.Class.B) %>%
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
 
@@
 
+#Camden
+
+test <- read.xlsx("Camden Exemptions LSOA - 20891480.xlsx")[1:4]
+
+Camden <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
+  group_by(Discount.type, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>% 
+  spread(., Discount.type, Counts, fill = 0) %>% 
+  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse - B) %>%
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+
+CAMDAT <- AG %>% filter(LAD11NM == "Camden") %>% 
+  left_join(., select(Camden, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Bromley
+
+Bromley <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,1:4] %>%
+  setNames(make.names(names(.))) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>% 
+  spread(., Exemption.type, Counts, fill = 0) %>%
+    setNames(make.names(names(.))) %>%
+  mutate(LowUse = rowSums(.[,c(6:8,29:31)]), Empty=LowUse - Empty.Class.B) %>%
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+
+BRODAT <- AG %>% filter(LAD11NM == "Bromley") %>% 
+  left_join(., select(Bromley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Haringey
+
+Haringey <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)] %>%
+    setNames(make.names(names(.))) %>%
+  group_by(Exemption...Discount.type, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>%
+  spread(., key = Exemption...Discount.type, 
+         value = Counts, fill = 0) %>%
+    setNames(make.names(names(.))) %>%
+  mutate(LowUse = rowSums(.[,21:25]), Empty=LowUse - PCLB0) %>%
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+
+HARDAT <- AG %>% filter(LAD11NM == "Haringey") %>% 
+  left_join(., select(Haringey, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
 #Sutton
 
-Sutton <- read_excel("SuttonExemptionsLSOA.xlsx"  )[,1:6]
+Sutton <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,1:6] %>%
+    setNames(make.names(names(.))) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>%
+  spread(., key = Exemption.type, 
+         value = Counts, fill = 0) %>%
+    setNames(make.names(names(.)))%>%
+  mutate(LowUse = rowSums(.[,-1]), Empty=LowUse - PCLB0) %>%
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+
+SUTDAT <- AG %>% filter(LAD11NM == "Sutton") %>% 
+  left_join(., select(Sutton, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Richmond
+
+Richmond <- read_csv("Richmond_2.csv" )[1:4] %>% setNames(make.names(names(.))) %>%
+  rename(Exemption.type = Discount.type) %>%
+  mutate(Exemption.type = Exemption.type %>% trimws %>%
+           make.names %>% 
+           gsub("\\.{2,}" , ".", .)) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>%
+    mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+RICDAT <- AG %>% filter(LAD11NM == "Richmond upon Thames") %>% 
+  left_join(., select(Richmond, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Hillingdon
+
+Hillingdon <- read.xlsx("HillingdonDiscountsLSOA.XLSX" )[1:4] %>% mutate(Exemption.type = Exemption.type %>% trimws %>%
+           make.names %>% 
+           gsub("\\.{2,}" , ".", .)) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>%  
+  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse- Class.B.Second.Home) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+HILDAT <- AG %>% filter(LAD11NM == "Hillingdon") %>% 
+  left_join(., select(Hillingdon, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Bexley
+
+Bexley <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
+  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>% 
+  mutate(LowUse = rowSums(.[,c(2,19,20)]), Empty = LowUse) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+BEXDAT <- AG %>% filter(LAD11NM == "Bexley") %>% 
+  left_join(., select(Bexley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
 
@@
 rm(Chelwards)
+
+Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
+  mutate(LowUsePerc = LowUse/WardHomes)
+
+cor(Chel2$PrimePerc, Chel2$LowUsePerc)
+cor(Chel2$MeanPrice, Chel2$LowUsePerc)
+
+Chel2 %>%
+  mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>% 
+  ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() + 
+  geom_smooth(method ="lm", se = FALSE) +
+  labs(title = "Relationship between % of Prime Sales and % Low Use", 
+       x = "% of properties sold in 2016 over £1M by electoral ward",
+       y = "% of properties either empty or second homes") +
+  theme(plot.title = element_text(hjust = 0.5))  +
+  coord_cartesian(xlim = c(15,78), expand = TRUE)
 
@@
 AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
-                 SOUDAT, KINDAT, TOWDAT, GREDAT) %>% 
+                 SOUDAT, KINDAT, TOWDAT, GREDAT, CAMDAT, 
+                 BRODAT, HARDAT, RICDAT, HILDAT, BEXDAT,
+                 SUTDAT) %>% 
   mutate(LowUsePerc = LowUse/WardHomes, 
@@
 colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
-  labs(title = "All Boroughs Percentage Empty") +
-  theme(plot.title = element_text(hjust = 0.5))
+  labs(title = "9 Boroughs: Ward Level % Empty") +
+  theme(plot.title = element_text(hjust = 0.5))+
+  theme(axis.title=element_blank(),
+        axis.text=element_blank(),
+        axis.ticks=element_blank())
 
@@
   ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =sqrt(EmptyPerc)), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+
+AG2 %>% 
+  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =EmptyPercRank), 
 colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
@@
 #single borough
-GREDAT %>%
-  mutate(LowUsePerc = LowUse/WardHomes, 
+CHELDAT %>%
+  mutate(LowUsePerc = LowUse/WardHomes*100, 
          EmptyPerc = Empty/WardHomes,
          EmptyPercRank = percent_rank(Empty/WardHomes)) %>%
-ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = EmptyPerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
+  labs(title = "Kensington and Chealsea: Ward Level % Low Use") +
+  theme(plot.title = element_text(hjust = 0.5))+ 
+  scale_fill_continuous(name = "Percentage")
 
+#SIngle borough detail
+SUTDAT %>%
+  mutate(LowUsePerc = LowUse/Homes, 
+         EmptyPerc = Empty/Homes,
+         EmptyPercRank = percent_rank(Empty/Homes)) %>%
+ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
+  ggtitle("Kensington and Chelsea ward level % low use") + 
+  theme(plot.title = element_text(hjust = 0.5))
 ```
@@
 
-test <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1) %>% setNames(make.names(names(.))) %>% .[,1:4] %>% filter(Current.Discount.Type.Code !="SINGLE") %>% group_by(LSOA_CODE) %>%
-  summarise(Empty = n())
+Barrow <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1) %>% setNames(make.names(names(.))) %>% .[,1:4] %>% filter(Current.Discount.Type.Code !="SINGLE") %>% group_by(LSOA_CODE, Current.Discount.Type.Code) %>%
+  summarise(Empty = n()) %>% 
+  spread(key=Current.Discount.Type.Code, value = Empty, fill = 0 ) %>% ungroup %>%
+ mutate( LowUse = rowSums(.[-1]), Empty = LowUse-PCLB0)
 
-Barrow2 <- test %>% left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)
+Barrow2 <- Barrow %>% 
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
+  mutate(LowUsePerc = LowUse/Homes, EmptyPerc = Empty/Homes)
 
-test2 <- test %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd")) %>% mutate(EmptyPerc = Empty/Homes)
+Barrow3 <- Barrow %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd")) %>% 
+  mutate(LowUsePerc = LowUse/Homes, EmptyPerc = Empty/Homes)
 
-ggplot()+ geom_polygon(data=test2, aes(long, lat, group = group, fill = EmptyPerc), 
+ggplot()+ geom_polygon(data=Barrow2, aes(long, lat, group = group, fill = PCLB0), 
 colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")
@@
 ```{r}
-test <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
+SLakeland <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
   group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% mutate(Empty = rowSums(.[,2:9])) %>%
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+  mutate(Empty = rowSums(.[,2:9])) %>%
   left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)
 
-test2 <- test %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))
+SLakeland2 <- SLakeland %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))
+
+ggplot()+ geom_polygon(data=SLakeland2, aes(long, lat, group = group, fill = EmptyPerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")
+
+bind_rows(Barrow3,SLakeland2) %>%ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = EmptyPerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + 
+  ggtitle("Cumbria Empty Percentage")+
+  theme(axis.title=element_blank(),
+        axis.text=element_blank(),
+        axis.ticks=element_blank())
 
@@
 
-Cornwall %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
+Cornwall %>% mutate(LowUsePerc = LowUsePerc*100) %>% 
+  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
   ggplot(.)+ 
   geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall Empty and second Homes %")+
-  theme(plot.title = element_text(hjust = 0.5))
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall: Ward level Empty and Second Homes %")+
+  theme(plot.title = element_text(hjust = 0.5)) + 
+  scale_fill_continuous(name = "Percentage")
 
- Cornwall %>% filter(Admin_ward_code !="E05009195") %>% summarise(x =cor(MeanPrice, WardLowUsePerc, use = 'complete.obs'))
+CornCor <- Cornwall %>% 
+  #filter(Admin_ward_code !="E05009195") %>% 
+  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))
 
- Cornwall %>% ggplot(., aes(y=MeanPrice, x= WardLowUsePerc )) + geom_point() +
-   labs(title = "Relationshibetween LowUse Percentage and Mean Price in Ward")+
+ Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
+   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
+        x = "Low Use Percentage by Ward", 
+        y = "Mean Price") +
+  theme(plot.title = element_text(hjust = 0.5)) + 
+    annotate("text", 
+             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
+             x = 0.35 , y = 7.5e5, size = 5) +
+   geom_smooth(method = "lm", se = FALSE)
+
+ #"Cornwall: Relationship between LowUse\n Percentage and Mean Price in Ward"
+
+```
+
+#Suffolk
+
+```{r}
+
+setwd(file.path(RegionsComp, "Region East of England"))
+list.files()
+
+CoastWave <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
+  mutate(Exemption.type = Exemption.type %>% trimws %>%
+           make.names %>% 
+           gsub("\\.{2,}" , ".", .)) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>%
+    mutate(LowUse = rowSums(.[,c(5,6,13,14,16:18)]), Empty = LowUse -Second.Home.Class.A -Second.Home.Class.B) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+CoastWave %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
+  ggplot(.)+ 
+  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+
+#corellation
+CoastWave %>% 
+  #filter(Admin_ward_code !="E05009195") %>% 
+  summarise(x =cor(MeanPrice, WardLowUsePerc, use = 'complete.obs'))
+
+ CoastWave %>% ggplot(., aes(y=MeanPrice, x= WardLowUsePerc )) + geom_point() +
+   labs(title = "Coastal and Waveny: Relationship between LowUse\n Percentage and Mean Price in Ward")+
   theme(plot.title = element_text(hjust = 0.5))

### 2017-05-08 CreateExcelTemplates.Rmd
Extra Boroughs and changed templates

@@
 
+#These three blocks are all you need to to generate the templates... I think it needs to be checked when the packages have updated
+
 # Load Post code data
 
-This chunk checks the exiatane of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup.
+This chunk checks the existance of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup.
 Creating the lookup takes quite a lot of time so it is good to only have to do it once.
@@
       ExemptionsFile <- paste0(LAD,"ExemptionsLSOA.xlsx")
-      CTBandsFile <- paste0(LAD,"CTBandsLSOA.xlsx")
+      DiscountsFile <- paste0(LAD,"DiscountsLSOA.xlsx")
       setwd(basewd)
@@
       saveWorkbook(wb,ExemptionsFile ,overwrite = T)
-      saveWorkbook(wb,CTBandsFile ,overwrite = T)
+      writeData(wb, "Input", "Discount_Class") #So that it says Discounts not exemptions, so nobody gets confused.
+      saveWorkbook(wb,DiscountsFile ,overwrite = T)
     })

### 2017-05-08 EmptyHomesV1.Rmd
Extra Boroughs and changed templates

@@
 
-# Using the semi data
+# Using the full data
 
@@
   left_join(., select(Lambeth, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Islington
+
+Islington <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4] %>% setNames(make.names(names(.))) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>% 
+  spread(., Exemption.type, Counts, fill = 0) %>%
+    setNames(make.names(names(.))) %>%
+  mutate(LowUse = rowSums(.[,-c(1,12,13)]), Empty = LowUse ) %>%
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+
+ISL2 <- Islington %>% mutate(LowUsePerc = LowUse/Homes)
+
+ISLDAT <- AG %>% filter(LAD11NM == "Islington") %>% 
+  left_join(., select(Islington, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Greenwhich
+list.files()
+wardnames %>% filter(grepl("city", LAD11NM))
+
+Greenwich <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% 
+  summarise(Counts = n()) %>% ungroup %>%
+  mutate(Exemption.type = trimws(Exemption.type))  %>%
+  spread(., Exemption.type, Counts, fill = 0) %>%
+    setNames(make.names(names(.))) %>%
+  mutate(LowUse = rowSums(.[,c(2,3,4,21,22)]), Empty = LowUse -  EMPTY.CLASS.B) %>%
+   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+
+Greenwhich2 <- Greenwich %>% mutate(LowUsePerc = signif(LowUse/Homes*100,3))
+
+GREDAT <- AG %>% filter(grepl("Greenwich", LAD11NM)) %>% left_join(., select(Greenwich, Admin_ward_code, LowUse, Empty))
 
@@
 
+#RBKC
+
+Chelsea <- read.xlsx( "Kensington and ChelseaDiscountsLSOA.xlsx" , colNames = TRUE) %>%
+  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>% 
+  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
+  filter(WD16NM!= "Kensal Green")
+
+#Barking
+Bark <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colNames = FALSE) %>%
+  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>% 
+  mutate(LowUse = rowSums(.[,c(2,3,6,7)]), Empty = LowUse) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+BARKDAT <- AG %>% filter(LAD11NM == "Barking and Dagenham") %>% 
+  left_join(., select(Bark, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Barnet
+
+Barnet <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
+  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>% 
+  mutate(LowUse = rowSums(.[,c(2:8)]), Empty = LowUse) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
+  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+#Newham
+
+Newham <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE) %>%
+  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
+  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+  spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.)))) %>% 
+  mutate(LowUse = rowSums(.[,c(2)]), Empty = LowUse) %>%
+  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
+  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+
+BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
+  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+
+```
+
+#Semi data 
+```{r}
 #ward folder
@@
 #Chelsea
-Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM))
-
-Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
-  mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(X.Ward) %>%
-  mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related., Empty..50..premium., Moorings , na.rm = TRUE),
-         LowUse = Empty + Second.Homes) %>% ungroup
-
-Chelsea[is.na(Chelsea)] <-0
-rm(Chelwards)
-
-Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
-  mutate(LowUsePerc = LowUse/WardHomes)
-
-cor(Chel2$PrimePerc, Chel2$LowUsePerc)
-cor(Chel2$MeanPrice, Chel2$LowUsePerc)
-
-Chel2 %>%
-  mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>% 
-  ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() + 
-  geom_smooth(method ="lm", se = FALSE) +
-  labs(title = "Relationship between % of Prime Sales and % Low Use", 
-       x = "% of properties sold in 2016 over £1M by electoral ward",
-       y = "% of properties either empty or second homes") +
-  theme(plot.title = element_text(hjust = 0.5))  +
-  coord_cartesian(xlim = c(15,78), expand = TRUE)
-
-CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
-  filter(WD16NM!= "Kensal Green")
+# Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM)) 
+# 
+# Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
+#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(X.Ward) %>%
+#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related., Empty..50..premium., Moorings , na.rm = TRUE),
+#          LowUse = Empty + Second.Homes) %>% ungroup
+# 
+# Chelsea[is.na(Chelsea)] <-0
+# rm(Chelwards)
+# 
+# Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
+#   mutate(LowUsePerc = LowUse/WardHomes)
+# 
+# cor(Chel2$PrimePerc, Chel2$LowUsePerc)
+# cor(Chel2$MeanPrice, Chel2$LowUsePerc)
+# 
+# Chel2 %>%
+#   mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>% 
+#   ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() + 
+#   geom_smooth(method ="lm", se = FALSE) +
+#   labs(title = "Relationship between % of Prime Sales and % Low Use", 
+#        x = "% of properties sold in 2016 over £1M by electoral ward",
+#        y = "% of properties either empty or second homes") +
+#   theme(plot.title = element_text(hjust = 0.5))  +
+#   coord_cartesian(xlim = c(15,78), expand = TRUE)
+#  
+# 
+# 
+# CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
+#   filter(WD16NM!= "Kensal Green")
 
@@
 wardnames %>% filter(LAD11NM == "Merton")
-Merton <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X) %>%
-  filter(X != "Norbury", X!="Nightingale", X !="Stonecot") %>% 
+Merton <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
+  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
     bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
@@
 Kingston <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
-  arrange(X) %>% slice(1:16) %>%
+  arrange(X__1) %>% slice(1:16) %>%
   bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
@@
 
-#Greenwhich
-list.files()
-wardnames %>% filter(grepl("Greenwich", LAD11NM))
-
-Greenwich <- read_excel( "FOI-3348 ctfoi35report.xlsx" ) %>%  
-  setNames(make.names(names(.))) %>%
-  filter(grepl("EMPTY",Exempt.Discount.Description)) %>% 
-  select(-Exempt.Code) %>%
-  spread(key= Exempt.Discount.Description, value = Total, fill = 0) %>%
-  mutate(Empty = rowSums(.[,-1]), LowUse = Empty) %>%
-   bind_cols(., wardnames %>% filter(grepl("Greenwich", LAD11NM)))
-
-GREDAT <- AG %>% filter(grepl("Greenwich", LAD11NM)) %>% left_join(., select(Greenwich, Admin_ward_code, LowUse, Empty))
+#Havering Is census wards not electoral ones
+# test <- wardnames %>% filter(grepl("Havering", LAD11NM))
+# 
+# Havering <- read.xlsx("Havering1.xlsx")[,-2] %>% gather(key = "Ward", value = "counts",-X1) %>%
+#   mutate(X1 = make.names(X1)) %>%
+#   spread(key = "X1", value = "counts", fill = 0)
 
@@
                  BRODAT, HARDAT, RICDAT, HILDAT, BEXDAT,
-                 SUTDAT) %>% 
-  mutate(LowUsePerc = LowUse/WardHomes, 
-         EmptyPerc = Empty/WardHomes,
+                 SUTDAT, ISLDAT, BARKDAT, BARNDAT) %>% 
+  mutate(LowUsePerc = LowUse/WardHomes*100, 
+         EmptyPerc = Empty/WardHomes*100,
          EmptyPercRank = percent_rank(Empty/WardHomes))
@@
 
-#SIngle borough detail
-SUTDAT %>%
-  mutate(LowUsePerc = LowUse/Homes, 
-         EmptyPerc = Empty/Homes,
-         EmptyPercRank = percent_rank(Empty/Homes)) %>%
+ggplotly() #STFD!
+#Single borough detail
+
+AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
+  left_join(., select(Chelsea, LSOA_CODE, LowUse, Empty, Homes), by = c("lsoa11cd"="LSOA_CODE")) %>% 
+  ungroup %>%
+  filter(WD16NM!= "Kensal Green") %>%
+  mutate(LowUsePerc = LowUse/Homes.y*100, 
+         EmptyPerc = Empty/Homes.y*100,
+         EmptyPercRank = percent_rank(Empty/Homes.y)) %>%
 ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
 colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
-  ggtitle("Kensington and Chelsea ward level % low use") + 
-  theme(plot.title = element_text(hjust = 0.5))
+  theme(plot.title = element_text(hjust = 0.5))+
+    theme(axis.title=element_blank(),
+        axis.text=element_blank(),
+        axis.ticks=element_blank())+ 
+  scale_fill_continuous(name = "Percentage")+
+  ggtitle("Islington Exemptions")
+
+Bourough2 <- Chelsea %>% ungroup %>% mutate(LowUsePerc = LowUse/Homes, 
+         EmptyPerc = Empty/Homes,
+         EmptyPercRank = percent_rank(Empty/Homes))
+
 ```
@@
              label = paste0("Correlation =", signif(CornCor[1,1],2)), 
-             x = 0.35 , y = 7.5e5, size = 5) +
+             x = 0.35 , y = 2.5e5, size = 5) +
    geom_smooth(method = "lm", se = FALSE)

### 2017-05-25 EmptyHomesV1.Rmd
Added functions
I added a load of functions to clean up and standardise the code.

@@
 Barnet <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
-  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
+  setNames(c("ExemAG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
+  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
+  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
+  filter(WD16NM!= "Kensal Green")ption.type", "LSOA_CODE", "X3", "X4")) %>%
   group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
@@
 
-#Chelsea
+# Chelsea
 # Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM))
@@
 # Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
-#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(X.Ward) %>%
-#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related., Empty..50..premium., Moorings , na.rm = TRUE),
+#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(Ward) %>%
+#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related, Empty..50..premium, Moorings , na.rm = TRUE),
 #          LowUse = Empty + Second.Homes) %>% ungroup
@@
 colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
-  labs(title = "9 Boroughs: Ward Level % Empty") +
+  labs(title = "Current London Data") +
   theme(plot.title = element_text(hjust = 0.5))+
@@
         axis.ticks=element_blank())
+
+SaveFig("London.png")
 
@@
   ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =EmptyPercRank), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
+  labs(title = "Current London Data Coloured by Percent Rank") +
+  theme(plot.title = element_text(hjust = 0.5))+
+  theme(axis.title=element_blank(),
+        axis.text=element_blank(),
+        axis.ticks=element_blank())
+
+SaveFig("LondonPerc.png")
 
@@
 #single borough
-CHELDAT %>%
-  mutate(LowUsePerc = LowUse/WardHomes*100, 
-         EmptyPerc = Empty/WardHomes,
-         EmptyPercRank = percent_rank(Empty/WardHomes)) %>%
-ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
-  labs(title = "Kensington and Chealsea: Ward Level % Low Use") +
+
+SingleB <- AG %>% filter(grepl("Kensington", LAD11NM))%>% 
+  left_join(., select(Chelsea, Admin_ward_code, WardLowUse, WardLowUsePerc)) %>% 
+  filter(WD16NM!= "Kensal Green") %>%
+  mutate(WardLowUsePerc = WardLowUsePerc*100)
+
+ggplot(SingleB) + 
+  geom_polygon( aes(long, lat, group = group, fill = WardLowUsePerc), 
+colour = alpha("black", 1/4), size = 0.2) + 
+  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(SingleB$WardLowUsePerc, na.rm = TRUE)) +
+  labs(title = "Kensington and Chealsea: Ward Level % Low Use", fill = "Percentage") +
+  theme(plot.title = element_text(hjust = 0.5)) +
     theme(plot.title = element_text(hjust = 0.5))+
-  scale_fill_continuous(name = "Percentage")
+    theme(axis.title=element_blank(),
+        axis.text=element_blank(),
+        axis.ticks=element_blank())
+
+SaveFig("RBKCLowUse.png")
 
@@
 
-AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
+Singlevis <- AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
   left_join(., select(Chelsea, LSOA_CODE, LowUse, Empty, Homes), by = c("lsoa11cd"="LSOA_CODE")) %>% 
@@
   filter(WD16NM!= "Kensal Green") %>%
-  mutate(LowUsePerc = LowUse/Homes.y*100, 
-         EmptyPerc = Empty/Homes.y*100,
-         EmptyPercRank = percent_rank(Empty/Homes.y)) %>%
-ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
+  mutate(LowUsePerc = round(LowUse/Homes.y*100), 
+         EmptyPerc = round(Empty/Homes.y*100),
+         EmptyPercRank = percent_rank(Empty/Homes.y))
+
+ggplot(Singlevis, aes(long, lat, group = group, fill = LowUsePerc))+ 
+  geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
+  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(Singlevis$LowUsePerc))+
   theme(plot.title = element_text(hjust = 0.5))+
@@
         axis.ticks=element_blank())+ 
-  scale_fill_continuous(name = "Percentage")+
-  ggtitle("Islington Exemptions")
+  ggtitle("Kensington and Chelsea Low use")
 
@@
 
-Cornwall %>% mutate(LowUsePerc = LowUsePerc*100) %>% 
-  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
-  ggplot(.)+ 
-  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Cornwall: Ward level Empty and Second Homes %")+
-  theme(plot.title = element_text(hjust = 0.5)) + 
-  scale_fill_continuous(name = "Percentage")
+C2 <- Cornwall %>% 
+  mutate(LowUsePerc = LowUsePerc*100,
+         WardLowUsePerc = WardLowUsePerc*100) %>% 
+  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))
+
+ggplot(C2, aes(long, lat, group = group, fill = WardLowUsePerc))+ 
+  geom_polygon(colour = alpha("black", 1/4), size = 0.2) + 
+  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(C2$WardLowUsePerc, na.rm = TRUE))+
+    theme(plot.title = element_text(hjust = 0.5))+
+    theme(axis.title=element_blank(),
+        axis.text=element_blank(),
+        axis.ticks=element_blank())+ 
+  labs(title = "Low Use Homes in the County of Cornwall", 
+       fill="Percentage")     
+SaveFig("Cornwall.png")
 
@@
              x = 0.35 , y = 2.5e5, size = 5) +
-   geom_smooth(method = "lm", se = FALSE)
-
- #"Cornwall: Relationship between LowUse\n Percentage and Mean Price in Ward"
+   geom_smooth(method = "lm", se = FALSE)#+
+#   coord_cartesian(xlim=c(0,0.2), ylim= c(1e5, 3.5e+5))
+SaveFig("CornCor.png")
 
@@
 ```
+
+#Hull
+```{r}
+
+test <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
+                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
+  CleanData(.)
+
+PlotMap(test,"Hull", variable = "WardLowUsePerc")
+
+```

### 2017-05-25 Functions/PlotMap.R

@@ -1,0 +1,19 @@
+PlotMap <- function(df, name, variable = "LowUsePerc", title = "Map of Region"){
+  
+  value <- mean(eval(parse(text= paste0("df$", variable))), na.rm = TRUE)
+  
+  Singlevis <- AG %>% filter(grepl(name, LAD11NM)) %>% 
+    left_join(., select(df, LSOA_CODE, LowUsePerc, WardLowUsePerc, LowUse, Empty, Homes), 
+              by = c("lsoa11cd"="LSOA_CODE")) %>% 
+    ungroup 
+  
+  ggplot(Singlevis, aes_string("long", "lat", group = "group", fill = variable))+ 
+    geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
+    scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = value)+
+    theme(plot.title = element_text(hjust = 0.5))+
+    theme(axis.title=element_blank(),
+          axis.text=element_blank(),
+          axis.ticks=element_blank())+ 
+    ggtitle(title) 
+  
+}

### 2017-05-25 EmptyHomesV1.Rmd
Fixed error in functions
The cleaning function wasn't working properly

@@
 source("Setup.R")
-```
 
-#Load completed data
-
-```{r}
-
-setwd(file.path(RegionsComp, "Region East of England"))
-list.files()
-
-test <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")
-
-unique(test$Exemption.type)
-
-```
-
-```{r}
-# setwd(ShapeFiles)
-# 
-# wards.shp <- readShapeSpatial("London_Ward.shp")
-# coords <- coordinates(wards.shp)
-# WardsAdj <- poly2nb(wards.shp, queen= FALSE)
-# plot(wards.shp, border="grey")
-# plot(WardsAdj, coords, add=TRUE, col="red")
-# 
-# test <- (nb2mat(WardsAdj)>0)*1
-# 
-# 
-# g=graph.data.frame(WardsAdj)
-# get.adjacency(WardsAdj,sparse=FALSE)
-
+setwd(Functions)
+list.files() %>% map(source)
 ```
@@
 setwd(file.path(RegionsComp, "Region London"))
+
+Lam2 <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
+    StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))
 

### 2017-05-25 Functions/StructureData.R

@@ -1,77 +1,45 @@
 
-StructureData <- function(df, full = TRUE, lowuse = NULL, empty = NULL){
+StructureData <- function(df, lowuse = NULL, empty = NULL, full = TRUE ){
   #Provides a standardised way of cleaning the data
   #df: data frame of the laoded excel template with only the first 4 columns
   #full: do you want the whole process or partial. a partial process is required to dins out
     #which columns are used for empty and low use.
   #lowuse: the columns of the spread dataframe that contain the discounts used for low use homes
   #empty: Columns used to identityf empty homes. if NULL defaults to the lowuse ones
-  if(is.null(lowuse)){
-    lowuse <- 1
-  } else {
-    low
-    CleanData <- function(df, full = TRUE, lowuse = NULL, empty = NULL){
-      
-      if(is.null(lowuse)){
-        lowuse <- 1
-      } else {
-        lowuse <- paste0(1,lowuse)
-      }
-      
-      if(is.null(empty)){
-        empty <-  lowuse
-      } else {
-        lowuse <- paste0(1,empty)
-      }
-      
-      df<- df %>%
-        setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
-        group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-        spread(key= Exemption.type, value = counts, fill = 0) %>% 
-        setNames(make.names(trimws(names(.))))
-      
-      if(full){
-        df<- df%>%
-          mutate(LowUse = rowSums(.[,-lowuse]), Empty = rowSums(.[,-empty])) %>%
-          left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
-          group_by(Admin_ward_code)  %>%
-          mutate(LowUsePerc = round(LowUse/Homes *100), 
-                 WardLowUse = sum(LowUse) ,
-                 WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
-          ungroup %>% 
-          left_join(., MeanWardPrice) %>% 
-          mutate(ValLow = LowUse*MeanPrice) 
-      }
-      return(df)
+
+    if(is.null(lowuse)){
+      lowuse <- -1
+    } else {
+      lowuse <- paste0(lowuse)
     }
[…]

### 2017-05-25 SubCode/Setup.R

@@ -27,6 +27,7 @@ AddGeog <- file.path(basewd, "AdditionalGeographies")
 Regions <- file.path(basewd, "Regions")
 RegionsComp <- file.path(basewd, "Regions-Complete")
 CommonCode <- file.path(basewd, "EmptyHomesCode", "SubCode")
+Functions <- file.path(basewd, "EmptyHomesCode", "Functions")
 SemiLondon <- file.path(basewd, "semi-data-london")
 Figures <- file.path(basewd, "Figures")
 select <-dplyr::select

### 2017-05-25 EmptyHomesV1.Rmd
Remove DAT
Changed the way maps are plotted so the DAT dataframe is no longer needed. It also allows for all data on a region to be plotted even when that data is missing

@@
 
-Lam2 <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
+Lambethinfo <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
     StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))
 
-Lambeth <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%
-  setNames(make.names(names(.))) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>% 
-  spread(., Exemption.type, Counts, fill = 0) %>%
-    setNames(make.names(names(.))) %>%
-  mutate(LowUse = rowSums(.[,c(2:5, 24:25)]), Empty = LowUse - Empty.Class.A-Empty.Class.B) %>%
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+#Islington is exemptions only
 
-LAMDAT <- AG %>% filter(LAD11NM == "Lambeth") %>% 
-  left_join(., select(Lambeth, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
-
-#Islington
-
-Islington <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4] %>% setNames(make.names(names(.))) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>% 
-  spread(., Exemption.type, Counts, fill = 0) %>%
-    setNames(make.names(names(.))) %>%
-  mutate(LowUse = rowSums(.[,-c(1,12,13)]), Empty = LowUse ) %>%
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
-
-ISL2 <- Islington %>% mutate(LowUsePerc = LowUse/Homes)
-
-ISLDAT <- AG %>% filter(LAD11NM == "Islington") %>% 
-  left_join(., select(Islington, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Islingtoninfo <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4]%>%  
+    StructureData(., lowuse = c(2:11,14:18))
 
 #Greenwhich
-list.files()
-wardnames %>% filter(grepl("city", LAD11NM))
 
-Greenwich <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>% ungroup %>%
-  mutate(Exemption.type = trimws(Exemption.type))  %>%
-  spread(., Exemption.type, Counts, fill = 0) %>%
-    setNames(make.names(names(.))) %>%
-  mutate(LowUse = rowSums(.[,c(2,3,4,21,22)]), Empty = LowUse -  EMPTY.CLASS.B) %>%
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
-
-Greenwhich2 <- Greenwich %>% mutate(LowUsePerc = signif(LowUse/Homes*100,3))
-
-GREDAT <- AG %>% filter(grepl("Greenwich", LAD11NM)) %>% left_join(., select(Greenwich, Admin_ward_code, LowUse, Empty))
+Greenwichinfo <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>%  
+    StructureData(., c(2,3,4,21,22), c(3,4,21,22))
 
@@
 
-test <- read.xlsx("Camden Exemptions LSOA - 20891480.xlsx")[1:4]
-
-Camden <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
-  group_by(Discount.type, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>% 
-  spread(., Discount.type, Counts, fill = 0) %>% 
-  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse - B) %>%
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
-
-CAMDAT <- AG %>% filter(LAD11NM == "Camden") %>% 
-  left_join(., select(Camden, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Camdeninfo <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
+ StructureData()
 
@@
 
-Bromley <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,1:4] %>%
-  setNames(make.names(names(.))) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>% 
-  spread(., Exemption.type, Counts, fill = 0) %>%
-    setNames(make.names(names(.))) %>%
-  mutate(LowUse = rowSums(.[,c(6:8,29:31)]), Empty=LowUse - Empty.Class.B) %>%
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
-
-BRODAT <- AG %>% filter(LAD11NM == "Bromley") %>% 
-  left_join(., select(Bromley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Bromleyinfo <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
+  StructureData(c(6:8,29:31))
 
@@
 
-Haringey <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)] %>%
-    setNames(make.names(names(.))) %>%
-  group_by(Exemption...Discount.type, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>%
-  spread(., key = Exemption...Discount.type, 
-         value = Counts, fill = 0) %>%
-    setNames(make.names(names(.))) %>%
-  mutate(LowUse = rowSums(.[,21:25]), Empty=LowUse - PCLB0) %>%
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
+#Haringey is funney and has to be worked over a bit first
+Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)]
 
-HARDAT <- AG %>% filter(LAD11NM == "Haringey") %>% 
-  left_join(., select(Haringey, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Haringeyinfo <- data_frame(Discount = rep(Haringey$`Exemption./.Discount.type`, Haringey$Count.of.Exemptions.by.Post.Code),
+           LSOA = rep(Haringey$LSOA_CODE, Haringey$Count.of.Exemptions.by.Post.Code)) %>%
+  mutate( a= NA, b = NA) %>%
+  StructureData(21:25)
 
@@
 
-Sutton <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,1:6] %>%
-    setNames(make.names(names(.))) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% 
-  summarise(Counts = n()) %>%
-  spread(., key = Exemption.type, 
-         value = Counts, fill = 0) %>%
-    setNames(make.names(names(.)))%>%
-  mutate(LowUse = rowSums(.[,-1]), Empty=LowUse - PCLB0) %>%
-   left_join(., EW2, by = c("LSOA_CODE" = "ECODE"))
-
-SUTDAT <- AG %>% filter(LAD11NM == "Sutton") %>% 
-  left_join(., select(Sutton, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Suttoninfo <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,c(1,4:6)] %>%
+  StructureData()
 
 #Richmond
-
-Richmond <- read_csv("Richmond_2.csv" )[1:4] %>% setNames(make.names(names(.))) %>%
-  rename(Exemption.type = Discount.type) %>%
-  mutate(Exemption.type = Exemption.type %>% trimws %>%
-           make.names %>% 
-           gsub("\\.{2,}" , ".", .)) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>%
-    mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-RICDAT <- AG %>% filter(LAD11NM == "Richmond upon Thames") %>% 
-  left_join(., select(Richmond, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Richmondinfo <- read_csv("Richmond_2.csv" )[1:4]%>%
+  StructureData()
 
@@
 
-Hillingdon <- read.xlsx("HillingdonDiscountsLSOA.XLSX" )[1:4] %>% mutate(Exemption.type = Exemption.type %>% trimws %>%
-           make.names %>% 
-           gsub("\\.{2,}" , ".", .)) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>%  
-  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse- Class.B.Second.Home) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-HILDAT <- AG %>% filter(LAD11NM == "Hillingdon") %>% 
-  left_join(., select(Hillingdon, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Hillingdoninfo <- read.xlsx("HillingdonDiscountsLSOA.XLSX" )[1:4]%>% 
+  StructureData()
 
@@
 Bexley <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
-  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>% 
-  mutate(LowUse = rowSums(.[,c(2,19,20)]), Empty = LowUse) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-BEXDAT <- AG %>% filter(LAD11NM == "Bexley") %>% 
-  left_join(., select(Bexley, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+StructureData
 
@@
 
-Chelsea <- read.xlsx( "Kensington and ChelseaDiscountsLSOA.xlsx" , colNames = TRUE) %>%
-  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>% 
-  mutate(LowUse = rowSums(.[,-1]), Empty = LowUse) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
-  filter(WD16NM!= "Kensal Green")
+Chelseainfo <- read_excel( "Kensington and ChelseaDiscountsLSOA.xlsx" )[,1:4] %>%
+  StructureData()
 
 #Barking
-Bark <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colNames = FALSE) %>%
-  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>% 
-  mutate(LowUse = rowSums(.[,c(2,3,6,7)]), Empty = LowUse) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-BARKDAT <- AG %>% filter(LAD11NM == "Barking and Dagenham") %>% 
-  left_join(., select(Bark, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Barkinginfo <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colNames = FALSE)[,1:4] %>%
+  StructureData(c(2,3,6,7))
 
@@
 
-Barnet <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
-  setNames(c("ExemAG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
-  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
-  filter(WD16NM!= "Kensal Green")AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
-  filter(WD16NM!= "Kensal Green")ption.type", "LSOA_CODE", "X3", "X4")) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>% 
-  mutate(LowUse = rowSums(.[,c(2:8)]), Empty = LowUse) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
-  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+Barnetinfo <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
+  StructureData(2:8)
 
@@
 
-Newham <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE) %>%
-  setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>% 
-  mutate(LowUse = rowSums(.[,c(2)]), Empty = LowUse) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
+Newhaminfo <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE)[,1:4] %>%
+  StructureData(2)
 
-BARNDAT <- AG %>% filter(LAD11NM == "Barnet") %>% 
-  left_join(., select(Barnet, LSOA_CODE, LowUse, Empty), by = c("lsoa11cd" = "LSOA_CODE"))
+test <- ls(pattern = "info") %>% map_df(~eval(parse(text=.x)))
 
@@
 test <- EW2 %>% filter(LAD11NM == "Wandsworth")
-
-# Chelsea
-# Chelwards <- wardnames %>% filter(grepl("Kensington", LAD11NM))
-# 
-# Chelsea <- read_excel("FOI2017-0143.xlsx" ) %>% setNames(make.names(names(.))) %>% slice(1:18) %>%
-#   mutate(Admin_ward_code = Chelwards$Admin_ward_code[c(1:10,12:17,19,18)]) %>% group_by(Ward) %>%
-#   mutate(Empty = sum(Empty..unfurnished, Empty..works, Job.related, Empty..50..premium, Moorings , na.rm = TRUE),
-#          LowUse = Empty + Second.Homes) %>% ungroup
-# 
-# Chelsea[is.na(Chelsea)] <-0
-# rm(Chelwards)
-# 
-# Chel2 <- Chelsea %>% left_join(., MeanWardPrice) %>% left_join(., EW2) %>%
-#   mutate(LowUsePerc = LowUse/WardHomes)
-# 
-# cor(Chel2$PrimePerc, Chel2$LowUsePerc)
-# cor(Chel2$MeanPrice, Chel2$LowUsePerc)
-# 
-# Chel2 %>%
-#   mutate(PrimePerc = PrimePerc*100, LowUsePerc = LowUsePerc*100) %>%
-#   ggplot(.,aes(x= PrimePerc, LowUsePerc)) +geom_point() +
-#   geom_smooth(method ="lm", se = FALSE) +
-#   labs(title = "Relationship between % of Prime Sales and % Low Use",
-#        x = "% of properties sold in 2016 over £1M by electoral ward",
-#        y = "% of properties either empty or second homes") +
-#   theme(plot.title = element_text(hjust = 0.5))  +
-#   coord_cartesian(xlim = c(15,78), expand = TRUE)
-# 
-# 
-# 
-# CHELDAT <-  AG %>% filter(grepl("Kensington", LAD11NM))%>% left_join(., select(Chelsea, Admin_ward_code, LowUse, Empty)) %>% 
-#   filter(WD16NM!= "Kensal Green")
 
@@
 
-SingleB <- AG %>% filter(grepl("Kensington", LAD11NM))%>% 
-  left_join(., select(Chelsea, Admin_ward_code, WardLowUse, WardLowUsePerc)) %>% 
-  filter(WD16NM!= "Kensal Green") %>%
-  mutate(WardLowUsePerc = WardLowUsePerc*100)
-
-ggplot(SingleB) + 
-  geom_polygon( aes(long, lat, group = group, fill = WardLowUsePerc), 
-colour = alpha("black", 1/4), size = 0.2) + 
-  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(SingleB$WardLowUsePerc, na.rm = TRUE)) +
-  labs(title = "Kensington and Chealsea: Ward Level % Low Use", fill = "Percentage") +
-  theme(plot.title = element_text(hjust = 0.5)) +
-    theme(plot.title = element_text(hjust = 0.5))+
-    theme(axis.title=element_blank(),
-        axis.text=element_blank(),
-        axis.ticks=element_blank())
+PlotMap(Chelsea, "Chelsea")
 
@@
 ggplotly() #STFD!
-#Single borough detail
-
-Singlevis <- AG %>% filter(grepl("Kensington", LAD11NM)) %>% 
-  left_join(., select(Chelsea, LSOA_CODE, LowUse, Empty, Homes), by = c("lsoa11cd"="LSOA_CODE")) %>% 
-  ungroup %>%
-  filter(WD16NM!= "Kensal Green") %>%
-  mutate(LowUsePerc = round(LowUse/Homes.y*100), 
-         EmptyPerc = round(Empty/Homes.y*100),
-         EmptyPercRank = percent_rank(Empty/Homes.y))
-
-ggplot(Singlevis, aes(long, lat, group = group, fill = LowUsePerc))+ 
-  geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
-  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(Singlevis$LowUsePerc))+
-  theme(plot.title = element_text(hjust = 0.5))+
-    theme(axis.title=element_blank(),
-        axis.text=element_blank(),
-        axis.ticks=element_blank())+ 
-  ggtitle("Kensington and Chelsea Low use")
-
-Bourough2 <- Chelsea %>% ungroup %>% mutate(LowUsePerc = LowUse/Homes, 
-         EmptyPerc = Empty/Homes,
-         EmptyPercRank = percent_rank(Empty/Homes))
 
@@
 
-PlotMap(test,"Hull", variable = "WardLowUsePerc")
+PlotMap(test, AG, variable = "WardLowUsePerc")
 

### 2017-05-25 EmptyHomesV1.Rmd
Includion of Southwark
Southwarks new data was included,. I attempted to include croydon but realsied I only have exemptions fromthem I will have to ask for discounts tomorrow. Hopefully it will be quicker than before.

@@
 
-test <- ls(pattern = "info") %>% map_df(~eval(parse(text=.x)))
+#City of London
 
+CoLinfo <- read_excel("City of LondonExemptionsLSOAApril2017.xlsx" )[,1:4] %>%
+  StructureData(c(2,3,4,13))
+
+#Southwark
+
+Southwarkinfo <- read_excel("Southwark discounts.xlsx")[1:4] %>%
+  StructureData(empty = -c(1,2,5))
+
+#Croydon
+CroydonInfo
+
+#All London With missing Boroughs
+PlotMap(Southwarkinfo, AG)
+
+ ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
+  PlotMap(., filter(AG, RGN15NM=="London"), filtermap = FALSE)
+
+list.files()
 ```

### 2017-05-28 Functions/PlotMap.R
Catagory plotting
Added in code that creates a catagorical variable for the percentage low-use. Inlcuded an if statment in the plotting code to do auto detection of factor variables and plots accordingly

@@ -1,24 +1,43 @@
 PlotMap <- function(df, ShapeData, variable = "LowUsePerc", title = "Map of Region", filtermap = TRUE){
   
   
-  #ONLY SET FITLER MAP TO FALSE WHEN the shape FILES HAVE BEEN PRE FILTERED OTHERWISE PUNISHMENT AND REGRET
-  value <- mean(eval(parse(text= paste0("df$", variable))), na.rm = TRUE)
-  
   Singlevis <- ShapeData %>% 
-    left_join(., select(df, LSOA_CODE, LowUsePerc, WardLowUsePerc, LowUse, Empty, Homes),
+    left_join(., df, #select(df, LSOA_CODE, LowUsePerc, WardLowUsePerc, LowUse, Empty, Homes),
               by = c("lsoa11cd"="LSOA_CODE")) %>% 
         ungroup
   
   if(filtermap){
   Singlevis <- Singlevis %>% filter(!is.na(LowUsePerc))
   }
-  ggplot(Singlevis, aes_string("long", "lat", group = "group", fill = variable))+ 
-    geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
-    scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = value)+
-    theme(plot.title = element_text(hjust = 0.5))+
-    theme(axis.title=element_blank(),
-          axis.text=element_blank(),
-          axis.ticks=element_blank())+ 
-    ggtitle(title) 
+  
+  
+  if(df %>% select_(variable) %>% unlist %>% class == "factor"){
+    
+    Outplot <- Singlevis %>%
+      ggplot(., aes_string("long", "lat", group = "group", fill = variable))+ 
+      geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
+      scale_fill_manual(values = c("blue", "white", "orange","red"), na.value="grey50")+
+      theme(plot.title = element_text(hjust = 0.5))+
+      theme(axis.title=element_blank(),
+            axis.text=element_blank(),
+            axis.ticks=element_blank())+ 
+      ggtitle(title)   
+    
+  } else {
+    #ONLY SET FITLER MAP TO FALSE WHEN the shape FILES HAVE BEEN PRE FILTERED OTHERWISE PUNISHMENT AND REGRET
+    value <- mean(eval(parse(text= paste0("df$", variable))), na.rm = TRUE)
+    
[…]

### 2017-05-28 Functions/StructureData.R

@@ -36,10 +36,13 @@ StructureData <- function(df, lowuse = NULL, empty = NULL, full = TRUE ){
                WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
         ungroup %>% 
         left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
-        mutate(ValLow = LowUse*MeanPrice) 
+        mutate(ValLow = LowUse*MeanPrice,
+               LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
+                                 labels =  c("0-10","11-20","21-30", "30+")),
+               WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
+                                     labels = c("0-10","11-20","21-30", "30+")) ) 
     }
     return(df)
   }
   
   
-

### 2017-05-28 EmptyHomesV1.Rmd
Catagory plotting
Added in code that creates a catagorical variable for the percentage low-use. Inlcuded an if statment in the plotting code to do auto detection of factor variables and plots accordingly
General Cleaning of Code
I created a new function that cleaned the Ward level data to make it more easily comparable to the proper data

@@
 
+test <- Lambethinfo %>% select(LowUsePerc, WardLowUsePerc, LowuseClass, WardLowuseClass)
+
 #Islington is exemptions only
@@
 
-Bexley <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
+Bexleyinfo <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
 StructureData
@@
 #All London With missing Boroughs
-PlotMap(Southwarkinfo, AG)
+PlotMap(Lambethinfo, AG)
 
@@
   PlotMap(., filter(AG, RGN15NM=="London"), filtermap = FALSE)
+SaveFig("LondonCont.png")
 
-list.files()
+ ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
+  PlotMap(., filter(AG, RGN15NM=="London"), variable = "LowuseClass", filtermap = FALSE)
+SaveFig("LondonDisc.png")
+
 ```
@@
 #Semi data
+
+The LSOA will be assigned empty and low use homes by percentage
+
 ```{r}
@@
 #Hammersmith 
-Hammersmith <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
+Hammersmithinfo <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
   bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
-  mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`)
-
-Hammersmith2 <- EW2 %>% filter(LAD11NM == "Hammersmith and Fulham") %>% left_join(., select(Hammersmith, Admin_ward_code, LowUse, Empty))
-
-HAMDAT <- AG %>% filter(LAD11NM == "Hammersmith and Fulham")%>% left_join(., select(Hammersmith, Admin_ward_code, LowUse, Empty))
+  mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`) %>%
+  SemiDataStructure
 
@@
 
-wardnames %>% filter(LAD11NM == "Wandsworth")
-
-Wandsworth <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
+Wandsworthinfo <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
   group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
@@
               select(Admin_ward_code)) %>%
-  mutate(LowUse = Empty)
-
-Wandsworth2 <- EW2 %>% filter(LAD11NM == "Wandsworth") %>% left_join(., select(Wandsworth, Admin_ward_code, Empty))
-WANDAT <- AG %>% filter(LAD11NM == "Wandsworth")%>% left_join(., select(Wandsworth, Admin_ward_code, LowUse, Empty))
+  mutate(LowUse = Empty) %>%
+  SemiDataStructure
 
 #Merton
-wardnames %>% filter(LAD11NM == "Merton")
-Merton <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
+
+Mertoninfo <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
   filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
@@
               select(Admin_ward_code)) %>%
-  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home )
-
-MERDAT <- AG %>% filter(LAD11NM == "Merton")%>% left_join(., select(Merton, Admin_ward_code, LowUse, Empty))
-
-#Southwark
-
-test <- wardnames %>% filter(LAD11NM == "Southwark")
-
-Southwark <- read_excel("southwark.xlsx" , skip = 1) %>% setNames(make.names(names(.))) %>% 
-  filter(Ward.codes != "TOTALS") %>% select(-Ward.codes) %>%
-  mutate(WARDS= na.locf(WARDS)) %>% group_by(WARDS) %>%
-  summarise_all(sum, na.rm = TRUE) %>% ungroup %>%
-  arrange(WARDS) %>%
-    bind_cols(., wardnames %>% filter(LAD11NM == "Southwark") %>% 
-              select(Admin_ward_code)) %>%
-  mutate(Empty =   Unoccupied.and.furnished.lets....0.
-+ Job.related.dwelling...50..discount + Second.Home...unoccupied.and.furnished...0.+Empty.and.unfurnished...0.
-+ Levy.on.long.term.empty...50..Premium + Uninhabitable.Works.required....0., LowUse =  Empty )
-
-Wandsworth2 <- EW2 %>% filter(LAD11NM == "Southwark") %>% left_join(., select(Southwark, Admin_ward_code, Empty))
-
-SOUDAT <- AG %>% filter(LAD11NM == "Southwark")%>% left_join(., select(Southwark, Admin_ward_code, LowUse, Empty))
+  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
+  SemiDataStructure
 
@@
 #Kingston
-test <- wardnames %>% filter(grepl("Kingston upon Thames", LAD11NM))
 
-Kingston <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
+Kingstoninfo <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
   arrange(X__1) %>% slice(1:16) %>%
@@
               select(Admin_ward_code)) %>%
-  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..)
-
-KINDAT <- AG %>% filter(LAD11NM == "Kingston upon Thames")%>% left_join(., select(Kingston, Admin_ward_code, LowUse, Empty))
+  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
+  SemiDataStructure
 
 #TowerHamlets
-test <- wardnames %>% filter(grepl("Tower", LAD11NM))
-
-Tower <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
+Towerinfo <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
   filter(!is.na(DiscClass)) %>%
@@
   slice(c(1:13, 15:17, 14, 18:20)) %>%
-   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM)))
-
-TOWDAT <- AG %>% filter(grepl("Tower", LAD11NM)) %>% left_join(., select(Tower, Admin_ward_code, LowUse, Empty))
+   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
+  SemiDataStructure
 
@@
 ```{r}
-AG2 <- bind_rows(CHELDAT,HAMDAT, WANDAT, LAMDAT, MERDAT, 
-                 SOUDAT, KINDAT, TOWDAT, GREDAT, CAMDAT, 
-                 BRODAT, HARDAT, RICDAT, HILDAT, BEXDAT,
-                 SUTDAT, ISLDAT, BARKDAT, BARNDAT) %>% 
-  mutate(LowUsePerc = LowUse/WardHomes*100, 
-         EmptyPerc = Empty/WardHomes*100,
-         EmptyPercRank = percent_rank(Empty/WardHomes))
 
-ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = EmptyPerc), 
-colour = alpha("darkred", 1/2), size = 0.1) + scale_colour_gradient2() +
-  labs(title = "Current London Data") +
-  theme(plot.title = element_text(hjust = 0.5))+
-  theme(axis.title=element_blank(),
-        axis.text=element_blank(),
-        axis.ticks=element_blank())
+ ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
+  PlotMap(., filter(AG, RGN15NM=="London"), 
+          filtermap = FALSE,
+          title = "Map of London with all current data")
+SaveFig("LondonCont.png")
 
-SaveFig("London.png")
-
-AG2 %>% 
-  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =sqrt(EmptyPerc)), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
-
-AG2 %>% 
-  ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill =EmptyPercRank), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() +
-  labs(title = "Current London Data Coloured by Percent Rank") +
-  theme(plot.title = element_text(hjust = 0.5))+
-  theme(axis.title=element_blank(),
-        axis.text=element_blank(),
-        axis.ticks=element_blank())
-
-SaveFig("LondonPerc.png")
-
-ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group, fill = LowUse/WardHomes), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
+ ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
+  PlotMap(., filter(AG, RGN15NM=="London"), variable = "LowuseClass", 
+          filtermap = FALSE, 
+          title = "Map of London by low-use class")
+SaveFig("LondonDisc.png")
 
@@
 
-PlotMap(Chelsea, "Chelsea")
-
+PlotMap(Chelseainfo, AG, title = "Low-use homes in Kensington and Chelsea")
 SaveFig("RBKCLowUse.png")
 
+PlotMap(CoLinfo, AG, title = "Low-use homes in the city of London")
+SaveFig("CoLLowUse.png")
+
+PlotMap(Lambethinfo, AG, title = "Low-use homes in Lambeth")
+SaveFig("LamLowUse.png")
+
 ggplotly() #STFD!
+
+ChelseaCor <- Chelseainfo %>% 
+  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))
+
+ Chelseainfo %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
+   labs(title = "Median Price vs Low Use % by ward in RBKC",
+        x = "Low Use Percentage by Ward", 
+        y = "Median Price") +
+  theme(plot.title = element_text(hjust = 0.5)) + 
+    annotate("text", 
+             label = paste0("Correlation = ", 
+             signif(ChelseaCor[1,1],2)), 
+             x = 5 , y = 3.5e5, size = 5) +
+   geom_smooth(method = "lm", se = FALSE)
+SaveFig("ChelseaCor.png")
 
@@
 
-list.files()
+Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
+  StructureData(lowuse = c(2,23:28))
 
-Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-  mutate(LowUse = rowSums(.[,c(FALSE,!grepl("exempt",(names(.)[-1])))])) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup
+PlotMap(Cornwall, AG, title = "Lowuse in Cornwall")
+SaveFig("Cornwall.png")
 
-Cornwall <- Cornwall %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-C2 <- Cornwall %>% 
-  mutate(LowUsePerc = LowUsePerc*100,
-         WardLowUsePerc = WardLowUsePerc*100) %>% 
-  left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))
-
-ggplot(C2, aes(long, lat, group = group, fill = WardLowUsePerc))+ 
-  geom_polygon(colour = alpha("black", 1/4), size = 0.2) + 
-  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = mean(C2$WardLowUsePerc, na.rm = TRUE))+
-    theme(plot.title = element_text(hjust = 0.5))+
-    theme(axis.title=element_blank(),
-        axis.text=element_blank(),
-        axis.ticks=element_blank())+ 
-  labs(title = "Low Use Homes in the County of Cornwall", 
-       fill="Percentage")     
-SaveFig("Cornwall.png")
+read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
+  StructureData(lowuse = c(2,7:16, 21:28) ) %>%
+  PlotMap(., AG,title = "all empties")
 
@@
     annotate("text", 
-             label = paste0("Correlation =", signif(CornCor[1,1],2)), 
-             x = 0.35 , y = 2.5e5, size = 5) +
-   geom_smooth(method = "lm", se = FALSE)#+
-#   coord_cartesian(xlim=c(0,0.2), ylim= c(1e5, 3.5e+5))
+             label = paste0("Correlation = ", signif(CornCor[1,1],2)), 
+             x = 5 , y = 3.5e5, size = 5) +
+   geom_smooth(method = "lm", se = FALSE)
 SaveFig("CornCor.png")
@@
                 "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
-  CleanData(.)
+  StructureData(.)
 

### 2017-05-28 Functions/PlotMap.R

@@ -16,7 +16,7 @@ PlotMap <- function(df, ShapeData, variable = "LowUsePerc", title = "Map of Regi
     Outplot <- Singlevis %>%
       ggplot(., aes_string("long", "lat", group = "group", fill = variable))+ 
       geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
-      scale_fill_manual(values = c("blue", "white", "orange","red"), na.value="grey50")+
+      scale_fill_manual(values = c("blue", "white", "salmon","red"), na.value="grey50")+
       theme(plot.title = element_text(hjust = 0.5))+
       theme(axis.title=element_blank(),
             axis.text=element_blank(),
@@ -27,10 +27,15 @@ PlotMap <- function(df, ShapeData, variable = "LowUsePerc", title = "Map of Regi
     #ONLY SET FITLER MAP TO FALSE WHEN the shape FILES HAVE BEEN PRE FILTERED OTHERWISE PUNISHMENT AND REGRET
     value <- mean(eval(parse(text= paste0("df$", variable))), na.rm = TRUE)
     
-        Outplot <- ggplot(Singlevis, aes_string("long", "lat", group = "group", fill = variable))+ 
+        Outplot <- ggplot(Singlevis, aes_string("long", "lat", group = "group", fill = variable)) + 
       geom_polygon(colour = alpha("black", 1/2), size = 0.2) + 
-      scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = value)+
-      theme(plot.title = element_text(hjust = 0.5))+
+      #scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = value) +
+      scale_fill_gradientn(
+        limits = c(0,40),
+        colours = c("blue", "white", "red"), 
+        values = c(0,.2,.4,1)
+        ) +
+          theme(plot.title = element_text(hjust = 0.5)) +
       theme(axis.title=element_blank(),
             axis.text=element_blank(),
             axis.ticks=element_blank())+ 

### 2017-05-28 Functions/SemiDataStructure.R

@@ -1,0 +1,21 @@
+SemiDataStructure <- function(df){
+  #does the standardised part of the semi data, useful after the initial cleaning.
+  #Is really smilar to the proper cleaning funct but adjusted for the wards only boroughs
+  #Should be phased out when better data comes in.
+  df <- df %>%
+    select(Admin_ward_code, LowUse, Empty) %>% 
+    left_join(., EW2, by = "Admin_ward_code") %>%
+    group_by(Admin_ward_code)  %>%
+    mutate(
+      WardLowUsePerc = round(LowUse/sum(Homes)*100),
+      LowUsePerc = WardLowUsePerc, 
+      WardLowUse = LowUse) %>% 
+    ungroup %>% 
+    left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
+    mutate(ValLow = LowUse*MeanPrice,
+           LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
+                             labels =  c("0-10","11-20","21-30", "30+")),
+           WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
+                                 labels = c("0-10","11-20","21-30", "30+")) ) %>%
+    rename(LSOA_CODE = ECODE)
+}

### 2017-05-29 EmptyHomesV1.Rmd
Corplotter
Added in the function that plots corellations of two variables. It is useful for reducing the code spaghetti that was forming as these plots are useful for inspecting relationships.

@@
 
-#Haringey is funney and has to be worked over a bit first
+#Haringey is funny and has to be worked over a bit first
 Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)]
@@
 
+PlotMap(Lambethinfo, AG, title = "Low-use homes in Kensington and Chelsea")
+
+Chelseainfo %>% mutate(Value = ValLow/1e6) %>%
+  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")
+
 PlotMap(Chelseainfo, AG, title = "Low-use homes in Kensington and Chelsea")
@@
 
-ChelseaCor <- Chelseainfo %>% 
-  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))
-
- Chelseainfo %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
-   labs(title = "Median Price vs Low Use % by ward in RBKC",
-        x = "Low Use Percentage by Ward", 
-        y = "Median Price") +
-  theme(plot.title = element_text(hjust = 0.5)) + 
-    annotate("text", 
-             label = paste0("Correlation = ", 
-             signif(ChelseaCor[1,1],2)), 
-             x = 5 , y = 3.5e5, size = 5) +
-   geom_smooth(method = "lm", se = FALSE)
+corplotter(Chelseainfo, "MedianPrice", "WardLowUsePerc", "Median Price vs Low Use % by ward in RBKC",
+           "Low Use Percentage by Ward",
+           "Median Price")
 SaveFig("ChelseaCor.png")
@@
 
-CornCor <- Cornwall %>% 
-  #filter(Admin_ward_code !="E05009195") %>% 
-  summarise(x =cor(MedianPrice, WardLowUsePerc, use = 'complete.obs'))
-
- Cornwall %>% ggplot(., aes(y=MedianPrice, x= WardLowUsePerc )) + geom_point() +
-   labs(title = "Mean Price vs Low Use % by ward in Cornwall",
-        x = "Low Use Percentage by Ward", 
-        y = "Mean Price") +
-  theme(plot.title = element_text(hjust = 0.5)) + 
-    annotate("text", 
-             label = paste0("Correlation = ", signif(CornCor[1,1],2)), 
-             x = 5 , y = 3.5e5, size = 5) +
-   geom_smooth(method = "lm", se = FALSE)
+corplotter(Cornwall, "MedianPrice", "WardLowUsePerc", 
+           "Median Price vs Low Use % by ward in Cornwall",
+           "Low Use Percentage by Ward",
+           "Median Price")
 SaveFig("CornCor.png")
@@
 
-test <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
+Hull <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                 "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
@@
 
-PlotMap(test, AG, variable = "WardLowUsePerc")
+PlotMap(Hull, AG, variable = "WardLowUsePerc")
 
+corplotter(Hull, "MedianPrice", "WardLowUsePerc", 
+           "Median Price vs Low Use % by ward in Hull",
+           "Low Use Percentage by Ward",
+           "Median Price")
 ```

### 2017-05-29 Functions/corplotter.R

@@ -1,0 +1,23 @@
+corplotter <- function(df, yaxis, xaxis, title, xaxisname = "xaxis", yaxisname= "yaxis"){
+  
+  dfcor <- signif(cor(eval(parse(text = paste0("df$", yaxis)
+  )), 
+  eval(parse(text = paste0("df$", xaxis))), 
+  use = 'complete.obs'),2)
+  
+  ypos <- mean(eval(parse(text = paste0("df$", yaxis))), na.rm = TRUE)/1.5
+  xpos <-range(eval(parse(text = paste0("df$", xaxis))), na.rm = TRUE) 
+  xpos <- (xpos[2]-xpos[1])*.8+xpos[1]
+  
+  
+  df %>% ggplot(., aes_string(y=yaxis, x= xaxis )) + geom_point() +
+    labs(title = title,
+         x = xaxisname,
+         y = yaxisname) +
+    theme(plot.title = element_text(hjust = 0.5)) +
+    annotate("text",
+             label = paste0("Correlation = ",
+                            signif(dfcor,2)),
+             x = xpos , y = ypos, size = 5) +
+    geom_smooth(method = "lm", se = FALSE)
+}

### 2017-05-29 EmptyHomesV1.Rmd
Leaflet
Attempting to plto with leaflet to make the maps more intereesting. It is proving very difficult.

@@
   group_by(MSOA11CD) %>%
-  summarise(MeanPrice = mean(X2), counts = n()) %>%
+  summarise(MedianPrice = median(X2), counts = n()) %>%
   left_join(., IncomeEst, by=c("MSOA11CD"= "MSOA.code")) %>%
-  mutate(Yearly.income= 52 * Total.weekly.income, ratio = MeanPrice/Yearly.income)
+  mutate(Yearly.income= 52 * Total.weekly.income, ratio = MedianPrice/Yearly.income)
 
@@
 sum(test2$ratio>6)/nrow(test2)  #about 50% EW
-test2 %>% filter(Region.name == "London") %>% mutate(HighRatio = ratio>10) %>%
+test2 %>% filter(Region.name == "London") %>% mutate(HighRatio = ratio>6) %>%
   summarise(total = sum(HighRatio)/n())
@@
 
- ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
-  PlotMap(., filter(AG, RGN15NM=="London"), filtermap = FALSE)
-SaveFig("LondonCont.png")
+```
 
- ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
-  PlotMap(., filter(AG, RGN15NM=="London"), variable = "LowuseClass", filtermap = FALSE)
-SaveFig("LondonDisc.png")
+#Chelsea sums
+```{r}
+
+sum(Chelseainfo$MeanPrice*Chelseainfo$counts)/sum(Chelseainfo$counts)
+
+prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))
 
@@
 
-PlotMap(Lambethinfo, AG, title = "Low-use homes in Kensington and Chelsea")
+Chelseainfo %>% mutate(Value = ValLow/1e6) %>%
+    filter(LAD11NM == "Kensington and Chelsea") %>%
+  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")
+
+Chelseainfo %>% 
+  filter(LAD11NM == "Kensington and Chelsea") %>%
+  group_by(Admin_ward_code) %>%
+  mutate(Value = sum(ValLow)/1e6) %>%
+  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")
+SaveFig("RBKCvalue.png")
 
 Chelseainfo %>% mutate(Value = ValLow/1e6) %>%
-  PlotMap(., AG, variable = "Value", title = "Low-use homes in Kensington and Chelsea")
-
-PlotMap(Chelseainfo, AG, title = "Low-use homes in Kensington and Chelsea")
+    filter(LAD11NM == "Kensington and Chelsea") %>%
+PlotMap(., AG, title = "Low-use homes in Kensington and Chelsea")
 SaveFig("RBKCLowUse.png")

### 2017-05-29 PlotwithLeaflet.Rmd
Leaflet
Attempting to plto with leaflet to make the maps more intereesting. It is proving very difficult.

---
title: "Untitled"
author: "Jonathan Bourne"
date: "29 May 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}

setwd("/home/jonno")
list.files()

states <- geojsonio::geojson_read("us-states.geojson" , what = "sp")
class(states)

m <- leaflet(states) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))

```

```{r}
MyData <- AG %>% filter(grepl("kensington", LAD11NM ,ignore.case = T)) %>%
  mutate(group = lsoa11cd)

MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
                               proj4string = CRS("+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +datum=OSGB36 +units=m +no_defs +ellps=airy +towgs84=446.448,-125.157,542.060,0.1502,0.2470,0.8421,-20.4894"))

#random thing
stuff <-data.frame(lsoa11cd=unique(MyData$lsoa11cd),row.names=unique(MyData$id))

MyData<- points2polygons(MyData,stuff)

plot(spDF,col=spDF$box_id+1)

class(MyData) # data.frame

m <- leaflet(MyData) %>%
  #setView(-96, 37.8, 4) %>%
  addTiles()

  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))

m %>% addPolygons()

```

```{r}
# this code just creates a sample SpatialPointsDataFrame 
x <- c(-10,-10,10,10,-10)
y <- c(-10,10,10,-10,-10)
df.1 <- data.frame(x,y,id=47, order=1:5,hole=F,piece=1,group=47.1,box_id=1)
coordinates(df.1)=c("x","y")
x <- c(+15+3*cos(2*pi/5*(0:5)))
y <- c(-15+3*sin(2*pi/5*(0:5)))
df.2 <- data.frame(x,y,id=48, order=1:6,hole=F,piece=1,group=48.1,box_id=2)
coordinates(df.2)=c("x","y")
x <- c(-15+2*cos(2*pi/8*(0:8)))
y <- c(+15+2*sin(2*pi/8*(0:8)))
df.3.1 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.1,box_id=3)
coordinates(df.3.1)=c("x","y")
x <- c(0+2*cos(2*pi/8*(0:8)))
y <- c(+15+2*sin(2*pi/8*(0:8)))
df.3.2 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.2,box_id=3)
coordinates(df.3.2)=c("x","y")
x <- c(+15+2*cos(2*pi/8*(0:8)))
y <- c(+15+2*sin(2*pi/8*(0:8)))
df.3.3 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.3,box_id=3)
coordinates(df.3.3)=c("x","y")
df <- rbind(df.1,df.2,df.3.1,df.3.2,df.3.3)
df
#              coordinates id order  hole piece group box_id
# 1             (-10, -10) 47     1 FALSE     1  47.1      1
# 2              (-10, 10) 47     2 FALSE     1  47.1      1
# 3               (10, 10) 47     3 FALSE     1  47.1      1
# 4              (10, -10) 47     4 FALSE     1  47.1      1
# 5             (-10, -10) 47     5 FALSE     1  47.1      1
# 6              (18, -15) 48     1 FALSE     1  48.1      2
# 7  (15.92705, -12.14683) 48     2 FALSE     1  48.1      2
# 8  (12.57295, -13.23664) 48     3 FALSE     1  48.1      2
# ...
data <- data.frame(box_id=unique(df$box_id),row.names=unique(df$id))
```

```{r}
points2polygons <- function(df,data) {
  get.grpPoly <- function(group,ID,df) {
         Polygon(coordinates(df[df$id==ID & df$group==group,]))
         }
  get.spPoly  <- function(ID,df) {
         Polygons(lapply(unique(df[df$id==ID,]$group),get.grpPoly,ID,df),ID)
         }
  spPolygons  <- SpatialPolygons(lapply(unique(df$id),get.spPoly,df))
  SpatialPolygonsDataFrame(spPolygons,match.ID=T,data=data)
}

spDF <- points2polygons(df,data)
plot(spDF,col=spDF$box_id+1)

library(rgdal)
writeOGR(spDF,dsn=".",layer="myShapefile", driver="ESRI Shapefile")
```

### 2017-05-29 PlotwithLeaflet.Rmd
LEaflet update
Have managed to make a leaflet doc and save it as an html widget

@@
 
-m <- leaflet(states) %>%
-  setView(-96, 37.8, 4) %>%
-  addProviderTiles("MapBox", options = providerTileOptions(
-    id = "mapbox.light",
-    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
-
-```
-
-```{r}
-MyData <- AG %>% filter(grepl("kensington", LAD11NM ,ignore.case = T)) %>%
-  mutate(group = lsoa11cd)
-
-MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
-                               proj4string = CRS("+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +datum=OSGB36 +units=m +no_defs +ellps=airy +towgs84=446.448,-125.157,542.060,0.1502,0.2470,0.8421,-20.4894"))
-
-#random thing
-stuff <-data.frame(lsoa11cd=unique(MyData$lsoa11cd),row.names=unique(MyData$id))
-
-MyData<- points2polygons(MyData,stuff)
-
-plot(spDF,col=spDF$box_id+1)
-
-class(MyData) # data.frame
-
-m <- leaflet(MyData) %>%
-  #setView(-96, 37.8, 4) %>%
-  addTiles()
-
-  addProviderTiles("MapBox", options = providerTileOptions(
-    id = "mapbox.light",
-    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
-
-m %>% addPolygons()
-
-```
-
-```{r}
-# this code just creates a sample SpatialPointsDataFrame 
-x <- c(-10,-10,10,10,-10)
-y <- c(-10,10,10,-10,-10)
-df.1 <- data.frame(x,y,id=47, order=1:5,hole=F,piece=1,group=47.1,box_id=1)
-coordinates(df.1)=c("x","y")
-x <- c(+15+3*cos(2*pi/5*(0:5)))
-y <- c(-15+3*sin(2*pi/5*(0:5)))
-df.2 <- data.frame(x,y,id=48, order=1:6,hole=F,piece=1,group=48.1,box_id=2)
-coordinates(df.2)=c("x","y")
-x <- c(-15+2*cos(2*pi/8*(0:8)))
-y <- c(+15+2*sin(2*pi/8*(0:8)))
-df.3.1 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.1,box_id=3)
-coordinates(df.3.1)=c("x","y")
-x <- c(0+2*cos(2*pi/8*(0:8)))
-y <- c(+15+2*sin(2*pi/8*(0:8)))
-df.3.2 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.2,box_id=3)
-coordinates(df.3.2)=c("x","y")
-x <- c(+15+2*cos(2*pi/8*(0:8)))
-y <- c(+15+2*sin(2*pi/8*(0:8)))
-df.3.3 <- data.frame(x,y,id=20, order=1:9,hole=F,piece=1,group=20.3,box_id=3)
-coordinates(df.3.3)=c("x","y")
-df <- rbind(df.1,df.2,df.3.1,df.3.2,df.3.3)
-df
-#              coordinates id order  hole piece group box_id
-# 1             (-10, -10) 47     1 FALSE     1  47.1      1
-# 2              (-10, 10) 47     2 FALSE     1  47.1      1
-# 3               (10, 10) 47     3 FALSE     1  47.1      1
-# 4              (10, -10) 47     4 FALSE     1  47.1      1
-# 5             (-10, -10) 47     5 FALSE     1  47.1      1
-# 6              (18, -15) 48     1 FALSE     1  48.1      2
-# 7  (15.92705, -12.14683) 48     2 FALSE     1  48.1      2
-# 8  (12.57295, -13.23664) 48     3 FALSE     1  48.1      2
-# ...
-data <- data.frame(box_id=unique(df$box_id),row.names=unique(df$id))
-```
-
-```{r}
 points2polygons <- function(df,data) {
@@
 
-spDF <- points2polygons(df,data)
-plot(spDF,col=spDF$box_id+1)
+m <- leaflet(states) %>%
+  #setView(-96, 37.8, 4) %>%
+  addTiles()
+  # addProviderTiles("MapBox", options = providerTileOptions(
+  #   id = "mapbox.light",
+  #   accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
 
-library(rgdal)
-writeOGR(spDF,dsn=".",layer="myShapefile", driver="ESRI Shapefile")
+m %>% addPolygons()
+
 ```
+
+```{r}
+MyData <- AG %>% filter(grepl("kensington", LAD11NM ,ignore.case = T)) %>%
+  rename(LSOA_CODE = lsoa11cd)
+
+MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
+                               proj4string = CRS('+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs'))
+MyData <- spTransform(MyData, CRS("+init=epsg:4326"))
+#random thing
+stuff <-data.frame(LSOA_CODE=unique(MyData$LSOA_CODE),row.names=unique(MyData$id))
+
+MyData<- points2polygons(MyData,stuff)
+
+AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))
+
+MyData <- merge(MyData, Chelseainfo)
+
+class(MyData) # data.frame
+
+v<-"pk.eyJ1Ijoiam9ubm9iIiwiYSI6ImNqM2FlNXhpbDAwM3gzMW83ZW1hbHI0bzYifQ.4AfaY0Un0bKU41hZscpy9Q"
+
+m <- leaflet(MyData) %>%
+    #addTiles()
+    addProviderTiles("MapBox", options = providerTileOptions(
+    id = "mapbox.light",
+    accessToken = v))
+
+bins <- c(0, 10, 20, 25, 100)
+pal <- colorBin("YlOrRd", domain = MyData$LowUsePerc, bins = bins)
+
+labels <- sprintf(
+  "<strong>%s</strong><br/>Low-use  %g &#37",
+  MyData$WD16NM, MyData$LowUsePerc
+) %>% lapply(htmltools::HTML)
+
+z <-m %>% addPolygons(
+  fillColor = ~pal(LowUsePerc),
+  weight = 2,
+  opacity = 1,
+  color = "white",
+  dashArray = "3",
+  fillOpacity = 0.7,
+  highlight = highlightOptions(
+    weight = 5,
+    color = "#666",
+    dashArray = "",
+    fillOpacity = 0.7,
+    bringToFront = TRUE),
+  label = labels,
+  labelOptions = labelOptions(
+    style = list("font-weight" = "normal", padding = "3px 8px"),
+    textsize = "15px",
+    direction = "auto")) %>%
+  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
+    position = "bottomright")
+
+saveWidget(z, file="m.html" )
+
+mapshot(z, url = paste0(getwd(), "/map.html"))
+```

### 2017-05-30 PlotwithLeaflet.Rmd
Simplify polygon
Used the rmapshaper package to simplify the polygons which means they take up less space than before, still the code can only be used if the other data is loaded in seperate files.

@@
 
-AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))
+#AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))
 
-MyData <- merge(MyData, Chelseainfo)
+MyData <- Chelseainfo %>%
+  select(LSOA_CODE, LowUsePerc, WD16NM)%>%
+  merge(MyData, .)
 
@@
 
-saveWidget(z, file="m.html" )
-
+#saveWidget(z, file="m.html", selfcontained = FALSE )
+setwd("/home/jonno")
 mapshot(z, url = paste0(getwd(), "/map.html"))
 ```
+
+gSimplify
+```{r}
+test <- gSimplify(MyData,tol= .0001, topologyPreserve = T) %>% 
+  SpatialPolygonsDataFrame(.)
+
+library(geojsonio)
+states_json <- geojson_json(MyData,geometry = "polygon")
+
+test <- states_json %>% 
+  ms_simplify(keep = 0.005,keep_shapes = TRUE, explode = TRUE) %>% # Simplify polygon
+  geojson_sp()
+
+plot(test)
+
+m2 <- leaflet(test) %>%
+    #addTiles()
+    addProviderTiles("MapBox", options = providerTileOptions(
+    id = "mapbox.light",
+    accessToken = v))
+
+bins <- c(0, 10, 20, 25, 100)
+pal <- colorBin("YlOrRd", domain = test$LowUsePerc, bins = bins)
+
+labels <- sprintf(
+  "<strong>%s</strong><br/>Low-use  %g &#37",
+  test$WD16NM, test$LowUsePerc
+) %>% lapply(htmltools::HTML)
+
+z2 <-m2 %>% addPolygons(
+  fillColor = ~pal(LowUsePerc),
+  weight = 2,
+  opacity = 1,
+  color = "white",
+  dashArray = "3",
+  fillOpacity = 0.7,
+  highlight = highlightOptions(
+    weight = 5,
+    color = "#666",
+    dashArray = "",
+    fillOpacity = 0.7,
+    bringToFront = TRUE),
+  label = labels,
+  labelOptions = labelOptions(
+    style = list("font-weight" = "normal", padding = "3px 8px"),
+    textsize = "15px",
+    direction = "auto")) %>%
+  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
+    position = "bottomright")
+saveWidget(z2, file="mapsimple2.html", selfcontained = FALSE )
+mapshot(z2, url = paste0(getwd(), "/mapsimple.html"))
+```

### 2017-06-02 EmptyHomesV1.Rmd
Chelsea Analysis
Added some code which performs an analysis for Chelsea.

@@
 ---
+
+man-whitney
 
@@
 https://www.ons.gov.uk/peoplepopulationandcommunity/personalandhouseholdfinances/incomeandwealth/datasets/nowcastinghouseholdincomeintheuk
+
+#savils definitions of prime also there segmentation of the market
+http://pdf.euro.savills.co.uk/spotlight-on/spotlight-on-london-housing-supply.pdf
 
@@
 
-Newhaminfo <- read.xlsx( "NewhamExemptionsLSOA.XLSX"  , colNames = TRUE)[,1:4] %>%
-  StructureData(2)
+Newhaminfo <- read.xlsx( "NewhamDiscountsLSOA.xlsx", colNames = TRUE)[,1:4] %>%
+  StructureData(full = F)
 
@@
 
+test <-  Chelseainfo %>% left_join(., AG)
+
 ```
@@
 
-sum(Chelseainfo$MeanPrice*Chelseainfo$counts)/sum(Chelseainfo$counts)
+#T test if there is a significant difference between 
+v <- Chelseainfo %>% filter(LAD11CD =="E09000020")
+
+#low-use value chelsea
+sum(v$MeanPrice*v$LowUse)
+ChelMeanPrice <- (sum(v$MeanPrice*v$counts)/sum(v$counts))
+ChelLowMean<- sum(v$MeanPrice*v$LowUse)/sum(v$LowUse)
+ChelLowMean/ChelMeanPrice
+v<- rep(v$MeanPrice, times = v$LowUse)-ChelMeanPrice
+
+t.test(v,alternative = "greater")
 
 prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))
+Admin_ward_code
+#c("Lower Mainstream", "Mid Mainstream", "Upper Mainstream", "Prime", "Super Prime"),
+test <- prices %>% 
+  filter( Admin_district_code =="E09000020") %>%
+  mutate(class = cut(X2, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
+            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
+             right = F)) %>%
+  select(Admin_ward_code, class) %>%
+  group_by(Admin_ward_code, class) %>% 
+  summarise(Counts = n()) %>%
+  group_by(Admin_ward_code) %>%
+  mutate(WardPerc = Counts/sum(Counts)) %>%
+  ungroup
 
+test3 <- Chelseainfo %>% 
+  group_by(Admin_ward_code) %>%
+  summarise_all(funs(first)) %>%
+  select(Admin_ward_code, WardLowUse, WardHomes) %>%
+  left_join(., test, "Admin_ward_code") %>%
+  mutate(LowUseClass = WardLowUse*WardPerc,
+         HomesClass = WardHomes*WardPerc) %>%
+  group_by(class) %>%
+  summarise(LowUseClass = sum(LowUseClass),
+            HomesClass = sum(HomesClass)) %>%
+  filter(complete.cases(.)) %>%
+  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
+         PercOfHomes = HomesClass/sum(HomesClass),
+         PercofClass = LowUseClass/HomesClass)
+
+#Percentage over and under of what would be expected if buying was random
+#The differences suggest that people are buying more expensive homes when there is no plan to live in them.
+round(test3$LowUseClass/(sum(test3$LowUseClass)*test3$PercOfHomes),2)
 ```
@@
 
+Value of low*use and total low use
+```{r}
+
+test <-  ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
+  group_by(Admin_ward_code) %>%
+  summarise(LAD11NM = first(LAD11NM),
+            MeanPrice = first(MeanPrice),
+            WardLowUse = first(WardLowUse)) %>%
+  group_by(LAD11NM) %>%
+  summarise(totalLow = sum(MeanPrice*WardLowUse)/1e6,
+            TotalEmpt = sum(WardLowUse))
+
+sum(test$totalLow, na.rm = T)  
+sum(test$TotalEmpt, na.rm = T)  
+length(unique(test$LAD11NM))
+
+```
+
 Plot Map
@@
 
-corplotter(Chelseainfo, "MedianPrice", "WardLowUsePerc", "Median Price vs Low Use % by ward in RBKC",
+corplotter(Chelseainfo, "MeanPrice", "WardLowUsePerc", "Mean Price vs Low Use % by ward in RBKC",
+           "Low Use Percentage by Ward",
+           "Mean Price")
+SaveFig("ChelseaCor.png")
+
+Chelseainfo %>% filter(WardLowUsePerc != max("WardLowUsePerc"),
+                       MeanPrice != max(MeanPrice)) %>%
+  corplotter(., "MeanPrice", "WardLowUsePerc", "Median Price vs Low Use % by ward in RBKC",
            "Low Use Percentage by Ward",
            "Median Price")
-SaveFig("ChelseaCor.png")
-
 ```

### 2017-06-05 EmptyHomesV1.Rmd
Bootstrapped ratios
Created bootstrapped ratios, the results are unexpected and need to be checked.

@@
 
+#the data is not normal
+plot(density(v))
+#this prob not valid
 t.test(v,alternative = "greater")
+
+#do a bootstrapped mean to see if it is greater than the mean of the homes overall.
+set.seed(1258)
+samps <-10000
+
+bootres <- 1:samps %>% map(~data.frame(res =sample(v, length(v), replace = T))) %>%
+  bind_cols()
+
+sum(colMeans(bootres)>0)/samps
+
+plot(density(colMeans(bootres+ChelMeanPrice)))
+
+#%>% setNames(paste0("samp",.x))
 
@@
          PercOfHomes = HomesClass/sum(HomesClass),
-         PercofClass = LowUseClass/HomesClass)
+         PercofClass = LowUseClass/HomesClass,
+         `Expected Homes` = PercOfHomes*sum(LowUseClass),
+         `Actual Homes` = PercOfLowUse*sum(LowUseClass))
+
+sum(test3$LowUseClass)*test3$PercOfHomes
 
@@
 round(test3$LowUseClass/(sum(test3$LowUseClass)*test3$PercOfHomes),2)
+
+ggplot(test3, aes(x= class, y = PercOfHomes*100)) +geom_bar(stat = "identity") + 
+  labs(title = "Distribution probability of homes in each class", y = "Percentage")
+
+test3 %>%
+  select(class, `Expected Homes`, `Actual Homes`) %>%
+  gather(key = "Type" , value = "Number", -class) %>%
+  ggplot(., aes(x= class, y = Number, fill = Type)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "Expected Number of low-use homes in each class")
+
+test3 %>%
+  mutate(`Percentage Difference` = (`Actual Homes`/`Expected Homes`)*100-100) %>%
+  ggplot(., aes(x= class, y = `Percentage Difference`)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Percentage difference between expected number of homes per class and actual")+
+  coord_cartesian(ylim=c(-20,20))
+
+```
+
+#Chelsea Bootstrapped ratios
+
+```{r}
+ ChelPrice <- prices %>% 
+  filter( Admin_district_code =="E09000020") %>%
+  select(lsoa11cd, Price =X2) %>%
+  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
+            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
+             right = F))
+
+set.seed(16544)
+Chelseastrapped <- ClassStrapper(ChelPrice, sum(Chelseainfo$LowUse))
+
+Chelseastrapped %>% ggplot(., aes(x= class, y = Counts, fill = class)) + geom_boxplot()
+
+test <- unique(ChelPrice$lsoa11cd)%>% 
+  map(~ ChelPrice %>% 
+        filter(lsoa11cd == .x) %>% 
+  ClassStrapper(., sum((filter(Chelseainfo, LSOA_CODE == .x))$LowUse)) %>%
+    mutate(class = as.character(class),
+           Counts = as.integer(Counts),
+           ID = as.integer(ID)) %>%
+      setNames(c("class", paste0("Counts", .x) ,"ID"))
+  )
+
+ChelseaLSOAstrap <- test %>%  
+    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
+  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE)) %>%
+select(class, ID, Totals)
+
+test1 <- Chelseastrapped %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
+  mutate(ratio = Totals/Counts)
+
+test1 %>% ggplot(., aes(x= class, y = ratio, fill = class)) + geom_boxplot() + 
+  labs(title = "Boxplot of bootstrapped Ratios")
+
 ```

### 2017-06-05 Functions/ClassStrapper.R

@@ -1,0 +1,20 @@
+ClassStrapper <- function(PriceData, LowUseCounts){
+  SampBlock <- sample(1:nrow(PriceData), LowUseCounts*1000, replace = TRUE ) %>% 
+    matrix(data = ., ncol = 1000)
+  
+  Out <- PriceData[,3] %>% 
+    slice(SampBlock[,1]) %>%
+    group_by(class) %>%
+    summarise(Counts = n()) %>%
+    mutate(ID = 1)
+  
+  
+  Out <- 1:1000 %>% map_df(~PriceData[,3] %>% 
+                             slice(SampBlock[,.x]) %>%
+                             group_by(class) %>%
+                             summarise(Counts = n()) %>%
+                             mutate(ID = .x)
+  )
+  
+  return(Out)
+}

### 2017-06-06 EmptyHomesV1.Rmd
Bootsrapped results
Worked through the bootstrapping process unpicking errors that had been made on the first attempt.

@@
 #c("Lower Mainstream", "Mid Mainstream", "Upper Mainstream", "Prime", "Super Prime"),
-test <- prices %>% 
+ClassCountsPerWard <- prices %>% 
   filter( Admin_district_code =="E09000020") %>%
@@
   select(Admin_ward_code, WardLowUse, WardHomes) %>%
-  left_join(., test, "Admin_ward_code") %>%
+  left_join(., ClassCountsPerWard, "Admin_ward_code") %>%
   mutate(LowUseClass = WardLowUse*WardPerc,
@@
          `Expected Homes` = PercOfHomes*sum(LowUseClass),
-         `Actual Homes` = PercOfLowUse*sum(LowUseClass))
+         `Actual Homes` = LowUseClass)
 
@@
   filter( Admin_district_code =="E09000020") %>%
-  select(lsoa11cd, Price =X2) %>%
+  select(Admin_ward_code, lsoa11cd, Price =X2) %>%
   mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
@@
 
+round(table(ChelPrice$class)/nrow(ChelPrice)*100)
+
 set.seed(16544)
@@
 
+Chelseastrapped %>% group_by(class)%>%
+  summarise(Counts = mean(Counts)) %>%
+  mutate(ratio = Counts/sum(Counts))
+
 Chelseastrapped %>% ggplot(., aes(x= class, y = Counts, fill = class)) + geom_boxplot()
 
-test <- unique(ChelPrice$lsoa11cd)%>% 
+ChelseainfoWard <- Chelseainfo %>%
+  group_by(Admin_ward_code) %>%
+  summarise_all(funs(first))
+
+set.seed(16540)
+ChelseaLSOAstrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
   map(~ ChelPrice %>% 
-        filter(lsoa11cd == .x) %>% 
-  ClassStrapper(., sum((filter(Chelseainfo, LSOA_CODE == .x))$LowUse)) %>%
+        filter(Admin_ward_code == .x) %>% 
+  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse)) %>%
     mutate(class = as.character(class),
@@
 
-ChelseaLSOAstrap <- test %>%  
+ChelseaLSOAstrap <- ChelseaLSOAstrap1 %>%  
     Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
-  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE)) %>%
+  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
+         class = fct_relevel(class, "Upper", after = 2)) %>%
+select(class, ID, Totals)
+
+#bootrapps Chelsea housing stock.
+set.seed(16540)
+ChelseaWardHomesStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
+  map(~ ChelPrice %>% 
+        filter(Admin_ward_code == .x) %>% 
+  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes)) %>%
+    mutate(class = as.character(class),
+           Counts = as.integer(Counts),
+           ID = as.integer(ID)) %>%
+      setNames(c("class", paste0("Counts", .x) ,"ID"))
+  ) %>%  
+    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
+  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
+         class = fct_relevel(class, "Upper", after = 2)) %>%
 select(class, ID, Totals)
@@
 
+test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
+  rename(LowUse = Totals.y,
+         Homes = Totals.x) %>%
+  group_by(ID)%>%
+  mutate(ratio = LowUse/Homes,
+         HomesPerc = Homes/sum(Homes),
+         LowUsePerc = LowUse/sum(LowUse),
+         ClassPerc = LowUse/Homes,
+         ExpectedHomes = HomesPerc*sum(LowUse),
+         RatioExvsAct = LowUse/ExpectedHomes)
+
 test1 %>% ggplot(., aes(x= class, y = ratio, fill = class)) + geom_boxplot() + 
   labs(title = "Boxplot of bootstrapped Ratios")
+
+test1 %>% ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Boxplot of bootstrapped Ratios")
+
+test1 %>% group_by(class) %>%
+  summarise(meanC = mean(Counts), 
+            meanT = mean(Totals), 
+            meanR = mean(ratio))
+
+ChelseaWardHomesStrap1 %>% group_by(class) %>%
+  summarise(meanC = mean(Totals))
 

### 2017-06-06 EmptyHomesV1.Rmd
Bootstrapped results
Bootrapped results are working properly

@@
 
-round(table(ChelPrice$class)/nrow(ChelPrice)*100)
-
-set.seed(16544)
-Chelseastrapped <- ClassStrapper(ChelPrice, sum(Chelseainfo$LowUse))
-
-Chelseastrapped %>% group_by(class)%>%
-  summarise(Counts = mean(Counts)) %>%
-  mutate(ratio = Counts/sum(Counts))
-
-Chelseastrapped %>% ggplot(., aes(x= class, y = Counts, fill = class)) + geom_boxplot()
-
-ChelseainfoWard <- Chelseainfo %>%
-  group_by(Admin_ward_code) %>%
-  summarise_all(funs(first))
-
-set.seed(16540)
-ChelseaLSOAstrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
+#bootrapps Chelsea housing stock.
+set.seed(16546)
+ChelseaWardLowUseStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
   map(~ ChelPrice %>% 
         filter(Admin_ward_code == .x) %>% 
-  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse)) %>%
+  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse), reps = 10000) %>%
     mutate(class = as.character(class),
@@
       setNames(c("class", paste0("Counts", .x) ,"ID"))
-  )
-
-ChelseaLSOAstrap <- ChelseaLSOAstrap1 %>%  
+  ) %>%  
     Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
@@
         filter(Admin_ward_code == .x) %>% 
-  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes)) %>%
+  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes), reps = 10000) %>%
     mutate(class = as.character(class),
@@
 
-test1 <- Chelseastrapped %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
-  mutate(ratio = Totals/Counts)
-
-test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
+test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaWardLowUseStrap1, by = c("class", "ID")) %>%
   rename(LowUse = Totals.y,
@@
 
-test1 %>% ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Boxplot of bootstrapped Ratios")
+test1 %>%
+mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+SaveFig("DistributionPlot.png")
 
 test1 %>% group_by(class) %>%
-  summarise(meanC = mean(Counts), 
-            meanT = mean(Totals), 
-            meanR = mean(ratio))
-
-ChelseaWardHomesStrap1 %>% group_by(class) %>%
-  summarise(meanC = mean(Totals))
+  summarise_all(funs(mean))
 

### 2017-06-13 EmptyHomesV1.Rmd
Function Update
Updated functions including new ones to make leaflet plotting easier. These were the last changes before publishing the chelsea blog

@@
 
+Chelseainfo2 <- read_excel( "Kensington and ChelseaDiscountsLSOA.xlsx" )[,1:4] %>%
+  StructureData(full= FALSE)
+colSums(Chelseainfo2[,-1])
+
 #Barking
@@
 ```{r}
+
+sum(Chelseainfo$LowUse)/sum(Chelseainfo$Homes)
 
@@
 
+ChelseainfoWard <- Chelseainfo %>% 
+  group_by(Admin_ward_code) %>%
+  summarise_all(funs(first))
+
 #bootrapps Chelsea housing stock.
@@
 select(class, ID, Totals)
+
+ChelseaWardHomesStrap2 <- ClassStrapper(ChelPrice, sum(ChelseainfoWard$WardHomes), 10000)
 

### 2017-06-13 PlotwithLeaflet.Rmd
Chelsea Analysis
Added some code which performs an analysis for Chelsea.
Function Update
Updated functions including new ones to make leaflet plotting easier. These were the last changes before publishing the chelsea blog

@@
 title: "Untitled"
-author: "Jonathan Bourne"
+author: "Jonathan Bourne
 date: "29 May 2017"
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r}
+
+library(htmlwidgets)
+gitpage <- "/home/jonno/JonnoB.github.io"
+
 ```
 
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
 ```{r cars}
-
-setwd("/home/jonno")
-list.files()
-
-states <- geojsonio::geojson_read("us-states.geojson" , what = "sp")
-class(states)
 
@@
 
-m <- leaflet(states) %>%
-  #setView(-96, 37.8, 4) %>%
-  addTiles()
-  # addProviderTiles("MapBox", options = providerTileOptions(
-  #   id = "mapbox.light",
-  #   accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
-
-m %>% addPolygons()
-
 ```
@@
 ```{r}
-MyData <- AG %>% filter(grepl("kensington", LAD11NM ,ignore.case = T)) %>%
-  rename(LSOA_CODE = lsoa11cd)
+setwd(gitpage)
+z <- MakeLeaflet("chelsea", Chelseainfo)
+z
+saveWidget(z, file="ChelseaLowUse.html", selfcontained = TRUE )
 
-MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
-                               proj4string = CRS('+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs'))
-MyData <- spTransform(MyData, CRS("+init=epsg:4326"))
-#random thing
-stuff <-data.frame(LSOA_CODE=unique(MyData$LSOA_CODE),row.names=unique(MyData$id))
+z<- MakeLeaflet("lambeth", Lambethinfo, c(0:5))
+saveWidget(z, file="LambethLowUSe.html", selfcontained = TRUE )
 
-MyData<- points2polygons(MyData,stuff)
-
-#AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))
-
-MyData <- Chelseainfo %>%
-  select(LSOA_CODE, LowUsePerc, WD16NM)%>%
-  merge(MyData, .)
-
-class(MyData) # data.frame
-
-v<-"pk.eyJ1Ijoiam9ubm9iIiwiYSI6ImNqM2FlNXhpbDAwM3gzMW83ZW1hbHI0bzYifQ.4AfaY0Un0bKU41hZscpy9Q"
-
-m <- leaflet(MyData) %>%
-    #addTiles()
-    addProviderTiles("MapBox", options = providerTileOptions(
-    id = "mapbox.light",
-    accessToken = v))
-
-bins <- c(0, 10, 20, 25, 100)
-pal <- colorBin("YlOrRd", domain = MyData$LowUsePerc, bins = bins)
-
-labels <- sprintf(
-  "<strong>%s</strong><br/>Low-use  %g &#37",
-  MyData$WD16NM, MyData$LowUsePerc
-) %>% lapply(htmltools::HTML)
-
-z <-m %>% addPolygons(
-  fillColor = ~pal(LowUsePerc),
-  weight = 2,
-  opacity = 1,
-  color = "white",
-  dashArray = "3",
-  fillOpacity = 0.7,
-  highlight = highlightOptions(
-    weight = 5,
-    color = "#666",
-    dashArray = "",
-    fillOpacity = 0.7,
-    bringToFront = TRUE),
-  label = labels,
-  labelOptions = labelOptions(
-    style = list("font-weight" = "normal", padding = "3px 8px"),
-    textsize = "15px",
-    direction = "auto")) %>%
-  addLegend(pal = pal, values = ~density, opacity = 0.7, title = NULL,
-    position = "bottomright")
-
-#saveWidget(z, file="m.html", selfcontained = FALSE )
 setwd("/home/jonno")

### 2017-06-13 SubCode/Setup.R

@@ -1,7 +1,8 @@
 ##This code is used to setup the project it is common to both the empty homes doc and also the template creation doc.
 
 
-packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet")
+packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
+              "forcats")
 
 new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
 if(length(new.packages)) install.packages(new.packages)

### 2017-06-25 LowUseEngland.Rmd
File Renames
Split London and England Low use homes and cleaned up the files to make them easier to understand.

---
title: "NON-London"
author: "Jonathan Bourne"
date: "25 June 2017"
output: html_document
---

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)
```

```{r}
source(file.path(CommonCode, "AuxdataLoad.R"))
```

Cumbria
```{r}
setwd(file.path(RegionsComp, "Region North West"))

BarrowCumbriaDATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
  StructureData(.,lowuse = c(2:6,8))

SLakelandCumbriaDATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData(., lowuse=2:9)

#only inlcudes postcodes so the mergeing needs to be done manually
CopelandCumbriaDATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData()

EdenCumbriaDATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.,lowuse = c(2:6,8))

 ls(pattern = "Cumbria") %>% map_df(~eval(parse(text=.x))) %>%
  PlotMap(., filter(AG,grepl(paste("Barrow-in-Furness", "Allerdale",
                                    "Carlisle","Copeland","Eden",  
                                    "South Lakeland", sep = "|"), 
                             LAD11NM ) ), 
          filtermap = FALSE,
          title = "Map of Cumbria with all current data")

#Removing Barrow due to the redevelopment only increases the cor slightly
#  ls(pattern = "Cumbria")[-1] %>% map_df(~eval(parse(text=.x)))  %>%
# corplotter(., "MedianPrice", "WardLowUsePerc", 
#            "Median Price vs Low Use % by ward in Cumbria",
#            "Low Use Percentage by Ward",
#            "Median Price")

 ls(pattern = "Cumbria") %>% map_df(~eval(parse(text=.x)))  %>%
corplotter(., "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Cumbria",
           "Low Use Percentage by Ward",
           "Median Price")

```

#Cornwall

```{r}

setwd(file.path(RegionsComp, "Region South West"))

Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,23:28))

PlotMap(Cornwall, AG, title = "Lowuse in Cornwall")
SaveFig("Cornwall.png")

read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,7:16, 21:28) ) %>%
  PlotMap(., AG,title = "all empties")

corplotter(Cornwall, "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Cornwall",
           "Low Use Percentage by Ward",
           "Median Price")
SaveFig("CornCor.png")

```

Suffolk

```{r}
setwd(file.path(RegionsComp, "Region East of England"))
list.files()

CoastWave <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(., lowuse = c(5,6,13,14,16:18))

PlotMap(CoastWave, AG, title ="Low-use Homes in Coastal Suffolk")

corplotter(CoastWave, "MedianPrice", "WardLowUsePerc", 
           "Median Price vs Low Use % by ward in Cumbria",
           "Low Use Percentage by Ward",
           "Median Price")

```

Hull

### 2017-06-25 LowUseLondon.Rmd
File Renames
Split London and England Low use homes and cleaned up the files to make them easier to understand.

--- 2017-06-13 EmptyHomesV1.Rmd
@@
 
-#VOA data
-
-Council tax bands from VOA
-https://www.gov.uk/government/statistics/council-tax-stock-of-properties-2016
-
-```{r PopandHomes}
-setwd(DataFolder)
-
-CTtaxstock<- read_csv("Table_CTSOP1.1_2016.csv")
-
-pop <- read_csv("SAPE2.csv")
-
-EW <- inner_join(select(CTtaxstock, ECODE, ALL_PROPERTIES),select(pop, `Area Codes`, `All Ages`),
-          by=c("ECODE" = "Area Codes")) %>% setNames(c("ECODE", "Homes", "Pop")) 
-```
-
-#Load the LSOA shape data for EW
-
 ```{r}
-setwd(LSOAshapedata)
-
-shape <- readOGR(dsn = list.files(pattern = "shp"))
-
-```
-
-# Load Post code data
-
-This chunk checks the exiatane of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup.
-Creating the lookup takes quite a lot of time so it is good to only have to do it once.
-```{r}
-
-if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
- PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
-} else {
-  source(file.path(CommonCode, "PostcodeLookup.R"))
-}
-
-```
-
-Bind the ward names and LAD names to the lsoa data
-```{r LAD/WARD data}
-setwd(PostcodeLookups)
-lsoa <- read_csv("PCD11_OA11_LSOA11_MSOA11_LAD11_EW_LU_aligned_v2.csv") %>%
-  select(LSOA11CD:LAD11NMW) %>% distinct(., LSOA11CD, .keep_all = TRUE)
-
-setwd(AddGeog)
-wardnames <- read_csv("Ward_to_Local_Authority_District_to_County_to_Region_to_Country_December_2016_Lookup_in_United_Kingdom_V2.csv") %>% setNames(c("Admin_ward_code", names(.)[-1]))
-
-#uses the dataframe from the CreateExceltemplates to get the ward names and the lsoa together
-wardlsoa <- PstCdLSOA.raw %>% distinct(lsoa11cd, .keep_all = TRUE) %>% 
-  select(lsoa11cd, Admin_ward_code)
-
-EW2 <- inner_join(EW, lsoa, by = c("ECODE" = "LSOA11CD") ) %>% 
-      left_join(., wardlsoa, by = c("ECODE"="lsoa11cd") ) %>% 
-  left_join(., select(wardnames, Admin_ward_code, WD16NM), by = "Admin_ward_code") %>%
-  group_by(Admin_ward_code) %>%
-  mutate(WardHomes = sum(Homes),  WardPop = sum(Pop)) %>% ungroup
-rm(wardlsoa)
-rm(wardnames)
-```
-
-Convert shape file to dataframe and join in the LSOA data
-```{r}
-
-if(file.exists(file.path(DataFolder,"shapeframe.rds"))){
- AG<- readRDS(file.path(DataFolder,"shapeframe.rds"))
-} else{
-    setwd(LSOAshapedata)
-
-    shape <- readOGR(dsn = list.files(pattern = "shp"))
-
-    AG <- fortify(shape, region = "objectid")
-
-    AG <- AG %>% mutate(id = as.integer(id)) %>% 
-      left_join(., shape@data, by = c("id" = "objectid")) %>% 
-    left_join(., EW2, by = c("lsoa11cd" = "ECODE"))
-
-    saveRDS(AG, file.path(DataFolder,"shapeframe.rds"))
-    }
-
-```
-
-#I should probably join the homes and pop at the same time I join the council tax data
-
-#get prices
-
-```{r}
-
-setwd(DataFolder)
-
-prices <-read_csv("pp-2016.csv", col_names = FALSE ) %>% 
-  mutate(X4 = gsub(" ", "", X4)) %>% 
-  left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), 
-            by = c("X4"="Postcode")) %>% 
-  filter(!is.na(lsoa11cd)) %>% mutate(Prime = X2>1e6, SuperPrime = X2>1e7)
-
-MeanWardPrice <- prices %>% 
-  group_by(Admin_ward_code) %>% 
-  summarise( MeanPrice = mean(X2), 
-             MedianPrice = median(X2),counts =n(),  
-             Prime = sum(Prime), 
-             SuperPrime = sum(SuperPrime)) %>% 
-  mutate(TotPrime = Prime/sum(Prime), TotSupPrime = SuperPrime/sum(SuperPrime),
-         PrimePerc = Prime/counts, SuperPrimePerc = SuperPrime/counts)
-
-MeanWardPrice %>% ggplot(., aes(x= counts)) + geom_density()
-
-WardDat2 <- WardDat %>% left_join(., MeanWardPrice) %>% mutate(vallow = LowUse*MeanPrice) %>%
-  filter(!is.na(MeanPrice))
-
-setwd(DataFolder)
-list.files()
-
-#Unnfordability at EW level salery 2014-2015
-mean(prices$X2)/31920
-
-#is mean income estimates
-IncomeEst <- read_excel("1smallareaincomeestimatesdataupdate.xls", sheet = 4, skip = 4) %>%
-  setNames(make.names(names(.)) %>% 
-             gsub("\\.(?=\\.*$)", "", ., perl=TRUE)) #removes trailing full stop.
-
-test2 <- prices %>% left_join(., select(EW2, ECODE, MSOA11CD), 
-                              by =c("lsoa11cd"="ECODE")) %>%
-  group_by(MSOA11CD) %>%
-  summarise(MedianPrice = median(X2), counts = n()) %>%
-  left_join(., IncomeEst, by=c("MSOA11CD"= "MSOA.code")) %>%
-  mutate(Yearly.income= 52 * Total.weekly.income, ratio = MedianPrice/Yearly.income)
-
-test2 %>% ggplot(.,aes(x=ratio)) +geom_density()
-
-sum(test2$ratio>6)/nrow(test2)  #about 50% EW
-test2 %>% filter(Region.name == "London") %>% mutate(HighRatio = ratio>6) %>%
-  summarise(total = sum(HighRatio)/n())
-
+source(file.path(CommonCode, "AuxdataLoad.R"))
 ```
@@
 ```{r}
-#Lambeth
-
-setwd(file.path(RegionsComp, "Region London"))
-
-Lambethinfo <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
-    StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))
-
-test <- Lambethinfo %>% select(LowUsePerc, WardLowUsePerc, LowuseClass, WardLowuseClass)
-
-#Islington is exemptions only
-
-Islingtoninfo <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4]%>%  
-    StructureData(., lowuse = c(2:11,14:18))
-
-#Greenwhich
-
-Greenwichinfo <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>%  
-    StructureData(., c(2,3,4,21,22), c(3,4,21,22))
-
-#Camden
-
-Camdeninfo <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
- StructureData()
-
-#Bromley
-
-Bromleyinfo <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
-  StructureData(c(6:8,29:31))
-
-#Haringey
-
-#Haringey is funny and has to be worked over a bit first
-Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)]
-
-Haringeyinfo <- data_frame(Discount = rep(Haringey$`Exemption./.Discount.type`, Haringey$Count.of.Exemptions.by.Post.Code),
-           LSOA = rep(Haringey$LSOA_CODE, Haringey$Count.of.Exemptions.by.Post.Code)) %>%
-  mutate( a= NA, b = NA) %>%
-  StructureData(21:25)
-
-#Sutton
-
-Suttoninfo <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,c(1,4:6)] %>%
-  StructureData()
-
-#Richmond
-Richmondinfo <- read_csv("Richmond_2.csv" )[1:4]%>%
-  StructureData()
-
-#Hillingdon
-
-Hillingdoninfo <- read.xlsx("HillingdonDiscountsLSOA.XLSX" )[1:4]%>% 
-  StructureData()
-
-#Bexley
-
-Bexleyinfo <- read.xlsx( "Bexley Exemptions.xlsx" , colNames = FALSE) %>%
-StructureData
-
-#RBKC
-
-Chelseainfo <- read_excel( "Kensington and ChelseaDiscountsLSOA.xlsx" )[,1:4] %>%
-  StructureData()
-
-Chelseainfo2 <- read_excel( "Kensington and ChelseaDiscountsLSOA.xlsx" )[,1:4] %>%
-  StructureData(full= FALSE)
-colSums(Chelseainfo2[,-1])
-
-#Barking
-Barkinginfo <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colNames = FALSE)[,1:4] %>%
-  StructureData(c(2,3,6,7))
-
-#Barnet
-
-Barnetinfo <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
-  StructureData(2:8)
-
-#Newham
-
-Newhaminfo <- read.xlsx( "NewhamDiscountsLSOA.xlsx", colNames = TRUE)[,1:4] %>%
-  StructureData(full = F)
-
-#City of London
-
-CoLinfo <- read_excel("City of LondonExemptionsLSOAApril2017.xlsx" )[,1:4] %>%
-  StructureData(c(2,3,4,13))
-
-#Southwark
-
-Southwarkinfo <- read_excel("Southwark discounts.xlsx")[1:4] %>%
-  StructureData(empty = -c(1,2,5))
-
-#Croydon
-CroydonInfo
+#Source the code from another file as it is very long
+source(file.path(CommonCode, "LondonFullProcesss.R"))
 
@@
 
-#Proper data Barrow
-
-```{r}
-setwd(file.path(RegionsComp, "Region North West"))
-
-list.files()
-
-Barrow <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1) %>% setNames(make.names(names(.))) %>% .[,1:4] %>% filter(Current.Discount.Type.Code !="SINGLE") %>% group_by(LSOA_CODE, Current.Discount.Type.Code) %>%
-  summarise(Empty = n()) %>% 
-  spread(key=Current.Discount.Type.Code, value = Empty, fill = 0 ) %>% ungroup %>%
- mutate( LowUse = rowSums(.[-1]), Empty = LowUse-PCLB0)
-
-Barrow2 <- Barrow %>% 
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
-  mutate(LowUsePerc = LowUse/Homes, EmptyPerc = Empty/Homes)
-
-Barrow3 <- Barrow %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd")) %>% 
-  mutate(LowUsePerc = LowUse/Homes, EmptyPerc = Empty/Homes)
-
-ggplot()+ geom_polygon(data=Barrow2, aes(long, lat, group = group, fill = PCLB0), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")
-```
-
-```{r}
-SLakeland <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-  mutate(Empty = rowSums(.[,2:9])) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% mutate(EmptyPerc = Empty/Homes)
-
-SLakeland2 <- SLakeland %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))
-
-ggplot()+ geom_polygon(data=SLakeland2, aes(long, lat, group = group, fill = EmptyPerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + ggtitle("Barrow in Furness Emptyness %")
-
-bind_rows(Barrow3,SLakeland2) %>%ggplot(.)+ geom_polygon( aes(long, lat, group = group, fill = EmptyPerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2() + 
-  ggtitle("Cumbria Empty Percentage")+
-  theme(axis.title=element_blank(),
-        axis.text=element_blank(),
-        axis.ticks=element_blank())
-
-```
-
-#Cornwall
-
-```{r}
-
-setwd(file.path(RegionsComp, "Region South West"))
-
-Cornwall <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
-  StructureData(lowuse = c(2,23:28))
-
-PlotMap(Cornwall, AG, title = "Lowuse in Cornwall")
-SaveFig("Cornwall.png")
-
-read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
-  StructureData(lowuse = c(2,7:16, 21:28) ) %>%
-  PlotMap(., AG,title = "all empties")
-
-corplotter(Cornwall, "MedianPrice", "WardLowUsePerc", 
-           "Median Price vs Low Use % by ward in Cornwall",
-           "Low Use Percentage by Ward",
-           "Median Price")
-SaveFig("CornCor.png")
-
-```
-
-#Suffolk
-
-```{r}
-
-setwd(file.path(RegionsComp, "Region East of England"))
-list.files()
-
-CoastWave <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
-  mutate(Exemption.type = Exemption.type %>% trimws %>%
-           make.names %>% 
-           gsub("\\.{2,}" , ".", .)) %>%
-  group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
-  spread(key= Exemption.type, value = counts, fill = 0) %>% 
-    setNames(make.names(trimws(names(.)))) %>%
-    mutate(LowUse = rowSums(.[,c(5,6,13,14,16:18)]), Empty = LowUse -Second.Home.Class.A -Second.Home.Class.B) %>%
-  left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% group_by(Admin_ward_code)  %>%
-  mutate(LowUsePerc = LowUse/Homes, WardLowUse = sum(LowUse) ,WardLowUsePerc = WardLowUse/WardHomes) %>% ungroup %>% left_join(., MeanWardPrice) %>% mutate(ValLow = LowUse*MeanPrice)
-
-CoastWave %>% left_join(., AG, by = c("LSOA_CODE" = "lsoa11cd"))  %>% 
-  ggplot(.)+ 
-  geom_polygon( aes(long, lat, group = group, fill = LowUsePerc), 
-colour = alpha("darkred", 1/2), size = 0.2) + scale_colour_gradient2()
-
-#corellation
-CoastWave %>% 
-  #filter(Admin_ward_code !="E05009195") %>% 
-  summarise(x =cor(MeanPrice, WardLowUsePerc, use = 'complete.obs'))
-
- CoastWave %>% ggplot(., aes(y=MeanPrice, x= WardLowUsePerc )) + geom_point() +
-   labs(title = "Coastal and Waveny: Relationship between LowUse\n Percentage and Mean Price in Ward")+
-  theme(plot.title = element_text(hjust = 0.5))
-
-```
-
 #Hull

### 2017-06-25 SubCode/LondonFullProcesss.R

@@ -1,0 +1,115 @@
+#This file loads all the data that has been sent in using the form, and so can be processed quite efficiently
+
+#Lambeth
+
+setwd(file.path(RegionsComp, "Region London"))
+
+Lambethinfo <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
+  StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))
+
+
+test <- Lambethinfo %>% select(LowUsePerc, WardLowUsePerc, LowuseClass, WardLowuseClass)
+
+#Islington is exemptions only
+
+Islingtoninfo <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4]%>%  
+  StructureData(., lowuse = c(2:11,14:18))
+
+#Greenwhich
+
+Greenwichinfo <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>%  
+  StructureData(., c(2,3,4,21,22), c(3,4,21,22))
+
+#Camden
+
+Camdeninfo <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
+  StructureData()
+
+#Bromley
+
+Bromleyinfo <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
+  StructureData(c(6:8,29:31))
+
+#Haringey
+
+
+
+#Haringey is funny and has to be worked over a bit first
+Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)] 
+
+Haringeyinfo <- data_frame(Discount = rep(Haringey$`Exemption./.Discount.type`, Haringey$Count.of.Exemptions.by.Post.Code),
+                           LSOA = rep(Haringey$LSOA_CODE, Haringey$Count.of.Exemptions.by.Post.Code)) %>%
+  mutate( a= NA, b = NA) %>%
+  StructureData(21:25)
+
+
+#Sutton
+
+Suttoninfo <- read_excel("SuttonExemptionsLSOADiscount.xlsx"  )[,c(1,4:6)] %>%
+  StructureData()
+
+#Richmond
+Richmondinfo <- read_csv("Richmond_2.csv" )[1:4]%>%
+  StructureData()
+
+#Hillingdon
+
[…]

### 2017-06-25 LowUseEngland.Rmd
Bootstrap check for regions
Functionalised the class ratio bootstrap and sreamlined the code so it works nicelu in the regions. The results are looking pretty fire

@@
 
-BarrowCumbriaDATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
+BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
   StructureData(.,lowuse = c(2:6,8))
 
-SLakelandCumbriaDATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
+SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
     StructureData(., lowuse=2:9)
@@
 #only inlcudes postcodes so the mergeing needs to be done manually
-CopelandCumbriaDATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
+CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
   mutate(Postcode = sub(" ", "", Postcode)) %>%
@@
 
-EdenCumbriaDATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
+EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
   StructureData(.,lowuse = c(2:6,8))
 
- ls(pattern = "Cumbria") %>% map_df(~eval(parse(text=.x))) %>%
+ ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>%
   PlotMap(., filter(AG,grepl(paste("Barrow-in-Furness", "Allerdale",
@@
 
- ls(pattern = "Cumbria") %>% map_df(~eval(parse(text=.x)))  %>%
+ ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x)))  %>%
 corplotter(., "MedianPrice", "WardLowUsePerc", 
@@
            "Median Price")
+
+ z1<-   ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)
+
+CumbriaStrap <- ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>%
+   DistribCompareBootstrapper(., 1652, 100)
+
+CumbriaStrap %>%
+mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
 
@@
 
+ z1<-   ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)
+
+CornStrap<- ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x))) %>%
+   DistribCompareBootstrapper(., 1652, 1000)
+
+CornStrap %>%
+mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
 ```
@@
 
+ z1<-   ls(pattern = "CoastWave") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)
+
 ```

### 2017-06-25 LowUseLondon.Rmd
Bootstrap check for regions
Functionalised the class ratio bootstrap and sreamlined the code so it works nicelu in the regions. The results are looking pretty fire

@@
 
-test <-  Chelseainfo %>% left_join(., AG)
-
 ```
@@
 
+Chelseainfo %>% filter(LAD11CD =="E09000020") %>%
+  BootStrapTtest(.)
+
 plot(density(colMeans(bootres+ChelMeanPrice)))
-
-#%>% setNames(paste0("samp",.x))
 
@@
 ```{r}
- ChelPrice <- prices %>% 
-  filter( Admin_district_code =="E09000020") %>%
-  select(Admin_ward_code, lsoa11cd, Price =X2) %>%
-  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
-            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
-             right = F))
 
-ChelseainfoWard <- Chelseainfo %>% 
-  group_by(Admin_ward_code) %>%
-  summarise_all(funs(first))
+chelstrap <-  Chelseainfo %>% filter(LAD11CD=="E09000020") %>% 
+  DistribCompareBootstrapper(., 1652, 100)
 
-#bootrapps Chelsea housing stock.
-set.seed(16546)
-ChelseaWardLowUseStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
-  map(~ ChelPrice %>% 
-        filter(Admin_ward_code == .x) %>% 
-  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardLowUse), reps = 10000) %>%
-    mutate(class = as.character(class),
-           Counts = as.integer(Counts),
-           ID = as.integer(ID)) %>%
-      setNames(c("class", paste0("Counts", .x) ,"ID"))
-  ) %>%  
-    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
-  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
-         class = fct_relevel(class, "Upper", after = 2)) %>%
-select(class, ID, Totals)
-
-ChelseaWardHomesStrap2 <- ClassStrapper(ChelPrice, sum(ChelseainfoWard$WardHomes), 10000)
-
-#bootrapps Chelsea housing stock.
-set.seed(16540)
-ChelseaWardHomesStrap1 <- unique(ChelPrice$Admin_ward_code)%>% 
-  map(~ ChelPrice %>% 
-        filter(Admin_ward_code == .x) %>% 
-  ClassStrapper(., sum((filter(ChelseainfoWard, Admin_ward_code == .x))$WardHomes), reps = 10000) %>%
-    mutate(class = as.character(class),
-           Counts = as.integer(Counts),
-           ID = as.integer(ID)) %>%
-      setNames(c("class", paste0("Counts", .x) ,"ID"))
-  ) %>%  
-    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
-  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
-         class = fct_relevel(class, "Upper", after = 2)) %>%
-select(class, ID, Totals)
-
-test1 <- ChelseaWardHomesStrap1  %>% left_join(., ChelseaWardLowUseStrap1, by = c("class", "ID")) %>%
-  rename(LowUse = Totals.y,
-         Homes = Totals.x) %>%
-  group_by(ID)%>%
-  mutate(ratio = LowUse/Homes,
-         HomesPerc = Homes/sum(Homes),
-         LowUsePerc = LowUse/sum(LowUse),
-         ClassPerc = LowUse/Homes,
-         ExpectedHomes = HomesPerc*sum(LowUse),
-         RatioExvsAct = LowUse/ExpectedHomes)
-
-test1 %>% ggplot(., aes(x= class, y = ratio, fill = class)) + geom_boxplot() + 
-  labs(title = "Boxplot of bootstrapped Ratios")
-
-test1 %>%
-mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+chelstrap %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 

### 2017-06-25 Functions/BootStrapTtest.R

@@ -1,0 +1,20 @@
+BootStrapTtest <- function(df, samps = 10000, seed = 1258){
+  #This is a function that bootstraps on the processed data files. NA values will be removed
+  #df: the processed datafile
+  #samples: the number of boostrap resamples
+  #seed: the random seed
+  
+  df <- df %>% filter(!is.na(MeanPrice))
+  
+  dfMeanPrice <- (sum(df$MeanPrice*df$counts)/sum(df$counts))
+  
+  df2<- rep(df$MeanPrice, times = df$LowUse)-dfMeanPrice
+  
+  set.seed(seed)
+  
+  bootres <- 1:samps %>% map(~data.frame(res =sample(df2, length(df2), replace = T))) %>%
+    bind_cols()
+  
+  sum(colMeans(bootres)>0)/samps
+  
+}

### 2017-06-25 Functions/DistribCompareBootstrapper.R

@@ -1,0 +1,65 @@
+
+DistribCompareBootstrapper <-function(df, seed, samples=100){
+#df:data frame of processed area/s data
+#LADCD: The LAD code to fetch the correct price data
+# Random seed
+#Number of Bootstrap samples.
+
+LADCD <- unique(df$LAD11CD)
+  
+dfPrice <- prices %>% 
+  filter( grepl(paste(LADCD, collapse="|"), Admin_district_code)) %>%
+  select(Admin_ward_code, lsoa11cd, Price =X2) %>%
+  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
+                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
+                     right = F))
+
+dfWard <- df %>% 
+  group_by(Admin_ward_code) %>%
+  summarise_all(funs(first))
+
+#bootrapps LAD housing stock.
+set.seed(seed)
+dfWardLowUseStrap1 <- unique(dfPrice$Admin_ward_code)%>% 
+  map(~ dfPrice %>% 
+        filter(Admin_ward_code == .x) %>% 
+        ClassStrapper(., sum((filter(dfWard, Admin_ward_code == .x))$WardLowUse), reps = samples) %>%
+        mutate(class = as.character(class),
+               Counts = as.integer(Counts),
+               ID = as.integer(ID)) %>%
+        setNames(c("class", paste0("Counts", .x) ,"ID"))
+  ) %>%  
+  Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
+  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE),
+         class = fct_relevel(class, "Upper", after = 2)) %>%
+  select(class, ID, Totals)
+
+#bootrapps LAD housing stock.
+set.seed(seed)
+dfWardHomesStrap1 <- unique(dfPrice$Admin_ward_code)%>% 
+  map(~ dfPrice %>% 
+        filter(Admin_ward_code == .x) %>% 
+        ClassStrapper(., sum((filter(dfWard, Admin_ward_code == .x))$WardHomes), reps = samples) %>%
+        mutate(class = as.character(class),
+               Counts = as.integer(Counts),
+               ID = as.integer(ID)) %>%
[…]

### 2017-06-25 SubCode/LondonFullProcesss.R

@@ -37,8 +37,8 @@ Bromleyinfo <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
 #Haringey is funny and has to be worked over a bit first
 Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)] 
 
-Haringeyinfo <- data_frame(Discount = rep(Haringey$`Exemption./.Discount.type`, Haringey$Count.of.Exemptions.by.Post.Code),
-                           LSOA = rep(Haringey$LSOA_CODE, Haringey$Count.of.Exemptions.by.Post.Code)) %>%
+Haringeyinfo <- data_frame(Discount = rep(Haringeyinfo $`Exemption./.Discount.type`, Haringeyinfo$Count.of.Exemptions.by.Post.Code),
+                           LSOA = rep(Haringeyinfo$LSOA_CODE, Haringeyinfo$Count.of.Exemptions.by.Post.Code)) %>%
   mutate( a= NA, b = NA) %>%
   StructureData(21:25)
 

### 2017-06-25 LowUseEngland.Rmd
Include Suffolk data
Suffolk boostrapped

@@
 
+ SuffStrap<- ls(pattern = "CoastWave") %>% map_df(~eval(parse(text=.x))) %>%
+   DistribCompareBootstrapper(., 1652, 1000)
+
+SuffStrap %>%
+mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
 ```

### 2017-06-26 LowUseEngland.Rmd
Code streamline
Ugraded the bootsrapping function so it does both value and class strapping at the same time. 
made a new function that does a value ttest and outputs a bunch of useful stats about the difference between homes and low-use homes.

@@
 
- z1<-   ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)
-
 CumbriaStrap <- ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>%
@@
   labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+Cumbriattest <- ValueTtest(CumbriaStrap)
 
@@
 
-read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
-  StructureData(lowuse = c(2,7:16, 21:28) ) %>%
-  PlotMap(., AG,title = "all empties")
+# read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
+#   StructureData(lowuse = c(2,7:16, 21:28) ) %>%
+#   PlotMap(., AG,title = "all empties")
 
@@
 
- z1<-   ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)
-
-CornStrap<- ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x))) %>%
-   DistribCompareBootstrapper(., 1652, 1000)
+Cornstrap <-DistribCompareBootstrapper(Cornwall, 1652, 100)
 
@@
   labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+Cornttest <- ValueTtest(Cornstrap)
+
+Cornttest$data.frame %>% select(LowUsePrice,HomesPrice) %>%
+  gather(key ="type", "meanprice") %>%
+  ggplot(., aes(x= type, y = meanprice, fill = type)) + geom_boxplot()
 
@@
 
- z1<-   ls(pattern = "CoastWave") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)
-
  SuffStrap<- ls(pattern = "CoastWave") %>% map_df(~eval(parse(text=.x))) %>%
@@
 
+Suffttest <- ValueTtest(SuffStrap)
+
 ```

### 2017-06-26 LowUseLondon.Rmd
Code streamline
Ugraded the bootsrapping function so it does both value and class strapping at the same time. 
made a new function that does a value ttest and outputs a bunch of useful stats about the difference between homes and low-use homes.

@@
 
-#Chelsea sums
+#Chelsea Bootstrapped ratios
 ```{r}
@@
 
-#the data is not normal
-plot(density(v))
-#this prob not valid
-t.test(v,alternative = "greater")
-
-#do a bootstrapped mean to see if it is greater than the mean of the homes overall.
-set.seed(1258)
-samps <-10000
-
-bootres <- 1:samps %>% map(~data.frame(res =sample(v, length(v), replace = T))) %>%
-  bind_cols()
-
-sum(colMeans(bootres)>0)/samps
-
-Chelseainfo %>% filter(LAD11CD =="E09000020") %>%
-  BootStrapTtest(.)
-
-plot(density(colMeans(bootres+ChelMeanPrice)))
-
-prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))
-Admin_ward_code
-#c("Lower Mainstream", "Mid Mainstream", "Upper Mainstream", "Prime", "Super Prime"),
-ClassCountsPerWard <- prices %>% 
-  filter( Admin_district_code =="E09000020") %>%
-  mutate(class = cut(X2, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
-            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
-             right = F)) %>%
-  select(Admin_ward_code, class) %>%
-  group_by(Admin_ward_code, class) %>% 
-  summarise(Counts = n()) %>%
-  group_by(Admin_ward_code) %>%
-  mutate(WardPerc = Counts/sum(Counts)) %>%
-  ungroup
-
-test3 <- Chelseainfo %>% 
-  group_by(Admin_ward_code) %>%
-  summarise_all(funs(first)) %>%
-  select(Admin_ward_code, WardLowUse, WardHomes) %>%
-  left_join(., ClassCountsPerWard, "Admin_ward_code") %>%
-  mutate(LowUseClass = WardLowUse*WardPerc,
-         HomesClass = WardHomes*WardPerc) %>%
-  group_by(class) %>%
-  summarise(LowUseClass = sum(LowUseClass),
-            HomesClass = sum(HomesClass)) %>%
-  filter(complete.cases(.)) %>%
-  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
-         PercOfHomes = HomesClass/sum(HomesClass),
-         PercofClass = LowUseClass/HomesClass,
-         `Expected Homes` = PercOfHomes*sum(LowUseClass),
-         `Actual Homes` = LowUseClass)
-
-sum(test3$LowUseClass)*test3$PercOfHomes
-
-#Percentage over and under of what would be expected if buying was random
-#The differences suggest that people are buying more expensive homes when there is no plan to live in them.
-round(test3$LowUseClass/(sum(test3$LowUseClass)*test3$PercOfHomes),2)
-
-ggplot(test3, aes(x= class, y = PercOfHomes*100)) +geom_bar(stat = "identity") + 
-  labs(title = "Distribution probability of homes in each class", y = "Percentage")
-
-test3 %>%
-  select(class, `Expected Homes`, `Actual Homes`) %>%
-  gather(key = "Type" , value = "Number", -class) %>%
-  ggplot(., aes(x= class, y = Number, fill = Type)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  labs(title = "Expected Number of low-use homes in each class")
-
-test3 %>%
-  mutate(`Percentage Difference` = (`Actual Homes`/`Expected Homes`)*100-100) %>%
-  ggplot(., aes(x= class, y = `Percentage Difference`)) +
-  geom_bar(stat = "identity") +
-  labs(title = "Percentage difference between expected number of homes per class and actual")+
-  coord_cartesian(ylim=c(-20,20))
-
-```
-
-#Chelsea Bootstrapped ratios
-
-```{r}
-
 chelstrap <-  Chelseainfo %>% filter(LAD11CD=="E09000020") %>% 
-  DistribCompareBootstrapper(., 1652, 100)
+  DistribCompareBootstrapper(., 1652, 1000)
 
@@
 
-test1 %>% group_by(class) %>%
-  summarise_all(funs(mean))
+ Chelttest <- ValueTtest(chelstrap)
 

### 2017-06-26 Functions/ClassStrapper.R

@@ -17,12 +17,12 @@ ClassStrapper <- function(PriceData, LowUseCounts, reps = 1000){
   # )
   # 
   
-    Out <- 1:reps %>% map_df(~PriceData[,"class"] %>% 
-                             sample_n(., LowUseCounts, replace = TRUE) %>%
-                             group_by(class) %>%
-                             summarise(Counts = n()) %>%
-                             mutate(ID = .x)
-  )
-  
+    Out <- 1:reps %>% map_df(~PriceData %>% 
+                               sample_n(., LowUseCounts, replace = TRUE) %>%
+                               group_by(class) %>%
+                               summarise(Counts = n(),
+                                         Value = sum(Price)) %>%
+                               mutate(ID = .x)
+    )
   return(Out)
 }

### 2017-06-26 Functions/ValueTtest.R

@@ -1,0 +1,24 @@
+ValueTtest <- function(df){
+#Performs a t test on the results of the bootstrapping function
+  #df: the output from the boostrapping function
+  #the percentage difference is relative to regular homes so positvevalue means lowuse more expensive
+  
+  test <- df %>% 
+    select(ID, Homes, LowUse, HomesValue, LowUseValue) %>%
+    group_by(ID) %>%
+    summarise_all(funs(sum)) %>%
+    mutate(HomesPrice = HomesValue/Homes,
+           LowUsePrice = LowUseValue/LowUse)
+  
+  res1 <- t.test(x= test$LowUsePrice, y= test$HomesPrice, alternative = "greater")
+  
+  HomePrice <- (sum(test$HomesValue, na.rm = TRUE)/sum(test$Homes, na.rm = TRUE))
+  LowUsePrice <- (sum(test$LowUseValue, na.rm = TRUE)/sum(test$LowUse, na.rm = TRUE))
+  
+  res2 <- (LowUsePrice - HomePrice)
+  res3 <- res2/HomePrice
+  
+  Out <-list(test, res1, res2, res3)
+  names(Out) <- c("data.frame", "t.test", "absdiff", "Percdiff")
+  return(Out)
+}

### 2017-06-26 LowUseEngland.Rmd
Fixing some bugs
there were all kinds of wied going on ... I think this has fixed it.

@@
 
+CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
+  StructureData(.)
+
  ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>%
@@
 Cumbriattest <- ValueTtest(CumbriaStrap)
+
+(218977.5-  184071.4 )/184071.4
 
@@
 
-Hull
+#Hull
+```{r}
+
+Hull <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
+                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
+  StructureData(.)
+
+PlotMap(Hull, AG, variable = "WardLowUsePerc")
+
+corplotter(Hull, "MedianPrice", "WardLowUsePerc", 
+           "Median Price vs Low Use % by ward in Hull",
+           "Low Use Percentage by Ward",
+           "Median Price")
+
+ HullStrap<-  DistribCompareBootstrapper(Hull, 1652, 1000)
+
+ HullStrap %>%
+mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+HullStrap <- ValueTtest(HullStrap)
+
+```

### 2017-06-26 LowUseLondon.Rmd
Fixing some bugs
there were all kinds of wied going on ... I think this has fixed it.

@@
 
+ 1762724.8-  426694.1
+
+   test <- chelstrap %>% 
+    select(class,ID, Homes, LowUse, HomesValue, LowUseValue) %>%
+    group_by(ID, class) %>%
+    summarise_all(funs(sum)) %>%
+    mutate(HomesPrice = HomesValue/Homes,
+           LowUsePrice = LowUseValue/LowUse)
+
+ggplot(test, aes(x= class, y = LowUsePrice, fill = class)) + geom_boxplot()
+ ggplot(test, aes(x= class, y = HomesPrice, fill = class)) + geom_boxplot()
+
+  ggplot(test, aes(x= log(LowUsePrice), y = log(HomesPrice), colour = class)) + geom_point()  
 ```
@@
 
-Hull <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
-                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
-  StructureData(.)
+LambethStrap<-  Lambethinfo %>% filter(LAD11CD == "E09000022") %>% 
+  DistribCompareBootstrapper(., 1652, 100)
 
-PlotMap(Hull, AG, variable = "WardLowUsePerc")
+LambethStrap %>%
+mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
 
-corplotter(Hull, "MedianPrice", "WardLowUsePerc", 
-           "Median Price vs Low Use % by ward in Hull",
-           "Low Use Percentage by Ward",
-           "Median Price")
+#Why are lambteths results junk?
+LamStrap <- ValueTtest(LambethStrap)
+
+df <- LambethStrap
+
+CamdenStrap<-  DistribCompareBootstrapper(Camdeninfo, 1652, 1000)
+
+CamdenStrap %>%
+mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+#Why are lambteths results junk?
+Camttest<- ValueTtest(CamdenStrap)
+
+PlotMap(Camdeninfo,AG)
+
 ```

### 2017-06-26 Functions/DistribCompareBootstrapper.R

@@ -16,7 +16,7 @@ dfPrice <- prices %>%
 
 dfWard <- df %>% 
   group_by(Admin_ward_code) %>%
-  summarise_all(funs(first))
+  summarise_all(funs(first)) %>% filter(!is.na(Admin_ward_code))
 
 print("Start Bootstrapping LSOA distribution")
 
@@ -45,7 +45,7 @@ set.seed(seed)
 dfWardHomesStrap1 <- unique(dfPrice$Admin_ward_code)%>% 
   map(~ dfPrice %>% 
         filter(Admin_ward_code == .x) %>% 
-        ClassStrapper(., sum((filter(dfWard, Admin_ward_code == .x))$WardHomes), reps = samples) %>%
+         ClassStrapper(., sum((filter(dfWard, Admin_ward_code == .x))$WardHomes), reps = samples) %>%
         mutate(class = as.character(class),
                Counts = as.integer(Counts),
                ID = as.integer(ID)) %>%
@@ -60,20 +60,30 @@ dfWardHomesStrap1 <- unique(dfPrice$Admin_ward_code)%>%
 
 print("LAD distribution Complete")
 
-test1 <- dfWardHomesStrap1  %>% left_join(., dfWardLowUseStrap1, by = c("class", "ID")) %>%
-  rename(LowUse = Counts.y,
+test1 <- dfWardHomesStrap1  %>% 
+  left_join(., dfWardLowUseStrap1, by = c("class", "ID")) %>%
+  rename(LowUse = Counts.y, 
          Homes = Counts.x,
          LowUseValue = Value.y,
          HomesValue = Value.x,
          LowUsePrice = Price.y,
-         HomesPrice =  Price.x) %>%
+         HomesPrice =  Price.x) 
+
+#NA values were causing N issues all over the place, the NA's were caused by low levels of super prime, 
+#I have put the ifelse in to convert any NA values into 0, also in the sum function, overkill but whatever
+
+test1 <- test1%>%
   group_by(ID)%>%
-  mutate(ratio = LowUse/Homes,
-         HomesPerc = Homes/sum(Homes),
-         LowUsePerc = LowUse/sum(LowUse),
+  mutate(LowUse = ifelse(is.na(LowUse), 0, LowUse),
+         LowUseValue = ifelse(is.na(LowUseValue), 0, LowUseValue),
+         HomesValue = ifelse(is.na(HomesValue), 0, HomesValue),
[…]

### 2017-06-27 LowUseLondon.Rmd
UPdateed leaflet plotter
Creates a leaflet plot automatically subsetting the spatial dataframe. this is helpful as it allows multiple LADs to be plotted at once, e.g the whole of Cumbria.

@@
 
+#percent of chelsea low-use
 sum(Chelseainfo$LowUse)/sum(Chelseainfo$Homes)
-
-#T test if there is a significant difference between 
-v <- Chelseainfo %>% filter(LAD11CD =="E09000020")
 
@@
 ChelMeanPrice <- (sum(v$MeanPrice*v$counts)/sum(v$counts))
-ChelLowMean<- sum(v$MeanPrice*v$LowUse)/sum(v$LowUse)
-ChelLowMean/ChelMeanPrice
-v<- rep(v$MeanPrice, times = v$LowUse)-ChelMeanPrice
 
@@
 
- 1762724.8-  426694.1
+ #boxplot comparison
+Chelttest$data.frame %>%
+  select(HomesPrice, LowUsePrice) %>%
+  gather(key ="type", value = "MeanPrice") %>%
+ggplot(., aes(x= type, y = MeanPrice, fill = type)) + geom_boxplot()
 
-   test <- chelstrap %>% 
-    select(class,ID, Homes, LowUse, HomesValue, LowUseValue) %>%
-    group_by(ID, class) %>%
-    summarise_all(funs(sum)) %>%
-    mutate(HomesPrice = HomesValue/Homes,
-           LowUsePrice = LowUseValue/LowUse)
+#density plot comparison
+Chelttest$data.frame %>%
+  select(HomesPrice, LowUsePrice) %>%
+  gather(key ="type", value = "MeanPrice") %>%
+ggplot(., aes(x = MeanPrice, fill = type)) + geom_density()
 
-ggplot(test, aes(x= class, y = LowUsePrice, fill = class)) + geom_boxplot()
- ggplot(test, aes(x= class, y = HomesPrice, fill = class)) + geom_boxplot()
-
-  ggplot(test, aes(x= log(LowUsePrice), y = log(HomesPrice), colour = class)) + geom_point()  
 ```

### 2017-06-27 PlotwithLeaflet.Rmd
Fixing some bugs
there were all kinds of wied going on ... I think this has fixed it.
UPdateed leaflet plotter
Creates a leaflet plot automatically subsetting the spatial dataframe. this is helpful as it allows multiple LADs to be plotted at once, e.g the whole of Cumbria.

@@
 setwd(gitpage)
-z <- MakeLeaflet("chelsea", Chelseainfo)
+z <- MakeLeaflet(Chelseainfo)
 z
@@
 
-z<- MakeLeaflet("lambeth", Lambethinfo, c(0:5))
+z<- MakeLeaflet(Lambethinfo, c(0:5))
 saveWidget(z, file="LambethLowUSe.html", selfcontained = TRUE )
@@
 mapshot(z, url = paste0(getwd(), "/map.html"))
+```
+
+```{r}
+z <- MakeLeaflet(Camdeninfo)
+z
+saveWidget(z, file="CamdenLowUse.html", selfcontained = TRUE )
 ```

### 2017-06-27 Functions/DistribCompareBootstrapper.R

@@ -12,8 +12,8 @@ dfPrice <- prices %>%
   select(Admin_ward_code, lsoa11cd, Price =X2) %>%
   mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
                      labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
-                     right = F))
-
+                     right = F),
+         Price = as.numeric(Price)) #there was some number overflow thing changing to numeric solves this
 dfWard <- df %>% 
   group_by(Admin_ward_code) %>%
   summarise_all(funs(first)) %>% filter(!is.na(Admin_ward_code))

### 2017-06-27 LowUseEngland.Rmd
UPdateed leaflet plotter
Creates a leaflet plot automatically subsetting the spatial dataframe. this is helpful as it allows multiple LADs to be plotted at once, e.g the whole of Cumbria.
Final Pre Blog
Last update before publsihing the 3rd blog

@@
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+  labs(title = "Cumbria", y = "% difference from expected")
+SaveFig("CumbriaDistributionPlot.png")
 
@@
 
-(218977.5-  184071.4 )/184071.4
+z <- ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x))) %>% MakeLeaflet(.)
+z
+saveWidget(z, file=file.path(gitpage, "CumbriaLowUse.html"), selfcontained = TRUE )
 
@@
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+  labs(title = "Cornwall", y = "% difference from expected")
+SaveFig("CornwallDistributionPlot.png")
 
@@
   ggplot(., aes(x= type, y = meanprice, fill = type)) + geom_boxplot()
+
+z <- MakeLeaflet(Cornwall)
+z
+saveWidget(z, file=file.path(gitpage, "CornwallLowUse.html"), selfcontained = TRUE )
 
@@
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+  labs(title = "Coastal Suffolk", y = "% difference from expected")
+SaveFig("CoastSuffDistributionPlot.png")
 
 Suffttest <- ValueTtest(SuffStrap)
+
+z <- MakeLeaflet(CoastWave)
+z
+saveWidget(z, file=file.path(gitpage, "CoastSuffLowUse.html"), selfcontained = TRUE )
 
@@
  HullStrap %>%
-mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+  labs(title = "Cumbria", y = "% difference from expected")
+SaveFig("HullDistributionPlot.png")
 
-HullStrap <- ValueTtest(HullStrap)
+HullTtest <- ValueTtest(HullStrap)
+
+z <- MakeLeaflet(Hull)
+z
+saveWidget(z, file=file.path(gitpage, "HullLowUse.html"), selfcontained = TRUE )
 

### 2017-07-06 LowUseEngland.Rmd
All kinds of debug

@@
 ---
+
+housing studies
+internat jouranl housing policy
+
+becky tunstall housing space inequality
+
+niall may - between 1990 - 1995 hoomes built loads of homes built small number owned
+
+positive money
 
@@
 saveWidget(z, file=file.path(gitpage, "CumbriaLowUse.html"), selfcontained = TRUE )
+
+```
+
+#business rates
+```{r}
+setwd(file.path(basewd, "Business rates"))
+SlakelBuss <- read_csv("sldc-business-rates-full-list-07042017.csv")
+
+test <- SlakelBuss %>% group_by(PropertyDescription) %>% 
+  summarise(counts = n())
+
+test2 <- test %>% filter(grepl("SELF", PropertyDescription))
+
+test2$counts %>% sum
+
+SlakelBuss<-SlakelBuss %>% 
+  rename(Postcode = PropPostCode) %>%
+  mutate(Postcode = gsub(" ", "" , Postcode)) %>%
+  filter(grepl("SELF", PropertyDescription)) %>% left_join(., PstCdLSOA.raw, by = "Postcode") %>%
+    mutate(LSOA_CODE = lsoa11cd,
+         `Exemption type` = "Discount Class B (Furnished & Unocc)") %>%
+  select(LSOA_CODE, `Exemption type`)
+
+    test <- SlakelBuss %>% group_by(LSOA_CODE) %>%
+    summarise(HomesB = n())
+
+#several hundred un-matchable postcodes
+test2 <- SlakelBuss%>% 
+  mutate(testme = is.na(lsoa11cd)) %>%
+  group_by(AccountName, testme) %>% 
+  summarise(count = n()) %>%
+  rename
+
+setwd(file.path(RegionsComp, "Region North West"))
+SLakelandCUMBRIADATA2 <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
+  bind_rows(SlakelBuss) %>%
+    StructureData(., lowuse=2:9)
+
+SLakelandCUMBRIADATA3 <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
+    StructureData2(., lowuse=2:9, Business = SlakelBuss)
+
+MakeLeaflet(SLakelandCUMBRIADATA2)
+
+MakeLeaflet(SLakelandCUMBRIADATA3)
+
+plot(SLakelandCUMBRIADATA$LowUsePerc,SLakelandCUMBRIADATA3$LowUsePerc)
+
+test <- data.frame(Biz =SLakelandCUMBRIADATA3$LowUsePerc, Norm = SLakelandCUMBRIADATA$LowUsePerc ) %>%
+  mutate(diff = Biz-Norm)
+
+test %>% ggplot(aes(x= diff)) + geom_density()
 

### 2017-07-06 LowUseLondon.Rmd
Final Pre Blog
Last update before publsihing the 3rd blog
All kinds of debug

@@
 #All London With missing Boroughs
-PlotMap(Lambethinfo, AG)
+PlotMap(Hammersmithinfo, AG)
+
+ test <- list("Hammersmithinfo", "Chelseainfo") %>% map_df(~eval(parse(text=.x)))
+
+ Hammersmithinfo %>% filter(LSOA_CODE!="E01001866") %>% 
+   bind_rows(Chelseainfo) %>%
+   MakeLeaflet(.)
+
+ PlotMap(test, AG)
+test %>% MakeLeaflet(.)
+
+test2 <- filter(test, LSOA_CODE=="E01001866")
 
@@
 
-#Hammersmith 
-Hammersmithinfo <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
-  bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
-  mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`) %>%
-  SemiDataStructure
+# #Hammersmith 
+# Hammersmithinfo <- read_excel("Hammersmith.xls", skip = 1 ) %>% filter(!is.na(Ward) ) %>% 
+#   bind_cols(., filter(wardnames,LAD11NM == "Hammersmith and Fulham")) %>% select(-Ward) %>%
+#   mutate(LowUse = `Second (B)` + `Empty Unocc`+ LTE + Premium, Empty = LowUse - `Second (B)`) %>%
+#   SemiDataStructure
 
@@
 
-#Hull
 ```{r}

### 2017-07-06 PaperCode.Rmd
All kinds of debug

---
title: "Untitled"
author: "Jonathan Bourne"
date: "5 July 2017"
output: html_document
---

```{r setup}
setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)
```

```{r}
source(file.path(CommonCode, "AuxdataLoad.R"))
```

Cumbria
```{r}
setwd(file.path(RegionsComp, "Region North West"))

BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
  StructureData(.,lowuse = c(2:6,8))

SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
    StructureData(., lowuse=2:9)

#only inlcudes postcodes so the mergeing needs to be done manually
CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData()

EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.,lowuse = c(2:6,8))

CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(.)

```

#Manchester

```{r}
list.files()

OldhamMANCDATA <- read_excel("FOI 10635 OldhamDiscounts LSOA.xlsx", sheet = 1 )[c(1,4:6)] %>%  
  StructureData(., c(5:6,8:11))

ManchesterMANCDATA <- read_excel("ManchesterDiscountsLSOA.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

RochdaleMANCDATA <- read_excel("Rochdale Both.xlsx" , sheet = 1 )[1:4] %>%  
  StructureData(., c(5,6,14,15,20:22))

TamesideMANCDATA <- read_excel("Tameside FOI 6257A2.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(. )

TraffordMANCDATA <- read_excel("Trafford Exemption and Levy.xlsx" , sheet = 1 )[1:4] %>%
  filter(Exemption_type =="LEVY") %>% 
  bind_rows(.,read_excel("TraffordDiscountsLSOA.XLSX", sheet = 1 )[1:4] %>% rename(Exemption_type = Class)) %>%
  StructureData()

WiganMANCDATA <- read_excel("Wigan 5528 DISCOUNTS.xlsx", sheet = 1 )[1:4] %>%  
  StructureData(., lowuse = c(2:3, 5:9) )

ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)

```

#Cornwall

```{r}

setwd(file.path(RegionsComp, "Region South West"))

CornwallDATA <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,23:28))
```

Suffolk

```{r}
setwd(file.path(RegionsComp, "Region East of England"))
list.files()

#Serparete in to the two LADS
CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
  mutate(Exemption.type = Exemption.type %>% trimws %>%
           make.names %>% 
           gsub("\\.{2,}" , ".", .))  %>%
  StructureData(., lowuse = c(5,6,13,14,16:18))

```

#Hull
```{r}

HullDATA <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
  StructureData(.)

```

# London using the full data

```{r}
#Source the code from another file as it is very long
source(file.path(CommonCode, "LondonFullProcesss.R"))

```

#Semi data

The LSOA will be assigned empty and low use homes by percentage

```{r}
#ward folder
setwd(SemiLondon)

wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)

test <- wardnames %>% filter(grepl("Kensington", LAD11NM))

test <- EW2 %>% filter(LAD11NM == "Wandsworth")

#Wandsworth

WandsworthDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
  arrange(`Ptc Wardname`) %>% 
  filter(!is.na(`Ptc Wardname`)) %>% 
  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
              select(Admin_ward_code)) %>%
  mutate(LowUse = Empty) %>%
  SemiDataStructure

#Merton

MertonDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
  SemiDataStructure

#Kingston

KingstonDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
  arrange(X__1) %>% slice(1:16) %>%
  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
              select(Admin_ward_code)) %>%
  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
  SemiDataStructure

#TowerHamlets
TowerDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
  filter(!is.na(DiscClass)) %>%
  group_by(Ward, DiscClass) %>%
  summarise(count = n()) %>% ungroup %>%
  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
  slice(c(1:13, 15:17, 14, 18:20)) %>%
   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
  SemiDataStructure

```

General Stats
```{r}

ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
  summarise(LowUse = sum(LowUse, na.rm = T),
           Homes = sum(Homes, na.rm = T))

```

#Plot stuff
```{r}
x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA) %>% MakeLeaflet

MakeLeaflet(IslingtonLONDATA)
```

#Bootstrap

Now all the data is loaded each LAD needs to be bootstrapped

```{r}

setwd(basewd)
#Boostrap each LAD
BootStrapRES <- ls(pattern = "DATA") %>% map(~{print(.x)
  DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})

saveRDS(BootStrapRES, file = "BootStrapRES.rds")

```

#Analyse Boostrap

```{r}
#Give the resulting list the name of each LAD
elementnames <- sub("DATA", "", ls(pattern = "DATA"))

names(BootStrapRES)<- elementnames

#Perform the t-test on the resulting lists
TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
#Tidy results of thejust the ttest
TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
  mutate(LAD = elementnames,
         absdiff = TtestRES %>% map_dbl(~.x$absdiff),
         Percdiff = TtestRES %>% map_dbl(~.x$Percdiff))

#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
TtestRES2 %>% ggplot(.,aes(x= absdiff, y = Percdiff)) + geom_point() 
TtestRES2 %>% ggplot(.,aes(x= absdiff, y = p.value)) + geom_point()
TtestRES2 %>% ggplot(.,aes(x= Percdiff, y = p.value)) + geom_point()

#Perform ANOVA on the difference between the ratios of the groups on the bootrapped list
ANOVARES <- BootStrapRES %>% 
  map_df(~aov(.x$RatioExvsAct~.x$class) %>% tidy) %>% 
  filter(term != "Residuals") %>%
  select(-term) %>%
  mutate(LAD = elementnames)

WardData <- ls(pattern = "DATA") %>%
  map_df(~eval(parse(text=.x)) %>%
           select(WardLowUsePerc) %>%
        mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
          summarise( maxPerc = max(WardLowUsePerc),
          minPerc = min(WardLowUsePerc),
          diffPerc = maxPerc-minPerc,
          LAD = sub("DATA", "", .x)))

skew <- BootStrapRES %>% map_df(~.x %>% group_by(class) %>%
  summarise(skew = mean(RatioExvsAct, na.rm = TRUE)) %>%
  summarise(skew = skewness(skew))
)

Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% bind_cols(skew)

#look at specific data
BootStrapRES$Redbridge %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
```

```{r}

Combine1 <- left_join(Combine1, WardData,by = "LAD" )

Combine1 %>% ggplot(.,aes(x= maxPerc, y = abs(Percdiff))) + geom_point()

#P value has an exponential decay
Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = p.value.y)) + geom_point()

#P.value is low if diff perc is over 5%
#Both southwark and Tower of london have concil flat renovation?
#Southwark the Aylesbury estate is being redeveloped maing emptyness much higher than expected
#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
Combine1 %>% ggplot(.,aes(x= diffPerc, y = p.value.y)) + geom_point()

test <- Combine1 %>%
  select(LAD, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)

Combine1 %>% ggplot(.,aes(x= skew, y= p.value.y)) + geom_point()

```

```{r}

test <- Combine1 %>% filter(p.value.y>0.05)
```

### 2017-07-06 Functions/MakeLeaflet.R

@@ -1,5 +1,19 @@
 MakeLeaflet <-function(dataframe, bins = c(0, 10, 20, 25, 100)){
 
+  #These two functions are necessary for Points to polygons
+  get.grpPoly <- function(group,ID,df) {
+    Polygon(coordinates(df[df$id==ID & df$group==group,]))
+  }
+  get.spPoly  <- function(ID,df) {
+    Polygons(lapply(unique(df[df$id==ID,]$group),get.grpPoly,ID,df),ID)
+  }
+  
+  #this function is necessary for the rest of the function
+  points2polygons <- function(df,data) {
+    spPolygons  <- SpatialPolygons(lapply(unique(df$id),get.spPoly,df))
+    SpatialPolygonsDataFrame(spPolygons,match.ID=T,data=data)
+  }
+  
   MyData <- AG %>% filter(AG$LAD11CD %in%  unique(dataframe$LAD11CD) ) %>%
     rename(LSOA_CODE = lsoa11cd)
   

### 2017-07-06 Functions/StructureData2.R

@@ -1,0 +1,61 @@
+StructureData2 <- function(df, lowuse = NULL, empty = NULL, full = TRUE, Business = NULL ){
+  #Provides a standardised way of cleaning the data
+  #df: data frame of the laoded excel template with only the first 4 columns
+  #full: do you want the whole process or partial. a partial process is required to dins out
+  #which columns are used for empty and low use.
+  #lowuse: the columns of the spread dataframe that contain the discounts used for low use homes
+  #empty: Columns used to identityf empty homes. if NULL defaults to the lowuse ones
+  
+  if(is.null(lowuse)){
+    lowuse <- -1
+  } else {
+    lowuse <- lowuse
+  }
+  
+  if(is.null(empty)){
+    empty <-  lowuse
+  } else {
+    empty <- empty
+  }
+  
+  if(!is.null(Business)){
+    df <- df %>% bind_rows(SlakelBuss)
+    
+    Business2 <- Business %>% group_by(LSOA_CODE) %>%
+    summarise(HomesB = n()) 
+  }
+  
+  df <- df %>%
+    setNames(c("Exemption.type", "LSOA_CODE", "X3", "X4")) %>%
+    group_by(Exemption.type, LSOA_CODE) %>% summarise(counts = n()) %>% 
+    spread(key= Exemption.type, value = counts, fill = 0) %>% 
+    setNames(make.names(trimws(names(.))))
+  
+  if(full){
+    df <- df%>%
+      mutate(LowUse = rowSums(.[,lowuse]), 
+             Empty = rowSums(.[,empty])) %>%
+      left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
+      group_by(Admin_ward_code)  
+  
+    if(!is.null(Business)){
+      df <- df %>% left_join(Business2, by="LSOA_CODE") %>%
+        mutate(HomesB = as.numeric(HomesB),
+          HomesB = ifelse(is.na(HomesB), 0, HomesB),
+          Homes = Homes + HomesB) 
+       }
+    
+    df<- df %>%
+      mutate(LowUsePerc = round(LowUse/Homes *100), 
+             WardLowUse = sum(LowUse) ,
+             WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
+      ungroup %>% 
+      left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
+      mutate(ValLow = LowUse*MeanPrice,
[…]

### 2017-07-06 Functions/ValueTtest.R

@@ -1,4 +1,4 @@
-ValueTtest <- function(df){
+ValueTtest <- function(df, alternative = "greater"){
 #Performs a t test on the results of the bootstrapping function
   #df: the output from the boostrapping function
   #the percentage difference is relative to regular homes so positvevalue means lowuse more expensive
@@ -11,12 +11,15 @@ ValueTtest <- function(df){
     mutate(HomesPrice = HomesValue/Homes,
            LowUsePrice = LowUseValue/LowUse)
   
-  res1 <- t.test(x= test$LowUsePrice, y= test$HomesPrice, alternative = "greater")
+  res1 <- t.test(x= test$LowUsePrice, y= test$HomesPrice, alternative)
   
   HomePrice <- (sum(test$HomesValue, na.rm = TRUE)/sum(test$Homes, na.rm = TRUE))
   LowUsePrice <- (sum(test$LowUseValue, na.rm = TRUE)/sum(test$LowUse, na.rm = TRUE))
   
+  #difference between low use price and home price
   res2 <- (LowUsePrice - HomePrice)
+  
+  #percentage difference of above
   res3 <- (res2/HomePrice)*100
   
   Out <-list(test, res1, res2, res3)

### 2017-07-06 SubCode/LondonFullProcesss.R

@@ -4,30 +4,30 @@
 
 setwd(file.path(RegionsComp, "Region London"))
 
-Lambethinfo <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
+LambethLONDATA <- read_excel("LambethExemptionsLSOA.xlsx")[,1:4] %>%  
   StructureData(., lowuse = c(2:5,24,25), empty =  c(4:5,24,25))
 
 
-test <- Lambethinfo %>% select(LowUsePerc, WardLowUsePerc, LowuseClass, WardLowuseClass)
+test <- LambethLONDATA %>% select(LowUsePerc, WardLowUsePerc, LowuseClass, WardLowuseClass)
 
 #Islington is exemptions only
 
-Islingtoninfo <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4]%>%  
+IslingtonLONDATA <- read_csv("IslingtonExemptionsLSOA as at 2017 03 24.csv"  )[1:4]%>%  
   StructureData(., lowuse = c(2:11,14:18))
 
 #Greenwhich
 
-Greenwichinfo <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>%  
+GreenwichLONDATA <- read_excel( "Royal Borough Of Greenwich.xlsx")[1:4] %>%  
   StructureData(., c(2,3,4,21,22), c(3,4,21,22))
 
 #Camden
 
-Camdeninfo <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
+CamdenLONDATA <- read.xlsx("Camden Discounts LSOA - 20891480.xlsx" )[,1:4] %>%
   StructureData()
 
 #Bromley
 
-Bromleyinfo <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
+BromleyLONDATA <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
   StructureData(c(6:8,29:31))
 
 #Haringey
@@ -35,81 +35,82 @@ Bromleyinfo <- read.xlsx("Copy of BromleyExemptionsLSOA.xlsx")[,c(1,4:6)] %>%
 
 
 #Haringey is funny and has to be worked over a bit first
-Haringeyinfo <- read.xlsx("Haringey_Exemptions_Discounts_LSOA.xlsx")[c(1,3,5)] 
[…]

### 2017-07-06 SubCode/Setup.R

@@ -2,7 +2,7 @@
 
 
 packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
-              "forcats")
+              "forcats", "e1071")
 
 new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
 if(length(new.packages)) install.packages(new.packages)

### 2017-07-13 LowUseLondon.Rmd
Addin stats
Added in some general stats about the data, and also included a few new LADs. Removed Islington until they give me proper data

@@
 
-test <-  ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
+test <-  ls(pattern = "LON") %>% map_df(~eval(parse(text=.x))) %>%
   group_by(Admin_ward_code) %>%
@@
 
- ls(pattern = "info") %>% map_df(~eval(parse(text=.x))) %>%
+ ls(pattern = "LON") %>% map_df(~eval(parse(text=.x))) %>%
   PlotMap(., filter(AG, RGN15NM=="London"), 

### 2017-07-13 PaperCode.Rmd
Addin stats
Added in some general stats about the data, and also included a few new LADs. Removed Islington until they give me proper data

@@
 
+Islington should be removed and put back in when they send the correct data, it is giving a false negative
+
 ```{r setup}
@@
 list.files() %>% map(source)
+
+Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
 ```
@@
 
-Cumbria
+#Cumbria
 ```{r}
@@
 
-Suffolk
+#Suffolk
 
@@
 #Serparete in to the two LADS
-CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
+# CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
+#   mutate(Exemption.type = Exemption.type %>% trimws %>%
+#            make.names %>% 
+#            gsub("\\.{2,}" , ".", .))  %>%
+#   StructureData(., lowuse = c(5,6,13,14,16:18))
+
+CoastSUFFDATA <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
+  mutate(Exemption.type = Exemption.type %>% trimws %>%
+           make.names %>% 
+           gsub("\\.{2,}" , ".", .))  %>%
+  StructureData(.,c(5,6,11,12,14:16))
+
+WaveneySUFFDATA <- read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
   mutate(Exemption.type = Exemption.type %>% trimws %>%
@@
   StructureData(., lowuse = c(5,6,13,14,16:18))
+
+```
+
+#Cambridge
+```{r}
+EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
+  StructureData()
+
+```
+
+#Brightong and Hove
+
+```{r}
+
+setwd(file.path(RegionsComp, "Region South East"))
+list.files()
+
+BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
+  StructureData(lowuse = 2:8)
+
+#MakeLeaflet(BrightonDATA)
 
@@
 
+#MakeLeaflet(NewhamLONDATA)
+
 ```
@@
 
-test <- wardnames %>% filter(grepl("Kensington", LAD11NM))
-
-test <- EW2 %>% filter(LAD11NM == "Wandsworth")
-
 #Wandsworth
 
-WandsworthDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
+WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
   group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
@@
 
-MertonDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
+MertonLONDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
   filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
@@
 
-KingstonDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
+KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
   arrange(X__1) %>% slice(1:16) %>%
@@
 #TowerHamlets
-TowerDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
+TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
   filter(!is.na(DiscClass)) %>%
@@
 General Stats
+#UK population
+
 ```{r}
 
+#number of LUPS and Total Homes
 ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
-  summarise(LowUse = sum(LowUse, na.rm = T),
-           Homes = sum(Homes, na.rm = T))
+  summarise(
+           TotalLads = length(unique(LAD11CD)),
+           LowUse = sum(LowUse, na.rm = T),
+           Homes = sum(Homes, na.rm = T),
+           PercHomes = Homes/sum(EW2$Homes),
+           Population = sum(Pop, na.rm= T),
+           Poperc = Population/sum(EW2$Pop))
+
+#Percentage of EW LADS
+length(ls(pattern = "DATA"))/(EW2$LAD11NM %>% unique %>% length())
 
@@
 ```{r}
-x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA) %>% MakeLeaflet
+x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet
 
-MakeLeaflet(IslingtonLONDATA)
+#MakeLeaflet(SouthwarkLONDATA)
+
+#testSouth <- DistribCompareBootstrapper(SouthwarkLONDATA, 1652, 1000)
+testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+ValueTtest(test)
+
 ```
@@
 #Boostrap each LAD
+elementnames <- sub("DATA", "", ls(pattern = "DATA"))
+
+if(file.exists("BootStrapRES.rds")){
+ #this sectio of code loads the old list and appends the new LADs
+
+  BootStrapRES<- readRDS("BootStrapRES.rds")
+  newLADsnames <- sub("DATA", "", ls(pattern = "DATA")) %>% 
+  .[!(. %in% names(BootStrapRES))] 
+  newLADs <- paste0(newLADsnames, "DATA")
+
+    #only bootstrap if there is something to add.
+    if(length(newLADsnames)>0){
+       newLADsBoot <- newLADs  %>% map(~{print(.x)
+          DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})  
+          names(newLADsBoot) <- newLADsnames
+          BootStrapRES <- c(BootStrapRES, newLADsBoot)
+     }
+
+ #re-roder the whole lot to be alphabetical
+ BootStrapRES <- BootStrapRES [order(names(BootStrapRES))]
+
+}else{
+  #If the list is not found it bootstrapps all the LADs at once, beware this can take a long time
+
   BootStrapRES <- ls(pattern = "DATA") %>% map(~{print(.x)
   DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})
+  #Give the resulting list the name of each LAD
+  names(BootStrapRES)<- elementnames
 
+}
+#SAve the file or updated file with the additional elements
 saveRDS(BootStrapRES, file = "BootStrapRES.rds")
+
+elementnames<- names(BootStrapRES)
 
@@
 ```{r}
-#Give the resulting list the name of each LAD
-elementnames <- sub("DATA", "", ls(pattern = "DATA"))
-
-names(BootStrapRES)<- elementnames
 
@@
   mutate(LAD = elementnames,
-         absdiff = TtestRES %>% map_dbl(~.x$absdiff),
-         Percdiff = TtestRES %>% map_dbl(~.x$Percdiff))
+         absdiff = TtestRESgreater %>% map_dbl(~.x$absdiff),
+         Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff))
 
@@
         mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
-          summarise( maxPerc = max(WardLowUsePerc),
-          minPerc = min(WardLowUsePerc),
+          summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
+          minPerc = min(WardLowUsePerc, na.rm=TRUE),
           diffPerc = maxPerc-minPerc,
@@
 
-Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% bind_cols(skew)
+Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% left_join(WardData,by = "LAD" ) %>% bind_cols(skew)
 
+test <- BootStrapRES$CoastWave
 #look at specific data
-BootStrapRES$Redbridge %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+BootStrapRES$SouthwarkLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
   labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
 ```
 
+Why are some areas with negative difference?
+
+The max percentage of low use is 5%
+There is the council estate renovation effect.
+All the areas are Urban
+Also check deprivation,
+
 ```{r}
-
-Combine1 <- left_join(Combine1, WardData,by = "LAD" )
 
@@
 #Both southwark and Tower of london have concil flat renovation?
-#Southwark the Aylesbury estate is being redeveloped maing emptyness much higher than expected
+#Southwark the Aylesbury estate is being redeveloped making emptyness much higher than expected
 #The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
@@
 
+Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y)) + geom_point() +
+  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")
+
+#Boring doesn't show anything interesting
+Combine1 %>% ggplot(.,aes(x= p.value.x, y = p.value.y, colour =diffPerc>5 )) + geom_point()
+
+Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y, colour =absdiff>0 )) + geom_point()
+
 test <- Combine1 %>%
-  select(LAD, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)
+  select(LAD,p.value.x, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)
 

### 2017-07-14 PaperCode.Rmd
Fix plotmap
Fixed a bug in plot map which stopped it from plotting other variables.

@@
 Islington should be removed and put back in when they send the correct data, it is giving a false negative
+
+Should type B be included? or just type A?
 
@@
 
+#Yorkshire and the Humber
+```{r}
+setwd(file.path(RegionsComp, "Region Yorkshire and The Humber"))
+
 #Hull
+
+HullDATA <-read_excel("KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX")[-c(c(1:6)),1:4] %>%
+  StructureData(.)
+
+#Harrowgate
+
+HarrogateDATA <-read_excel("Harrogate DiscountsExemptionsLSOA.xlsx" )[,1:4] %>%
+  StructureData(.,3:10)
+
+```
+
+#Wales
+
 ```{r}
 
-HullDATA <-read_excel(file.path(RegionsComp, "Region Yorkshire and The Humber",
-                "KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX"))[-c(c(1:6)),1:4] %>%
-  StructureData(.)
+setwd(file.path(RegionsComp, "Region Wales"))
+list.files()
+
+CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
+  StructureData(lowuse =c(8:13,15))
 
@@
 ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
+  filter(!is.na(LAD11NM)) %>%
   summarise(
@@
 
+#check which lads are present even though I don't have data due to postcode matching
+#test <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x)))  %>% arrange(LAD11NM)
+#unique(test$LAD11NM)
+
 ```
@@
 
-#MakeLeaflet(SouthwarkLONDATA)
+z<- MakeLeaflet(CeredigionDATA)
+z
+
+saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )
 
@@
 
+#Investigating Ceredigion
+
+```{r}
+
+CeredPrice <- prices %>% 
+  filter( grepl("W06000008", Admin_district_code)) %>%
+  select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
+  #filter(X15 == "A") %>%
+  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
+                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
+                     right = F),
+         Price = as.numeric(Price))
+
+CeredPrice2 <- CeredPrice %>%
+  group_by(lsoa11cd, class) %>%
+  summarise(Admin_ward_code = first(Admin_ward_code),
+            LSOAcounts = n())
+
+CeredPrice2 <- CeredPrice2  %>%
+  group_by(Admin_ward_code, class) %>%
+  summarise(counts = n()) %>%
+  group_by(class) %>%
+  mutate(ClassPercent = counts/sum(counts)) %>%
+  ungroup %>% group_by(Admin_ward_code) %>%
+  mutate(WardPercent = counts/sum(counts))%>%
+  left_join(CeredPrice2,. ,by=c("Admin_ward_code", "class")) %>%
+  rename(LSOA_CODE = lsoa11cd)
+
+RBKCPrice <- prices %>% 
+  filter( grepl("E09000020", Admin_district_code)) %>%
+    select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
+  #filter(X15 == "A") %>%
+  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
+                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
+                     right = F),
+         Price = as.numeric(Price))
+
+RBKCPrice2 <- RBKCPrice %>%
+  group_by(lsoa11cd, class) %>%
+  summarise(Admin_ward_code = first(Admin_ward_code),
+            LSOAcounts = n())
+
+RBKCPrice2 <- RBKCPrice  %>%
+  group_by(Admin_ward_code, class) %>%
+  summarise(counts = n()) %>%
+  group_by(class) %>%
+  mutate(ClassPercent = counts/sum(counts)) %>%
+  ungroup %>% group_by(Admin_ward_code) %>%
+  mutate(WardPercent = counts/sum(counts))%>%
+  left_join(RBKCPrice2,. ,by=c("Admin_ward_code", "class")) %>%
+  rename(LSOA_CODE = lsoa11cd)
+
+RBKCtot <- RBKCPrice2 %>%
+  group_by(class) %>%
+  summarise(counts = sum(counts))
+
+summary(CeredPrice$Price)
+summary(RBKCPrice$Price)
+
+RBKCPrice %>% group_by(X15) %>%
+  summarise(mean = mean(Price))
+
+CeredPrice %>% group_by(X15) %>%
+  summarise(mean = mean(Price))
+
+ RBKCPrice2 %>%
+   filter(class == "Prime") %>%
+   PlotMap(.,AG,  "ClassPercent")
+
+  CeredPrice2 %>%
+   filter(class == "Mid") %>%
+   PlotMap(.,filter(AG, LAD11CD=="W06000008"), variable = "ClassPercent", filtermap = FALSE)
+
+```
+
 #Analyse Boostrap
@@
 
-test <- BootStrapRES$CoastWave
+test <- BootStrapRES$Ceredigion
 #look at specific data
-BootStrapRES$SouthwarkLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
   labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+prices %>%
 

### 2017-07-14 PaperCode.Rmd
Change distrib
Edited distrib so it can adjust to full priced or other prices.

@@
 
+#Norfolk
+```{r}
+#Broadlands is unsuable, due to lack of data collection.
+#This is being checked
+# BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
+#   StructureData()
+
+```
+
 #Cambridge
@@
   StructureData(lowuse =c(8:13,15))
+
+MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
+  StructureData(lowuse = c(4:8))
+
+CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
+  StructureData(2:4)
 
@@
 
-z<- MakeLeaflet(CeredigionDATA)
+z<- MakeLeaflet(MonmouthDATA)
 z
-
-saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )
+# 
+# saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )
 
@@
 
+Ceredigion has cheaper LUps even though it has areas with high LUP.
+When investigating I changed the classes to take account of the different pricing levels in the LAD.
+This made no difference.
+However re-running the bootstrapping including only A type purchases in the LAD gave the expected result of high LUP prices.
+What appeared to be happening was a lot of property was being transferred in unsual ways.
+
 ```{r}
@@
 summary(RBKCPrice$Price)
+
+CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
+CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )
+
+CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )
+
+ValueTtest(CeredBootAB)
+ValueTtest(CeredBootA)
+ValueTtest(CeredBootAnorm)
+
+CeredBootAB %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+CeredBootA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+CeredBootAnorm %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
 
@@
 
-prices %>%
-
 ```
@@
 
-#P value has an exponential decay
 Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = p.value.y)) + geom_point()

### 2017-07-14 Functions/DistribCompareBootstrapper.R

@@ -1,16 +1,21 @@
 
-DistribCompareBootstrapper <-function(df, seed, samples=100){
+DistribCompareBootstrapper <-function(df, seed, samples=100, PriceCuts = c(0,  490,      750,   2000, 12000, Inf)*10^3, type = NULL){
 #df:data frame of processed area/s data
 #LADCD: The LAD code to fetch the correct price data
 # Random seed
 #Number of Bootstrap samples.
 
 LADCD <- unique(df$LAD11CD)
-  
+
+if(!is.null(type)){
+  prices <- prices %>%
+    filter(X15 == type)
+}
+
 dfPrice <- prices %>% 
   filter( grepl(paste(LADCD, collapse="|"), Admin_district_code)) %>%
   select(Admin_ward_code, lsoa11cd, Price =X2) %>%
-  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
+  mutate(class = cut(Price, PriceCuts , 
                      labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                      right = F),
          Price = as.numeric(Price)) #there was some number overflow thing changing to numeric solves this

### 2017-07-14 SubCode/Setup.R

@@ -2,7 +2,7 @@
 
 
 packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
-              "forcats", "e1071")
+              "forcats", "e1071", "hmtlwidgets")
 
 new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
 if(length(new.packages)) install.packages(new.packages)

### 2017-07-15 PaperCode.Rmd
DistribCompare upgrade
I have changed Distrib compare to be able to create bootstrapps of type A and B purchases only

@@
 setwd(basewd)
-#Boostrap each LAD
-elementnames <- sub("DATA", "", ls(pattern = "DATA"))
 
-if(file.exists("BootStrapRES.rds")){
- #this sectio of code loads the old list and appends the new LADs
+#load full data
+BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")
 
-  BootStrapRES<- readRDS("BootStrapRES.rds")
-  newLADsnames <- sub("DATA", "", ls(pattern = "DATA")) %>% 
-  .[!(. %in% names(BootStrapRES))] 
-  newLADs <- paste0(newLADsnames, "DATA")
+#Include only full price standard purchases
+BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")
 
-    #only bootstrap if there is something to add.
-    if(length(newLADsnames)>0){
-       newLADsBoot <- newLADs  %>% map(~{print(.x)
-          DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})  
-          names(newLADsBoot) <- newLADsnames
-          BootStrapRES <- c(BootStrapRES, newLADsBoot)
-     }
-
- #re-roder the whole lot to be alphabetical
- BootStrapRES <- BootStrapRES [order(names(BootStrapRES))]
-
-}else{
-  #If the list is not found it bootstrapps all the LADs at once, beware this can take a long time
-
-  BootStrapRES <- ls(pattern = "DATA") %>% map(~{print(.x)
-  DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000)})
-  #Give the resulting list the name of each LAD
-  names(BootStrapRES)<- elementnames
-
-}
-#SAve the file or updated file with the additional elements
-saveRDS(BootStrapRES, file = "BootStrapRES.rds")
+#Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
+BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")
 
@@
 #look at specific data
-BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 

### 2017-07-15 PaperCode.Rmd
Summary Function
Created a function to create summary statistics of the BootStrapRES function

@@
 
-#Perform the t-test on the resulting lists
-TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
-TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
-#Tidy results of thejust the ttest
-TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
-  mutate(LAD = elementnames,
-         absdiff = TtestRESgreater %>% map_dbl(~.x$absdiff),
-         Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff))
+Combine1 <- BootResSummaryData(BootStrapRES)
 
 #This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
-TtestRES2 %>% ggplot(.,aes(x= absdiff, y = Percdiff)) + geom_point() 
-TtestRES2 %>% ggplot(.,aes(x= absdiff, y = p.value)) + geom_point()
-TtestRES2 %>% ggplot(.,aes(x= Percdiff, y = p.value)) + geom_point()
-
-#Perform ANOVA on the difference between the ratios of the groups on the bootrapped list
-ANOVARES <- BootStrapRES %>% 
-  map_df(~aov(.x$RatioExvsAct~.x$class) %>% tidy) %>% 
-  filter(term != "Residuals") %>%
-  select(-term) %>%
-  mutate(LAD = elementnames)
-
-WardData <- ls(pattern = "DATA") %>%
-  map_df(~eval(parse(text=.x)) %>%
-           select(WardLowUsePerc) %>%
-        mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
-          summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
-          minPerc = min(WardLowUsePerc, na.rm=TRUE),
-          diffPerc = maxPerc-minPerc,
-          LAD = sub("DATA", "", .x)))
-
-skew <- BootStrapRES %>% map_df(~.x %>% group_by(class) %>%
-  summarise(skew = mean(RatioExvsAct, na.rm = TRUE)) %>%
-  summarise(skew = skewness(skew))
-)
-
-Combine1 <- left_join(ANOVARES, TtestRES2, by = "LAD" ) %>% left_join(WardData,by = "LAD" ) %>% bind_cols(skew)
+Combine1 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()
 
@@
 
-Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = p.value.y)) + geom_point()
+Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = Ttest.p.value)) + geom_point()
 
@@
 #The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
-Combine1 %>% ggplot(.,aes(x= diffPerc, y = p.value.y)) + geom_point()
+Combine1 %>% ggplot(.,aes(x= diffPerc, y = Ttest.p.value)) + geom_point()
 
-Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y)) + geom_point() +
+Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
   labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")
@@
 #Boring doesn't show anything interesting
-Combine1 %>% ggplot(.,aes(x= p.value.x, y = p.value.y, colour =diffPerc>5 )) + geom_point()
+Combine1 %>% ggplot(.,aes(x= p.value.x, y = Ttest.p.value, colour =diffPerc>5 )) + geom_point()
 
-Combine1 %>% ggplot(.,aes(x= maxPerc, y = p.value.y, colour =absdiff>0 )) + geom_point()
+Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour =absdiff>0 )) + geom_point()
 
 test <- Combine1 %>%
-  select(LAD,p.value.x, p.value.y, absdiff , maxPerc, minPerc,diffPerc, skew)
+  select(LAD,p.value.x, Ttest.p.value, absdiff , maxPerc, minPerc,diffPerc, skew)
 
-Combine1 %>% ggplot(.,aes(x= skew, y= p.value.y)) + geom_point()
+Combine1 %>% ggplot(.,aes(x= skew, y= Ttest.p.value)) + geom_point()
 
@@
 
-test <- Combine1 %>% filter(p.value.y>0.05)
+test <- Combine1 %>% filter(Ttest.p.value>0.05)
 ```

### 2017-07-15 Functions/DistribCompareBootstrapper.R

@@ -1,10 +1,13 @@
 
-DistribCompareBootstrapper <-function(df, seed, samples=100, PriceCuts = NULL, type = NULL){
+DistribCompareBootstrapper <-function(df, seed, samples=100, type = NULL, PriceCuts = NULL){
 #df:data frame of processed area/s data
 #LADCD: The LAD code to fetch the correct price data
 # Random seed
 #Number of Bootstrap samples.
-
+#type: whether all purchese or only classes A or b are taken, enter a character "A" or "B" or leave NULL for all
+#PriceCuts: the cut points for the different classes of housing, used only occaisionally has to start with 0 and end with Inf
+  #and in total have 6 elements
+  
 LADCD <- unique(df$LAD11CD)
 
 if(!is.null(type)){

### 2017-07-15 Functions/LoadAddDistribCompare.R

@@ -24,7 +24,7 @@ if(file.exists(FileName)){
   #only bootstrap if there is something to add.
   if(length(newLADsnames)>0){
     newLADsBoot <- newLADs  %>% map(~{print(.x)
-      DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000, type)})  
+      DistribCompareBootstrapper(get(.x), 1652, 1000, type = type)})  
     names(newLADsBoot) <- newLADsnames
     BootStrapRES <- c(BootStrapRES, newLADsBoot)
   }
@@ -36,7 +36,7 @@ if(file.exists(FileName)){
   #If the list is not found it bootstrapps all the LADs at once, beware this can take a long time
   
   BootStrapRES <- ls(pattern = "DATA",envir = globalenv()) %>% map(~{print(.x)
-    DistribCompareBootstrapper(eval(parse(text=.x)), 1652, 1000, type)})
+    DistribCompareBootstrapper(get(.x), 1652, 1000, type = type)})
   #Give the resulting list the name of each LAD
   names(BootStrapRES)<- elementnames
   

### 2017-07-19 PaperCode.Rmd
Remove ANOVA
the anova doesn't work when only A is used doe to the class bounardies. It is n't very interesting anyway so I removed it from the function

@@
 
+#Devon
+
+```{r}
+
+NorthDevonDATA <- read_excel("North DevonDiscountsLSOA.XLSX", sheet=1)[1:4] %>%
+  StructureData
+
+```
+
+#Somerset
+
+```{r}
+NorthSomsertDATA <- read_excel("1501796 North SomersetDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
+  StructureData(lowuse= 2:6)
+
+```
+
+#Dorset
+
+```{r}
+BournemouthDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
+  StructureData(lowuse = c(5,11:14,18))
+```
+
 #Suffolk
@@
 
+StEdmundsDATA <- read.xlsx("se FOI 146  3948502_Copy+of+St+EdmundsburyDiscountsLSOA.xlsx")[1:4] %>%
+  StructureData()
+
+ForestHeathDATA <- read.xlsx("FH FOI 146 Discounts.xlsx")[1:4] %>%
+  StructureData()
+
 ```
@@
 #This is being checked
-# BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
-#   StructureData()
+BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
+  StructureData(4:9)
+
+KingsLynnDATA <- read_excel("197782 - King s Lynn and West NorfolkDiscountsLSOA (2).xlsx" , sheet=1)[1:4] %>%
+  StructureData(2:11)
+
+NorthNorfolkDATA <- read_excel("North NorfolkDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
+  StructureData()
 
@@
 EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
+  StructureData()
+
+FenlandDATA <- read_excel("FL FOI 4544 DISCOUNTS.XLSX" , sheet=1)[1:4] %>%
   StructureData()
@@
   StructureData(lowuse = 2:8)
-
-#MakeLeaflet(BrightonDATA)
+#MakeLeaflet(BournemouthDATA)
 
@@
 
+#Selby
+SelbyDATA <-read_excel("SelbyExemptionsLSOA.xlsx" )[,1:4]%>%
+  StructureData(20:27)
+
 ```
@@
 
+#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
+
 CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
@@
 
+#includes the zero class which is descibeed as 
+#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
   CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
-  StructureData(2:4)
+    StructureData()
 
@@
 
-z<- MakeLeaflet(MonmouthDATA)
+z<- MakeLeaflet(CeredigionDATA)
 z
 # 
-# saveWidget(z, file=file.path(basewd, "CeredigionDATA"), selfcontained = TRUE )
+setwd(basewd)
+ saveWidget(z, file=file.path(basewd, "CeredigionDATA.html"), selfcontained = TRUE )
 
-#testSouth <- DistribCompareBootstrapper(SouthwarkLONDATA, 1652, 1000)
+#testSouth <- DistribCompareBootstrapper(SouthwarkLONDAls(pattern = "DATA")TA, 1652, 1000)
 testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
@@
 #Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
-BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")
+BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")
 
 elementnames<- names(BootStrapRES)
+
+ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~get(.x) %>%ncol))==4]
 
@@
 CeredPrice <- prices %>% 
-  filter( grepl("W06000008", Admin_district_code)) %>%
+  filter( grepl("E09000001", Admin_district_code)) %>%
   select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
@@
 
-CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
-CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )
-
-CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )
+# CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
+# CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )
+# 
+# CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )
 
@@
 
-CeredBootAB %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
@@
 
-CeredBootA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
@@
 
-CeredBootAnorm %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+BootStrapRESB$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
@@
 
+#check any that are accidently not processed
+ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~.x %>% get %>% ncol))<10]
+
 Combine1 <- BootResSummaryData(BootStrapRES)
+
+Combine2 <- BootResSummaryData(BootStrapRESA)
+
+Combine3 <- BootResSummaryData(BootStrapRESB)
 
@@
 Combine1 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()
+Combine2 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()
 
@@
 BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+BootStrapRES$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+BootStrapRESA$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+BootStrapRESB$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+BootStrapRES$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+BootStrapRESA$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+BootStrapRESB$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
   ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
@@
 
+sum(Combine1$Ttest.p.value>0.5)/nrow(Combine1)
+sum(Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)/sum(Combine1$maxPerc>5)
+
+Combine1[Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5,]
+Combine2[Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5,]
+Combine3[Combine3$Ttest.p.value>0.5 & Combine3$maxPerc>5,]
+
+table(Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5, Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)
+
+LADAB <- ChelseaLONDATA%>% SubsetPrice
+  table(LADAB$X15, LADAB$class)
+
 Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = Ttest.p.value)) + geom_point()
@@
 Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
+  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")
+
+Combine2 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
   labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")

### 2017-07-20 PaperCode.Rmd
Exploring B type  and "other"
Started looking into the strange behaviour of B property and Other property

@@
 
-ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)
+#hide plot
+#ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)
 
@@
 
-#Cornwall
+#SouthWest
+
+##Cornwall
 
@@
 
-#Devon
+##Devon
 
@@
 
+PlymouthDATA <- read_excel("PlymouthDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
+  StructureData(lowuse = 4:8)
+
 ```
 
-#Somerset
+##Somerset
 
@@
 
-#Dorset
+##Dorset
 
@@
   StructureData(lowuse = c(5,11:14,18))
+
+ChristchurchDATA <- read_excel("Christchurch FOI17 - 0312 - Bourne - Ctax Discounts and Exemptions.xls",
+                               sheet=1)[1:4] %>%
+  StructureData(lowuse = c(6,12:17,20))
+
 ```
 
-#Suffolk
+##Wiltshire
+
+```{r}
+#Wiltshire have not included everything
+# WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts.xlsx",
+#                                sheet=1)[1:4] %>%
+#   StructureData()
+```
+
+#East of England
+
+##Suffolk
 
@@
 
-#Norfolk
+##Norfolk
 ```{r}
@@
 
-#Cambridge
+##Cambridge
 ```{r}
@@
 
+#North East
+
+##Tyneside
+
+```{r}
+
+setwd(file.path(RegionsComp, "Region North East"))
+#Not sure all are there ask for confirmation
+# SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
+#   StructureData(lowuse = c(2:4,6,8:10))
+
+```
+
 #Wales
@@
     StructureData()
+
+#Strangely low numbers checking
+# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
+#   StructureData(lowuse = c(3,5:6))
 
@@
 
+land registry 
+sue gambles
+
 ```{r}
+
+#gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
+CurrentLADS <- ls(pattern = "DATA") %>%
+  map_chr(~{df<- get(.x)
+  df$LAD11CD[which.max(table(df$LAD11CD) %>% as.matrix)] }
+)
 
@@
 
-Combine1 <- BootResSummaryData(BootStrapRES)
+Combine1 <- BootResSummaryData(BootStrapRES) %>% mutate(LAD11CD = CurrentLADS)
 
-Combine2 <- BootResSummaryData(BootStrapRESA)
+Combine2 <- BootResSummaryData(BootStrapRESA) %>% mutate(LAD11CD = CurrentLADS)
 
-Combine3 <- BootResSummaryData(BootStrapRESB)
+Combine3 <- BootResSummaryData(BootStrapRESB) %>% mutate(LAD11CD = CurrentLADS)
 
@@
 
+HouseMatch <- data_frame(PropType = "D,S,T,F,O" %>% str_split(",") %>% unlist,
+type = "Detached,Semi-Detached,Terraced,Flats/Maisonettes,Other"%>% str_split(",") %>% unlist)
+
+#test CoL after adding in filtering for other LADs
+testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000)
+testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A")
+testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B")
+
+testColA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+testColA %>% 
+  group_by(class) %>%
+  summarise_all(funs(mean(., na.rm = TRUE)))
+
+test <- CoLLONDATA %>% SubsetPrice() %>% left_join(HouseMatch)
+testB <- CoLLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
+testA <- CoLLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)
+
+testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
+testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)
+
+testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
+testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)
+
+test <- CoLLONDATA %>% SubsetPrice("A")
+
+CoLnums <- BootStrapRES$CoLLON %>% 
+  group_by(class) %>%
+  summarise_all(funs(mean(., na.rm = TRUE)))
+
+CoLnumsA <- BootStrapRESA$CoLLON %>% 
+  group_by(class) %>%
+  summarise_all(funs(mean(., na.rm = TRUE)))
+
+table(test$type, test$class)
+table(testA$type, testA$class)
+table(testB$type, testB$class)
+
+LADNMs <- EW2 %>% group_by(LAD11CD) %>%
+  summarise(LAD11NM = first(LAD11NM))
+
+PropertyTypes <- c("D", "S", "T", "F")
+
+ABratio <- prices %>% 
+  filter(X5 %in% PropertyTypes) %>%
+  group_by(Admin_district_code, X15) %>%
+  summarise(count = n(), 
+            mean = mean(X2)) %>%
+  rename(LAD11CD = Admin_district_code)
+
+ABratio2 <- ABratio%>%
+  select(-mean) %>%
+spread(key = X15, value = count) %>%
+  mutate(Countratio = B/(A+B))
+
+ABratio3 <- ABratio%>%
+  select(-count) %>%
+spread(key = X15, value = mean) %>%
+  mutate(Valueratio = B/(A))
+
+ABratio4 <-  left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
+  left_join(LADNMs) %>%
+  left_join(prices %>% 
+  group_by(Admin_district_code) %>%
+summarise(mean = mean(X2)) %>%
+  rename(LAD11CD = Admin_district_code))
+
+sum(prices$X15 == "B")/nrow(prices)
+
+test <- ABratio4 %>% 
+  filter(LAD11CD %in% CurrentLADS)
+
+ABratio3 %>% ggplot(., aes(x = Valueratio)) +geom_density()
+
+test <- Combine1 %>% 
+  left_join(ABratio4)
+
+test %>%
+  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()
+
+test %>%
+  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Countratio>0.2)) + geom_point()
+
+test %>%
+  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = mean)) + geom_point()
+
 ```
@@
 ```{r}
-
-Combine1 %>% ggplot(.,aes(x= maxPerc, y = abs(Percdiff))) + geom_point()
 

### 2017-07-20 Functions/DistribCompareBootstrapper.R

@@ -8,7 +8,7 @@ DistribCompareBootstrapper <-function(df, seed, samples=100, type = NULL, PriceC
 #PriceCuts: the cut points for the different classes of housing, used only occaisionally has to start with 0 and end with Inf
   #and in total have 6 elements
   
-LADCD <- unique(df$LAD11CD)
+LADCD <- df$LAD11CD[which.max(table(df$LAD11CD) %>% as.matrix)] 
 
 if(!is.null(type)){
   prices <- prices %>%

### 2017-07-20 PaperCode.Rmd
Exclude Other
Set up the code to be able to bootstrap excluding the "other" type of ptoperty

@@
 
+#ExO excluding Other
+#A only A type sales
+#B only Btype sales
+
 #load full data
@@
 BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")
+
+#Repeat excluding all the properties classed as other
+
+BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
+                                         PropertyTypes = c("D", "S", "T", "F"))
+
+BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
+                                         PropertyTypes = c("D", "S", "T", "F"))
+
+BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
+                                         PropertyTypes = c("D", "S", "T", "F"))
 

### 2017-07-20 Functions/LoadAddDistribCompare.R

@@ -1,4 +1,4 @@
-LoadAddDistribCompare<-function(FileName = "BootStrapRES.rds", type = NULL){
+LoadAddDistribCompare<-function(FileName = "BootStrapRES.rds", type = NULL, PropertyTypes = NULL, PriceCuts = NULL){
 # This function smooths the process of loading the BootStrapRES file and adding new LADs to it
 #   It Also allows for type A and B purchases only to be bootstrapped
 #   This gives a more nuanced picture of the purchases and some analysis suggests
@@ -24,7 +24,7 @@ if(file.exists(FileName)){
   #only bootstrap if there is something to add.
   if(length(newLADsnames)>0){
     newLADsBoot <- newLADs  %>% map(~{print(.x)
-      DistribCompareBootstrapper(get(.x), 1652, 1000, type = type)})  
+      DistribCompareBootstrapper(get(.x), 1652, 1000, type, PropertyTypes, PriceCuts)})  
     names(newLADsBoot) <- newLADsnames
     BootStrapRES <- c(BootStrapRES, newLADsBoot)
   }

### 2017-07-20 Functions/SubsetPrice.R

@@ -1,5 +1,5 @@
 
-SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL){
+SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, PriceCuts = NULL){
   #Subsets the price frame to be just for the specific LAD
   #Takes either the DATA dataframe or the character string LAD11CD
   #this allows the subsetting of the price list without looking up the LAD code
@@ -23,16 +23,26 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL){
       filter(X5 %in% PropertyTypes)
   }
   
+  if(is.null(PriceCuts)){
+    PriceCuts<-c(0,  490,      750,   2000, 12000, Inf)*10^3
+  }
+  
   
     
   filter(prices, grepl(Code, Admin_district_code)) %>%
     select(Admin_ward_code, lsoa11cd, Price =X2, X15, PropType = X5) %>%
-    #filter(X15 == "A") %>%
-    mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
+    mutate(class = cut(Price, PriceCuts, 
                        labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                        right = F),
            Price = as.numeric(Price)) 
   
-  
+  dfPrice <- prices %>% 
+    filter( grepl(paste(LADCD, collapse="|"), Admin_district_code)) %>%
+    select(Admin_ward_code, lsoa11cd, Price =X2) %>%
+    mutate(class = cut(Price, PriceCuts , 
+                       labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
+                       right = F),
+           Price = as.numeric(Price)) #there was some number overflow thing changing to numeric solves this
+   
 }
 

### 2017-07-21 PaperCode.Rmd
Big Fix on property types
I hadn't put in the property types value in the section that creates the new BootStrapRES data, this mean that property types were ignored.

@@
 
-#Investigating Ceredigion
-
-Ceredigion has cheaper LUps even though it has areas with high LUP.
-When investigating I changed the classes to take account of the different pricing levels in the LAD.
-This made no difference.
-However re-running the bootstrapping including only A type purchases in the LAD gave the expected result of high LUP prices.
-What appeared to be happening was a lot of property was being transferred in unsual ways.
-
-```{r}
-
-CeredPrice <- prices %>% 
-  filter( grepl("E09000001", Admin_district_code)) %>%
-  select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
-  #filter(X15 == "A") %>%
-  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
-                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
-                     right = F),
-         Price = as.numeric(Price))
-
-CeredPrice2 <- CeredPrice %>%
-  group_by(lsoa11cd, class) %>%
-  summarise(Admin_ward_code = first(Admin_ward_code),
-            LSOAcounts = n())
-
-CeredPrice2 <- CeredPrice2  %>%
-  group_by(Admin_ward_code, class) %>%
-  summarise(counts = n()) %>%
-  group_by(class) %>%
-  mutate(ClassPercent = counts/sum(counts)) %>%
-  ungroup %>% group_by(Admin_ward_code) %>%
-  mutate(WardPercent = counts/sum(counts))%>%
-  left_join(CeredPrice2,. ,by=c("Admin_ward_code", "class")) %>%
-  rename(LSOA_CODE = lsoa11cd)
-
-RBKCPrice <- prices %>% 
-  filter( grepl("E09000020", Admin_district_code)) %>%
-    select(Admin_ward_code, lsoa11cd, Price =X2, X15) %>%
-  #filter(X15 == "A") %>%
-  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
-                     labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
-                     right = F),
-         Price = as.numeric(Price))
-
-RBKCPrice2 <- RBKCPrice %>%
-  group_by(lsoa11cd, class) %>%
-  summarise(Admin_ward_code = first(Admin_ward_code),
-            LSOAcounts = n())
-
-RBKCPrice2 <- RBKCPrice  %>%
-  group_by(Admin_ward_code, class) %>%
-  summarise(counts = n()) %>%
-  group_by(class) %>%
-  mutate(ClassPercent = counts/sum(counts)) %>%
-  ungroup %>% group_by(Admin_ward_code) %>%
-  mutate(WardPercent = counts/sum(counts))%>%
-  left_join(RBKCPrice2,. ,by=c("Admin_ward_code", "class")) %>%
-  rename(LSOA_CODE = lsoa11cd)
-
-RBKCtot <- RBKCPrice2 %>%
-  group_by(class) %>%
-  summarise(counts = sum(counts))
-
-summary(CeredPrice$Price)
-summary(RBKCPrice$Price)
-
-# CeredBootAnorm <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, type = "A" )
-# CeredBootAB <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3 )
-# 
-# CeredBootA <- DistribCompareBootstrapper(CeredigionDATA, 1652,1000, c(0, 60, 120, 200, 500, Inf)*10^3, type = "A" )
-
-ValueTtest(CeredBootAB)
-ValueTtest(CeredBootA)
-ValueTtest(CeredBootAnorm)
-
-BootStrapRES$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-BootStrapRESB$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-RBKCPrice %>% group_by(X15) %>%
-  summarise(mean = mean(Price))
-
-CeredPrice %>% group_by(X15) %>%
-  summarise(mean = mean(Price))
-
- RBKCPrice2 %>%
-   filter(class == "Prime") %>%
-   PlotMap(.,AG,  "ClassPercent")
-
-  CeredPrice2 %>%
-   filter(class == "Mid") %>%
-   PlotMap(.,filter(AG, LAD11CD=="W06000008"), variable = "ClassPercent", filtermap = FALSE)
-
-```
-
 #Analyse Boostrap
@@
 
+#Excluding Other
+Combine1ExO <- BootResSummaryData(BootStrapRESExO) %>% mutate(LAD11CD = CurrentLADS)
+
+Combine2ExO <- BootResSummaryData(BootStrapRESExOA) %>% mutate(LAD11CD = CurrentLADS)
+
+Combine3ExO <- BootResSummaryData(BootStrapRESExOB) %>% mutate(LAD11CD = CurrentLADS)
+
 #This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
@@
 
-test <- BootStrapRES$Ceredigion
-#look at specific data
-BootStrapRESA$Ceredigion %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+```
 
-BootStrapRES$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+#Explore results
 
-BootStrapRESA$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+```{r}
 
-BootStrapRESB$ChelseaLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-BootStrapRES$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-BootStrapRESA$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-BootStrapRESB$CoLLON %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+BootStrapRES$CoLLON %>% PlotClassDiff()
+BootStrapRESExO$CoLLON %>% PlotClassDiff()
+BootStrapRESA$CoLLON %>% PlotClassDiff()
+BootStrapRESB$CoLLON %>% PlotClassDiff()
 
@@
 #test CoL after adding in filtering for other LADs
-testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000)
-testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A")
-testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B")
+testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, PropertyTypes = c("D", "S", "T", "F"))
 
-testColA %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A", PropertyTypes = c("D", "S", "T", "F"))
+testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B", PropertyTypes = c("D", "S", "T", "F"))
+
+all_equal(Boottest$CoLLON, testCol)
+
+all_equal(Boottest$CoLLON, BootStrapRES$CoLLON)
+
+testCol %>% PlotClassDiff()
 
@@
 
-testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
-testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)
-
-testB <- ChelseaLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
-testA <- ChelseaLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)
-
-test <- CoLLONDATA %>% SubsetPrice("A")
+table(test$type, test$class)
+table(testA$type, testA$class)
+table(testB$type, testB$class)
 
@@
   summarise_all(funs(mean(., na.rm = TRUE)))
-
-table(test$type, test$class)
-table(testA$type, testA$class)
-table(testB$type, testB$class)
 

### 2017-07-21 Functions/LoadAddDistribCompare.R

@@ -24,7 +24,7 @@ if(file.exists(FileName)){
   #only bootstrap if there is something to add.
   if(length(newLADsnames)>0){
     newLADsBoot <- newLADs  %>% map(~{print(.x)
-      DistribCompareBootstrapper(get(.x), 1652, 1000, type, PropertyTypes, PriceCuts)})  
+      DistribCompareBootstrapper(get(.x), 1652, 1000, type, PropertyTypes)})  
     names(newLADsBoot) <- newLADsnames
     BootStrapRES <- c(BootStrapRES, newLADsBoot)
   }
@@ -36,7 +36,7 @@ if(file.exists(FileName)){
   #If the list is not found it bootstrapps all the LADs at once, beware this can take a long time
   
   BootStrapRES <- ls(pattern = "DATA",envir = globalenv()) %>% map(~{print(.x)
-    DistribCompareBootstrapper(get(.x), 1652, 1000, type = type)})
+    DistribCompareBootstrapper(get(.x), 1652, 1000, type = type, PropertyTypes)})
   #Give the resulting list the name of each LAD
   names(BootStrapRES)<- elementnames
   

### 2017-07-21 Functions/PlotClassDiff.R

@@ -1,0 +1,10 @@
+PlotClassDiff <-function(df){
+   #Takes the Out put of Bootstrap Res and plots a box plot of the difference from expected
+   #df: The dataframe of a specific LAD from BootStrapRES
+  df %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
+     geom_boxplot() + 
+     labs(title = "Bootstrapped difference from expected number of low-use homes", 
+          y = "% difference from expected")
+   
+}

### 2017-07-21 Functions/SubsetPrice.R

@@ -27,19 +27,12 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, PriceCuts = NULL)
     PriceCuts<-c(0,  490,      750,   2000, 12000, Inf)*10^3
   }
   
-  
-    
-  filter(prices, grepl(Code, Admin_district_code)) %>%
+  #The  model used to take multiple councils if there was overlap, but this caused some strange
+  #Problems So I removed it. The current version only takes a single LAD
+  prices %>%
+  filter(., grepl(Code, Admin_district_code)) %>%
     select(Admin_ward_code, lsoa11cd, Price =X2, X15, PropType = X5) %>%
     mutate(class = cut(Price, PriceCuts, 
-                       labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
-                       right = F),
-           Price = as.numeric(Price)) 
-  
-  dfPrice <- prices %>% 
-    filter( grepl(paste(LADCD, collapse="|"), Admin_district_code)) %>%
-    select(Admin_ward_code, lsoa11cd, Price =X2) %>%
-    mutate(class = cut(Price, PriceCuts , 
                        labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
                        right = F),
            Price = as.numeric(Price)) #there was some number overflow thing changing to numeric solves this

### 2017-07-23 Average local prices.Rmd
Average local prices
Wrote a script to calculate the price of a LAD relative to the local population of LADs... it doesn't improve any models

---
title: "Untitled"
author: "Jonathan Bourne"
date: "23 July 2017"
output: html_document
---

This file find out whether an are is more or less expensive than the local average, where local is defined as the number of x hops from the root node in the LAD network of main land UK

source: http://geoportal.statistics.gov.uk/datasets/osni-open-data-largescale-boundaries-local-government-districts-2012

```{r}
library(shp2graph)

setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
source("Setup.R")

setwd(Functions)
list.files() %>% map(source)

```

```{r}

NILADshapedata <- file.path(basewd,"ShapeFiles","OSNI_Open_Data_Largescale_Boundaries__Local_Government_Districts_2012")
setwd(NILADshapedata)

LADshape <- readOGR(dsn = list.files(pattern = "shp"))

Adjmat <- Shape2Adjmat(LADshape, "LGDCode")

g1 <- graph_from_adjacency_matrix(Adjmat, mode = "undirected")

plot(g1)

BFS1 <- bfs(g1, root = 1, unreachable = FALSE, rank = TRUE, dist = TRUE)

BFS1$dist

NetworkDist <- 1:length(V(g1)) %>% 
  map(~{
  bfs(g1, root = .x, unreachable = FALSE, rank = TRUE, dist = TRUE)$rank %>%
      as.matrix %>% t %>% as.data.frame
  }) %>% 
  bind_rows()

test <- prices %>% filter(grepl("N", Admin_district_code))
  filter(Admin_district_code == "N09000001")

```

```{r}

LADshapedata <- file.path(basewd,"ShapeFiles","Local_Authority_Districts_December_2016_Full_Extent_Boundaries_in_Great_Britain")
setwd(LADshapedata)

LADshape <- readOGR(dsn = list.files(pattern = "shp"))

Adjmat <- Shape2Adjmat(LADshape, "lad16cd")

g1 <- graph_from_adjacency_matrix(Adjmat, mode = "undirected")

#plot the graph
plot(g1)

#Construct a distance network across all the LADs
NetworkDist <- 1:length(V(g1)) %>% 
  map(~{
  bfs(g1, root = .x, unreachable = FALSE, rank = TRUE, dist = TRUE)$rank %>%
      as.matrix %>% t %>% as.data.frame
  }) %>% 
  bind_rows() %>% mutate(LAD11CD = names(.))

LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(meandiff = price-mean(price),
         pricepercent = percent_rank(price))

#Filter the data to only LADs that I have data for

LocalMean <- NetworkDist %>% 
  gather(key= "LAD11CD2", value = "distance", -LAD11CD) %>%
  filter(LAD11CD %in% CombineAB$LAD11CD, distance <=3) %>%
#join on the average prices per LAD
  left_join(LADprice, by = c("LAD11CD2"="Admin_district_code")) %>%
  #find local mean
  group_by(LAD11CD) %>%
  summarise(LocalMean = mean(price,na.rm = TRUE))

test <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent, LAD11CD) %>%
  mutate(outcome = LUPdepExt>Extent)  %>% 
  left_join(LocalMean, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
  mutate(priceRatio = (price/LocalMean)) #%>%
  #select(LAD11CD, LAD11NM, priceRatio, price, LocalMean, absdiff, Ttest.p.value, maxPerc, LUPdepExt)

test %>%
  ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour = priceRatio>1)) + geom_jitter()

rpart.model <- rpart(as.factor(absdiff>0) ~ maxPerc, test)
rpart.model1 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
rpart.model2 <- rpart(as.factor(absdiff>0) ~ priceRatio+ maxPerc, test)
rpart.model3 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc + priceRatio, test)

confusionMatrix( predict(rpart.model, test, type = "class"),as.factor(test$absdiff>0))
confusionMatrix( predict(rpart.model1, test, type = "class"),as.factor(test$absdiff>0))
confusionMatrix( predict(rpart.model2, test, type = "class"),as.factor(test$absdiff>0))
confusionMatrix( predict(rpart.model3, test, type = "class"),as.factor(test$absdiff>0))

```

### 2017-07-23 PaperCode.Rmd
Average local prices
Wrote a script to calculate the price of a LAD relative to the local population of LADs... it doesn't improve any models

@@
 
+#Overall price data 
+```{r}
+#Other property is massively more valuable on average than the rest of the property types
+#mean value is 10 Million as such it has to be excluded
+prices %>% group_by(X5) %>% 
+  mutate(X2 = as.numeric(X2)) %>%
+  summarise(count = n(),
+            Value = sum(X2, na.rm =T),
+            mean = mean(X2, na.rm = T)) %>%
+mutate(countperc = (count/sum(count)),
+       ValuePerc = Value/sum(Value))
+
+#Looking at A and B property we can see that B properties are more expensive than A type
+prices %>% group_by(X15) %>% 
+  mutate(X2 = as.numeric(X2)) %>%
+  summarise(count = n(),
+            Value = sum(X2, na.rm =T),
+            mean = mean(X2, na.rm = T)) %>%
+mutate(countperc = (count/sum(count)),
+       ValuePerc = Value/sum(Value))
+
+#Other only appears in the B type sales never in A type
+prices %>% 
+  mutate(X2 = as.numeric(X2)) %>%
+    group_by(X15, X5) %>% 
+  summarise(count = n(),
+            Value = sum(X2, na.rm =T),
+            mean = mean(X2, na.rm = T)) %>%
+  ungroup %>%
+mutate(countperc = (count/sum(count)),
+       ValuePerc = Value/sum(Value))  
+```
+
 #Bootstrap
@@
   map_chr(~{df<- get(.x)
-  df$LAD11CD[which.max(table(df$LAD11CD) %>% as.matrix)] }
+  df <- df %>%
+  group_by(LAD11CD) %>%
+  summarise(count = n())
+df$LAD11CD[which.max(df$count)]}
 )
@@
 BootStrapRESExO$CoLLON %>% PlotClassDiff()
-BootStrapRESA$CoLLON %>% PlotClassDiff()
-BootStrapRESB$CoLLON %>% PlotClassDiff()
+BootStrapRESExOA$CoLLON %>% PlotClassDiff()
+BootStrapRESExOB$CoLLON %>% PlotClassDiff()
 
@@
 type = "Detached,Semi-Detached,Terraced,Flats/Maisonettes,Other"%>% str_split(",") %>% unlist)
-
-#test CoL after adding in filtering for other LADs
-testCol <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, PropertyTypes = c("D", "S", "T", "F"))
-
-testColA <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "A", PropertyTypes = c("D", "S", "T", "F"))
-testColB <- DistribCompareBootstrapper(CoLLONDATA,1652, 1000, "B", PropertyTypes = c("D", "S", "T", "F"))
-
-all_equal(Boottest$CoLLON, testCol)
-
-all_equal(Boottest$CoLLON, BootStrapRES$CoLLON)
-
-testCol %>% PlotClassDiff()
-
-testColA %>% 
-  group_by(class) %>%
-  summarise_all(funs(mean(., na.rm = TRUE)))
 
@@
 
-test <- Combine1 %>% 
-  left_join(ABratio4)
+CombineAB <- Combine1ExO %>% 
+  left_join(ABratio4, by = "LAD11CD")
 
-test %>%
+CombineAB %>%
   ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()
 
-test %>%
+CombineAB %>%
   ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Countratio>0.2)) + geom_point()
 
-test %>%
+CombineAB %>%
   ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = mean)) + geom_point()
+
+```
+
+#Inlcuding deprivation
+```{r}
+setwd(file.path(basewd, "Deprivation"))
+list.files()
+LADDep<-read_excel("File_10_ID2015_Local_Authority_District_Summaries.xlsx", sheet = 2) %>%
+  setNames(make.names(names(.)) %>% gsub("IMD...", "",.) %>% trimws ) %>%
+  rename(LAD11CD = Local.Authority.District.code..2013.)
+
+LSOADomDep<-read_excel("File_2_ID_2015_Domains_of_deprivation.xlsx" , sheet = 2) %>%
+  setNames(make.names(names(.))) %>%
+  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
+  rename(LAD11CD = Local.Authority.District.code..2013.)
+
+LSOADep<-read_excel("File_1_ID_2015_Index_of_Multiple_Deprivation.xlsx", sheet = 2) %>%
+  setNames(make.names(names(.))) %>%
+  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
+  rename(LAD11CD = Local.Authority.District.code..2013.,
+         LSOA_CODE = LSOA.code..2011.)
+
+CombineAB <- CombineAB %>% left_join(LADDep, by = "LAD11CD")
+
+CombineAB %>%
+  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, color =Rank.of.extent<100)) + geom_jitter()
+
+#Look Kings Lynn and harrogate as they are strange results
+
+KingsLynnDep <- KingsLynnDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>% 
+  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))
+
+HarrogateDep <- HarrogateDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>%
+  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))
+
+#creating the empty deprivation extent
+maxLSOA <- max(LSOADep$Rank..where.1.is.most.deprived.)
+
+ExtentWeight <- LSOADep%>%
+  mutate(percentile = (Rank..where.1.is.most.deprived./maxLSOA),
+         perc2 = percentile-0.11,
+         weight = ifelse(percentile<.11|percentile>.3,0, 0.95 - (0.95/.20)*perc2 ),
+         weight = ifelse(percentile<0.11, 1, weight)) %>%
+  select(LSOA_CODE, weight)
+
+test <- KingsLynnDep %>% 
+  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
+  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))
+
+test <- BromleyLONDATA %>% 
+  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
+  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))
+
+sum(test$WeightedLUP, na.rm = TRUE)
+
+LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
+df <- get(.x)
+test <- df %>% 
+  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
+  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))
+
+sum(test$WeightedLUP, na.rm = TRUE)
+})
+
+Combine1ExO2 <- CombineAB%>%
+  mutate(LUPdepExt)
+
+Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
+  geom_point()
+
+Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
+  geom_point()
+
+LADprice <- prices %>%
+  filter(X5!= "O") %>%
+  group_by(Admin_district_code) %>%
+summarise(price = mean(X2)) %>%
+  mutate(meandiff = price-mean(price),
+         pricepercent = percent_rank(price))
+
+test <- Combine1ExO2 %>%
+  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
+  #filter out wales
+  filter(!grepl("W", LAD11CD))%>%
+  select(LAD, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent) %>%
+  mutate(outcome = LUPdepExt>Extent)
+
+test %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
+  geom_point()
+
+svm.model <- svm(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
+#why do the two rforest models have such different results
+rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
+rpart.model <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
+
+confusionMatrix(predict(svm.model, test, type = class),as.factor(test$absdiff>0))
+
+confusionMatrix( predict(rpart.model, test, type = "class"),as.factor(test$absdiff>0))
+
+```
+
+```{r}
+
+library(e1071)
+ library(rpart)
+ data(Glass, package="mlbench")
+ ## split data into a train and test set
+ index <- 1:nrow(Glass)
+ testindex <- sample(index, trunc(length(index)/3))
+ testset <- Glass[testindex,]
+ trainset <- Glass[-testindex,]
+
+svm.model <- svm(Type ~ ., data = trainset, cost = 100, gamma = 1)
+svm.pred <- predict(svm.model, testset[,-10])
+
+rpart.model <- rpart(Type ~ ., data = trainset)
+rpart.pred <- predict(rpart.model, testset[,-10], type = "class")
+
+confusionMatrix( rpart.pred, testset$Type)
+confusionMatrix( svm.pred, testset$Type)
+```
+
+```{r}
 
@@
 
-Combine1[Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5,]
-Combine2[Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5,]
-Combine3[Combine3$Ttest.p.value>0.5 & Combine3$maxPerc>5,]
+Combine1ExO[Combine1ExO$Ttest.p.value>0.5 & Combine1ExO$maxPerc>5,]
+Combine2ExO[Combine2ExO$Ttest.p.value>0.5 & Combine2ExO$maxPerc>5,]
+Combine3ExO[Combine3ExO$Ttest.p.value>0.5 & Combine3ExO$maxPerc>5,]
 
@@
 
-Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
+Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
   labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")
@@
 ```{r}
-
 test <- Combine1 %>% filter(Ttest.p.value>0.05)

### 2017-07-23 Functions/PlotMap.R

@@ -1,5 +1,11 @@
-PlotMap <- function(df, ShapeData, variable = "LowUsePerc", title = "Map of Region", filtermap = TRUE){
-  
+PlotMap <- function(df, ShapeData = AG, variable = "LowUsePerc", title = "Map of Region", filtermap = TRUE){
+  # 
+  # df: The LAD dataframe
+  # ShapeData: The Shape file, defaults to AG becuase that is what I called the shape file for some reason
+  # variable = the variable to choose
+  # title: map title
+  # filtermap: whether teh shape file should be filtered to include only the the data being inputted or everything
+  #             It should only be set to FALSE if the shape file has been pre-filtered
   
   Singlevis <- ShapeData %>% 
     left_join(., df, by = c("lsoa11cd"="LSOA_CODE")) %>% 

### 2017-07-23 Functions/Shape2Adjmat.R

@@ -1,0 +1,16 @@
+Shape2Adjmat <- function(Shape, Nodename){
+  #Creates an adjacency matrix from a shape file
+  #Shape: the shape file
+  #Nodename: the attribute of the shape file you want to be the node names. defaults to the first type.
+  
+  if(is.null(Nodename)){
+    Nodename <- names(Shape)[1]
+  }
+  
+  row.names(Shape) <- as.character(Shape[[Nodename]])
+  nb <- poly2nb(Shape)
+  Shapemat <- nb2mat(nb, style="B", zero.policy = TRUE) #zero policy is for islands
+  colnames(Shapemat) <- rownames(Shapemat)
+  
+  return(Shapemat)
+}

### 2017-07-30 Average local prices.Rmd
Local prices tweak

@@
 source: http://geoportal.statistics.gov.uk/datasets/osni-open-data-largescale-boundaries-local-government-districts-2012
+
+#this uses rank I think it should be dist check this
 
@@
   left_join(LADprice, by = c("LAD11CD2"="Admin_district_code")) %>%
+  filter(LAD11CD=="E07000029")
+
+LocalMean <- NetworkDist %>% 
+  gather(key= "LAD11CD2", value = "distance", -LAD11CD) %>%
+  filter(LAD11CD %in% CombineAB$LAD11CD, distance <=3) %>%
+#join on the average prices per LAD
+  left_join(LADprice, by = c("LAD11CD2"="Admin_district_code")) %>%
   #find local mean
@@
   left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
-  mutate(priceRatio = (price/LocalMean)) #%>%
+  mutate(priceRatio = (price/LocalMean)) %>%
+  mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price>LocalMean ) #%>%
 #select(LAD11CD, LAD11NM, priceRatio, price, LocalMean, absdiff, Ttest.p.value, maxPerc, LUPdepExt)
+#remove barrow
+#filter(LAD11CD !="E07000027")
 
 test %>%
+  filter(maxPerc<10) %>%
   ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour = priceRatio>1)) + geom_jitter()
+
+test %>%
+  filter(maxPerc<10) %>%
+  ggplot(.,aes(x= Extent, y = LUPdepExt, colour = absdiff>0)) + geom_jitter()
+
+test2 <- test %>% 
+  select(LAD11NM, absdiff, LUPdepExt, Extent, LocalMean, price, priceRatio, maxPerc) %>%
+  mutate(LUPdepExt.Extent = LUPdepExt>Extent, price.LocalMean = price>LocalMean ) %>%
+  filter( price.LocalMean == FALSE)
+
+table(test$maxPerc>5, test$LUPdepExt.Extent>0, test$absdiff>0)
 
@@
 rpart.model1 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
-rpart.model2 <- rpart(as.factor(absdiff>0) ~ priceRatio+ maxPerc, test)
-rpart.model3 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc + priceRatio, test)
+rpart.model2 <- rpart(as.factor(absdiff>0) ~ LUPdepExt.Extent + maxPerc + priceRatio, test)
+rpart.model3 <- svm(as.factor(absdiff>0) ~ LUPdepExt+Extent + maxPerc + priceRatio, test, type = "C", kernel = "radial")
+rpart.model3 <- svm(as.factor(absdiff>0) ~ maxPerc + LUPdepExt+ Extent, test, type = "C", kernel = "radial")
 
@@
 
+test2 <- test[predict(rpart.model2, test, type = "class")!=as.factor(test$absdiff>0),]
+
 ```

### 2017-07-30 PaperCode.Rmd
Local prices tweak

@@
 Islington should be removed and put back in when they send the correct data, it is giving a false negative
+
+#this uses rank for distance from LAD I think it should be dist check this
 
@@
 #Wiltshire have not included everything
-# WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts.xlsx",
-#                                sheet=1)[1:4] %>%
-#   StructureData()
+WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts 2.xlsx",
+                               sheet=1)[1:4] %>%
+  StructureData(lowuse = 3:8)
 ```
@@
 
+BrecklandsDATA <- read_excel("BFOI-003031 BrecklandDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
+  StructureData()
+
+#they deleted the classes
+SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
+  StructureData()
+
 ```
@@
   StructureData()
+
+HuntingdonDATA <- read_excel("Huntingdonshire  FOI 568discounts.xlsx" , sheet=1)[1:4] %>%
+  StructureData(lowuse = 2:8)
+
+PeterboroughDATA <- read_excel("Peterborough 1707267585 completed.xlsx" , sheet=1)[1:4] %>%
+  StructureData(lowuse = c(4,6:7,11))
 
@@
 
+# HambletonDATA <- read_excel("HDC1088.xlsx")[,1:4] %>%
+#  StructureData()
+
+ScarboroughDATA <- read_excel("FOIA 5156 Scarborough Discounts LSOA.xlsx"  )[,1:4]%>%
+  StructureData(2:8)
+
 ```
@@
 setwd(file.path(RegionsComp, "Region North East"))
+list.files()
 #Not sure all are there ask for confirmation
@@
 #   StructureData(lowuse = c(2:4,6,8:10))
+
+NewcastleDATA <- read_excel("Newcastle upon TyneDiscountsLSOA.xlsx", sheet=1)%>% .[,c(1,3:5)] %>%
+    StructureData(lowuse = 2:7)
+
+#FOr some reason Gateshead has the wrong LAD11CD I don't know why. I have changed it to the right one but feel that perhaps I should check them all, but how?
+GatesheadDATA <- read_excel("Copy of GatesheadExemptionsLSOA.XLSX"   , sheet=1)%>% .[,1:4] %>%
+   StructureData(lowuse = c(2:3, 20,22:25)) %>%
+  mutate(LAD11CD = ifelse(is.na(LAD11CD), NA, "E08000037"))
+
+```
+
+##Durham
+```{r}
+  DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
+    StructureData()
+
+  HartlepoolData <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
+    StructureData(2:7)
 
@@
 #   StructureData(lowuse = c(3,5:6))
+
+#Conway have sen the wrong stuff  
+# ConwayDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
+#   rename(Postcode = geo_postcode) %>%
+#   mutate(Postcode = sub(" ", "", Postcode)) %>%
+#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
+#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
+#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
+#   StructureData()
 
@@
 
-#load full data
-BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")
-
-#Include only full price standard purchases
-BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")
-
-#Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
-BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")
+# #load full data
+# BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")
+# 
+# #Include only full price standard purchases
+# BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")
+# 
+# #Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
+# BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")
 
@@
 
-elementnames<- names(BootStrapRES)
+elementnames<- names(BootStrapRESExO)
 
@@
 
+```
+
+```{r}
+test <- BootStrapRESExO$ChelseaLON %>% 
+  group_by(class) %>%
+  summarise_all(funs(mean))
+
+test2 <- test %>%
+  select(-class) %>%
+  summarise_all(funs(sum)) %>%
+  mutate(LowUseValue = LowUseValue/1e9)
 ```
@@
 Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
-  geom_point()
+  geom_jitter()
 
 Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
-  geom_point()
+  geom_jitter()
 
@@
 test %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
-  geom_point()
+  geom_jitter()
 
@@
 #why do the two rforest models have such different results
-rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
+#rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
 rpart.model <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
@@
 
-```
-
-```{r}
-
-library(e1071)
- library(rpart)
- data(Glass, package="mlbench")
- ## split data into a train and test set
- index <- 1:nrow(Glass)
- testindex <- sample(index, trunc(length(index)/3))
- testset <- Glass[testindex,]
- trainset <- Glass[-testindex,]
-
-svm.model <- svm(Type ~ ., data = trainset, cost = 100, gamma = 1)
-svm.pred <- predict(svm.model, testset[,-10])
-
-rpart.model <- rpart(Type ~ ., data = trainset)
-rpart.pred <- predict(rpart.model, testset[,-10], type = "class")
-
-confusionMatrix( rpart.pred, testset$Type)
-confusionMatrix( svm.pred, testset$Type)
 ```

### 2017-08-15 Average local prices.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

@@
 
+Test on northern Ireland
 ```{r}
@@
 #Construct a distance network across all the LADs
+#dist now fixed!
 NetworkDist <- 1:length(V(g1)) %>% 
   map(~{
-  bfs(g1, root = .x, unreachable = FALSE, rank = TRUE, dist = TRUE)$rank %>%
+  bfs(g1, root = .x, unreachable = FALSE, rank = TRUE, dist = TRUE)$dist %>%
       as.matrix %>% t %>% as.data.frame
@@
 
+#three or less distance
 LocalMean <- NetworkDist %>% 
   gather(key= "LAD11CD2", value = "distance", -LAD11CD) %>%
-  filter(LAD11CD %in% CombineAB$LAD11CD, distance <=3) %>%
+  filter(LAD11CD %in% CombineAB$LAD11CD, distance <=4) %>%
 #join on the average prices per LAD
@@
   filter(!grepl("W", LAD11CD))%>%
-  select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent, LAD11CD) %>%
+  select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value,  LAD11CD) %>%
   mutate(outcome = LUPdepExt>Extent)  %>% 
@@
   mutate(priceRatio = (price/LocalMean)) %>%
-  mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price>LocalMean ) #%>%
+  mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price-LocalMean ) #%>%
 #select(LAD11CD, LAD11NM, priceRatio, price, LocalMean, absdiff, Ttest.p.value, maxPerc, LUPdepExt)
@@
 rpart.model1 <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
-rpart.model2 <- rpart(as.factor(absdiff>0) ~ LUPdepExt.Extent + maxPerc + priceRatio, test)
+rpart.model2 <- rpart(as.factor(absdiff>0) ~ LUPdepExt + maxPerc + priceRatio, test)
 rpart.model3 <- svm(as.factor(absdiff>0) ~ LUPdepExt+Extent + maxPerc + priceRatio, test, type = "C", kernel = "radial")

### 2017-08-15 CreateExcelTemplates.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

@@
 } else {
-  source(file.path(CommonCode, "PostcodeLookup.R"))
+  PstCdLSOA.raw  <- MatchPostCode2LSOA(file.path(basewd, "ONS postcodes May17", "Data", "CSV"),
+                        file.path(basewd, "ONS postcodes May17", "Doc") )
+  setwd(DataFolder)
+  saveRDS(PstCdLSOA.raw, "PstCdLSOA.rds")
 }
@@
 
-PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BA", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)] 
-PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BB", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)]
+PstCdLSOA[PstCdLSOA$Postcode=="DY44BA", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY40YX", c(3,4,7)] 
+PstCdLSOA[PstCdLSOA$Postcode=="DY44BB", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY40YX", c(3,4,7)]
 

### 2017-08-15 LowUseLondon.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

@@
             MeanPrice = first(MeanPrice),
-            WardLowUse = first(WardLowUse)) %>%
+            WardLowUse = first(WardLowUse),
+            WardPop = first(WardPop)) %>%
   group_by(LAD11NM) %>%
   summarise(totalLow = sum(MeanPrice*WardLowUse)/1e6,
-            TotalEmpt = sum(WardLowUse))
+            TotalEmpt = sum(WardLowUse),
+            TotalPop = sum(WardPop))
 
-sum(test$totalLow, na.rm = T)  
+#possible extra 8-14 billion more in the remaining boroughs anout 90b total
+#poss addition 7k LUPS about 80k total
+
+sum(test$totalLow, na.rm = T)*10^6/  
 sum(test$TotalEmpt, na.rm = T)  
+sum(test$TotalPop, na.rm = T)  
 length(unique(test$LAD11NM))
@@
 ```{r}
+
+test <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA, LambethLONDATA, SouthwarkLONDATA, HammersmithLONDATA,
+             WandsworthLONDDATA) %>%
+  bind_rows() %>%
+  PlotMap(.,
+          title = "Map of London with all current data")
 

### 2017-08-15 PaperCode.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

@@
 
+#ico complaint ref
+fs-506-897-47
+
 Should type B be included? or just type A?
+
+What's the Deal with Westminster?
+Westminsters Data is very low, I want to check what codes are going on.
+Westminster
+PCLB00: Second home class B/A
+PCLB50: 
+PCLC00: Empty and unfurnsished
+PCLC99: 
+PCLD00: Undergoing major repairs
+PCLJ50:
+Single:
+
+#Setup
 
@@
 Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
-```
-
-```{r}
 source(file.path(CommonCode, "AuxdataLoad.R"))
@@
 
+TorbayDATA <- read_excel("Torbay_discounts 1718551.xlsx"  , sheet=1)[1:4] %>%
+  StructureData()
+
+MidDevonDATA <- read_excel("MidDevon FOI04942Information 3.xlsx" , sheet=1)[1:4] %>%
+  StructureData(c(7,10:11,20:22,26,28))
+
+TorridgeDATA <- read_excel("FOI_TorridgeDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
+  StructureData(c(4:5,7:10,13))
+
 ```
@@
 
+MendipDATA <- read_excel("Mendip 356 20170706 Response.xlsx" , sheet=1)[1:4] %>%
+  StructureData(lowuse= c(37:39,52:54,65:66,69))
+
 ```
@@
 ```{r}
-BournemouthDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
+PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
   StructureData(lowuse = c(5,11:14,18))
@@
   StructureData(lowuse = c(6,12:17,20))
+
+WeymouthDATA <-  read_excel("63687 Weymouth and PortlandDiscountsLSOA - 010817.xlsx"    ,
+                               sheet=1)[1:4] %>%
+  StructureData()
+
+WestDorsetDATA <-  read_excel("47019 West DorsetDiscountsLSOA - 010817.xlsx"     ,
+                               sheet=1)[1:4] %>%
+  StructureData()
+
+PurbeckDATA <-  read_excel("PurbeckDiscountsLSOA - 010817.xlsx"      ,
+                               sheet=1)[1:4] %>%
+  StructureData()
 
@@
   StructureData(lowuse = 3:8)
+
+SwindonDATA <- read_excel("Swindon - 7th July 2017 - Part 2 (Discounts).xlsx" ,
+                               sheet=1)[1:4] %>%
+  StructureData(2:6)
 ```
@@
   StructureData()
+
+IpswichDATA <- read_xlsx("IpswichDiscountsLSOA.xlsx")[1:4] %>%
+   StructureData(c(2:4,6:11,13:15))
+
+#Mid Suffolk and Babergh
+#These have been combined and are just the postcodes so need to be fixed
+#Missing loads of postcodes
+MidSuffolkDATA <- read_excel("MidSuffolk FOI MF379 1718 Discount.xlsx") %>%
+mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
+ left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
+  StructureData(c(2:12,14:15))
+
+BaberghDATA <- read_excel("Babergh FOI BF378 1718 Discount.xlsx")%>%
+mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
+ left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
+  StructureData(c(2:6,8:11,13:15))
 
@@
   StructureData(lowuse = c(4,6:7,11))
+
+CambridgeDATA <- read_excel("566 - Copy of Copy of CambridgeDiscountsLSOA .xlsx" , sheet=1)[1:4] %>%
+  StructureData(2:5)
 
@@
 
+# Middlesbrough sent the wrong data
+# MiddlesbroughDATA <- read_excel( "Middlesbrough FOI RES - 011397 Discounts.xlsx"   )[,1:4]%>%
+#   StructureData()
+
+#Ryedale
+RyedaleDATA <-  read_excel("Ryedale FOI 4597.xlsx")[,1:4]%>%
+  StructureData(2:6)
+
+#Crave they sent full addresses by mistake I'll do a temporary fix
+CravenDATA <- read_excel("Craven Discounts.xlsx" ) %>%
+  setNames(make.names(names(.))) %>%
+  mutate(Postcode = str_split(Full.Property.Address, "(,)(?!.*,)", simplify = T)[,2] %>% 
+           gsub(" ", "", .)) %>%
+  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(Exemption.type=Discount.Type.Description, LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
+  StructureData(c(2:5,7))
+
+#Redcar and cleveland
+
+RedcarDATA <-  read_excel("Redcar 0614 attachment 1.xlsx")[,1:4]%>%
+  StructureData(2:10)
+
 ```
@@
 
+STynesideDATA <- read_excel("FOI 17.18456 - South Tyneside Discounts.xlsx", sheet=1)[,c(1,4:6)] %>%
+    StructureData(c(32:35,38))
+
+```
+
+##Northumberland
+
+```{r}
+NorthumberlandDATA <- read_excel("FOI 2762 data NorthumberlandDiscounts.xlsx", sheet=1)%>% .[,1:4] %>%
+    StructureData(2:7) %>%
+  #The LAD code is wrong for some reason
+  mutate(LAD11CD = "E06000057")
+
 ```
@@
 ```{r}
+
+DurhamDATA <- read_excel("County DurhamDiscountsLSOA.XLSX" , sheet=1) %>% .[,c(1,4:6)] %>%
+    StructureData()
+
   DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
@@
 
-  HartlepoolData <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
+  HartlepoolDATA <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
     StructureData(2:7)
@@
 
-#Conway have sen the wrong stuff  
-# ConwayDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
-#   rename(Postcode = geo_postcode) %>%
-#   mutate(Postcode = sub(" ", "", Postcode)) %>%
-#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
-#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
-#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
-#   StructureData()
+#It seems Conwy really is this short on the discounts  
+ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
+  rename(Postcode = geo_postcode) %>%
+  mutate(Postcode = sub(" ", "", Postcode)) %>%
+  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
+  StructureData(lowuse = c(2,4))
+
+DenbigshireDATA <- read_excel("FOI 2503 DenbighshireDiscountsLSOA.xlsx" , sheet=1)%>% .[,1:4] %>%
+    StructureData(8:9)
+
+WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
+    StructureData(2:5)
+
+#Pembrokeshire didn't send all the data
+PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
+    StructureData(3)
+
+FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
+    StructureData()
 
@@
   summarise(
-           TotalLads = length(unique(LAD11CD)),
+           TotalLads = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
            LowUse = sum(LowUse, na.rm = T),
@@
 
-z<- MakeLeaflet(CeredigionDATA)
+z<- MakeLeaflet(DurhamDATA)
 z
@@
 setwd(basewd)
- saveWidget(z, file=file.path(basewd, "CeredigionDATA.html"), selfcontained = TRUE )
+ saveWidget(z, file=file.path(basewd, "RBKC&Westminster.html"), selfcontained = TRUE )
 
@@
 ValueTtest(test)
+
+PlotMap(BexleyLONDATA)
+
+z <-ChelseaLONDATA %>% 
+  filter(LAD11CD =="E09000020") %>% 
+  bind_rows(WestminsterLONDATA) %>%
+  MakeLeaflet()
 
@@
 #Repeat excluding all the properties classed as other
-
+setwd(basewd)
 BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                          PropertyTypes = c("D", "S", "T", "F"))
-
-BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
-                                         PropertyTypes = c("D", "S", "T", "F"))
-
-BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
-                                         PropertyTypes = c("D", "S", "T", "F"))
+# 
+# BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
+#                                          PropertyTypes = c("D", "S", "T", "F"))
+# 
+# BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
+#                                          PropertyTypes = c("D", "S", "T", "F"))
 
@@
 ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~get(.x) %>%ncol))==4]
+
+#saveRDS(BootStrapRESExO, file = "BootStrapRESExO.rds")
 
@@
 
-#This is so cool, Also needs to be discussed in great detail, it is probablu due to the demolition and renovation of council housing
-Combine1 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()
-Combine2 %>% ggplot(.,aes(x= absdiff, y = Ttest.p.value)) + geom_point()
-
 ```
@@
 ```{r}
-test <- BootStrapRESExO$ChelseaLON %>% 
+test <- BootStrapRESExO$WestminsterLON%>% 
   group_by(class) %>%
@@
   mutate(LowUseValue = LowUseValue/1e9)
+
 ```
@@
 ```{r}
-
-BootStrapRES$CoLLON %>% PlotClassDiff()
-BootStrapRESExO$CoLLON %>% PlotClassDiff()
-BootStrapRESExOA$CoLLON %>% PlotClassDiff()
-BootStrapRESExOB$CoLLON %>% PlotClassDiff()
-
-HouseMatch <- data_frame(PropType = "D,S,T,F,O" %>% str_split(",") %>% unlist,
-type = "Detached,Semi-Detached,Terraced,Flats/Maisonettes,Other"%>% str_split(",") %>% unlist)
-
-test <- CoLLONDATA %>% SubsetPrice() %>% left_join(HouseMatch)
-testB <- CoLLONDATA %>% SubsetPrice("B") %>% left_join(HouseMatch)
-testA <- CoLLONDATA %>% SubsetPrice("A") %>% left_join(HouseMatch)
-
-table(test$type, test$class)
-table(testA$type, testA$class)
-table(testB$type, testB$class)
-
-CoLnums <- BootStrapRES$CoLLON %>% 
-  group_by(class) %>%
-  summarise_all(funs(mean(., na.rm = TRUE)))
-
-CoLnumsA <- BootStrapRESA$CoLLON %>% 
-  group_by(class) %>%
-  summarise_all(funs(mean(., na.rm = TRUE)))
 
@@
 
-sum(prices$X15 == "B")/nrow(prices)
-
-test <- ABratio4 %>% 
-  filter(LAD11CD %in% CurrentLADS)
-
-ABratio3 %>% ggplot(., aes(x = Valueratio)) +geom_density()
-
 CombineAB <- Combine1ExO %>% 
@@
   ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()
-
-CombineAB %>%
-  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Countratio>0.2)) + geom_point()
-
-CombineAB %>%
-  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = mean)) + geom_point()
 
@@
 
-#Look Kings Lynn and harrogate as they are strange results
-
-KingsLynnDep <- KingsLynnDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>% 
-  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))
-
-HarrogateDep <- HarrogateDATA %>% left_join(LSOADep, by = "LSOA_CODE") %>%
-  mutate(deprank = rank(Decile..where.1.is.most.deprived.10..of.LSOAs.))
-
 #creating the empty deprivation extent
@@
 
-test <- KingsLynnDep %>% 
-  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
-  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))
-
-test <- BromleyLONDATA %>% 
-  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
-  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))
-
-sum(test$WeightedLUP, na.rm = TRUE)
-
+#Create the extent of deprivation of the LUPs
 LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
@@
 
+```
+
+#Model
+
+```{r}
 LADprice <- prices %>%
@@
 
-test <- Combine1ExO2 %>%
+ModelMe <- Combine1ExO2 %>%
   left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
@@
   select(LAD, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent) %>%
-  mutate(outcome = LUPdepExt>Extent)
+  mutate(Reference = as.factor(absdiff>0) ) %>%
+  #scaled so that the binomial can be interpreted
+  mutate(pricepercent = scale(pricepercent),
+         LUPdepExt = scale(LUPdepExt),
+         maxPerc = scale(maxPerc))
 
-test %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
+#This uses the local mean so that has to be run first before the code works
+# ModelMe <- Combine1ExO2 %>%
+#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
+#   #filter out wales
+#   filter(!grepl("W", LAD11CD))%>%
+#   select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value,  LAD11CD) %>%
+#   mutate(outcome = LUPdepExt>Extent)  %>% 
+#   left_join(LocalMean, by = "LAD11CD") %>%
+#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
+#   mutate(priceRatio = (price/LocalMean)) %>%
+#   mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price-LocalMean ) %>%
+#   #make the Reference column properly
+#   mutate(Reference = as.factor(absdiff>0) ) %>%
+#   #scaled so that the binomial can be interpreted
+#   mutate(pricepercent = scale(pricepercent),
+#          LUPdepExt = scale(LUPdepExt),
+#          maxPerc = scale(maxPerc),
+#          priceRatio = scale(priceRatio))
+
+ModelMe %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
   geom_jitter()
 
-svm.model <- svm(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
-#why do the two rforest models have such different results
-#rpart.model <- randomForest(as.factor((absdiff>0))~ LUPdepExt+ maxPerc, test)
-rpart.model <- rpart(as.factor(absdiff>0) ~ LUPdepExt+ maxPerc, test)
+library(rpart)
+library(caret)
 
-confusionMatrix(predict(svm.model, test, type = class),as.factor(test$absdiff>0))
+#classification
+#three models
+svm.model <- svm(Reference~ pricepercent +LUPdepExt+ maxPerc, ModelMe)
+rpart.model <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, ModelMe)
+Binom <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, family=binomial(link='logit'),data=ModelMe)
 
-confusionMatrix( predict(rpart.model, test, type = "class"),as.factor(test$absdiff>0))
+linear.model <- lm(absdiff~ LUPdepExt + maxPerc+ pricepercent,data=ModelMe)
 
+confusionMatrix(predict(svm.model, ModelMe, type = "class"), ModelMe$Reference) %>% unlist
+confusionMatrix( predict(rpart.model, ModelMe, type = "class"), ModelMe$Reference)
+confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)
+
+predict(linear.model, ModelMe)
+summary(linear.model)
 ```
+
+##perform many mode resamples and plot the results
 
@@
 
-```
+set.seed(1983)
+test <- 1:1000 %>% map_df(~{
+TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
 
-Why are some areas with negative difference?
+rpart.model2 <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))
 
-The max percentage of low use is 5%
-There is the council estate renovation effect.
-All the areas are Urban
-Also check deprivation,
+Confmat <- confusionMatrix( predict(rpart.model2, as.data.frame(TestResample$test), type = "class"), as.data.frame(TestResample$test)$Reference)
 
-```{r}
+Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
 
-sum(Combine1$Ttest.p.value>0.5)/nrow(Combine1)
-sum(Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)/sum(Combine1$maxPerc>5)
+}
+)
 
-Combine1ExO[Combine1ExO$Ttest.p.value>0.5 & Combine1ExO$maxPerc>5,]
-Combine2ExO[Combine2ExO$Ttest.p.value>0.5 & Combine2ExO$maxPerc>5,]
-Combine3ExO[Combine3ExO$Ttest.p.value>0.5 & Combine3ExO$maxPerc>5,]
+test %>% ggplot(., aes(x= Accuracy)) +geom_density()
 
-table(Combine2$Ttest.p.value>0.5 & Combine2$maxPerc>5, Combine1$Ttest.p.value>0.5 & Combine1$maxPerc>5)
+test %>%
+  mutate(diff = Accuracy - AccuracyNull) %>% 
+  ggplot(., aes(x= diff)) +geom_density()
 
-LADAB <- ChelseaLONDATA%>% SubsetPrice
-  table(LADAB$X15, LADAB$class)
+t.test(test$Accuracy, test$AccuracyNull, alternative = "greater")
 
-Combine1 %>% ggplot(.,aes(x= abs(maxPerc), y = Ttest.p.value)) + geom_point()
+set.seed(1983)
+test2 <- 1:1000 %>% map_df(~{
+  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
 
-#P.value is low if diff perc is over 5%
-#Both southwark and Tower of london have concil flat renovation?
-#Southwark the Aylesbury estate is being redeveloped making emptyness much higher than expected
-#The blackwall an cubitt are being redevleoped with the blackwall reach, some housing is empty others are still occupied demolishin has not occured
-Combine1 %>% ggplot(.,aes(x= diffPerc, y = Ttest.p.value)) + geom_point()
+  model <- svm(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))
 
-Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
-  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")
+  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "class"),
+                              as.data.frame(TestResample$test)$Reference)
 
-Combine2 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value)) + geom_point() +
-  labs(title = "Comparing tatistical Significance of LUPs being more expensive than RHs and the maximum concentration of LUPs in a ")
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
 
-#Boring doesn't show anything interesting
-Combine1 %>% ggplot(.,aes(x= p.value.x, y = Ttest.p.value, colour =diffPerc>5 )) + geom_point()
+}
+)
 
-Combine1 %>% ggplot(.,aes(x= maxPerc, y = Ttest.p.value, colour =absdiff>0 )) + geom_point()
+test2 %>% ggplot(., aes(x= Accuracy)) +geom_density()
 
-test <- Combine1 %>%
-  select(LAD,p.value.x, Ttest.p.value, absdiff , maxPerc, minPerc,diffPerc, skew)
+test2 %>%
+  mutate(diff = Accuracy - AccuracyNull) %>% 
+  ggplot(., aes(x= diff)) +geom_density()
 
-Combine1 %>% ggplot(.,aes(x= skew, y= Ttest.p.value)) + geom_point()
+t.test(test2$Accuracy, test2$AccuracyNull, alternative = "greater")
+
+#binom
+
+set.seed(1983)
+test3 <- 1:1000 %>% map_df(~{
+  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
+
+  model <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, 
+               family=binomial(link='logit'),
+               as.data.frame(TestResample$train))
+
+  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
+                              as.data.frame(TestResample$test)$Reference)
+
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
+          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
+
+}
+)
+
+test3 %>% ggplot(., aes(x= Accuracy)) +geom_density()
+
+test3 %>%
+  mutate(diff = Accuracy - AccuracyNull) %>% 
+  ggplot(., aes(x= diff)) +geom_density()
+
+t.test(test3$Accuracy, test3$AccuracyNull, alternative = "greater")
+
+# 
+# set.seed(1983)
+# test4 <- 1:1000 %>% map_df(~{
+#   TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
+# 
+#   model <- glm(Reference~ LUPdepExt + maxPerc+ priceRatio, 
+#                family=binomial(link='logit'),
+#                as.data.frame(TestResample$train))
+# 
+#   Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
+#                               as.data.frame(TestResample$test)$Reference) 
+# 
+#   Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+#           Confmat$byClass %>% as.matrix %>%t %>% data.frame,
+#           coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
+#   mutate(ID = .x)
+# 
+# }
+# )
+# 
+# test4 %>% ggplot(., aes(x= Accuracy)) +geom_density()
+# 
+# test4 %>%
+#   mutate(diff = Accuracy - AccuracyNull) %>% 
+#   ggplot(., aes(x= diff)) +geom_density()
+# 
+# t.test(test4$Accuracy, test4$AccuracyNull, alternative = "greater")
+# 
+# 
+# t.test(test3$Accuracy- test3$AccuracyNull, test4$Accuracy - test4$AccuracyNull, alternative = "greater")
 
 ```
-
-```{r}
-test <- Combine1 %>% filter(Ttest.p.value>0.05)
-```

### 2017-08-15 testCode.Rmd
New postcodes
New postcodes have been included to make the LSOA matching better.

Also loads more local regions have been added and modelling of the negative positive split.

---
title: "Untitled"
author: "Jonathan Bourne"
date: "10 August 2017"
output: html_document
---

```{r}

CalcLowUse<- function(df){ 
  df %>%
  select(LSOA_CODE, LowUse) %>%
        left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
        group_by(Admin_ward_code)  %>%
        mutate(LowUsePerc = round(LowUse/Homes *100), 
               WardLowUse = sum(LowUse) ,
               WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
        ungroup %>% 
        left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
        mutate(ValLow = LowUse*MeanPrice,
               LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
                                 labels =  c("0-10","11-20","21-30", "30+")),
               WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
                                     labels = c("0-10","11-20","21-30", "30+")) )
}

test <- ChelseaLONDATA

test <- ls(pattern = "LON") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

z<- MakeLeaflet(test)

test <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA) %>%
  map_df(~.x) %>%   
  group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

z<- MakeLeaflet(test)

z

```

https://voaratinglists.blob.core.windows.net/html/rlidata.htm

```{r}

setwd(file.path(basewd,"VOA data"))

file2load <-"uk-englandwales-ndr-2017-summaryvaluations-compiled-epoch-0002-baseline-csv.csv"

test0<- read_lines(file2load, n_max=10)

test <- read_delim(file2load, delim = "*", col_names = F)

test2 <- test$`Offices And Premises` %>% table %>% as.data.frame

g1 <- test %>% filter(X1=="01")
g2 <- test %>% filter(X1=="02")

test3 <- g1$X5 %>% table %>% as.data.frame
test4 <- g2$X4 %>% table %>% as.data.frame

```

```{r}
  file2load2 <- "uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv"
test0<- read_lines(file2load2, n_max=10)

CorePstCd <- PstCdLSOA.raw %>%
  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
  select(Postcode, lsoa11cd, LAD11CD, LAD11NM, Admin_ward_code, WD16NM)

CompanyData <- read_delim(file2load2, delim = "*", col_names = F) %>%
  mutate(X15 = gsub(" ", "", X15)) %>%
  left_join(., CorePstCd, by = c("X15" = "Postcode"))

LSOABiz <- CompanyData %>%
  filter(!is.na(LAD11CD)) %>%
  mutate(X6 = gsub("( AND PREMISES)|( & PREMISES)", "",X6),
         X6 = gsub("(AND PREMISES)|(& PREMISES)", "",X6)) %>%
  group_by(lsoa11cd, X6) %>%
  summarise(counts = n(),
            LAD11CD = first(LAD11CD),
            LAD11NM = first(LAD11NM),
            Admin_ward_code = first(Admin_ward_code),
            WD16NM = first(WD16NM))

FirmCounts <- LSOABiz %>%
  group_by(X6) %>%
  summarise(counts = n()) %>%
  arrange(-counts)

Dom <- FirmCounts %>%
  filter(grepl("DOMESTIC",X6))

HOLS <- FirmCounts %>%
  filter(grepl("HOLIDAY",X6))

Catering <- FirmCounts %>%
  filter(grepl("SELF CATER",X6))

```

Look at Westminster

```{r}

West <- LSOABiz %>%
  filter(LAD11CD=="E09000033")

Catering <- West %>%
  filter(grepl("SELF CATER",X6))

test <- list(HammersmithLONDATA, WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA, LambethLONDATA) %>% 
  map_df(~.x) %>%
  group_by(LAD11CD) %>%
  summarise(
    LAD11NM =first(LAD11NM),
    LowUse = sum(LowUse, na.rm= T),
    Homes = sum(Homes, na.rm= T),
    Pop = sum(Pop, na.rm= T)
            ) %>%
  filter(Homes >2000) %>%
  mutate(LowUseH = LowUse/Homes,
         LowUseP = LowUse/Pop)

```

### 2017-08-15 Functions/SubsetPrice.R

@@ -9,7 +9,7 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, PriceCuts = NULL)
     Code <- df
   } else{
     #Som LADS have bits of other LADS mixed in this removes those
-    Code <- df$LAD11CD[which.max(table(df$LAD11CD) %>% as.matrix)] 
+    Code <- names(table(df$LAD11CD))[which.max(table(df$LAD11CD) %>% as.matrix)] 
   }
   
   if(!is.null(type)){

### 2017-08-15 SubCode/AuxdataLoad.R

@@ -30,7 +30,10 @@ shape <- readOGR(dsn = list.files(pattern = "shp"))
 if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
 PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
 } else {
-source(file.path(CommonCode, "PostcodeLookup.R"))
+  PstCdLSOA.raw  <- MatchPostCode2LSOA(file.path(basewd, "ONS postcodes May17", "Data", "CSV"),
+                        file.path(basewd, "ONS postcodes May17", "Doc") )
+  setwd(DataFolder)
+  saveRDS(PstCdLSOA.raw, "PstCdLSOA.rds")
 }
 
 

### 2017-08-15 SubCode/LondonFullProcesss.R

@@ -100,15 +100,46 @@ RedbridgeLONDATA <- read_excel("RedbridgeDiscountsLSOA.XLSX" )[1:4]  %>%
   StructureData
 
 #Brent
-#Brent data only inlcudes 2nd homes, but they struggled with understanding the request will try again when data consistancy becomes more important or I get help from f.eks mayors office.
 
-BrentLONDATA <- read_excel("Brent Second homes and post codes.xlsx", col_names = FALSE) %>% 
-  left_join(., PstCdLSOA.raw,  by=c("X__2"="Postcode") ) %>%
+BrentLONDATA <- read_excel("FOI  6900196 Brent empty domestic properties.xlsx", col_names = TRUE)[,c(1,5)] %>%
+  setNames(c("X__1", "Postcode")) %>%
+  mutate(Postcode = gsub(" ", "", Postcode)) %>%
+  left_join(., PstCdLSOA.raw,  by="Postcode" ) %>%
   rename(Exemption.type=X__1, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, X__2, Country_code) %>%
-  StructureData()
+  select(Exemption.type, LSOA_CODE, Admin_ward_code, Country_code) %>%
+  StructureData(c(2,15:19))
 
 #Hammersmith and fulham
 
 HammersmithLONDATA <- read_excel("Hammersmith and FulhamExemptionsLSOA.xls"  )[1:4] %>%
   StructureData(lowuse = 19:23)
+
+#Waltham Forest
+WalthamforestLONDATA <- read_excel("J Bourne Waltham ForestDiscountsLSOA 8.8.17.xlsx")[1:4] %>%
+  StructureData(c(3:7))
+
+
+#Westminster
+#Holy SHIT!
+
+#They sent it in the wrong format becuase they are annoying
+LSOA2LSOA <- PstCdLSOA.raw %>% group_by(lsoa11cd) %>%
+  summarise(LSOA = first(lsoa11nm)) %>%
+  ungroup %>%
+  rename(LSOA_CODE = lsoa11cd)
+
+#They have missed something out
+WestminsterLONDATA <- read_excel("Westminster 3123133  data Aug 2017.xlsx")[2:5] %>%
+  left_join(., LSOA2LSOA, by = "LSOA") %>%
+  select(1,5,3,4) %>%
+  StructureData(2:7)
+
[…]

### 2017-08-15 SubCode/Setup.R

@@ -2,7 +2,7 @@
 
 
 packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
-              "forcats", "e1071", "htmlwidgets")
+              "forcats", "e1071", "htmlwidgets", "stringr", "modelr")
 
 new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
 if(length(new.packages)) install.packages(new.packages)
@@ -19,8 +19,8 @@ ShapeFiles <- file.path(basewd,"ShapeFiles/statistical-gis-boundaries-london/ESR
 Figures <- file.path(basewd, "Figures")
 PostcodeLookups <- file.path(DataFolder, "PostcodeLookups")
 ExcelLookups <- file.path(basewd, "ExcelLookups")
-ONSpostcodes <- file.path(basewd, "ONS postcodes", "CSV")
-ONSpostcodeMeta <- file.path(basewd, "ONS postcodes", "Doc")
+ONSpostcodes <- file.path(basewd, "ONS postcodes May17", "Data", "CSV")
+ONSpostcodeMeta <- file.path(basewd, "ONS postcodes May17", "Doc")
 LSOAshapedata <- file.path(basewd,"ShapeFiles",
                            "Lower_Layer_Super_Output_Areas_December_2011_Generalised_Clipped__Boundaries_in_England_and_Wales")
 AddGeog <- file.path(basewd, "AdditionalGeographies")

### 2017-08-21 PaperCode.Rmd
upgrade
Code clean up and also, modelling to allow the whole of England to be predicted.

@@
   StructureData(.)
+
+AllerdaleCUMBRIADATA <- read_excel("F17.132_Copy of Allerdale discounts LSOA_170815.xlsx"  , sheet=1)[1:4] %>%  
+  StructureData(c(4:10))
 
@@
   StructureData(lowuse= c(37:39,52:54,65:66,69))
+
+#Bristol appears to have not included second homes
+#BristolDATA <- read_excel("Bristol%2c City ofDiscountsLSOA_as at 110817.xlsx")[c(1:4)] %>%
+#  StructureData()
 
@@
 
+CalderdaleDATA <- read_excel("Copy of CalderdaleDiscountsLSOA.xlsx" )[,1:4]%>%
+  StructureData(c(7,10,22:25))
+
+BradfordDATA <- read_excel("Copy of BradfordDiscountsLSOA.xlsx")[1:4] %>%
+  StructureData(c(2:7))
+
+RichmondshireDATA <- read_excel("Richmondshire FOI 4960.xls", col_names = FALSE)[1:2] %>%
+    setNames(c("Exemption.type", "Postcode")) %>%
+  mutate(Postcode = sub(" ", "", Postcode)) %>%
+  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
+  StructureData(lowuse = c(2:7))
+
 ```
@@
 #Not sure all are there ask for confirmation
-# SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
-#   StructureData(lowuse = c(2:4,6,8:10))
+ SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
+   StructureData(lowuse = c(2:4,6,8:10))
 
@@
 
+HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
+  rename(DiscClass = X__1) %>%
+  select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
+  gather(key = "ward", value = "counts", -DiscClass) %>%
+  spread(key= DiscClass, value = counts, fill = 0) %>%
+  mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
+  bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
+  SemiDataStructure
+
 ```
@@
 
-z<- MakeLeaflet(DurhamDATA)
+z<- MakeLeaflet(AllerdaleDATA)
 z
@@
 setwd(basewd)
- saveWidget(z, file=file.path(basewd, "RBKC&Westminster.html"), selfcontained = TRUE )
+ saveWidget(z, file=file.path(basewd, "Cumbria.html"), selfcontained = TRUE )
 
@@
   MakeLeaflet()
+
+BradfordDATA %>% filter(LAD11NM=="Bradford") %>%
+  MakeLeaflet
 
@@
 
-#ExO excluding Other
-#A only A type sales
-#B only Btype sales
-
-# #load full data
-# BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")
-# 
-# #Include only full price standard purchases
-# BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")
-# 
-# #Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
-# BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")
-
-#Repeat excluding all the properties classed as other
-setwd(basewd)
 BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                          PropertyTypes = c("D", "S", "T", "F"))
-# 
-# BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
-#                                          PropertyTypes = c("D", "S", "T", "F"))
-# 
-# BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
-#                                          PropertyTypes = c("D", "S", "T", "F"))
 
@@
 
-ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~get(.x) %>%ncol))==4]
-
-#saveRDS(BootStrapRESExO, file = "BootStrapRESExO.rds")
-
+#Make a summary dataframe
+Combine1ExO <- BootResSummaryData(BootStrapRESExO) 
 ```
@@
 #Analyse Boostrap
-
-land registry 
-sue gambles
-
-```{r}
-
-#gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
-CurrentLADS <- ls(pattern = "DATA") %>%
-  map_chr(~{df<- get(.x)
-  df <- df %>%
-  group_by(LAD11CD) %>%
-  summarise(count = n())
-df$LAD11CD[which.max(df$count)]}
-)
-
-#check any that are accidently not processed
-ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~.x %>% get %>% ncol))<10]
-
-Combine1 <- BootResSummaryData(BootStrapRES) %>% mutate(LAD11CD = CurrentLADS)
-
-Combine2 <- BootResSummaryData(BootStrapRESA) %>% mutate(LAD11CD = CurrentLADS)
-
-Combine3 <- BootResSummaryData(BootStrapRESB) %>% mutate(LAD11CD = CurrentLADS)
-
-#Excluding Other
-Combine1ExO <- BootResSummaryData(BootStrapRESExO) %>% mutate(LAD11CD = CurrentLADS)
-
-Combine2ExO <- BootResSummaryData(BootStrapRESExOA) %>% mutate(LAD11CD = CurrentLADS)
-
-Combine3ExO <- BootResSummaryData(BootStrapRESExOB) %>% mutate(LAD11CD = CurrentLADS)
-
-```
 
@@
 
+#calulcate the number of properties sold and the mean price
 ABratio <- prices %>% 
@@
 spread(key = X15, value = count) %>%
-  mutate(Countratio = B/(A+B))
+  mutate(Countratio = B/(A+B)) %>%
+  rename(CountofA = A, CountofB = B)
 
@@
 spread(key = X15, value = mean) %>%
-  mutate(Valueratio = B/(A))
+  mutate(Valueratio = B/(A)) %>%
+  rename(MeanofA= A, MeanofB = B)
 
-ABratio4 <-  left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
-  left_join(LADNMs) %>%
-  left_join(prices %>% 
-  group_by(Admin_district_code) %>%
-summarise(mean = mean(X2)) %>%
-  rename(LAD11CD = Admin_district_code))
+CombineAB <-left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
+  left_join(Combine1ExO, ., by = "LAD11CD")
 
-CombineAB <- Combine1ExO %>% 
-  left_join(ABratio4, by = "LAD11CD")
+rm(ABratio); rm(ABratio2); rm(ABratio3)
 
@@
 ```{r}
-setwd(file.path(basewd, "Deprivation"))
-list.files()
-LADDep<-read_excel("File_10_ID2015_Local_Authority_District_Summaries.xlsx", sheet = 2) %>%
-  setNames(make.names(names(.)) %>% gsub("IMD...", "",.) %>% trimws ) %>%
-  rename(LAD11CD = Local.Authority.District.code..2013.)
-
-LSOADomDep<-read_excel("File_2_ID_2015_Domains_of_deprivation.xlsx" , sheet = 2) %>%
-  setNames(make.names(names(.))) %>%
-  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
-  rename(LAD11CD = Local.Authority.District.code..2013.)
-
-LSOADep<-read_excel("File_1_ID_2015_Index_of_Multiple_Deprivation.xlsx", sheet = 2) %>%
-  setNames(make.names(names(.))) %>%
-  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
-  rename(LAD11CD = Local.Authority.District.code..2013.,
-         LSOA_CODE = LSOA.code..2011.)
-
-CombineAB <- CombineAB %>% left_join(LADDep, by = "LAD11CD")
-
-CombineAB %>%
-  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, color =Rank.of.extent<100)) + geom_jitter()
 
@@
 
-Combine1ExO2 <- CombineAB%>%
+#Add in deprivation
+Combine1ExO <- select(LADDep, LAD11CD ,Extent) %>% 
+  left_join(CombineAB, ., by = "LAD11CD") %>%
   mutate(LUPdepExt)
 
-Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
+Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
   geom_jitter()
 
-Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
+Combine1ExO %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
   geom_jitter()
@@
 summarise(price = mean(X2)) %>%
-  mutate(meandiff = price-mean(price),
-         pricepercent = percent_rank(price))
+  mutate(pricepercent = percent_rank(price))
 
-ModelMe <- Combine1ExO2 %>%
+ModelMe <- Combine1ExO %>%
   left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
+  left_join(Vacants, by = "LAD11CD") %>%
+  mutate(VacantsPerc = Vacants/Homes,
+         LTVPerc = Vacants/Homes) %>%
   #filter out wales
-  filter(!grepl("W", LAD11CD))%>%
-  select(LAD, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent) %>%
+  filter(!grepl("W", LAD11CD)) %>%
+#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
   mutate(Reference = as.factor(absdiff>0) ) %>%
@@
 
-library(rpart)
-library(caret)
+rowsum(.)>5 ~TRUE
+#classification
 
-#classification
-#three models
-svm.model <- svm(Reference~ pricepercent +LUPdepExt+ maxPerc, ModelMe)
-rpart.model <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, ModelMe)
-Binom <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, family=binomial(link='logit'),data=ModelMe)
+#LUPdepExt and Pricepercent are the only useful ones really
+Binom <- glm(Reference~ LUPdepExt +LADPerc +maxPerc+ mean.y, family=binomial(link='logit'),data=ModelMe)
 
-linear.model <- lm(absdiff~ LUPdepExt + maxPerc+ pricepercent,data=ModelMe)
+Binom <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
 
-confusionMatrix(predict(svm.model, ModelMe, type = "class"), ModelMe$Reference) %>% unlist
-confusionMatrix( predict(rpart.model, ModelMe, type = "class"), ModelMe$Reference)
 confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)
 
-predict(linear.model, ModelMe)
-summary(linear.model)
+test <- lm(Percdiff ~ LUPdepExt +LADPerc +maxPerc+ mean.y, data = ModelMe)
+
+summary(test)
+
+summary(Binom)
+
+coef(Binom) %>% as.data.frame
 ```
@@
 
-set.seed(1983)
-test <- 1:1000 %>% map_df(~{
-TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
-
-rpart.model2 <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))
-
-Confmat <- confusionMatrix( predict(rpart.model2, as.data.frame(TestResample$test), type = "class"), as.data.frame(TestResample$test)$Reference)
-
-Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
-
-}
-)
-
-test %>% ggplot(., aes(x= Accuracy)) +geom_density()
-
-test %>%
-  mutate(diff = Accuracy - AccuracyNull) %>% 
-  ggplot(., aes(x= diff)) +geom_density()
-
-t.test(test$Accuracy, test$AccuracyNull, alternative = "greater")
-
-set.seed(1983)
-test2 <- 1:1000 %>% map_df(~{
-  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
-
-  model <- svm(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))
-
-  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "class"),
-                              as.data.frame(TestResample$test)$Reference)
-
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
-
-}
-)
-
-test2 %>% ggplot(., aes(x= Accuracy)) +geom_density()
-
-test2 %>%
-  mutate(diff = Accuracy - AccuracyNull) %>% 
-  ggplot(., aes(x= diff)) +geom_density()
-
-t.test(test2$Accuracy, test2$AccuracyNull, alternative = "greater")
-
 #binom
@@
 set.seed(1983)
-test3 <- 1:1000 %>% map_df(~{
+ModelStats <- 1:1000 %>% map_df(~{
   TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
 
-  model <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, 
+  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
                family=binomial(link='logit'),
@@
 
-test3 %>% ggplot(., aes(x= Accuracy)) +geom_density()
+ModelStats %>% ggplot(., aes(x= Accuracy)) +geom_density()
 
-test3 %>%
+ModelStats %>%
   mutate(diff = Accuracy - AccuracyNull) %>% 
@@
 
-t.test(test3$Accuracy, test3$AccuracyNull, alternative = "greater")
+ModelStats %>% ggplot(., aes(x= AccuracyPValue)) +geom_density()
+ModelStats %>% ggplot(., aes(x= Kappa)) +geom_density()
 
-# 
-# set.seed(1983)
-# test4 <- 1:1000 %>% map_df(~{
-#   TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
-# 
-#   model <- glm(Reference~ LUPdepExt + maxPerc+ priceRatio, 
-#                family=binomial(link='logit'),
-#                as.data.frame(TestResample$train))
-# 
-#   Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
-#                               as.data.frame(TestResample$test)$Reference) 
-# 
-#   Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-#           Confmat$byClass %>% as.matrix %>%t %>% data.frame,
-#           coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
-#   mutate(ID = .x)
-# 
-# }
-# )
-# 
-# test4 %>% ggplot(., aes(x= Accuracy)) +geom_density()
-# 
-# test4 %>%
-#   mutate(diff = Accuracy - AccuracyNull) %>% 
-#   ggplot(., aes(x= diff)) +geom_density()
-# 
-# t.test(test4$Accuracy, test4$AccuracyNull, alternative = "greater")
-# 
-# 
-# t.test(test3$Accuracy- test3$AccuracyNull, test4$Accuracy - test4$AccuracyNull, alternative = "greater")
+t.test(ModelStats$Accuracy, ModelStats$AccuracyNull, alternative = "greater")
+
+test <- ModelStats %>% 
+  select( X.Intercept., LUPdepExt, maxPerc, pricepercent) %>%
+  gather
+
+test %>% ggplot(.,aes(x = key, y = value, fill = key)) + geom_boxplot() + 
+  labs(title = "Direction each variable pushes the outcome")
+
+test %>% ggplot(.,aes(x = value, fill = key)) + geom_density( alpha = 0.5)
 
 ```
+
+```{r}
+set.seed(1983)
+ModelStats2 <- 1:1000 %>% map_df(~{
+  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
+
+  model <- glm(Reference~ Extent + price + VacantsPerc, 
+               family=binomial(link='logit'),
+               as.data.frame(TestResample$train))
+
+  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
+                              as.data.frame(TestResample$test)$Reference)
+
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
+          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
+
+}
+)
+
+set.seed(1983)
+ModelStats3 <- 1:1000 %>% map_df(~{
+  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
+
+  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
+               family=binomial(link='logit'),
+               as.data.frame(TestResample$train))
+
+  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
+                              as.data.frame(TestResample$test)$Reference)
+
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
+          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
+
+}
+)
+
+Outcome <- bind_rows(data_frame(model = "generic", Accuracy = ModelStats2$Accuracy), 
+data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )
+
+Outcome %>%
+  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3)
+
+#The model that uses easily available data is 3% less accurate than the other model.
+t.test(ModelStats2$Accuracy, ModelStats1$Accuracy)
+
+cor(ModelMe$Vacants, ModelMe$VacantsPerc)
+
+cor(ModelMe$Vacants, ModelMe$LTV)
+cor(ModelMe$VacantsPerc, ModelMe$LTVPerc)
+
+```
+
+interpreting the coefficients of the model shows us that there is a natural tendency for LUPs to be more expensive than regular housing, the probability of them being more expensive increases if the local authority is already expensive compared to the rest of the local authorities.
+In addition the greater the maximum concentration of LUPs also increase the probability of them being more expensive than regular housing.
+However if the LUPs are generally in deprived areas then the probability of them being more expensive than regular housing decreases.
+
+Using the models produced in the previous section I can now predict areas where primary purchases are being out competed across the England
+
+```{r}
+
+set.seed(1983)
+MultiCheck <- 1:21 %>% map(~{
+  TestResample <- resample_bootstrap(ModelMe)
+
+  model <- glm(Reference~ Extent + price + VacantsPerc, 
+               family=binomial(link='logit'),
+               as.data.frame(TestResample))
+
+  data_frame(x = predict(model, ModelMe, type = "response")>0.5) %>%
+    setNames(paste("Model", .x, sep="_"))
+}
+) %>% bind_cols() %>% mutate(
+  Outcome = case_when(
+  rowSums(.)>ncol(.)/2 ~TRUE,
+  rowSums(.)<=ncol(.)/2 ~FALSE
+))
+
+test <- ModelMe %>%
+  bind_cols(., select(MultiCheck, Outcome)) %>%
+  mutate(Correct = Reference == Outcome) %>%
+  filter(!Correct) %>%
+  select(LAD, Reference, Outcome)
+
+confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)
+
+BinomSimp <- glm(Reference~ price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
+
+BinomExtent <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
+rpartExtent <- rpart(Reference~ Extent + price + VacantsPerc,data=ModelMe)
+
+confusionMatrix(predict(BinomSimp, ModelMe, type = "response")>0.5 , ModelMe$Reference)
+
+confusionMatrix((predict(BinomExtent, ModelMe, type = "response")>0.5) , ModelMe$Reference)
+confusionMatrix(predict(rpartExtent, ModelMe, type = "prob")[,2] , ModelMe$Reference)
+
+LadHomes <-  EW2 %>%
+  group_by(LAD11CD) %>%
+  summarise(Homes = sum(Homes, na.rm = TRUE),
+            Pop = sum(Pop, na.rm = TRUE))
+
+tol <- 0
+
+#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
+EnglandComp <- LADDep %>% 
+  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
+  left_join(., Vacants, by = "LAD11CD") %>%
+  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
+  left_join( LadHomes, by = "LAD11CD") %>%
+  mutate(VacantsPerc = Vacants/Homes) %>%
+  mutate(Significant.Competition = predict(BinomExtent, ., type = "response")) %>%
+  mutate(Comp.Type = case_when(
+    .$Significant.Competition<0.5-tol ~"No",
+    .$Significant.Competition>0.5 + tol ~"Yes",
+    .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
+  ))
+
+EnglandComp %>%
+  ggplot(aes(x = Comp.Type, y= price, fill = Comp.Type)) + geom_boxplot()
+
+EnglandComp %>%
+  group_by(Comp.Type) %>%
+  summarise(mean = mean(price),
+            median = median(price),
+            Homes = sum(Homes),
+            Pop = sum(Pop)) %>%
+  mutate(HomesPerc = Homes/sum(Homes),
+         PopPerc = Pop/sum(Pop))
+
+```
+
+```{r}
+
+test <-ls(pattern = "DATA") %>%
+  map_df(~get(.x) %>%
+           group_by(LAD11CD) %>%
+           mutate(LowUsePercentile = percent_rank(LowUsePerc),
+                  MeanPricePercentile = percent_rank(MeanPrice)))
+
+cor(test$LowUsePerc,test$MeanPrice,"complete.obs")
+cor(test$LowUsePerc,test$MedianPrice, "complete.obs")
+
+cor(test$LowUsePercentile,test$MeanPricePercentile , "complete.obs")
+
+test %>%
+  ggplot(aes(x= LowUsePercentile, y = MeanPricePercentile)) +geom_point()
+
+test <-ls(pattern = "DATA") %>%
+  map_dbl(~{ df <-get(.x)
+    cor(df$LowUsePerc,df$MeanPrice,"complete.obs", method = "kendall")
+  })
+
+  plot(density(abs(test)))
+
+  Combine1ExO %>%
+    ggplot(., aes(x = absdiff>0 )) +geom_bar()
+
+```

### 2017-08-21 allEnglandMap.Rmd
upgrade
Code clean up and also, modelling to allow the whole of England to be predicted.

---
title: "Untitled"
author: "Jonathan Bourne"
date: "20 August 2017"
output: html_document
---

```{r}

if(file.exists(file.path(DataFolder,"LADShape.rds"))){
LADShape<- readRDS(file.path(DataFolder,"LADShape.rds"))
} else{
setwd(file.path(basewd,"ShapeFiles", "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain"))

ladshape <- readOGR(dsn = list.files(pattern = "shp"))

LADShape <- fortify(ladshape, region = "objectid")

LADShape <- LADShape %>% mutate(id = as.integer(id)) %>% 
left_join(., ladshape@data, by = c("id" = "objectid")) #%>% 
#left_join(., EW2, by = c("lsoa11cd" = "ECODE"))

saveRDS(LADShape, file.path(DataFolder,"LADShape.rds"))
}

```

```{r}

LADShape <- LADShape %>%
  filter(grepl("E",lad14cd))

LADShape2 <- LADShape %>% left_join(EnglandComp, by = c("lad14cd" = "LAD11CD"))

```

```{r}
  #These two functions are necessary for Points to polygons
  get.grpPoly <- function(group,ID,df) {
    Polygon(coordinates(df[df$id==ID & df$group==group,]))
  }
  get.spPoly  <- function(ID,df) {
    Polygons(lapply(unique(df[df$id==ID,]$group),get.grpPoly,ID,df),ID)
  }

  #this function is necessary for the rest of the function
  points2polygons <- function(df,data) {
    spPolygons  <- SpatialPolygons(lapply(unique(df$id),get.spPoly,df))
    SpatialPolygonsDataFrame(spPolygons,match.ID=T,data=data)
  }

   MyData <- LADShape2 %>% #filter(AG$LAD11CD %in%  unique(dataframe$LAD11CD) ) %>%
    rename(LAD11CD = lad14cd)

  MyData <- SpatialPointsDataFrame(coords =MyData[,c(1,2)], data = MyData,
                                   proj4string = CRS('+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs'))
  MyData <- spTransform(MyData, CRS("+init=epsg:4326"))
  #random thing
  stuff <-data.frame(LAD11CD=unique(MyData$LAD11CD),row.names=unique(MyData$id))

  MyData<- points2polygons(MyData,stuff)

  #AG2 <- AG %>% group_by(LSOA_CODE) %>% summarise_all(funs(first))

  MyData <- EnglandComp %>%
    select(LAD11CD, Significant.Competition, LAD11NM, Comp.Type) %>%
    merge(MyData, .)

  class(MyData) # data.frame

  v<-"pk.eyJ1Ijoiam9ubm9iIiwiYSI6ImNqM2FlNXhpbDAwM3gzMW83ZW1hbHI0bzYifQ.4AfaY0Un0bKU41hZscpy9Q"

  m <- leaflet(MyData) %>%
    #addTiles()
    addProviderTiles("MapBox", options = providerTileOptions(
      id = "mapbox.light",
      accessToken = v))

  pal <- colorFactor("Accent", domain = MyData$Comp.Type)

  labels <- sprintf(
    "<strong>%s</strong><br/>Market affected %s",
    MyData$LAD11NM, MyData$Comp.Type
  ) %>% lapply(htmltools::HTML)

  z <-m %>% addPolygons(
    fillColor = ~pal(Comp.Type),
    weight = 2,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    highlight = highlightOptions(
      weight = 5,
      color = "#666",
      dashArray = "",
      fillOpacity = 0.7,
      bringToFront = TRUE),
    label = labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")
    ) %>%
    addLegend(pal = pal, values = ~Comp.Type, opacity = 0.7, title = NULL,
              position = "bottomright")
```

### 2017-08-21 testCode.Rmd
upgrade
Code clean up and also, modelling to allow the whole of England to be predicted.

@@
 
-CalcLowUse<- function(df){ 
+CombineLowUse<- function(df){ 
   df %>%
   select(LSOA_CODE, LowUse) %>%
-        left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
-        group_by(Admin_ward_code)  %>%
-        mutate(LowUsePerc = round(LowUse/Homes *100), 
-               WardLowUse = sum(LowUse) ,
-               WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
-        ungroup %>% 
-        left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
-        mutate(ValLow = LowUse*MeanPrice,
-               LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
-                                 labels =  c("0-10","11-20","21-30", "30+")),
-               WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
-                                     labels = c("0-10","11-20","21-30", "30+")) )
+    CalcLowUse()
+
 }
@@
 
-test <- ls(pattern = "LON") %>% 
+test <- ls(pattern = "CUMBRIA") %>% 
   map_df(~get(.x)) %>%
@@
 
-test <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA) %>%
+testTower <- TowerLONDATA %>%
+  CalcLowUse()
+
+test2 <- ls(pattern = "LON") %>%
+  map_df(~get(.x)) %>%   
+  group_by(LSOA_CODE) %>%
+   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
+  CalcLowUse()
+
+test2 <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA, TowerLONDATA) %>%
   map_df(~.x) %>%   
@@
 
-z<- MakeLeaflet(test)
+y<- MakeLeaflet(test2)
 
-z
+y
+
+y2<- MakeLeaflet(TowerLONDATA)
+
+y2
 
@@
 ```
+
+```{r}
+
+SalesLAD <- prices %>%
+  group_by(Admin_district_code) %>%
+    filter(X5 %in% c("D", "S", "T", "F")) %>%
+    summarise(sales = n(), 
+            mean = mean(X2, na.tm = TRUE))
+
+SalesWard <- prices %>%
+  group_by(Admin_ward_code) %>%
+    filter(X5 %in% c("D", "S", "T", "F")) %>%
+    summarise(sales = n(), 
+            mean = mean(X2, na.tm = TRUE))
+
+SalesWard %>% ggplot(aes(x = sales, y = mean )) + geom_point()
+
+```
+
+```{r}
+test <- ChelseaLONDATA %>%
+            # select(WardLowUsePerc, WardLowUse) %>%
+             mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
+             summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
+                        minPerc = min(WardLowUsePerc, na.rm=TRUE),
+                        diffPerc = maxPerc-minPerc,
+                        max = max(WardLowUse, na.rm=TRUE),
+                        min = min(WardLowUse, na.rm=TRUE),
+                        diff = max-min,
+                        mean = mean(WardLowUse, na.rm=TRUE),
+                        median = median(WardLowUse, na.rm=TRUE),
+                        LAD = sub("DATA", "", "ChelseaLONDATA"),
+                        TurnoverPerc = sum(PercTurnover*Homes, na.rm = TRUE)/sum(Homes, na.rm = TRUE),
+                        LUPTurnoverPerc = sum(PercTurnover*LowUse, na.rm = TRUE)/sum(LowUse, na.rm = TRUE)
+                        )
+```

### 2017-08-21 Functions/BootResSummaryData.R

@@ -1,14 +1,27 @@
 BootResSummaryData <- function(BootStrapRES){
   
   
+  #gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
+  CurrentLADS <- ls(pattern = "DATA", envir = globalenv()) %>%
+    map_chr(~{df<- get(.x)
+    df <- df %>%
+      group_by(LAD11CD) %>%
+      summarise(count = n())
+    df$LAD11CD[which.max(df$count)]}
+    )
+  
   #Perform the t-test on the resulting lists
   TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
   #TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
   #Tidy results of thejust the ttest
   TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
+    select(p.value) %>%
     mutate(LAD = elementnames,
+           LAD11CD = CurrentLADS,
+           HomePrice = TtestRESgreater %>% map_dbl(~.x$HomePrice),
+           LowUsePrice = TtestRESgreater %>% map_dbl(~.x$LowUsePrice),
            absdiff = TtestRESgreater %>% map_dbl(~.x$absdiff),
-           Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff))
+           Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff)) 
   
   #Removing ANOVA as it causes probs when only tyoe a are included
   #Perform ANOVA on the difference between the ratios of the groups on the bootrapped list
@@ -20,17 +33,24 @@ BootResSummaryData <- function(BootStrapRES){
   
   WardData <- ls(pattern = "DATA", envir = globalenv()) %>%
     map_df(~eval(parse(text=.x)) %>%
-             select(WardLowUsePerc, WardLowUse) %>%
+             #select(WardLowUsePerc, WardLowUse) %>%
              mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
              summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
                         minPerc = min(WardLowUsePerc, na.rm=TRUE),
+                        LADPerc = sum(WardLowUsePerc, na.rm=TRUE)/sum(Homes, na.rm=TRUE),
                         diffPerc = maxPerc-minPerc,
[…]

### 2017-08-21 Functions/ProcessDataMeanPrice.R

@@ -1,0 +1,9 @@
+ProcessDataMeanPrice <- function(df) {
+  df %>% left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
+    mutate(ValLow = LowUse*MeanPrice,
+           PercTurnover = counts/WardHomes,
+           LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
+                             labels =  c("0-10","11-20","21-30", "30+")),
+           WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
+                                 labels = c("0-10","11-20","21-30", "30+")) ) 
+}

### 2017-08-21 Functions/SemiDataStructure.R

@@ -5,17 +5,13 @@ SemiDataStructure <- function(df){
   df <- df %>%
     select(Admin_ward_code, LowUse, Empty) %>% 
     left_join(., EW2, by = "Admin_ward_code") %>%
-    group_by(Admin_ward_code)  %>%
+    group_by(Admin_ward_code) %>%
+    rename(LSOA_CODE = ECODE) %>%
     mutate(
       WardLowUsePerc = round(LowUse/sum(Homes)*100),
-      LowUsePerc = WardLowUsePerc, 
-      WardLowUse = LowUse) %>% 
+      WardLowUse = LowUse,
+      LowUse = LowUse*(Homes/sum(Homes)),
+      LowUsePerc = round(LowUse*100/Homes)) %>% 
     ungroup %>% 
-    left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
-    mutate(ValLow = LowUse*MeanPrice,
-           LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
-                             labels =  c("0-10","11-20","21-30", "30+")),
-           WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
-                                 labels = c("0-10","11-20","21-30", "30+")) ) %>%
-    rename(LSOA_CODE = ECODE)
+    ProcessDataMeanPrice(.)
 }

### 2017-08-21 Functions/StructureData.R

@@ -29,18 +29,7 @@ StructureData <- function(df, lowuse = NULL, empty = NULL, full = TRUE ){
       df <- df%>%
         mutate(LowUse = rowSums(.[,lowuse]), 
                Empty = rowSums(.[,empty])) %>%
-        left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
-        group_by(Admin_ward_code)  %>%
-        mutate(LowUsePerc = round(LowUse/Homes *100), 
-               WardLowUse = sum(LowUse) ,
-               WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
-        ungroup %>% 
-        left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
-        mutate(ValLow = LowUse*MeanPrice,
-               LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
-                                 labels =  c("0-10","11-20","21-30", "30+")),
-               WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
-                                     labels = c("0-10","11-20","21-30", "30+")) ) 
+        CalcLowUse(.)
     }
     return(df)
   }

### 2017-08-21 SubCode/AuxdataLoad.R

@@ -43,8 +43,22 @@ PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
 #
 #
 setwd(PostcodeLookups)
+#It turned out  that the LAD11CD is out of date and so some of the LAD's aren't matching. I am replacing the LAD11CD with an
+#Upt to date version, it is a bit of a hack but hopefully it will work an mean that areas like 
+#St Albarns and Northumberland are not missed out
 lsoa <- read_csv("PCD11_OA11_LSOA11_MSOA11_LAD11_EW_LU_aligned_v2.csv") %>%
-select(LSOA11CD:LAD11NMW) %>% distinct(., LSOA11CD, .keep_all = TRUE)
+select(LSOA11CD:LAD11NMW) %>% distinct(., LSOA11CD, .keep_all = TRUE) 
+
+LSOAfix <- PstCdLSOA.raw %>% 
+  select(Admin_district_code, LSOA11CD = lsoa11cd) %>%
+  distinct(LSOA11CD, .keep_all = TRUE)
+
+lsoa <- lsoa %>% 
+  left_join(LSOAfix) %>%
+  select(-LAD11CD) %>%
+  rename(LAD11CD = Admin_district_code)
+
+rm(LSOAfix)
 
 setwd(AddGeog)
 wardnames <- read_csv("Ward_to_Local_Authority_District_to_County_to_Region_to_Country_December_2016_Lookup_in_United_Kingdom_V2.csv") %>% setNames(c("Admin_ward_code", names(.)[-1]))
@@ -53,11 +67,12 @@ wardnames <- read_csv("Ward_to_Local_Authority_District_to_County_to_Region_to_C
 wardlsoa <- PstCdLSOA.raw %>% distinct(lsoa11cd, .keep_all = TRUE) %>% 
 select(lsoa11cd, Admin_ward_code)
 
-EW2 <- inner_join(EW, lsoa, by = c("ECODE" = "LSOA11CD") ) %>% 
-left_join(., wardlsoa, by = c("ECODE"="lsoa11cd") ) %>% 
-left_join(., select(wardnames, Admin_ward_code, WD16NM), by = "Admin_ward_code") %>%
-group_by(Admin_ward_code) %>%
-mutate(WardHomes = sum(Homes),  WardPop = sum(Pop)) %>% ungroup
+EW2 <- inner_join(EW, lsoa, by = c("ECODE" = "LSOA11CD") ) %>%
[…]

### 2017-08-23 PaperCode.Rmd
Unaffordability
Fixed the AUX code so that Income is loaded. Added in the unnaffordability section

@@
 
+#Look at saleries
+```{r}
+
+unafford <- ls(pattern = "DATA") %>%
+  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
+  group_by(MSOA11CD) %>%
+  summarise(LowUse = sum(LowUse, na.rm = T),
+            Homes = sum(Homes, na.rm = T),
+            Pop = sum(Pop, na.rm = T)) %>%
+  mutate(LowUsePerc = LowUse/Homes) %>%
+  left_join(IncomeEst, by = "MSOA11CD") %>%
+  mutate(decile = ntile(ratio, 20))
+
+unaffordExLon <- unafford %>%
+  filter(Region.name != "London") %>%
+  mutate(decile = ntile(ratio, 50))
+
+#London follows the same pattern it just happens further up the scale
+unaffordLon <- unafford %>%
+  filter(Region.name == "London") %>%
+  mutate(decile = ntile(ratio, 50))
+
+cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
+cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
+cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
+cor(unafford$Yearly.income, unafford$MedianPrice, "complete.obs")
+
+test <- lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford)
+
+summary(test)
+
+#This is no Longer useful due to using the whole percentile range 
+# test <- 2:50 %>% 
+#   map_df(~{
+#   decile <- unaffordExLon %>%
+#     mutate(decilev = ntile(ratio, .x)) %>%
+#     filter(decilev == 1 | decilev == .x) %>%
+#     group_by(decilev) %>%
+#     summarise(mean = mean(LowUsePerc)) %>%
+#     mutate(group = .x) %>%
+#     spread(key = decilev, value = mean) %>%
+#     setNames(c("group", "LowMean", "HighMean"))
+#   
+# }) 
+# 
+# test %>%
+#   gather(key = type, value = mean, -group)%>%  
+#   ggplot(aes(x = type, y = mean )) + geom_boxplot()
+# 
+# 
+# test %>%
+#   gather(key = type, value = mean, -group)%>% 
+#   ggplot(aes(x = group, y = mean, colour = type )) + geom_point()
+# 
+# 
+# test2 <- test %>%
+#   mutate(ratio = HighMean/LowMean) 
+# test2 %>%
+#   ggplot(aes(x = group, y = ratio,)) + geom_point()
+# 
+# cor(test2$ratio, test2$group)
+
+decile <- bind_rows(mutate(unaffordExLon, type = "Excl London"), 
+                    mutate(unafford, type = "Inc London"),
+                    mutate(unaffordLon, type = "London")) %>%
+    group_by(type) %>%
+    mutate(decile = ntile(ratio, 50)) %>%
+      group_by(decile, type) %>%
+    summarise(mean = mean(LowUsePerc),
+              median = median(LowUsePerc),
+              counts = n()
+              )
+
+#Looking at the relationship between unaffordability and LUP percentage
+
+decile %>% ggplot() + 
+  facet_grid(.~type) + 
+  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
+  geom_point(aes(x= decile, y = median, colour = type))
+
+#Example of the theoretical relationship
+
+data_frame(Index = 1:100) %>%
+  mutate(Primary = exp(-0.05*(Index))+0.05, 
+         Auxilary = (exp(Index/100)-1),
+    Total = Primary + Auxilary) %>%
+  gather(key = "Type", value = "value", -Index) %>%
+  ggplot(aes(x= Index, y = value, colour = Type )) +
+  geom_point() +
+  labs(title = "LUP percentage as a function of primary and Auxilary demand",
+       x = "Demand",
+       y = "LUP percentage") +
+  theme(
+  axis.text.x = element_blank(),
+  axis.text.y = element_blank()
+  )
+
+```
+
 #Overall price data 
@@
   geom_jitter()
+
+```
+
+Rural Urban split
+```{r}
+setwd(DataFolder)
+
+Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
+  setNames(make.names(names(.))) %>%
+  rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
+  select(LAD11CD, PercRural) %>%
+  mutate(PercRural = as.numeric(PercRural))
+
+#Update Gateshead and Northumberland Codes
+Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
+Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"
+
+Combine1ExO <- Combine1ExO %>%
+  left_join(Rural, by = "LAD11CD")
 
@@
 #The model that uses easily available data is 3% less accurate than the other model.
-t.test(ModelStats2$Accuracy, ModelStats1$Accuracy)
+t.test(ModelStats2$Accuracy, ModelStats3$Accuracy)
 
@@
 
+#Linear
 set.seed(1983)
@@
 
+#Tree
+set.seed(1983)
+MultiCheck <- 1:111 %>% map(~{
+  TestResample <- resample_bootstrap(ModelMe)
+
+  model <- rpart(Reference~ Extent + price + VacantsPerc+ PercRural,data=as.data.frame(TestResample))
+
+  data_frame(x = predict(model, ModelMe, type = "prob")[,2]>0.5) %>%
+    setNames(paste("Model", .x, sep="_"))
+}
+) %>% bind_cols() %>% 
+  mutate(
+  Outcome = case_when(
+  rowSums(.)>ncol(.)/2 ~TRUE,
+  rowSums(.)<=ncol(.)/2 ~FALSE
+))
+
 test <- ModelMe %>%
@@
 
-BinomSimp <- glm(Reference~ price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
-
 BinomExtent <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
 rpartExtent <- rpart(Reference~ Extent + price + VacantsPerc,data=ModelMe)
-
-confusionMatrix(predict(BinomSimp, ModelMe, type = "response")>0.5 , ModelMe$Reference)
 
@@
   left_join( LadHomes, by = "LAD11CD") %>%
-  mutate(VacantsPerc = Vacants/Homes) %>%
-  mutate(Significant.Competition = predict(BinomExtent, ., type = "response")) %>%
-  mutate(Comp.Type = case_when(
+  left_join(Rural, by = "LAD11CD") %>%
+  mutate(VacantsPerc = Vacants/Homes)
+
+#Preds <- predict(BinomExtent, EnglandComp , type = "response")
+set.seed(1983)
+Preds <- 1:111 %>% map(~{
+  TestResample <- resample_bootstrap(ModelMe)
+
+  model <- rpart(Reference~ Extent + price + VacantsPerc,data=as.data.frame(TestResample))
+
+  data_frame(x = predict(model, EnglandComp, type = "prob")[,2]>0.5) %>%
+    setNames(paste("Model", .x, sep="_"))
+}
+) %>% bind_cols() %>% 
+  mutate(
+  Outcome = rowSums(.)/ncol(.))
+
+EnglandComp <- EnglandComp%>% 
+  left_join(select(ModelMe, LAD11CD, Reference), by = "LAD11CD") %>%
+  mutate(
+    Significant.Competition = ifelse(is.na(Reference),
+                                     unlist(Preds$Outcome), 
+                                     as.logical(Reference))
+    ) %>%
+  mutate(
+
+      Comp.Type = case_when(
       .$Significant.Competition<0.5-tol ~"No",
@@
       .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
-  ))
+      )
+  ) %>%
+  select(-Reference)
 
@@
   ggplot(aes(x = Comp.Type, y= price, fill = Comp.Type)) + geom_boxplot()
+
+#Estimated
 
@@
 
+#Observed
+Combine1ExO %>%
+  group_by((absdiff>0)) %>%
+  summarise(mean = mean(HomePrice),
+            median = median(HomePrice),
+            Homes = sum(Homes),
+            Pop = sum(Pop)) %>%
+  mutate(HomesPerc = Homes/sum(Homes),
+         PopPerc = Pop/sum(Pop))
+
 ```

### 2017-08-24 PaperCode.Rmd
Extra plots
Added in some plots which get printed to the Latex file. for weasy updating. also for tables

@@
 #number of LUPS and Total Homes
-ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
+DataCover <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
   filter(!is.na(LAD11NM)) %>%
   summarise(
-           TotalLads = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
+           TotalLADs = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
+           PercLADs = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length()),
            LowUse = sum(LowUse, na.rm = T),
@@
            Population = sum(Pop, na.rm= T),
-           Poperc = Population/sum(EW2$Pop))
+           PercPop = Population/sum(EW2$Pop)) %>%
+  mutate_if(.<1, funs(signif(.,3))) %>%
+  mutate_if(.>1, as.integer) %>%
+  mutate_all(as.character) %>% 
+  gather
+
+DataCover
+
+xtable(DataCover, caption="Summary of collected data coverage",
+       label = "tab:DataCover") %>% 
+  print(., type="latex", file=file.path(TexTables,"DataCover.tex"))
 
@@
 z <-ChelseaLONDATA %>% 
-  filter(LAD11CD =="E09000020") %>% 
-  bind_rows(WestminsterLONDATA) %>%
+  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
+  filter(LAD11NM =="Kensington and Chelsea") %>% 
   MakeLeaflet()
 
-BradfordDATA %>% filter(LAD11NM=="Bradford") %>%
-  MakeLeaflet
+mapshot(z, file = file.path(Figures, "Chelsea.pdf"))
+
+CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
+  map_df(~get(.x)) %>%
+   group_by(LSOA_CODE) %>%
+   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
+  CalcLowUse()
+
+z<- MakeLeaflet(CumbriaPlot)
+
+mapshot(z, file = file.path(Figures, "Cumbria.pdf"))
+
+z<- MakeLeaflet(CornwallDATA)
+mapshot(z, file = file.path(Figures, "Cornwall.pdf"))
+
+z<- MakeLeaflet(BarrowCUMBRIADATA)
+mapshot(z, file = file.path(Figures, "Barrow.pdf"))
 
@@
 cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
+cor(unafford$Yearly.income, unafford$ratio, "complete.obs")
+
 cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
 cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
-cor(unafford$Yearly.income, unafford$MedianPrice, "complete.obs")
+cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")
 
@@
 
-#This is no Longer useful due to using the whole percentile range 
-# test <- 2:50 %>% 
-#   map_df(~{
-#   decile <- unaffordExLon %>%
-#     mutate(decilev = ntile(ratio, .x)) %>%
-#     filter(decilev == 1 | decilev == .x) %>%
-#     group_by(decilev) %>%
-#     summarise(mean = mean(LowUsePerc)) %>%
-#     mutate(group = .x) %>%
-#     spread(key = decilev, value = mean) %>%
-#     setNames(c("group", "LowMean", "HighMean"))
-#   
-# }) 
-# 
-# test %>%
-#   gather(key = type, value = mean, -group)%>%  
-#   ggplot(aes(x = type, y = mean )) + geom_boxplot()
-# 
-# 
-# test %>%
-#   gather(key = type, value = mean, -group)%>% 
-#   ggplot(aes(x = group, y = mean, colour = type )) + geom_point()
-# 
-# 
-# test2 <- test %>%
-#   mutate(ratio = HighMean/LowMean) 
-# test2 %>%
-#   ggplot(aes(x = group, y = ratio,)) + geom_point()
-# 
-# cor(test2$ratio, test2$group)
-
-decile <- bind_rows(mutate(unaffordExLon, type = "Excl London"), 
-                    mutate(unafford, type = "Inc London"),
-                    mutate(unaffordLon, type = "London")) %>%
+decile <- bind_rows(mutate(unaffordExLon, type = "Excluding London"), 
+                    mutate(unafford, type = "Including London"),
+                    mutate(unaffordLon, type = "Only London")) %>%
     group_by(type) %>%
@@
 
-decile %>% ggplot() + 
+decile %>% ggplot(aes(x= decile, y = median)) + 
   facet_grid(.~type) + 
   #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
-  geom_point(aes(x= decile, y = median, colour = type))
+  geom_point(aes(colour = type))  +
+  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
+  theme(legend.position= "none") + 
+  geom_smooth(method="loess",se=FALSE, colour = "black")
+SaveFig("LowUsePercVSratio.pdf")
+
+unafford %>%
+  ggplot(aes(x= ratio, y = MeanPrice)) + geom_point()
 
@@
   )
-
-```
-
-#Overall price data 
-```{r}
-#Other property is massively more valuable on average than the rest of the property types
-#mean value is 10 Million as such it has to be excluded
-prices %>% group_by(X5) %>% 
-  mutate(X2 = as.numeric(X2)) %>%
-  summarise(count = n(),
-            Value = sum(X2, na.rm =T),
-            mean = mean(X2, na.rm = T)) %>%
-mutate(countperc = (count/sum(count)),
-       ValuePerc = Value/sum(Value))
-
-#Looking at A and B property we can see that B properties are more expensive than A type
-prices %>% group_by(X15) %>% 
-  mutate(X2 = as.numeric(X2)) %>%
-  summarise(count = n(),
-            Value = sum(X2, na.rm =T),
-            mean = mean(X2, na.rm = T)) %>%
-mutate(countperc = (count/sum(count)),
-       ValuePerc = Value/sum(Value))
-
-#Other only appears in the B type sales never in A type
-prices %>% 
-  mutate(X2 = as.numeric(X2)) %>%
-    group_by(X15, X5) %>% 
-  summarise(count = n(),
-            Value = sum(X2, na.rm =T),
-            mean = mean(X2, na.rm = T)) %>%
-  ungroup %>%
-mutate(countperc = (count/sum(count)),
-       ValuePerc = Value/sum(Value))  
+SaveFig("TheoreticalDemand.pdf")
+
 ```
@@
   mutate(LowUseValue = LowUseValue/1e9)
+
+#99% of the LADs are significantly different from 0 at the 95% level
+sum(Combine1ExO$Ttest.p.value>0.975 |Combine1ExO$Ttest.p.value<0.025)/nrow(Combine1ExO)
+
+PlotClassDiff(BootStrapRESExO$ChelseaLON, "Kensington and Chelsea")
+SaveFig("ClassdiffChelsea.pdf")
+
+PlotClassDiff(BootStrapRESExO$Cornwall, "Cornwall")
+SaveFig("ClassdiffCornwall.pdf")
+
+PlotClassDiff(BootStrapRESExO$BarrowCUMBRIA, "Barrow")
+SaveFig("ClassdiffBarrow.pdf")
+
+test <- BootStrapRESExO %>% 
+  bind_rows %>%
+  group_by(class, ID) %>%
+  summarise_all(sum) %>%
+  ungroup %>%
+  mutate(HomesPrice = HomesValue/Homes,
+         LowUsePrice = LowUseValue/LowUse,         
+         ratio = LowUse/Homes,
+         HomesPerc = Homes/sum(Homes, rm.na = T),
+         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
+         ClassPerc = LowUse/Homes,
+         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
+         RatioExvsAct = LowUse/ExpectedHomes
+         ) %>%
+        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")) )
+
+test2 <- test %>% group_by(class) %>%
+  summarise_all(mean)
+
+PlotClassDiff(test)
+SaveFig("ClassdiffAllData.pdf")
+
+test %>% 
+  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
+   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
+     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
+     geom_boxplot() + 
+     labs(title = "Observed within class difference in Price from expected for LUPs", 
+          y = "% difference from expected")
+SaveFig("PricediffAllData.pdf")
 
@@
 set.seed(1983)
-MultiCheck <- 1:21 %>% map(~{
+MultiCheckL <- 1:21 %>% map(~{
   TestResample <- resample_bootstrap(ModelMe)
@@
 
-  model <- rpart(Reference~ Extent + price + VacantsPerc+ PercRural,data=as.data.frame(TestResample))
+  model <- rpart(Reference~ Extent + price + VacantsPerc,data=as.data.frame(TestResample))
 
@@
 confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)
+confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)
 
@@
   left_join( LadHomes, by = "LAD11CD") %>%
-  left_join(Rural, by = "LAD11CD") %>%
+  #left_join(Rural, by = "LAD11CD") %>%
   mutate(VacantsPerc = Vacants/Homes)

### 2017-08-27 PaperCode.Rmd
Added Hounslow

@@
 
+#West Midlands Brum
+```{r}
+
+setwd(file.path(RegionsComp, "Region West Midlands"))
+
+SandWellDATA <- read_excel("FOI - SandwellDiscountsLSOA - FS57000079 Disc.xlsx" )[1:4] %>%  
+  StructureData(2:6)
+
+WolverhamptonDATA <- read_excel("WolverhamptonDiscountsLSOA.XLSX"  )[1:4] %>%  
+  StructureData(c(2:5,7))
+
+WalsallDATA <- read_excel("WalsallDiscountsLSOA.XLSX" )[1:4] %>%  
+  StructureData(c(4:5,7:8))
+
+```
+
 #SouthWest
@@
 
+KirkleesDATA <- read_excel("Jonathan Bourne KirkleesDiscountsLSOA Complete.xlsx" )[1:4] %>%
+  StructureData(2:5)
+
 ```
@@
 
-DenbigshireDATA <- read_excel("FOI 2503 DenbighshireDiscountsLSOA.xlsx" , sheet=1)%>% .[,1:4] %>%
-    StructureData(8:9)
+DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
+    StructureData(c(8:9,11,13))
 
@@
 
+unaffordLAD <- unafford %>%
+  rename(LAD11CD = Local.authority.code) %>%
+  group_by(LAD11CD) %>%
+  mutate(TotInc = Yearly.income*Pop) %>%
+  summarise(TotInc = sum(TotInc),
+            Pop = sum(Pop)) %>%
+  mutate(meanInc = TotInc/Pop)
+
 ```
@@
 elementnames<- names(BootStrapRESExO)
+
+#Used when elements need to be deleted and reloaded
+#saveRDS(BootStrapRESExO, "BootStrapRESExO.rds")
 
@@
 CombineAB %>%
-  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()
+  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valuerat HounslowLONDATA <- read_excel("Hounslow Discounts - Bourne Info -210817.xls" )io>1)) + geom_point()
 
@@
 #  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
+  left_join(Rural, by = "LAD11CD") %>%
   mutate(Reference = as.factor(absdiff>0) ) %>%
@@
 
-  model <- rpart(Reference~ Extent + price + VacantsPerc,data=as.data.frame(TestResample))
+  model <- rpart(Reference~ Extent + 
+                   price + 
+                   VacantsPerc  
+                 ,data=as.data.frame(TestResample))
 
@@
 
+confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)  
 confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)
-confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)
-
-BinomExtent <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
-rpartExtent <- rpart(Reference~ Extent + price + VacantsPerc,data=ModelMe)
-
-confusionMatrix((predict(BinomExtent, ModelMe, type = "response")>0.5) , ModelMe$Reference)
-confusionMatrix(predict(rpartExtent, ModelMe, type = "prob")[,2] , ModelMe$Reference)
+
+ModelMe %>% 
+  mutate(Outcome = as.logical(MultiCheck$Outcome)) %>%
+  filter(Outcome != Reference) %>%
+  select(LAD, Outcome, Reference)
 
@@
 
-EnglandComp %>%
+EnglandCompTab <- EnglandComp %>%
   group_by(Comp.Type) %>%
@@
          PopPerc = Pop/sum(Pop))
+
+EnglandCompTab
+
+xtable(EnglandCompTab, caption="Summary of effecrt across England",
+       label = "tab:EnglandCompTab") %>% 
+  print(., type="latex", file=file.path(TexTables,"EnglandCompTab.tex"))
 

### 2017-09-05 PaperCode.Rmd
Cascading
Addede code to being trying to cascade. Included two new functions to smooth the code. the first identifies validnodes for the injection vector. the second balances the generation and demand of the valid nodes across islolated graph componants

@@
 ---
+
+98nmol/L
 
@@
 
+BirminghamDATA <-  read_excel("Birmingham CT EMPTIES.xlsx" )%>%
+mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
+ left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(Exemption.type=`Current Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
+  StructureData()
+
 ```
@@
 ```{r}
+BournemouthDATA <- read_excel("BournemouthDiscountsLSOA_R.xlsx" )[1:4] %>%
+  StructureData(c(6,8,9:13))
+
 PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
@@
   mutate(LowUse = Empty) %>%
-  SemiDataStructure
-
-#Merton
-
-MertonLONDATA <- read_excel("merton1.xlsx" )[,-2] %>%setNames(make.names(names(.))) %>% slice(-1) %>% arrange(X__1) %>%
-  filter(X__1 != "Norbury", X__1!="Nightingale", X__1 !="Stonecot") %>% 
-    bind_cols(., wardnames %>% filter(LAD11NM == "Merton") %>% 
-              select(Admin_ward_code)) %>%
-  mutate(Empty =   Disc.Class.C.Vacant.dwelling + Disc.class.C.Long.term.empty + Premium.Levy, LowUse =  Disc.Class.A.Second.home + Disc.Class.B.second.home ) %>%
   SemiDataStructure
@@
 ```{r}
-setwd(DataFolder)
-
-Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
-  setNames(make.names(names(.))) %>%
-  rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
-  select(LAD11CD, PercRural) %>%
-  mutate(PercRural = as.numeric(PercRural))
-
-#Update Gateshead and Northumberland Codes
-Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
-Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"
-
-Combine1ExO <- Combine1ExO %>%
-  left_join(Rural, by = "LAD11CD")
+# setwd(DataFolder)
+# 
+# Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
+#   setNames(make.names(names(.))) %>%
+#   rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
+#   select(LAD11CD, PercRural) %>%
+#   mutate(PercRural = as.numeric(PercRural))
+# 
+# #Update Gateshead and Northumberland Codes
+# Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
+# Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"
+# 
+# Combine1ExO <- Combine1ExO %>%
+#   left_join(Rural, by = "LAD11CD")
 
@@
 #  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
-  left_join(Rural, by = "LAD11CD") %>%
+#  left_join(Rural, by = "LAD11CD") %>%
   mutate(Reference = as.factor(absdiff>0) ) %>%
@@
          LUPdepExt = scale(LUPdepExt),
-         maxPerc = scale(maxPerc))
+         maxPerc = scale(maxPerc),
+         VacantsPerc = scale(VacantsPerc),
+         price = scale(price),
+         Extent = scale(Extent))
 
@@
 
-ModelStats %>% ggplot(., aes(x= Accuracy)) +geom_density()
-
-ModelStats %>%
-  mutate(diff = Accuracy - AccuracyNull) %>% 
-  ggplot(., aes(x= diff)) +geom_density()
-
-ModelStats %>% ggplot(., aes(x= AccuracyPValue)) +geom_density()
-ModelStats %>% ggplot(., aes(x= Kappa)) +geom_density()
-
-t.test(ModelStats$Accuracy, ModelStats$AccuracyNull, alternative = "greater")
-
 test <- ModelStats %>% 
-  select( X.Intercept., LUPdepExt, maxPerc, pricepercent) %>%
+  select( X.Intercept., LUPdepExt, price, VacantsPerc) %>%
   gather
@@
 
-Outcome <- bind_rows(data_frame(model = "generic", Accuracy = ModelStats2$Accuracy), 
+Outcome <- bind_rows(data_frame(model = "Open Data", Accuracy = ModelStats2$Accuracy), 
 data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )
@@
 Outcome %>%
-  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3)
+  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3) +
+  labs(title = "Density plot of the model outcomes, using custom FOI data vs generic open data")
+SaveFig("CustomGenericOutcomes.pdf")
 
@@
 cor(ModelMe$VacantsPerc, ModelMe$LTVPerc)
+
+#Plot the model coefficients
+
+ModelStats2 %>%
+  select(X.Intercept. ,Extent,price , VacantsPerc) %>%
+  gather() %>%
+  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
+  labs(title = "Coefficient values across 1000 random partitions")
+SaveFig("ModelCoeffs.pdf")
+
+#only one of these is necessary they hold almost the same information
+ModelStats3 %>%
+  select(X.Intercept. ,LUPdepExt,price , VacantsPerc) %>%
+  gather() %>%
+  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
+  labs(title = "Coefficient values across 1000 random partitions")
 
@@
 set.seed(1983)
-MultiCheckL <- 1:21 %>% map(~{
+MultiCheckL <- 1:111 %>% map(~{
   TestResample <- resample_bootstrap(ModelMe)
@@
       )
-  ) %>%
-  select(-Reference)
+  )
 
@@
 
+#Plotting the expected range of
+
+valuecheck <- sample(c(TRUE, FALSE), size = nrow(EnglandComp)*1000, replace = TRUE, prob = c(0.888, 1-0.888)) %>%
+  matrix(., nrow=nrow(EnglandComp)) 
+valuecheck <-   (valuecheck * ifelse(EnglandComp$Comp.Type == "Yes", TRUE, FALSE ) )%>% data.frame %>%
+  bind_cols(select(EnglandComp, LAD11CD, Reference),.) %>%
+  #Where ever the outcome is known it is reverted back to the true value, only estimated values are flipped.
+  gather(key = "ID", value = "affected",-LAD11CD,-Reference) %>%
+  mutate(Reference = as.logical(Reference)*1,
+    affected = ifelse(is.na(Reference), affected, Reference)) %>%
+  left_join(LadHomes) %>%
+  group_by(ID, affected) %>%
+  summarise(Homes = sum(Homes),
+            Pop = sum(Pop)) %>%
+  group_by(affected) %>%
+  mutate(Rank = percent_rank(Pop),
+    Outlier = ifelse(percent_rank(Pop)<0.0275 | percent_rank(Pop)>0.975, "Yes", "No")) %>%
+  group_by(ID) %>%
+  mutate(affected = ifelse(affected == 1, "Yes", "No"),
+         PercPop = Pop/sum(Pop))%>%
+  ungroup #%>%
+# mutate(PercPop = Pop)
+#The NNUMBERS DONT MATCH WITH THE TABLE WHY?
+
+#95 range is 78 to 84
+affected <- valuecheck %>% filter(affected == "Yes")
+q5 <- quantile(affected$PercPop,.05)
+q95 <- quantile(affected$PercPop,.95)
+x.dens <- density(affected$PercPop)
+df.dens <- data.frame(x = x.dens$x, y = x.dens$y)
+median(affected$PercPop)
+affected %>%
+  ggplot(aes(x = PercPop)) + geom_density() +
+  geom_area(data = subset(df.dens, x <= q5), 
+              aes(x=x,y=y))  +
+    geom_area(data = subset(df.dens, x >= q95), 
+              aes(x=x,y=y))+
+labs(title = "The estimated percentage of English population affected by LUPs")
+SaveFig("PopPercLUPAfftect.pdf")
+
+valuecheck %>% filter(affected == "No") %>%
+  ggplot(aes(x = PercPop)) + geom_density()
+
 ```

### 2017-09-05 allEnglandMap.Rmd
Cascading
Addede code to being trying to cascade. Included two new functions to smooth the code. the first identifies validnodes for the injection vector. the second balances the generation and demand of the valid nodes across islolated graph componants

@@
               position = "bottomright")
+
 ```
+
+```{r}
+  z
+
+  mapshot(z, file = file.path(Figures, "EnglandMarket.pdf"))
+```

### 2017-09-05 SubCode/LondonFullProcesss.R

@@ -165,3 +165,7 @@ EnfieldLONDATA <- read_excel("EnfieldDiscountsLSOA.xlsx")[c(1,4:6)] %>%
    StructureData(c(2:4,6))
 
  
+ MertonLONDATA <- read_excel("Merton Discounts for FoI Jonathan Bourne.xlsx" )[1:4] %>%
+   StructureData()
+ 
+ 

### 2017-09-25 testCode.Rmd
VOA and offshore
made loads of regex for address cleaning etc

@@
 ---
+
+```{r setup}
+setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
+source("Setup.R")
+
+setwd(Functions)
+list.files() %>% map(source)
+
+Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
+source(file.path(CommonCode, "AuxdataLoad.R"))
+```
 
@@
 
+#VOA stuff
+
 ```{r}
@@
   left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
-  select(Postcode, lsoa11cd, LAD11CD, LAD11NM, Admin_ward_code, WD16NM)
+  select(Postcode, lsoa11cd, LAD11CD, LAD11NM,Admin_ward_code = Admin_ward_code.x, WD16NM)
+
+setwd(file.path(basewd, "VOA data"))
 
@@
   left_join(., CorePstCd, by = c("X15" = "Postcode"))
+
+#X10 address
+#X11 is road
+#X15 is postcode
 
@@
 ```
+
+#Match VOA to offshore test work
+
+```{r}
+
+setwd(DataFolder)
+
+Offshore <- read_excel("OV_FULL_2016_02 (with PEP database for lookup).xlsx", sheet = "OV_FULL_2016_02")
+
+test <- Offshore %>%
+  filter(!is.na(Price_Paid))
+
+Offshore$Property_Address %>% head(20)
+
+Offshore2 <- Offshore %>%
+    select(Property_Address, Postcode) %>%
+    mutate(streetAddress = str_split(Offshore$Property_Address, ",", n = 2) %>% 
+  map_chr(~.x[1]),
+           Postcode = gsub(" ", "",Postcode))
+
+NumberofPostocodes <-CompanyData %>% filter(X15 %in% Offshore2$Postcode) %>%
+  group_by(X15) %>%
+  summarise(counts = n()) %>%
+  left_join(Offshore2, ., by = c("Postcode" = "X15")) %>%
+  filter(!is.na(Postcode))
+
+#20,000 flat or apartments
+grepl("^flat|^apartment|^penthouse", Offshore2$Property_Address, ignore.case = T) %>% table
+ffshore$Property_Address
+grepl("suite", Offshore2$Property_Address, ignore.case = T) %>% table
+grepl("unit", Offshore2$Property_Address, ignore.case = T) %>% table
+
+test <- Offshore2 %>%
+  filter(grepl("unit", Offshore2$Property_Address, ignore.case = T))
+
+#need another regex which looks at number and if followed by apartement etc uses the number as the flat number
+Flatregex <- "(the.+)?(flat|apartment|penthouse)(s)?(\\s(no)?(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)"
+
+Flats <- Offshore2 %>%
+  filter(grepl("flat|apartment|penthouse", Property_Address, ignore.case = T))%>%
+  mutate(FlatNumber = str_extract(tolower(Property_Address), 
+            Flatregex) %>%
+           sub("\\s$|,$", "", .)
+)
+
+# (the.+)?(flat|apartment|penthouse)(s)?(\\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
+# 
+# some flats start with a "the eastern" or "the penthouse" this is optional
+# (the.+)?
+# 
+# the main expression it has to say this! optioanl "s" on the end
+# (flat|apartment|penthouse)(s)?
+#
+#the additional matching characteristics these come either side of and or statement
+# ((s)?\\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
+# (A|B)
+# 
+# 
+# A = \\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?
+# A = (A1)(A2)
+# 
+# space followed by some characters followed by a space or a comma this extracts the flat number eg "flat c"
+# A1 = \\s(.+?)(\\s|,)
+# 
+# optional space then either "to" or "-" followed by optional space followed by some characters followed by space or comma. This is to catch things like "flats 1 to 5" or flat 4-6
+# A2 = (\\s?(to|-)\\s?.+?(\\s|,))?
+# 
+# This is simple some are simply called "flat"  or "the penthouse" this catches those
+# B = ,
+
+Flats <- Flats%>%
+  mutate(leng = str_split(Flats$Property_Address, ",", n = 2) %>% 
+  map_chr(~length(.x)) 
+  ) %>% 
+  filter(leng == 2) %>%
+  mutate( address2 = str_split(Property_Address, ",", n = 2) %>% 
+  map_chr(~.x[[2]]) %>% 
+    gsub("\\s*\\([^\\)]+\\)", "",.)%>% 
+    gsub(" and .+", "",.)
+  )
+
+Flats2 <- Flats %>%
+  group_by(address2) %>%
+  summarise(counts = n()) %>%
+  arrange(-counts)
+
+test <- Flats2 %>%
+  filter(grepl("Dolphin Square", address2, ignore.case = TRUE))
+
+sum(test$counts)
+
+test <- Offshore2 %>%
+  filter(grepl("^[a-z]+( [a-z])* house", Offshore2$Property_Address, ignore.case = T))
+
+#car parks
+grepl("car", Offshore2$Property_Address, ignore.case = T) %>% table
+
+ParkingSpaces <- Offshore2 %>%
+  filter(grepl("^car |^park", Offshore2$Property_Address, ignore.case = T))
+
+#random land
+grepl("^land", Offshore2$Property_Address, ignore.case = T) %>% table
+
+test <- Offshore2 %>%
+  filter(grepl("^land", Offshore2$Property_Address, ignore.case = T))
+
+Roadnames <- unique(CompanyData$X11) %>% 
+  gsub(" north| south| east| west", "",., ignore.case = TRUE) %>% 
+  word(.,-1) %>% data_frame(Endings = .) %>%
+  group_by(Endings) %>%
+  summarise(count = n()) %>%
+  arrange(-count) %>%
+  mutate(cumsum = cumsum(count),
+         cumperc = cumsum/sum(count))
+
+test2 <- test %>%
+  group_by(Endings) %>%
+  summarise(count = n())
+
+#A list of road names to remove as they cause problems
+removeNames <- "park house buildings green end farm estate court bridge hall drove" %>% str_split(., " ", simplify = TRUE)
+
+#match the top most occuring endings to the offshore list and get the counts
+TopRoadEndings <- Roadnames$Endings[1:50] %>%  map_dbl(~ sum(grepl(.x, Offshore$Property_Address, ignore.case = TRUE)))
+
+#arrange in order of occurnace and remove the tricky ones
+Road2 <- Roadnames[1:50,] %>% mutate(occs = TopRoadEndings) %>%
+  arrange(-occs) %>%
+  mutate(Endings = tolower(Endings)) %>%
+  filter(!(Endings %in% removeNames)) %>%
+  mutate(cumsum = cumsum(occs))
+
+length(Offshore$Property_Address)
+
+#need to include thigs like gate
+
+#create the regex string to match
+Wordswithapotrophes <- paste0("(( \\w+)('s)?)+ (",paste(c(Road2$Endings),  collapse = "|"),")")
+roadmatchregex <- paste0("([0-9]+)", Wordswithapotrophes)
+
+paste0("(( \\w+)('s)?)+(gate,)")
+
+StreetNum <- str_extract(tolower(Offshore2$Property_Address), roadmatchregex )
+
+Offshore3 <- Offshore2 %>% 
+  mutate(
+    Property_Address =  gsub(" \\(.+?\\)", "", Property_Address),
+    class = case_when(
+    grepl(Flatregex, Property_Address, ignore.case = T) ~ "domestic",
+    grepl("^car |^park", Property_Address, ignore.case = T) ~"parking space",
+    grepl("^land", Property_Address, ignore.case = T) ~ "land",
+    grepl("^[a-z]+( [a-z])* cottage", Property_Address, ignore.case = T) ~"domestic",
+    grepl("(^[0-9]+)(( \\w+)('s)?)+ (court|villas)", Property_Address, ignore.case = T) ~"domestic",
+    TRUE ~ "unknown"
+  )) %>%
+  mutate(Streetadd = StreetNum,
+    Streetnumber =gsub("[a-z]", "", StreetNum, ignore.case = T), 
+         Street = gsub("[0-9]", "", StreetNum),
+    Street = case_when(
+      !is.na(Street) ~ Street,
+      grepl("^land", Property_Address, ignore.case = T) ~ 
+        str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
+        gsub("(of |at )", "",.), #begins with land about 13k
+      grepl("( \\w+)+(way|gate,)", Property_Address, ignore.case = T) ~ #roadds that er blblablaGATE
+        str_extract(tolower(Property_Address), "( \\w+)+(way|gate)," ),
+      #Fixing for knightsbridge
+       grepl("knightsbridge", Property_Address, ignore.case = T) ~ "knightsbridge",
+      grepl("holland", Property_Address, ignore.case = T) ~ "holland",
+      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
+    )
+    )
+
+test<- Offshore3%>%
+  #sorting houses
+  mutate(
+    HouseName = str_extract(tolower(Property_Address), "^[a-z]+( [a-z])* house")
+
+    )
+
+grep("( \\w+)+(way|gate),", " parkway,")
+
+table(is.na(Offshore3$Street))
+table(is.na(Offshore3$Streetnumber))
+
+table(Offshore3$class)
+
+#Everything that is not land about 7000 items 
+  test <- Offshore3 %>%
+  filter(is.na(Street))  %>%
+  filter(grepl(paste0("^[^(land)]"), Property_Address, ignore.case = TRUE))
+
+  #random
+    OffshoreHouse <- Offshore3 %>%
+  filter(grepl("house", tolower(Property_Address)), class =="unknown")
+
+    #why are there no overlaps?
+    #look at needham house
+
+    CompanyHouse <- CompanyData %>%
+      mutate(House = tolower(X10)) %>%
+  filter(grepl("house", House))
+
+ test <-    CompanyHouse %>%
+      filter(grepl( "Darcy House",  House, ignore.case = T))
+
+ #this matchers
+   MMhouse <-    OffshoreHouse %>%
+      filter(grepl( "Matthew Murray House",  Property_Address, ignore.case = T))
+
+#Darcy matches
+Darcy <-    CompanyHouse %>%
+      filter(grepl( "Darcy House",  House, ignore.case = T))
+
+#hotel where some rooms are owned offshore
+  Needham <-    OffshoreHouse %>%
+      filter(grepl( "Needham",  Property_Address, ignore.case = T))
+
+  #All the directorss are registered to the same place and have no digital foot print
+  Debenham <-    OffshoreHouse %>%
+      filter(grepl( "debenham",  Property_Address, ignore.case = T))
+
+    %>%
+    filter(class == "unknown")
+
+table(test$class)
+
+test <- Offshore3 %>% 
+  filter(Offshore3$Street %in% tolower(CompanyData$X11)) %>%
+  filter(!is.na(Street), class == "unknown") %>%
+  group_by(Street) %>%
+  summarise(counts = n())
+
+```
+
+#Unique Company's
+
+```{r}
+
+CompCounts <- Offshore %>%
+select(c(grep("Proprietor_Name",names(Offshore)) )) %>% unlist %>%
+  data.frame(comp = .) %>%
+  group_by(comp) %>%
+  summarise(counts = n()) %>%
+  filter(!is.na(comp))
+
+sum(CompCounts$counts)
+
+plot(density(CompCounts$counts))
+
+test <- CompCounts %>%
+  filter(grepl("trustee", comp, ignore.case = T))
+
+```
+
+```{r}
+
+Flats3<- Flats %>% left_join(PstCdLSOA.raw)%>%
+   group_by(lsoa11cd) %>%
+  summarise(Total = n()) %>%
+#  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
+  rename(LSOA_CODE = lsoa11cd)
+
+Flats4 <- Flats3 %>% group_by(LAD11NM) %>%
+  summarise(Total = sum(Total))
+
+test <-ls(pattern = "LON") %>% 
+  map_df(~get(.x))  %>%
+   group_by(LSOA_CODE) %>%
+   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
+  CalcLowUse() %>%
+  select(LSOA_CODE, Homes, LowUse,LAD11NM:MeanPrice) %>%
+  left_join(filter(Flats3, !is.na(LSOA_CODE))) %>%
+  mutate(Total = ifelse(is.na(Total), 0, Total),
+         LowUsePerc = round(Total/Homes,3)*100)
+
+sum(test$Total)
+
+test %>% 
+  group_by(LAD11NM) %>%
+  summarise(Total = sum(Total)) %>%
+  mutate(perc = round(Total/sum(Total),3)) %>%
+  arrange(-perc)
+
+g <- MakeLeaflet(test, type = "jyg", bins = c(0, 5,10,15,100))
+
+Dolph<- Offshore %>%
+  filter(grepl("dolphin square", Offshore$Property_Address, ignore.case = T))
+
+```
+
+UK has 20k flats owned by offshore companies. 75% are in #London and of those 43% are in #Westminster.
+
+#London Flats owned by offshore companies as a % of all homes. 43% are in #Westminster, 20% in #RBKC
+
+#London has 14k flats owned by offshore companies. 43% are in #Westminster, 20% in #RBKC. Map % of ALL homes
+
+#Address fixing
+
+```{r}
+
+library(poster)
+test <- parse_addr(Offshore$Property_Address)
+
+test <- paste(Offshore$Property_Address, "United Kingdom", sep= ", ") %>%
+   normalise_addr %>%
+  parse_addr
+
+#\([a-z0-9]+\s[a-z0-9]+
+
+    test1 <-paste(Offshore$Property_Address, "United Kingdom", sep= ", ")
+
+    test2 <- paste(Offshore$Property_Address, "United Kingdom", sep= ", ") %>%
+     gsub(" \\(.+?\\)", "", .) %>%
+            #gsub("(\\s\\()(?=[a-z0-9]+\\s[a-z0-9]+)", ", ", ., ignore.case = TRUE, perl= TRUE) %>%
+      gsub("(and )?(car )?(park(ing)?)( space(\\w)?)?", "", .) %>%
+    normalise_addr %>%
+    parse_addr
+
+    test3 <- test2 %>% mutate(postal_code = gsub(" ", "", Offshore$Postcode)) %>%
+      filter(!is.na(postal_code))
+
+    test4 <- test3 %>%
+      group_by(postal_code, road) %>%
+      summarise(counts = n())
+
+        CompPostRoad <- CompanyData %>%
+      group_by(X11, X15) %>%
+      summarise(counts = n())
+
+CompAddress <- paste(CompanyData$X8, CompanyData$X15, "United Kingdom", sep =",") %>%
+    normalise_addr %>%
+    parse_addr
+
+test5 <- CompAddress %>%
+      group_by(postal_code, road) %>%
+      summarise(counts = n())
+
+  sum(paste(test4$road, test4$postal_code) %in% paste(test5$road, test5$postal_code))
+
+#savved to VOA folder    
+#saveRDS(CompAddress, "CompanyAddresseslibpostal.rds")
+
+    test2[1:20] 
+    Offshore$Property_Address[1:20]
+
+    sum(grepl("gate", Offshore$Property_Address, ignore.case = TRUE))
+
+test <- Offshore %>%
+  select(Property_Address) %>%
+  mutate(Property_Address = gsub(" \\(.+?\\)", "", Property_Address) )%>%
+  filter(grepl("(and )?(car )?park(ing)? space(s)?|(and )?car park(ing)?( space(s)?)?", Property_Address, ignore.case = T))
+
+test <- Offshore %>%
+  select(Property_Address) %>%
+  mutate(Property_Address = gsub(" \\(.+?\\)", "", Property_Address) )%>%
+  filter(grepl(" bridge", Property_Address, ignore.case = T))
+
+test[1:20,1]
+
+removeNames <- "park house buildings green end farm estate court bridge hall" %>% str_split(., " ", simplify = TRUE)
+
+TopRoadEndings <- Roadnames$Endings[1:50] %>%  map_dbl(~ sum(grepl(.x, Offshore$Property_Address, ignore.case = TRUE)))
+
+Road2 <- Roadnames[1:50,] %>% mutate(occs = TopRoadEndings) %>%
+  arrange(-occs) %>%
+  mutate(Endings = tolower(Endings)) %>%
+  filter(!(Endings %in% removeNames)) %>%
+  mutate(cumsum = cumsum(occs))
+
+length(Offshore$Property_Address)
+
+table(is.na(StreetNum))
+
+```

### 2017-11-23 PaperCode.Rmd
Not sure
Bunch of small changes

@@
               median = median(LowUsePerc),
-              counts = n()
-              )
+              counts = n(),
+              ratio= mean(ratio)
+              ) %>%
+  mutate(decile2 = decile^2,
+         ratio2 = ratio^2,
+         logval = log(decile),
+         expval = exp(decile),
+         expvalneg = exp(-decile)) %>%
+  filter(!is.na(decile))
 
@@
 
-decile %>% ggplot(aes(x= decile, y = median)) + 
+decile %>% 
+#  filter(type == "Only London") %>% 
+  ggplot(aes(x= decile, y = median)) + 
+  facet_grid(.~type) + 
+  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
+  geom_point(aes(colour = type))  +
+  labs(x = "2 percentile group", y = "median Percent Low Use") + 
+  theme(legend.position= "none") + 
+  geom_smooth(method="loess",se=FALSE, colour = "black")
+SaveFig("LowUsePercVSratio.pdf")
+
+decile %>% 
+  filter(type == "Including London") %>% 
+  ggplot(aes(x= ratio, y = median)) + 
   facet_grid(.~type) + 
@@
   geom_smooth(method="loess",se=FALSE, colour = "black")
-SaveFig("LowUsePercVSratio.pdf")
+
+#model fit
+decile %>% 
+    filter(type == "Excluding London") %>% 
+  lm(median~decile +decile2, data = .) %>% summary
+
+#model fit
+decile %>% 
+    filter(type == "Excluding London") %>% 
+lm(median~ratio + ratio2, data = .) %>% summary
+
+decile %>% 
+    filter(type == "Excluding London") %>% 
+lm(median~expval + expvalneg, data = .) %>% summary
+
+#make nonlinear  model
+mod <- decile %>% 
+    filter(type == "Excluding London") %>% 
+  nls(median ~ exp(a + b*decile)+  exp(d + c*decile), data = ., 
+      start = list(a = 0, b = -3, c = 0, d = 0))
+
+mod2 <- decile %>% 
+    filter(type == "Only London") %>% 
+  nls(median ~ exp(a + b*decile), data = ., 
+      start = list(a = 0, b = -3))
+
+summary(mod)
+
+decile %>%
+      filter(type == "Excluding London") %>% 
+  ggplot(aes(x = decile, y = median))+
+  geom_point() +
+  geom_line(aes(y = predict(mod, list(x = decile))))
 
@@
 ```
+
+Big Stats
+```{r}
+
+```

### 2017-11-23 testCode.Rmd
Not sure
Bunch of small changes

@@
     select(Property_Address, Postcode) %>%
-    mutate(streetAddress = str_split(Offshore$Property_Address, ",", n = 2) %>% 
-  map_chr(~.x[1]),
-           Postcode = gsub(" ", "",Postcode))
+    mutate(Postcode = gsub(" ", "",Postcode))
 
@@
 #need another regex which looks at number and if followed by apartement etc uses the number as the flat number
-Flatregex <- "(the.+)?(flat|apartment|penthouse)(s)?(\\s(no)?(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)"
+Flatregex <- "(the.+)?(flat|apartment|penthouse)(s)?(\\s(no)?(\\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)"
 
 Flats <- Offshore2 %>%
-  filter(grepl("flat|apartment|penthouse", Property_Address, ignore.case = T))%>%
+  filter(grepl(Flatregex , Property_Address, ignore.case = T))%>%
   mutate(FlatNumber = str_extract(tolower(Property_Address), 
@@
 )
+
+(flat|apartment|penthouse)(s)?
 
@@
 # 
-# the main expression it has to say this! optioanl "s" on the end
+# the main expression it has to say this! optional "s" on the end
 # (flat|apartment|penthouse)(s)?
@@
 #the additional matching characteristics these come either side of and or statement
-# ((s)?\\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
+# ((s)?\\s(\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?|,)
 # (A|B)
@@
 # 
-# A = \\s(.+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?
+# A = \\s(\S+?)(\\s|,)(\\s?(to|-)\\s?.+?(\\s|,))?
 # A = (A1)(A2)
 # 
-# space followed by some characters followed by a space or a comma this extracts the flat number eg "flat c"
-# A1 = \\s(.+?)(\\s|,)
+# space followed by anything that is not whitespace followed by a space or a comma this extracts the flat number eg "flat c"
+# A1 = \\s(\S+?)(\\s|,)
 # 
@@
 
+#Use Dolphin Square to extract house names
 test <- Flats2 %>%
-  filter(grepl("Dolphin Square", address2, ignore.case = TRUE))
+  filter(grepl("Dolphin Square", address2, ignore.case = TRUE)) %>%
+  mutate(address2 = str_extract(tolower(address2), "([a-z0-9]+)\\s(house)"))
 
@@
 
-test2 <- test %>%
-  group_by(Endings) %>%
-  summarise(count = n())
-
 #A list of road names to remove as they cause problems
@@
 
-length(Offshore$Property_Address)
-
 #need to include thigs like gate
@@
 #create the regex string to match
-Wordswithapotrophes <- paste0("(( \\w+)('s)?)+ (",paste(c(Road2$Endings),  collapse = "|"),")")
-roadmatchregex <- paste0("([0-9]+)", Wordswithapotrophes)
+Wordswithapotrophes <- paste0("(( \\w+)('s)?)+ (",
+                              paste(c(Road2$Endings, 
+                                      "( \\w+)+(way|gate,)",
+                                      "knightsbridge",
+                                      "holland"
+                                      ),  collapse = "|"),")")
+roadmatchregex <- paste0("(([0-9]+([a-z])?))?", Wordswithapotrophes)
 
@@
 
+#This is used in the next code cleaning block it is done here to keep the code easier to read
 StreetNum <- str_extract(tolower(Offshore2$Property_Address), roadmatchregex )
@@
   mutate(
-    Property_Address =  gsub(" \\(.+?\\)", "", Property_Address),
+    Property_Address =  gsub(" \\(.+?\\)", "", Property_Address), #remove anything in brackets e.g postcodes
+    #Label some classes
     class = case_when( 
@@
     grepl("^[a-z]+( [a-z])* cottage", Property_Address, ignore.case = T) ~"domestic",
-    grepl("(^[0-9]+)(( \\w+)('s)?)+ (court|villas)", Property_Address, ignore.case = T) ~"domestic",
+    grepl("(^[0-9]+([a-z])?)(( \\w+)('s)?)+ (court|villas|mansions)", Property_Address, ignore.case = T) ~"domestic",
     TRUE ~ "unknown"
   )) %>%
-  mutate(Streetadd = StreetNum,
-    Streetnumber =gsub("[a-z]", "", StreetNum, ignore.case = T), 
-         Street = gsub("[0-9]", "", StreetNum),
+  #Do Streets
+  mutate( Street = gsub("([0-9]+([a-z])?)", "", StreetNum),
+          Streetnumber =gsub("([a-z])+", "", StreetNum, ignore.case = T),
           Street = case_when(
-      !is.na(Street) ~ Street,
+      !is.na(Street) ~ Street, #if not NA keep as is otherwise...
+      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
+    ),
+    Street = case_when(
             grepl("^land", Property_Address, ignore.case = T) ~ 
         str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
-        gsub("(of |at )", "",.), #begins with land about 13k
-      grepl("( \\w+)+(way|gate,)", Property_Address, ignore.case = T) ~ #roadds that er blblablaGATE
-        str_extract(tolower(Property_Address), "( \\w+)+(way|gate)," ),
-      #Fixing for knightsbridge
-       grepl("knightsbridge", Property_Address, ignore.case = T) ~ "knightsbridge",
-      grepl("holland", Property_Address, ignore.case = T) ~ "holland",
-      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
-    )
-    )
+          gsub("of |at ", "",.), #begins with land about 13k
+        TRUE ~ Street
 
-test<- Offshore3%>%
+    ) %>% gsub(" (and|to) ", "", .)
+    ) %>%
   #sorting houses
   mutate(
-    HouseName = str_extract(tolower(Property_Address), "^[a-z]+( [a-z])* house")
+    HouseName  = str_extract(tolower(Property_Address), "^([a-z]+)( [a-z]+)* (house|court|farm|villa|cottage|lodge)(s)?") %>%
+      ifelse(grepl("^land",.), NA,.)
 
-    )
-
-grep("( \\w+)+(way|gate),", " parkway,")
-
-table(is.na(Offshore3$Street))
-table(is.na(Offshore3$Streetnumber))
-
-table(Offshore3$class)
-
-#Everything that is not land about 7000 items 
-  test <- Offshore3 %>%
-  filter(is.na(Street))  %>%
-  filter(grepl(paste0("^[^(land)]"), Property_Address, ignore.case = TRUE))
+    ) %>%
+#Trim whitspace
+mutate(Street = trimws(Street))
 
@@
 
+        OffshoreHouse <- Offshore %>%
+  filter(grepl("house", tolower(Property_Address)))
+
     #why are there no overlaps?
@@
     CompanyHouse <- CompanyData %>%
-      mutate(House = tolower(X10)) %>%
+      mutate(House = tolower(X8)) %>%
   filter(grepl("house", House))
@@
  test <-    CompanyHouse %>%
-      filter(grepl( "Darcy House",  House, ignore.case = T))
+      filter(grepl( "mansions",  House, ignore.case = T))
 
@@
   summarise(counts = n())
+
+```
+
+#Split out VOA addresses
+
+```{r}
+
+rm(columnnames)
+
+#create street and number split out like for offshore
+CompanyData2 <- CompanyData %>%
+  rename(Property_Address = X8)
+
+StreetNum <- str_extract(tolower(CompanyData2$Property_Address), roadmatchregex )
+
+CompanyData2 <- CompanyData2 %>%
+    mutate( Street = gsub("([0-9]+([a-z])?)", "", StreetNum),
+          Streetnumber =gsub("([a-z])+", "", StreetNum, ignore.case = T),
+          Street = case_when(
+      !is.na(Street) ~ Street, #if not NA keep as is otherwise...
+      TRUE ~ str_extract(tolower(Property_Address), Wordswithapotrophes ) #no street number
+    ),
+    Street = case_when(
+            grepl("^land", Property_Address, ignore.case = T) ~ 
+        str_extract(tolower(Property_Address), paste0("(of|at)", Wordswithapotrophes) ) %>%
+          gsub("of |at ", "",.), #begins with land about 13k
+        TRUE ~ Street
+
+    ) %>% gsub(" (and|to) ", "", .)
+    )
+
+#overlapping street names
+sum(unique(Offshore3$Street) %in% tolower(unique(CompanyData$X11)))
+
+sum(unique(Offshore3$HouseName) %in% tolower(unique(CompanyData$X25)))
+
+test <- Offshore3 %>%
+  filter(HouseName %in% tolower(unique(CompanyData$X25)), !is.na(HouseName))
+
+#match house name and street
+StreetHouseComp <- tolower(paste(CompanyData$X11,CompanyData$X25)) %>% unique
+StreetHouseOffshore <- tolower(paste(Offshore3$Street,Offshore3$HouseName))[!is.na(Offshore3$HouseName)] %>% unique
+
+#Actual companies!
+CompMatch <- CompanyData %>%
+  filter(  tolower(paste(X11,X25)) %in% StreetHouseOffshore, is.na(X23)  )
+
+OffshoreMatch <- Offshore3 %>%
+  filter(paste(Street,HouseName) %in% StreetHouseComp, !is.na(HouseName))
+
+OffshoreMatch2 <- Offshore3 %>%
+  mutate(test = paste(Street,HouseName))
+"matthew murray house"
+name <- "matthew murray house"
+
+Companyinfo <- CompanyData %>%
+  filter(grepl(name, tolower(X25), ignore.case = T))
+
+OffshoreInfo <-Offshore3 %>%
+  filter(grepl(name, HouseName, ignore.case = T))
+
+```
+
+#match lsoa for offshore postcodes
+
+```{r}
+test <- Offshore %>%
+  filter(!is.na(Postcode)) %>%
+  mutate(Postcode = gsub(" ", "", Postcode)) %>%
+  left_join(., CorePstCd, "Postcode")
+
+table(is.na(test$lsoa11cd))
+
+test2 <- test %>%
+  filter(!is.na(lsoa11cd)) %>%
+  group_by(lsoa11cd) %>%
+  summarise(counts = n(),
+            LAD11CD = first(LAD11CD),
+            LAD11NM = first(LAD11NM),
+            Admin_ward_code = first(Admin_ward_code),
+            WD16NM = first(WD16NM)) %>%
+  arrange(desc(counts))
+
+examin <- test %>% 
+  filter(lsoa11cd =="E01006854")
+
+table(examin$Proprietor_Name_1)
+```
+
+#Improve geoloacation
+
+```{r}
+setwd(file.path(DataFolder, "GeoNames"))
+
+columnnames <- "geonameid
+name
+asciiname
+alternatenames
+latitude
+longitude
+feature class
+feature code
+country code
+cc2
+admin1 code
+admin2 code 
+admin3 code
+admin4 code
+population
+elevation
+dem
+timezone
+modification date " %>% str_split(., "\n", simplify = T) %>% trimws
+
+GeoNames <- read_tsv("GB.txt", col_names = FALSE) %>%
+  setNames(columnnames)
+
+MaxMind <- read_csv("worldcitiespop.txt")
+
+test <- MaxMind %>%
+  filter(Country == "gb")
+
+test %>%
+  filter(grepl("queens", City, ignore.case = TRUE) )
+
+test <- GeoNames %>%
+filter(grepl("queens", name, ignore.case = TRUE) )
 

### 2017-11-23 Functions/BootResSummaryData.R

@@ -45,6 +45,7 @@ BootResSummaryData <- function(BootStrapRES){
                         mean = mean(WardLowUse, na.rm=TRUE),
                         median = median(WardLowUse, na.rm=TRUE),
                         Pop = sum(Pop, na.rm = TRUE),
+                        LUPS = sum(LowUse, na.rm = TRUE),
                         Homes = sum(Homes, na.rm = TRUE),
                         LAD = sub("DATA", "", .x),
                         TurnoverPerc = sum(PercTurnover*Homes, na.rm = TRUE)/sum(Homes, na.rm = TRUE),

### 2017-11-23 SubCode/Setup.R

@@ -2,7 +2,7 @@
 
 
 packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
-              "forcats", "e1071", "htmlwidgets", "stringr", "modelr", "caret", "xtable", "rpart")
+              "forcats", "e1071", "htmlwidgets", "stringr", "modelr", "caret", "xtable", "rpart", "broom")
 
 #, "mapview"
 new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]

### 2018-07-15 PaperCode.Rmd
Final LADS
Added in lads that had been received but not included. Total LADS 114. upgraded kingston and Wandsworth to LSOA from ward level

@@
 
-98nmol/L
+new article and paper on airbnb effecr
+https://www.citylab.com/equity/2018/03/what-airbnb-did-to-new-york-city/552749/?utm_source=atlfb
 
@@
 #this uses rank for distance from LAD I think it should be dist check this
+
+Intellectual property rights and
+disclosures under the Freedom of
+Information Act
+
+16. It may not be apparent to recipients that the information is
+protected by copyright. Therefore when a public authority
+wishes to protect its own copyright, or the copyright is owned
+by a third party, it should advise the applicant that the
+information remains copyright protected.
+
+Please can you provide excel the file sent to Jonathan Bourne on xxx
+
+The reference number for this case is xxx.
+
+Yours faithfully,
+
+Jonathan Bourne
 
@@
 
-Should type B be included? or just type A?
-
-What's the Deal with Westminster?
-Westminsters Data is very low, I want to check what codes are going on.
-Westminster
-PCLB00: Second home class B/A
-PCLB50: 
-PCLC00: Empty and unfurnsished
-PCLC99: 
-PCLD00: Undergoing major repairs
-PCLJ50:
-Single:
+#OGL licence claim
+
+All data used in this paper is covered by the Open Government Licence.
+
+The Data meets all 4 criteria described in section 56 of "Datasets (sections 11, 19 & 45)" FOI guidance document.
+These criteria are that the data is held by the authority, The data is part of a relveant copyright work (The data is held in a databse), the authority holds the copyright to the data (The information in the database is owned by the local council).
+As local authorities are public sector bodies (shown in the public sector classification guide) and that council tax is a core task, normally the data would be covered by the RPSI.
+However, following section 5 of the Re use of public sector infrmation regulations 2015.
+
+"5.—(1) These Regulations do not apply to a document where—
+
+(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review; or""
+
+As the document the councils needed to complete is custom made and not part of the public task, the RPSI does not cover the resultant work and licencing reverts to the FOIA. 
+The FOIA states that a specific licence must be given for all datasets released under the act.
+As no charge has been levied against the use of the data then the default Open government licence is applied following section 69 of the "Datasets (sections 11, 19 & 45)" FOI guidance document.
 
@@
 
-Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up/Figures"
+Figures <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Figures" #file.path(basewd, "Figures")
+TexTables <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Tables"
 source(file.path(CommonCode, "AuxdataLoad.R"))
+
 ```
@@
   select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
+  StructureData()
+
+DudleyDATA <- read_excel("Completed DudleyDiscountsLSOA.xlsx"  )[1:4] %>%  
   StructureData()
@@
 ```{r}
-#Broadlands is unsuable, due to lack of data collection.
 #This is being checked
@@
 
-#they deleted the classes
 SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
   StructureData()
+
+NorwichDATA <- read_excel("Norwich Discounts FINAL.xlsx"  , sheet=1)[1:4] %>%
+  StructureData(2:8)
 
@@
 
-#Brightong and Hove
+#South East
 
@@
 #MakeLeaflet(BournemouthDATA)
+
+ValeWhiteDATA <- read_excel("Vale of White HorseDiscountsLSOA (00000002).xlsx" , sheet=1)[1:4] %>%
+  StructureData(c(5,7,8,9,10,14))
+
+SouthOxfordDATA <- read_excel("South OxfordshireDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
+  StructureData(c(5,7,8,9,10,14))
 
@@
 
+WakefieldData <-  read_excel("WakefieldDiscountsLSOA.xlsx" )[1:4] %>%
+  StructureData(2:7)
+
 ```
@@
 
-WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
-  group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
-  arrange(`Ptc Wardname`) %>% 
-  filter(!is.na(`Ptc Wardname`)) %>% 
-  bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
-              select(Admin_ward_code)) %>%
-  mutate(LowUse = Empty) %>%
-  SemiDataStructure
-
-#Kingston
-
-KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
-  arrange(X__1) %>% slice(1:16) %>%
-  bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
-              select(Admin_ward_code)) %>%
-  mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
-  SemiDataStructure
+# WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
+#   group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
+#   arrange(`Ptc Wardname`) %>% 
+#   filter(!is.na(`Ptc Wardname`)) %>% 
+#   bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
+#               select(Admin_ward_code)) %>%
+#   mutate(LowUse = Empty) %>%
+#   SemiDataStructure
+# 
+# 
+# #Kingston
+# 
+# KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
+#   arrange(X__1) %>% slice(1:16) %>%
+#   bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
+#               select(Admin_ward_code)) %>%
+#   mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
+#   SemiDataStructure
 
@@
   summarise(
-           TotalLADs = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
-           PercLADs = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length()),
-           LowUse = sum(LowUse, na.rm = T),
+           'LADs' = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
+           '% of all LADs' = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length())*100,
+           LUPs = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
-           PercHomes = Homes/sum(EW2$Homes),
+           '% of all Homes' = Homes/sum(EW2$Homes)*100,
            Population = sum(Pop, na.rm= T),
-           PercPop = Population/sum(EW2$Pop)) %>%
+           '% of total population' = Population/sum(EW2$Pop)*100) %>%
   mutate_if(.<1, funs(signif(.,3))) %>%
@@
 
-PlotMap(BexleyLONDATA)
+PlotMap(WandsworthLONDDATA)
 
@@
 
-#Analyse Boostrap
-
-```{r}
-test <- BootStrapRESExO$WestminsterLON%>% 
+#Analyse Bootstrap
+
+```{r}
+test <- BootStrapRESExO$WestminsterLON %>% 
   group_by(class) %>%
@@
          ) %>%
-        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")) )
+        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")),
+               LUPmore = RatioExvsAct>1)
 
@@
      geom_boxplot() + 
-     labs(title = "Observed within class difference in Price from expected for LUPs", 
-          y = "% difference from expected")
+     labs(title = "Observed within class difference in Price from expected for LUPs")
 SaveFig("PricediffAllData.pdf")
+
+#Total value of homes and LUPS
+
+BootStrapRESExO2 <- BootStrapRESExO %>% map(~.x %>% ungroup)
+
+LADnames <- names(BootStrapRESExO)
+
+LUPval <-   map2(.x =BootStrapRESExO2, .y =   names(BootStrapRESExO2),~ {.x %>% mutate(LAD  = .y)}) %>%
+  bind_rows %>%
+  select(-class) %>%
+  group_by(LAD, ID) %>%
+  summarise_all(sum) %>%
+  group_by(LAD) %>%
+  summarise_all(mean) %>%
+  ungroup %>%
+  mutate(HomesPrice = HomesValue/Homes,
+         LowUsePrice = LowUseValue/LowUse,         
+         ratio = LowUse/Homes,
+         HomesPerc = Homes/sum(Homes, rm.na = T),
+         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
+         ClassPerc = LowUse/Homes,
+         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
+         RatioExvsAct = LowUse/ExpectedHomes
+         ) %>%
+  mutate(VancouverTax = LowUseValue*0.01/1000)
+
+LUPval$VancouverTax %>% sum(.)/1000
 
@@
 CombineAB %>%
-  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valuerat HounslowLONDATA <- read_excel("Hounslow Discounts - Bourne Info -210817.xls" )io>1)) + geom_point()
+  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()
 
@@
             Pop = sum(Pop)) %>%
-  mutate(HomesPerc = Homes/sum(Homes),
-         PopPerc = Pop/sum(Pop))
+  mutate(HomesPerc = Homes/sum(Homes)*100,
+         PopPerc = Pop/sum(Pop)*100) %>%
+  rename('LUPs>Homes' = Comp.Type, 
+         Population = Pop,
+         'Homes %' = HomesPerc,
+         'Population %' = PopPerc) %>%
+  gather(key = "key", "value"= value, -"LUPs>Homes") %>%
+  mutate(value = value %>% round %>%as.integer) %>%
+  spread(key = "LUPs>Homes", value = value)
 
@@
 
-xtable(EnglandCompTab, caption="Summary of effecrt across England",
+xtable(EnglandCompTab, caption="Summary of effect across England",
        label = "tab:EnglandCompTab") %>% 
@@
 
-Big Stats
-```{r}
-
-```
+```{r}
+
+```

### 2018-07-17 PaperCode.Rmd
High value LUPS
I added in the number of LUPS that are worth more than the LAD median. This required changing BootsratpDistribcompare. However I can now predict the LADs where the majority of LUPs are high value, which is easier for people to understand.

@@
   rename(Exemption.type=`Current Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
-  StructureData()
+  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
+  StructureData(c(2,4:9))
 
@@
   rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
+  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
   StructureData(c(2:12,14:15))
@@
   rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Postcode, Country_code, Admin_district_code) %>%
+  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
   StructureData(c(2:6,8:11,13:15))
@@
 wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)
-
-#Wandsworth
-
-# WandsworthLONDDATA <- read_excel("wandsworth2.xlsx",  skip = 3 ) %>% select(1,3) %>% 
-#   group_by(`Ptc Wardname`) %>% summarise(Empty = sum(`Count Current Occupancy Discounts`)) %>% ungroup %>% 
-#   arrange(`Ptc Wardname`) %>% 
-#   filter(!is.na(`Ptc Wardname`)) %>% 
-#   bind_cols(., wardnames %>% filter(LAD11NM == "Wandsworth") %>% 
-#               select(Admin_ward_code)) %>%
-#   mutate(LowUse = Empty) %>%
-#   SemiDataStructure
-# 
-# 
-# #Kingston
-# 
-# KingstonLONDATA <- read_excel("Kingston1.xlsx"  )%>% setNames(make.names(names(.))) %>%
-#   arrange(X__1) %>% slice(1:16) %>%
-#   bind_cols(., wardnames %>% filter(LAD11NM == "Kingston upon Thames") %>% 
-#               select(Admin_ward_code)) %>%
-#   mutate(Empty = Empty...Furnished..0.. + Empty.Homes.Premium + LONG.TERM.EMPTY..0.. + Structural.Repair..0.., LowUse = Empty + X2nd.Home..0..) %>%
-#   SemiDataStructure
 
@@
 
-PlotMap(WandsworthLONDDATA)
+PlotMap(ConwyDATA)
 
@@
 mapshot(z, file = file.path(Figures, "Barrow.pdf"))
+
+MakeLeaflet(ConwyDATA)
 
@@
 decile %>% 
-  filter(type == "Including London") %>% 
+  filter(type == "Excluding London") %>% 
   ggplot(aes(x= ratio, y = median)) + 
@@
   ggplot(aes(x= Index, y = value, colour = Type )) +
-  geom_point() +
+  geom_line() +
   labs(title = "LUP percentage as a function of primary and Auxilary demand",
@@
 
-setwd(basewd)
-
-BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
-                                         PropertyTypes = c("D", "S", "T", "F"))
-
-elementnames<- names(BootStrapRESExO)
-
-#Used when elements need to be deleted and reloaded
-#saveRDS(BootStrapRESExO, "BootStrapRESExO.rds")
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities")
+
+#Find what needs to be bootstrapped
+BootStrapFiles <- list.files(getwd()) %>% gsub("DATA.rds", "",.)
+  newLADsnames <- sub("DATA", "", ls(pattern = "DATA", envir = globalenv())) %>% 
+    .[!(. %in% BootStrapFiles)] 
+  newLADs <- paste0(newLADsnames, "DATA")
+
+   #only bootstrap if there is something to add.
+  #Save each boostrap as you go along to avoid losing it all in a crash
+  if(length(newLADsnames)>0){
+    newLADs  %>% walk(~{print(.x)
+      DistribCompareBootstrapper(get(.x), 1652, 10, type, PropertyTypes)%>%
+      saveRDS(., file = paste0(.x, ".rds"))
+      }) 
+  }
+
+  #once all Bootratps complete load them all into a list
+ BootStrapRES <- list.files(getwd()) %>%
+   map(~readRDS(.x))
+
+ #name the list
+ names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)
+
+BootStrapRESExO <- BootStrapRES
+#Should clean up and remove EXO
+rm(BootStrapRES)
 
@@
 Combine1ExO <- BootResSummaryData(BootStrapRESExO)
+
 ```
@@
   bind_rows %>%
+  select(-LAD11CD) %>%
   group_by(class, ID) %>%
@@
 
-BootStrapRESExO2 <- BootStrapRESExO %>% map(~.x %>% ungroup)
-
 LADnames <- names(BootStrapRESExO)
 
-LUPval <-   map2(.x =BootStrapRESExO2, .y =   names(BootStrapRESExO2),~ {.x %>% mutate(LAD  = .y)}) %>%
+LUPval <-   map2(.x =BootStrapRESExO, .y =   names(BootStrapRESExO),~ {.x %>% mutate(LAD  = .y)}) %>%
   bind_rows %>%
-  select(-class) %>%
+  select(-class, -LAD11CD) %>%
   group_by(LAD, ID) %>%
@@
 
+#value is billions of pounds of a vancouver tax in England and wales.
 LUPval$VancouverTax %>% sum(.)/1000
@@
 
-Combine1ExO %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
-  geom_jitter()
-
-```
-
-Rural Urban split
-```{r}
-# setwd(DataFolder)
-# 
-# Rural <- read_csv( "RUC11_LAD11_ENv2.csv" )[-1,] %>%
-#   setNames(make.names(names(.))) %>%
-#   rename(PercRural = Rural.including.hub.towns..rural...rural.related..population1_1) %>%
-#   select(LAD11CD, PercRural) %>%
-#   mutate(PercRural = as.numeric(PercRural))
-# 
-# #Update Gateshead and Northumberland Codes
-# Rural$LAD11CD[Rural$LAD11CD == "E08000020"] <-"E08000037"
-# Rural$LAD11CD[Rural$LAD11CD == "E06000048"] <- "E06000057"
-# 
-# Combine1ExO <- Combine1ExO %>%
-#   left_join(Rural, by = "LAD11CD")
-
 ```
@@
 #Model
+
+##Create modelling dataframe
 
@@
   filter(!grepl("W", LAD11CD)) %>%
-#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
-#  left_join(Rural, by = "LAD11CD") %>%
   mutate(Reference = as.factor(absdiff>0) ) %>%
   #scaled so that the binomial can be interpreted
-  mutate(pricepercent = scale(pricepercent),
-         LUPdepExt = scale(LUPdepExt),
-         maxPerc = scale(maxPerc),
-         VacantsPerc = scale(VacantsPerc),
-         price = scale(price),
-         Extent = scale(Extent))
-
-#This uses the local mean so that has to be run first before the code works
-# ModelMe <- Combine1ExO2 %>%
-#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
-#   #filter out wales
-#   filter(!grepl("W", LAD11CD))%>%
-#   select(LAD11NM, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value,  LAD11CD) %>%
-#   mutate(outcome = LUPdepExt>Extent)  %>% 
-#   left_join(LocalMean, by = "LAD11CD") %>%
-#   left_join(LADprice, by = c("LAD11CD"="Admin_district_code")) %>%
-#   mutate(priceRatio = (price/LocalMean)) %>%
-#   mutate(LUPdepExt.Extent = LUPdepExt-Extent, price.LocalMean = price-LocalMean ) %>%
-#   #make the Reference column properly
-#   mutate(Reference = as.factor(absdiff>0) ) %>%
-#   #scaled so that the binomial can be interpreted
-#   mutate(pricepercent = scale(pricepercent),
-#          LUPdepExt = scale(LUPdepExt),
-#          maxPerc = scale(maxPerc),
-#          priceRatio = scale(priceRatio))
-
-ModelMe %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = outcome)) +
-  geom_jitter()
-
-rowsum(.)>5 ~TRUE
-#classification
-
-#LUPdepExt and Pricepercent are the only useful ones really
-Binom <- glm(Reference~ LUPdepExt +LADPerc +maxPerc+ mean.y, family=binomial(link='logit'),data=ModelMe)
-
-Binom <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
-
-confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)
-
-test <- lm(Percdiff ~ LUPdepExt +LADPerc +maxPerc+ mean.y, data = ModelMe)
-
-summary(test)
-
-summary(Binom)
-
-coef(Binom) %>% as.data.frame
-```
-
-##perform many mode resamples and plot the results
-
-```{r}
-
-#binom
-
-set.seed(1983)
-ModelStats <- 1:1000 %>% map_df(~{
-  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
-
-  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
-               family=binomial(link='logit'),
-               as.data.frame(TestResample$train))
-
-  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
-                              as.data.frame(TestResample$test)$Reference)
-
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
-          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
-
-}
-)
-
-test <- ModelStats %>% 
-  select( X.Intercept., LUPdepExt, price, VacantsPerc) %>%
+  mutate(pricepercent = scale(pricepercent) %>% as.numeric,
+         LUPdepExt = scale(LUPdepExt) %>% as.numeric,
+         maxPerc = scale(maxPerc) %>% as.numeric,
+         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
+         price = scale(price) %>% as.numeric,
+         Extent = scale(Extent) %>% as.numeric) %>%
+  mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)
+```
+
+##create functions to get out model preds
+
+```{r}
+ GetAccuracy <- function(df, splits , Var ) {
+  select_(df,splits) %>% flatten %>%
+           map2_dbl(select_(df,Var) %>% flatten, ., ~{ augment(.x, newdata = assessment(.y)) %>%
+               mutate(.fitted = factor(.fitted > 0,
+                        levels = as.factor(c("FALSE", "TRUE"))))  %>%
+              accuracy(., Reference, .fitted)} ) }
+
+#If this one is used on the logistic regression I get an "incorrect number of dimensions error"
+GetAccuracyForest <- function(df, splits , Var ) {
+   select_(df,splits) %>% flatten %>%
+map2_dbl( select_(df,Var) %>% flatten, ~{assessment(.x) %>%
+   mutate(fitted = predict(.y, .) %>% .[,colnames(.)=="TRUE"],
+          fitted = factor(fitted > 0,
+                        levels = as.factor(c("FALSE", "TRUE")))) %>%
+              accuracy(., Reference, fitted) 
+}) }
+
+```
+
+#Create Models
+```{r}
+
+FOIFormula <- as.formula(Reference~ LUPdepExt + price + VacantsPerc)
+OpenFormula <- as.formula(Reference~ Extent + price + VacantsPerc)
+
+set.seed(4622)
+Modeldf <- ModelMe  %>%
+  vfold_cv(., V = 10, repeats = 100) %>%
+  mutate(LogisticFOI = splits %>%
+  map(.,~{ glm(FOIFormula, data = analysis(.x),binomial(link='logit'))}
+        ),
+  LogisticOpen = splits %>%
+  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
+        ),
+  ForestOpen = splits %>% 
+    map(., ~{rpart(OpenFormula, data=analysis(.x))})
+  ) %>%
+  mutate(LogFoiAcc = GetAccuracy(., "splits", "LogisticFOI"),
+         LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"), 
+         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))
+
+Modeldf$LogisticOpen %>%
+   map_df(., ~coefficients(.x) %>%
+            as.data.frame(.) %>% rownames_to_column()) %>%
+   setNames(c("key", "value")) %>%
+  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
+  labs(title = "Coefficient values across 100 samples of 10 fold cross validation")
+SaveFig("ModelCoeffs.pdf")
+
+ModComp <- Modeldf %>%
+  select(LogFoiAcc, LogOpenAcc) %>%
   gather
 
-test %>% ggplot(.,aes(x = key, y = value, fill = key)) + geom_boxplot() + 
-  labs(title = "Direction each variable pushes the outcome")
-
-test %>% ggplot(.,aes(x = value, fill = key)) + geom_density( alpha = 0.5)
-
-```
-
-```{r}
-set.seed(1983)
-ModelStats2 <- 1:1000 %>% map_df(~{
-  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
-
-  model <- glm(Reference~ Extent + price + VacantsPerc, 
-               family=binomial(link='logit'),
-               as.data.frame(TestResample$train))
-
-  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
-                              as.data.frame(TestResample$test)$Reference)
-
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
-          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
-
-}
-)
-
-set.seed(1983)
-ModelStats3 <- 1:1000 %>% map_df(~{
-  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
-
-  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
-               family=binomial(link='logit'),
-               as.data.frame(TestResample$train))
-
-  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
-                              as.data.frame(TestResample$test)$Reference)
-
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
-          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
-
-}
-)
-
-Outcome <- bind_rows(data_frame(model = "Open Data", Accuracy = ModelStats2$Accuracy), 
-data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )
-
-Outcome %>%
-  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3) +
-  labs(title = "Density plot of the model outcomes, using custom FOI data vs generic open data")
-SaveFig("CustomGenericOutcomes.pdf")
-
-#The model that uses easily available data is 3% less accurate than the other model.
-t.test(ModelStats2$Accuracy, ModelStats3$Accuracy)
-
-cor(ModelMe$Vacants, ModelMe$VacantsPerc)
-
-cor(ModelMe$Vacants, ModelMe$LTV)
-cor(ModelMe$VacantsPerc, ModelMe$LTVPerc)
-
-#Plot the model coefficients
-
-ModelStats2 %>%
-  select(X.Intercept. ,Extent,price , VacantsPerc) %>%
-  gather() %>%
-  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
-  labs(title = "Coefficient values across 1000 random partitions")
-SaveFig("ModelCoeffs.pdf")
-
-#only one of these is necessary they hold almost the same information
-ModelStats3 %>%
-  select(X.Intercept. ,LUPdepExt,price , VacantsPerc) %>%
-  gather() %>%
-  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
-  labs(title = "Coefficient values across 1000 random partitions")
-
-```
-
-interpreting the coefficients of the model shows us that there is a natural tendency for LUPs to be more expensive than regular housing, the probability of them being more expensive increases if the local authority is already expensive compared to the rest of the local authorities.
-In addition the greater the maximum concentration of LUPs also increase the probability of them being more expensive than regular housing.
-However if the LUPs are generally in deprived areas then the probability of them being more expensive than regular housing decreases.
-
-Using the models produced in the previous section I can now predict areas where primary purchases are being out competed across the England
-
-```{r}
-
-#Linear
-set.seed(1983)
-MultiCheckL <- 1:111 %>% map(~{
-  TestResample <- resample_bootstrap(ModelMe)
-
-  model <- glm(Reference~ Extent + price + VacantsPerc, 
-               family=binomial(link='logit'),
-               as.data.frame(TestResample))
-
-  data_frame(x = predict(model, ModelMe, type = "response")>0.5) %>%
-    setNames(paste("Model", .x, sep="_"))
-}
-) %>% bind_cols() %>% mutate(
-  Outcome = case_when(
-  rowSums(.)>ncol(.)/2 ~TRUE,
-  rowSums(.)<=ncol(.)/2 ~FALSE
-))
-
-#Tree
-set.seed(1983)
-MultiCheck <- 1:111 %>% map(~{
-  TestResample <- resample_bootstrap(ModelMe)
-
-  model <- rpart(Reference~ Extent + 
-                   price + 
-                   VacantsPerc  
-                 ,data=as.data.frame(TestResample))
-
-  data_frame(x = predict(model, ModelMe, type = "prob")[,2]>0.5) %>%
-    setNames(paste("Model", .x, sep="_"))
-}
-) %>% bind_cols() %>% 
-  mutate(
-  Outcome = case_when(
-  rowSums(.)>ncol(.)/2 ~TRUE,
-  rowSums(.)<=ncol(.)/2 ~FALSE
-))
-
-test <- ModelMe %>%
-  bind_cols(., select(MultiCheck, Outcome)) %>%
-  mutate(Correct = Reference == Outcome) %>%
-  filter(!Correct) %>%
-  select(LAD, Reference, Outcome)
-
-confusionMatrix(MultiCheckL$Outcome, ModelMe$Reference)  
-confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)
-
-ModelMe %>% 
-  mutate(Outcome = as.logical(MultiCheck$Outcome)) %>%
-  filter(Outcome != Reference) %>%
-  select(LAD, Outcome, Reference)
+  ModComp %>%
+  ggplot(aes(x=model, y = statistic, fill = model)) + 
+  geom_boxplot()
+
+  ModComp %>%
+  group_by(model) %>%
+  summarise(mean =mean(statistic))
+
+```
+
+#All England Bootstrap
+
+```{r}
+#Create model using all data
+Mod <- ModelMe %>% 
+  glm(OpenFormula, data = ., binomial(link='logit'))
 
@@
 
-tol <- 0
-
-#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
 EnglandComp <- LADDep %>% 
@@
   left_join( LadHomes, by = "LAD11CD") %>%
+  ungroup %>%
   #left_join(Rural, by = "LAD11CD") %>%
-  mutate(VacantsPerc = Vacants/Homes)
-
-#Preds <- predict(BinomExtent, EnglandComp , type = "response")
-set.seed(1983)
-Preds <- 1:111 %>% map(~{
-  TestResample <- resample_bootstrap(ModelMe)
-
-  model <- rpart(Reference~ Extent + price + VacantsPerc,data=as.data.frame(TestResample))
-
-  data_frame(x = predict(model, EnglandComp, type = "prob")[,2]>0.5) %>%
-    setNames(paste("Model", .x, sep="_"))
-}
-) %>% bind_cols() %>% 
-  mutate(
-  Outcome = rowSums(.)/ncol(.))
-
-EnglandComp <- EnglandComp%>% 
-  left_join(select(ModelMe, LAD11CD, Reference), by = "LAD11CD") %>%
-  mutate(
-    Significant.Competition = ifelse(is.na(Reference),
-                                     unlist(Preds$Outcome), 
-                                     as.logical(Reference))
-    ) %>%
-  mutate(
-
-      Comp.Type = case_when(
-      .$Significant.Competition<0.5-tol ~"No",
-      .$Significant.Competition>0.5 + tol ~"Yes",
-      .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
-      )
-  )
-
-EnglandComp %>%
-  ggplot(aes(x = Comp.Type, y= price, fill = Comp.Type)) + geom_boxplot()
-
-#Estimated
-
-EnglandCompTab <- EnglandComp %>%
-  group_by(Comp.Type) %>%
-  summarise(mean = mean(price),
-            median = median(price),
-            Homes = sum(Homes),
-            Pop = sum(Pop)) %>%
-  mutate(HomesPerc = Homes/sum(Homes)*100,
-         PopPerc = Pop/sum(Pop)*100) %>%
-  rename('LUPs>Homes' = Comp.Type, 
-         Population = Pop,
-         'Homes %' = HomesPerc,
-         'Population %' = PopPerc) %>%
-  gather(key = "key", "value"= value, -"LUPs>Homes") %>%
-  mutate(value = value %>% round %>%as.integer) %>%
-  spread(key = "LUPs>Homes", value = value)
-
-EnglandCompTab
-
-xtable(EnglandCompTab, caption="Summary of effect across England",
-       label = "tab:EnglandCompTab") %>% 
-  print(., type="latex", file=file.path(TexTables,"EnglandCompTab.tex"))
-
-#Observed
-Combine1ExO %>%
-  group_by((absdiff>0)) %>%
-  summarise(mean = mean(HomePrice),
-            median = median(HomePrice),
-            Homes = sum(Homes),
-            Pop = sum(Pop)) %>%
-  mutate(HomesPerc = Homes/sum(Homes),
-         PopPerc = Pop/sum(Pop))
-
-#Plotting the expected range of
-
-valuecheck <- sample(c(TRUE, FALSE), size = nrow(EnglandComp)*1000, replace = TRUE, prob = c(0.888, 1-0.888)) %>%
-  matrix(., nrow=nrow(EnglandComp)) 
-valuecheck <-   (valuecheck * ifelse(EnglandComp$Comp.Type == "Yes", TRUE, FALSE ) )%>% data.frame %>%
-  bind_cols(select(EnglandComp, LAD11CD, Reference),.) %>%
-  #Where ever the outcome is known it is reverted back to the true value, only estimated values are flipped.
-  gather(key = "ID", value = "affected",-LAD11CD,-Reference) %>%
-  mutate(Reference = as.logical(Reference)*1,
-    affected = ifelse(is.na(Reference), affected, Reference)) %>%
-  left_join(LadHomes) %>%
-  group_by(ID, affected) %>%
-  summarise(Homes = sum(Homes),
-            Pop = sum(Pop)) %>%
-  group_by(affected) %>%
-  mutate(Rank = percent_rank(Pop),
-    Outlier = ifelse(percent_rank(Pop)<0.0275 | percent_rank(Pop)>0.975, "Yes", "No")) %>%
-  group_by(ID) %>%
-  mutate(affected = ifelse(affected == 1, "Yes", "No"),
-         PercPop = Pop/sum(Pop))%>%
-  ungroup #%>%
-# mutate(PercPop = Pop)
-#The NNUMBERS DONT MATCH WITH THE TABLE WHY?
-
-#95 range is 78 to 84
-affected <- valuecheck %>% filter(affected == "Yes")
-q5 <- quantile(affected$PercPop,.05)
-q95 <- quantile(affected$PercPop,.95)
-x.dens <- density(affected$PercPop)
-df.dens <- data.frame(x = x.dens$x, y = x.dens$y)
-median(affected$PercPop)
-affected %>%
-  ggplot(aes(x = PercPop)) + geom_density() +
-  geom_area(data = subset(df.dens, x <= q5), 
-              aes(x=x,y=y))  +
-    geom_area(data = subset(df.dens, x >= q95), 
-              aes(x=x,y=y))+
-labs(title = "The estimated percentage of English population affected by LUPs")
-SaveFig("PopPercLUPAfftect.pdf")
-
-valuecheck %>% filter(affected == "No") %>%
-  ggplot(aes(x = PercPop)) + geom_density()
-
-```
-
-```{r}
-
-test <-ls(pattern = "DATA") %>%
-  map_df(~get(.x) %>%
-           group_by(LAD11CD) %>%
-           mutate(LowUsePercentile = percent_rank(LowUsePerc),
-                  MeanPricePercentile = percent_rank(MeanPrice)))
-
-cor(test$LowUsePerc,test$MeanPrice,"complete.obs")
-cor(test$LowUsePerc,test$MedianPrice, "complete.obs")
-
-cor(test$LowUsePercentile,test$MeanPricePercentile , "complete.obs")
-
-test %>%
-  ggplot(aes(x= LowUsePercentile, y = MeanPricePercentile)) +geom_point()
-
-test <-ls(pattern = "DATA") %>%
-  map_dbl(~{ df <-get(.x)
-    cor(df$LowUsePerc,df$MeanPrice,"complete.obs", method = "kendall")
-  })
-
-  plot(density(abs(test)))
-
-  Combine1ExO %>%
-    ggplot(., aes(x = absdiff>0 )) +geom_bar()
-
-```
-
-```{r}
-
-```
+  as.data.frame() %>%
+  mutate(VacantsPerc = Vacants/Homes,
+  #scaled so that the binomial can be interpreted
+  pricepercent = pricepercent %>% scale %>% as.numeric,
+         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
+         price = scale(price) %>% as.numeric,
+         Extent = scale(Extent) %>% as.numeric) %>%
+  mutate(Prob = predict(Mod, newdata = ., type ="response")) %>%
+  #merge on the truth
+  left_join(ModelMe %>% select(LAD11CD, Reference), by = "LAD11CD") %>%
+  mutate(BootCol = case_when(Reference == TRUE ~1,
+                             Reference == FALSE ~ 0,
+                             TRUE ~ Prob),
+         Comp.Type = Prob>0.5)
+
+BootPopHigh <-map2(EnglandComp$Pop, EnglandComp$BootCol, 
+            ~sample(c(.x, 0), size = 1000, 
+                    replace = TRUE,
+                    prob = c(.y, 1-.y)) %>%
+              as.tibble) %>%
+  bind_cols() %>%
+  rowSums() %>%
+  tibble(Pop=.) %>%
+  mutate(PercPop = Pop/sum(EnglandComp$Pop))
+
+BootPopHigh %>%
+  ggplot(aes(x = PercPop)) +
+  geom_density()
+
+#The 95 percent confidence interval of the mean
+QuantInfo<-quantile(BootPopHigh$Pop, probs = c(0.05, 0.5 ,0.95))
+quantile(BootPopHigh$PercPop, probs = c(0.05, 0.5 ,0.95))
+#diff is 3.6M
+QuantInfo[3]-QuantInfo[1]
+
+```

### 2018-07-17 allEnglandMap.Rmd
High value LUPS
I added in the number of LUPS that are worth more than the LAD median. This required changing BootsratpDistribcompare. However I can now predict the LADs where the majority of LUPs are high value, which is easier for people to understand.

@@
     MyData <- EnglandComp %>%
-    select(LAD11CD, Significant.Competition, LAD11NM, Comp.Type) %>%
+    select(LAD11CD, LAD11NM, Comp.Type) %>%
     merge(MyData, .)
+  # MyData <- EnglandComp %>%
+  #   select(LAD11CD, Significant.Competition, LAD11NM, Comp.Type) %>%
+  #   merge(MyData, .)
 
@@
   labels <- sprintf(
-    "<strong>%s</strong><br/>Market affected %s",
+    "<strong>%s</strong><br/>Predominantly high value LUPs %s",
     MyData$LAD11NM, MyData$Comp.Type
@@
 
+  z
+
 ```

### 2018-07-17 Functions/BootResSummaryData.R

@@ -1,40 +1,13 @@
 BootResSummaryData <- function(BootStrapRES){
   
   
-  #gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
-  CurrentLADS <- ls(pattern = "DATA", envir = globalenv()) %>%
-    map_chr(~{df<- get(.x)
-    df <- df %>%
-      group_by(LAD11CD) %>%
-      summarise(count = n())
-    df$LAD11CD[which.max(df$count)]}
-    )
-  
-  #Perform the t-test on the resulting lists
-  TtestRESgreater <-BootStrapRES %>% map(~ValueTtest(.x))
-  #TtestREStwo.sided <-BootStrapRES %>% map(~ValueTtest(.x, alternative = "two.sided"))
-  #Tidy results of thejust the ttest
-  TtestRES2 <- TtestRESgreater %>% map_df(~.x$t.test %>% tidy) %>%
-    select(p.value) %>%
-    mutate(LAD = elementnames,
-           LAD11CD = CurrentLADS,
-           HomePrice = TtestRESgreater %>% map_dbl(~.x$HomePrice),
-           LowUsePrice = TtestRESgreater %>% map_dbl(~.x$LowUsePrice),
-           absdiff = TtestRESgreater %>% map_dbl(~.x$absdiff),
-           Percdiff = TtestRESgreater %>% map_dbl(~.x$Percdiff)) 
-  
-  #Removing ANOVA as it causes probs when only tyoe a are included
-  #Perform ANOVA on the difference between the ratios of the groups on the bootrapped list
-  # ANOVARES <- BootStrapRES %>% 
-  #   map_df(~aov(.x$RatioExvsAct~.x$class) %>% tidy) %>% 
-  #   filter(term != "Residuals") %>%
-  #   select(-term) %>%
-  #   mutate(LAD = elementnames)
-  
   WardData <- ls(pattern = "DATA", envir = globalenv()) %>%
     map_df(~eval(parse(text=.x)) %>%
-             #select(WardLowUsePerc, WardLowUse) %>%
-             mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
+             group_by(LAD11CD) %>%
+             mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc),
+                     LAD11CDCounts = n()) %>%
+             ungroup %>%
[…]

### 2018-07-17 Functions/DistribCompareBootstrapper.R

@@ -1,85 +1,111 @@
-
-DistribCompareBootstrapper <-function(df, seed, samples=100, type = NULL, PropertyTypes = NULL){
-#df:data frame of processed area/s data
-#LADCD: The LAD code to fetch the correct price data
-# Random seed
-#Number of Bootstrap samples.
-#type: whether all purchese or only classes A or b are taken, enter a character "A" or "B" or leave NULL for all
-#PriceCuts: the cut points for the different classes of housing, used only occaisionally has to start with 0 and end with Inf
+DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL){
+  #df:data frame of processed area/s data
+  #LADCD: The LAD code to fetch the correct price data
+  # Random seed
+  #Number of Bootstrap samples.
+  #type: whether all purchese or only classes A or b are taken, enter a character "A" or "B" or leave NULL for all
+  #PriceCuts: the cut points for the different classes of housing, used only occaisionally has to start with 0 and end with Inf
   #and in total have 6 elements
- 
-  dfPrice <- SubsetPrice(df, type, PropertyTypes)
   
-dfWard <- df %>% 
-  group_by(Admin_ward_code) %>%
-  summarise_all(funs(first)) %>% filter(!is.na(Admin_ward_code))
-
-print("Start Bootstrapping LSOA distribution")
-
-#bootrapps LAD housing stock.
-set.seed(seed)
-dfWardLowUseStrap1 <- unique(dfPrice$Admin_ward_code)%>% 
-  map(~ dfPrice %>% 
-        filter(Admin_ward_code == .x) %>% 
-        ClassStrapper(., sum((filter(dfWard, Admin_ward_code == .x))$WardLowUse), reps = samples) %>%
-        mutate(class = as.character(class),
-               Counts = as.integer(Counts),
-               ID = as.integer(ID)) %>%
-        setNames(c("class", paste0("Counts", .x), paste0("Value", .x) ,"ID"))
-  ) %>%  
-  Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
-  mutate(Counts = rowSums(.[,grep("Counts", names(.))], na.rm = TRUE),
-         Value = rowSums(.[,grep("Value", names(.))], na.rm = TRUE),
-         Price = Value/Counts,
[…]

### 2018-07-17 SubCode/LondonFullProcesss.R

@@ -71,7 +71,7 @@ BarkingLONDATA <- read.xlsx( "Barking and DagenhamExemptionsLSOA v3.xlsx" , colN
 
 #Barnet
 
-BarnetLONDATA <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE) %>%
+BarnetLONDATA <- read.xlsx( "3386297 Attachment BarnetDiscounts.xlsx"  , colNames = TRUE)[1:4] %>%
   StructureData(2:8)
 
 

### 2018-07-17 SubCode/Setup.R

@@ -2,7 +2,7 @@
 
 
 packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
-              "forcats", "e1071", "htmlwidgets", "stringr", "modelr", "caret", "xtable", "rpart", "broom")
+              "forcats", "e1071", "htmlwidgets", "stringr", "modelr", "caret", "xtable", "rpart", "broom", "yardstick", "rsample")
 
 #, "mapview"
 new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]

### 2018-07-18 PaperCode.Rmd
New branch for quantiles
I realised calculating based on quantiles not price classes would be much easier. this requires much bigger changes

@@
     newLADs  %>% walk(~{print(.x)
-      DistribCompareBootstrapper(get(.x), 1652, 10, type, PropertyTypes)%>%
+      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes)%>%
       saveRDS(., file = paste0(.x, ".rds"))
@@
 
-#Analyse Bootstrap
+#Make class plots of bootstrap results
 
@@
 
+This chunk calculates for both A and B
+
 ```{r}
@@
 rm(ABratio); rm(ABratio2); rm(ABratio3)
-
-CombineAB %>%
-  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()
 
@@
 Modeldf <- ModelMe  %>%
-  vfold_cv(., V = 10, repeats = 100) %>%
+  vfold_cv(., V = 10, repeats = 10) %>%
   mutate(LogisticFOI = splits %>%
@@
 ModComp <- Modeldf %>%
-  select(LogFoiAcc, LogOpenAcc) %>%
+  select(LogFoiAcc, LogOpenAcc, ForestOpenAcc) %>%
   gather
@@
 QuantInfo<-quantile(BootPopHigh$Pop, probs = c(0.05, 0.5 ,0.95))
+QuantInfo
 quantile(BootPopHigh$PercPop, probs = c(0.05, 0.5 ,0.95))

### 2018-07-31 PaperCode.Rmd
Simplify
Removed Wales
Tried to re-do the model
Reduced the model coefficients

--- 2018-07-17 PaperCode.Rmd
@@
 
+Are LUPS concentrated in specific areas?
+  They are more concentrated than homes in general
+Are LUPs more or less expensive?
+  They tend to be concentrated in more expensive areas
+Are High value LUP LADS predictable?
+   They are predictable using number of vacants deprivation and price
+What is the relationship between LUPs and affordability?
+   A bath Tub curve
+What would the revenue from an empty homes tax be in the current situation?
+  A lot
+
+What do I conclude?
+  That there is a clear relationship between LUPs and price/unnafordability with the theorized curve being observed.
+  That areas with high prices tend to have more LUPs
+  That these areas may not have the space to build new property
+That building property in areas of high value LUPs means more LUPs as buyers invest in property, thus negating the purpose of the buidling.
+
 new article and paper on airbnb effecr
@@
 
-(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review; or""
+(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review"
 
@@
 
-```{r}
-
-setwd(file.path(RegionsComp, "Region Wales"))
-list.files()
-
-#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
-
-CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
-  StructureData(lowuse =c(8:13,15))
-
-MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
-  StructureData(lowuse = c(4:8))
-
-#includes the zero class which is descibeed as 
-#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
-  CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
-    StructureData()
-
-#Strangely low numbers checking
-# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
-#   StructureData(lowuse = c(3,5:6))
-
-#It seems Conwy really is this short on the discounts  
-ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
-  rename(Postcode = geo_postcode) %>%
-  mutate(Postcode = sub(" ", "", Postcode)) %>%
-  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
-  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
-  StructureData(lowuse = c(2,4))
-
-DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
-    StructureData(c(8:9,11,13))
-
-WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
-    StructureData(2:5)
-
-#Pembrokeshire didn't send all the data
-PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
-    StructureData(3)
-
-FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
-    StructureData()
+Wales is removed to simplify the process.
+As the deprivation scales are separate for all countries this means wales cannot be included in the predictive model later. Also the council tax is seperate.
+
+```{r}
+# 
+# setwd(file.path(RegionsComp, "Region Wales"))
+# list.files()
+# 
+# #Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
+# 
+# CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
+#   StructureData(lowuse =c(8:13,15))
+# 
+# MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
+#   StructureData(lowuse = c(4:8))
+# 
+# 
+# #includes the zero class which is descibeed as 
+# #ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
+#   CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
+#     StructureData()
+# 
+# #Strangely low numbers checking
+# # PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
+# #   StructureData(lowuse = c(3,5:6))
+# 
+# #It seems Conwy really is this short on the discounts  
+# ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
+#   rename(Postcode = geo_postcode) %>%
+#   mutate(Postcode = sub(" ", "", Postcode)) %>%
+#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
+#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
+#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
+#   StructureData(lowuse = c(2,4))
+# 
+# DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
+#     StructureData(c(8:9,11,13))
+# 
+# WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
+#     StructureData(2:5)
+# 
+# #Pembrokeshire didn't send all the data
+# PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
+#     StructureData(3)
+# 
+# FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
+#     StructureData()
 
@@
 
-#Plot stuff
-```{r}
-x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet
-
-z<- MakeLeaflet(AllerdaleDATA)
-z
-# 
-setwd(basewd)
- saveWidget(z, file=file.path(basewd, "Cumbria.html"), selfcontained = TRUE )
-
-#testSouth <- DistribCompareBootstrapper(SouthwarkLONDAls(pattern = "DATA")TA, 1652, 1000)
-testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-ValueTtest(test)
-
-PlotMap(ConwyDATA)
-
-z <-ChelseaLONDATA %>% 
-  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
-  filter(LAD11NM =="Kensington and Chelsea") %>% 
-  MakeLeaflet()
-
-mapshot(z, file = file.path(Figures, "Chelsea.pdf"))
-
-CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
-  map_df(~get(.x)) %>%
-   group_by(LSOA_CODE) %>%
-   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
-  CalcLowUse()
-
-z<- MakeLeaflet(CumbriaPlot)
-
-mapshot(z, file = file.path(Figures, "Cumbria.pdf"))
-
-z<- MakeLeaflet(CornwallDATA)
-mapshot(z, file = file.path(Figures, "Cornwall.pdf"))
-
-z<- MakeLeaflet(BarrowCUMBRIADATA)
-mapshot(z, file = file.path(Figures, "Barrow.pdf"))
-
-MakeLeaflet(ConwyDATA)
-
-```
-
-#Look at saleries
+#Saleries
 ```{r}
@@
   map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
-  group_by(MSOA11CD) %>%
-  summarise(LowUse = sum(LowUse, na.rm = T),
+  group_by(MSOA11CD) %>% # ward code is used for consistency
+  summarise(
+    #MSOA11CD = first(MSOA11CD), #MSOA is kept to allow joining of income
+    LowUse = sum(LowUse, na.rm = T),
             Homes = sum(Homes, na.rm = T),
@@
   mutate(decile = ntile(ratio, 50))
-
-cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
-cor(unafford$Yearly.income, unafford$ratio, "complete.obs")
-
-cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
-cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
-cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")
-
-test <- lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford)
-
-summary(test)
 
@@
 
+cor(unafford$Yearly.income, unafford$ratio, "complete.obs")
+cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
+cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")
+lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford) %>% summary
+
+rm(unafford); rm(unaffordExLon); rm(unaffordLon)
+
 #Looking at the relationship between unaffordability and LUP percentage
@@
 decile %>% 
-#  filter(type == "Only London") %>% 
+  #filter(type == "Excluding London") %>% 
   ggplot(aes(x= decile, y = median)) + 
@@
   theme(legend.position= "none") + 
-  geom_smooth(method="loess",se=FALSE, colour = "black")
+  geom_smooth(method="loess",se=FALSE, colour = "black") +
+ coord_cartesian(ylim = c(0.01, 0.05)) +
+   scale_y_continuous(labels = scales::percent)
 SaveFig("LowUsePercVSratio.pdf")
-
-decile %>% 
-  filter(type == "Excluding London") %>% 
-  ggplot(aes(x= ratio, y = median)) + 
-  facet_grid(.~type) + 
-  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
-  geom_point(aes(colour = type))  +
-  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
-  theme(legend.position= "none") + 
-  geom_smooth(method="loess",se=FALSE, colour = "black")
-
-#model fit
-decile %>% 
-    filter(type == "Excluding London") %>% 
-  lm(median~decile +decile2, data = .) %>% summary
-
-#model fit
-decile %>% 
-    filter(type == "Excluding London") %>% 
-lm(median~ratio + ratio2, data = .) %>% summary
-
-decile %>% 
-    filter(type == "Excluding London") %>% 
-lm(median~expval + expvalneg, data = .) %>% summary
 
@@
 
-mod2 <- decile %>% 
-    filter(type == "Only London") %>% 
-  nls(median ~ exp(a + b*decile), data = ., 
-      start = list(a = 0, b = -3))
-
 summary(mod)
@@
   geom_line(aes(y = predict(mod, list(x = decile))))
-
-unafford %>%
-  ggplot(aes(x= ratio, y = MeanPrice)) + geom_point()
 
@@
 ```{r}
-
+PropertyTypes <- c("D", "S", "T", "F")
 setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities")
@@
 
-BootStrapRESExO <- BootStrapRES
-#Should clean up and remove EXO
-rm(BootStrapRES)
-
 #Make a summary dataframe
-Combine1ExO <- BootResSummaryData(BootStrapRESExO)
+Combine1ExO <- BootResSummaryData(BootStrapRES)
 
@@
 ```{r}
-test <- BootStrapRESExO$WestminsterLON %>% 
-  group_by(class) %>%
-  summarise_all(funs(mean))
-
-test2 <- test %>%
-  select(-class) %>%
-  summarise_all(funs(sum)) %>%
-  mutate(LowUseValue = LowUseValue/1e9)
-
 #99% of the LADs are significantly different from 0 at the 95% level
@@
 
-PlotClassDiff(BootStrapRESExO$ChelseaLON, "Kensington and Chelsea")
+CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
+  df %>% 
+  group_by(ID, class) %>%
+  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
+  group_by(ID)%>%
+  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
+  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
+}
+
+CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
+PlotClassDiff(., "Kensington and Chelsea")
 SaveFig("ClassdiffChelsea.pdf")
 
-PlotClassDiff(BootStrapRESExO$Cornwall, "Cornwall")
+CleanForPlotClassDiff(BootStrapRES$Cornwall)  %>%
+PlotClassDiff(., "Cornwall")
 SaveFig("ClassdiffCornwall.pdf")
 
-PlotClassDiff(BootStrapRESExO$BarrowCUMBRIA, "Barrow")
+CleanForPlotClassDiff(BootStrapRES$BarrowCUMBRIA) %>%
+PlotClassDiff(., "Barrow")
 SaveFig("ClassdiffBarrow.pdf")
 
-test <- BootStrapRESExO %>% 
+#Plot for all data
+All_data_class <- BootStrapRES %>% 
   bind_rows %>%
-  select(-LAD11CD) %>%
-  group_by(class, ID) %>%
-  summarise_all(sum) %>%
-  ungroup %>%
-  mutate(HomesPrice = HomesValue/Homes,
-         LowUsePrice = LowUseValue/LowUse,         
-         ratio = LowUse/Homes,
-         HomesPerc = Homes/sum(Homes, rm.na = T),
-         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
-         ClassPerc = LowUse/Homes,
-         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
-         RatioExvsAct = LowUse/ExpectedHomes
-         ) %>%
-        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")),
-               LUPmore = RatioExvsAct>1)
-
-test2 <- test %>% group_by(class) %>%
+  select(CountryClass, ID, LowUse, Homes) %>%
+  rename(class = CountryClass)%>%
+  CleanForPlotClassDiff
+
+All_data_class %>% group_by(class) %>%
   summarise_all(mean)
 
-PlotClassDiff(test)
+PlotClassDiff(All_data_class)
 SaveFig("ClassdiffAllData.pdf")
 
-test %>% 
-  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
-   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
-     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
-     geom_boxplot() + 
-     labs(title = "Observed within class difference in Price from expected for LUPs")
-SaveFig("PricediffAllData.pdf")
-
 #Total value of homes and LUPS
 
-LADnames <- names(BootStrapRESExO)
-
-LUPval <-   map2(.x =BootStrapRESExO, .y =   names(BootStrapRESExO),~ {.x %>% mutate(LAD  = .y)}) %>%
+#LADnames <- names(BootStrapRES)
+
+LUPval <-   map2(.x =BootStrapRES, .y =   names(BootStrapRES),~ {.x %>% mutate(LAD  = .y)}) %>%
   bind_rows %>%
-  select(-class, -LAD11CD) %>%
+  select(-class, -LAD11CD, -CountryClass,-classVal) %>%
   group_by(LAD, ID) %>%
@@
 
-PropertyTypes <- c("D", "S", "T", "F")
-
 #calulcate the number of properties sold and the mean price
@@
 
+#Overall Concentration plot
+
+This chunk makes a plot that shows that LUPs are more heavily concentrated than Homes
+
+```{r}
+   test <- ls(pattern = "DATA") %>%
+  map_df( ~get(.x) %>%
+            select(LSOA_CODE, Admin_ward_code, LowUse, Homes))%>%
+  group_by(Admin_ward_code) %>%
+  summarise(LowUse = sum(LowUse),
+            Homes = sum(Homes)) %>%
+  filter(!is.na(Homes))
+
+%>%
+  arrange(-LowUse) %>%
+  mutate(
+    CumsumLUP = cumsum(LowUse),
+    CumsumLUPPerc = CumsumLUP/sum(LowUse),
+    CumsumHomes = cumsum(Homes),
+    CumsumHomesPerc = CumsumHomes/max(CumsumHomes),
+    CumsumNumber = 1:nrow(.),
+    CumsumPercNumber = CumsumNumber/max(CumsumNumber))
+
+test2 <- test %>%
+  gather(key = Type, value = value, -Admin_ward_code) %>%
+  group_by(Type) %>%
+  arrange(-value) %>%
+  mutate(
+    Cumsum = cumsum(value),
+    CumPerc = Cumsum/sum(value),
+    CumsumNumber = 1:n(),
+    CumsumPercNumber = CumsumNumber/max(CumsumNumber))
+
+test2%>%
+  ggplot(aes(x = CumsumPercNumber, y = CumPerc, colour = Type)) + geom_line() +
+  labs(
+    title= "Comparison of LUP vs Home concentration", 
+       y= "Percent of total property type", 
+    x= "Cumulative percent of administrative wards") +
+  scale_color_discrete(labels = c("Homes", "LUPs"))+
+   scale_y_continuous(labels = scales::percent)+
+  scale_x_continuous(labels = scales::percent)
+SaveFig("LUPConcentration.pdf")
+
+test3 <-test2 %>%
+  select(Type, CumPerc, CumsumPercNumber) %>%
+  spread(key = "Type", value = "CumPerc") %>%
+  mutate(ratio = LowUse/Homes-1)
+
+test3 %>%
+  ggplot(aes(x= CumsumPercNumber, y = ratio)) + geom_line()
+
+```
+
 #Inlcuding deprivation
@@
 ```{r}
+LADincome <- EW2 %>%
+  group_by(MSOA11CD) %>%
+  summarise(Pop = sum(Pop),
+            LAD11CD = first(LAD11CD)) %>%
+  ungroup %>%
+  select(LAD11CD,MSOA11CD, Pop)%>%
+ left_join(IncomeEst %>%
+              select( MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
+  mutate(TotalIncome = Pop*Yearly.income) %>%
+  group_by(LAD11CD) %>%
+  summarise(Pop = sum(Pop),
+            income = sum(TotalIncome)) %>%
+   mutate(income = income/Pop)
+
 LADprice <- prices %>%
@@
 summarise(price = mean(X2)) %>%
-  mutate(pricepercent = percent_rank(price))
+  mutate(pricepercent = percent_rank(price)) %>%
+  ungroup
 
@@
   left_join(Vacants, by = "LAD11CD") %>%  
+  left_join(LADincome %>%
+              select(LAD11CD, income ), by = "LAD11CD") %>%
   mutate(VacantsPerc = Vacants/Homes,
-         LTVPerc = Vacants/Homes) %>%
+         LTVPerc = Vacants/Homes,
+         afford = price/income) %>%
   #filter out wales
@@
          VacantsPerc = scale(VacantsPerc) %>% as.numeric,
-         price = scale(price) %>% as.numeric,
-         Extent = scale(Extent) %>% as.numeric) %>%
-  mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)
+         price = price %>% scale %>% as.numeric,
+         Extent = scale(Extent) %>% as.numeric) #%>%
+ # mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)
+
+ModelMe %>% ggplot(aes(x = afford, y = (LUPS/(Homes+LUPS)), colour = Reference)) + geom_point()
+
+#57% of LADs have mostly high value properties
+table(ModelMe$Reference)
+
+rm(LADincome)
+
 ```
@@
 OpenFormula <- as.formula(Reference~ Extent + price + VacantsPerc)
+OpenFormula2 <- as.formula(Reference~ Extent + price)
 
@@
 Modeldf <- ModelMe  %>%
-  vfold_cv(., V = 10, repeats = 100) %>%
+  vfold_cv(., V = 5, repeats = 200) %>%
   mutate(LogisticFOI = splits %>%
@@
         ),
+  LogisticOpen2 = splits %>%
+  map(.,~{ glm(OpenFormula2, data = analysis(.x),binomial(link='logit'))}
+        ),
   ForestOpen = splits %>% 
-    map(., ~{rpart(OpenFormula, data=analysis(.x))})
+    map(., ~{rpart(OpenFormula2, data=analysis(.x))})
   ) %>%
@@
          LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"),
+         LogOpenAcc2 = GetAccuracy(., "splits", "LogisticOpen2"),
          ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))
@@
 ModComp <- Modeldf %>%
-  select(LogFoiAcc, LogOpenAcc) %>%
+  select(LogFoiAcc, LogOpenAcc, ForestOpenAcc, LogOpenAcc2) %>%
   gather
@@
   group_by(model) %>%
-  summarise(mean =mean(statistic))
+  summarise(mean =mean(statistic),
+            median = median(statistic))
+
+   test <- select_(Modeldf, "splits") %>% 
+     flatten %>%
+     map2(select_(Modeldf,"LogisticFOI") %>% flatten, ., ~{ augment(.x, newdata = assessment(.y)) %>%
+               mutate(.fitted = factor(.fitted > 0,
+                        levels = as.factor(c("FALSE", "TRUE"))))
+     })
+
+```
+
+#Model two
+
+Older modelling style as I am not sure what is happening with the current method.
+```{r}
+reps <- 1000
+
+set.seed(1983)
+TestResample <- 1:reps %>% map(~  resample_partition(ModelMe, c(test = 0.2, train = 0.8)))
+
+LogFOI <- 1:reps %>% map_df(~{
+  train<- TestResample[[.x]]$train %>% as.data.frame
+  test <- TestResample[[.x]]$test %>% as.data.frame
+  ;
+  model <- glm(FOIFormula, 
+               family=binomial(link='logit'),
+               train)
+
+  Confmat <- confusionMatrix( predict(model, test, type = "response")>0.5,
+                              test$Reference)
+
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
+          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
+
+}
+)
+
+LogOpen<- 1:reps %>% map_df(~{
+  TestResample<- TestResample[[.x]]
+
+  model <- glm(OpenFormula, 
+               family=binomial(link='logit'),
+               as.data.frame(TestResample$train))
+
+  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
+                              as.data.frame(TestResample$test)$Reference)
+
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
+          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
+
+}
+)
+
+ForestOpen<- 1:reps %>% map_df(~{
+  TestResample<- TestResample[[.x]]
+
+  model <- rpart(OpenFormula, data = as.data.frame(TestResample$train))
+
+  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "prob")[,2]>0.5,
+                              as.data.frame(TestResample$test)$Reference)
+
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
+
+}
+)
+
+ModRes <- bind_rows(LogFOI, LogOpen, ForestOpen) %>%
+  mutate(Model = rep(c("LogFOI", "LogOpen", "ForestOpen"), each = reps))
+
+ModRes %>%
+  ggplot(aes(x= Model, y = Accuracy)) +
+  geom_boxplot()
+
+ModRes %>%
+  group_by(Model) %>%
+  summarise(mean = mean(Accuracy),
+            median = median(Accuracy),
+            above = sum(Accuracy>AccuracyNull)/reps,
+            above2 = median(Accuracy-AccuracyNull),
+            NullMean = mean(AccuracyNull),
+            NullMedian = median(AccuracyNull))
+
+```
+
+```{r}
+
+  BootDeets <- BootStrapRES %>% map_df(~.x %>% group_by(ID) %>%
+                                    summarise(HighVal = sum(HighVal, na.rm = T),
+                                              LAD11CD= first(LAD11CD),) 
+  ) %>% 
+  left_join(., Combine1ExO %>% select(LAD11CD, LUPS)) %>%
+  mutate(Majority = HighVal>=(LUPS/2)) %>%
+  left_join(., select(ModelMe, LAD11CD, Extent, price, VacantsPerc), by = "LAD11CD") %>%
+  mutate(Reference = HighVal>(LUPS/2))
+
+#There is in fact boostrap variation on which LADS are majority
+test <- BootDeets %>%
+  group_by(LAD11CD) %>%
+  summarise(Majority = sum(Majority, na.rm = T)/1000,
+            Total = n(),
+            t2 = abs(Majority-0.5)+0.5)
+
+test %>%
+  ggplot(aes(x = Majority)) + geom_density()
+
+test2 <- BootStrapRES$IslingtonLONDATA %>%
+  group_by( ID) %>%
+  summarise(HighVal = sum(HighVal),
+            LowUse = sum(LowUse))
+
+median(test$t2)
+
+BootModData <- select(BootDeets, ID, LAD11CD, Majority) %>%
+  left_join(., select(ModelMe, LAD11CD, Reference,LUPdepExt, price, VacantsPerc, Extent))
+
+#make list of bootstrap models
+MakeBootModels <- function(df, trainvect, ModForm = OpenFormula){
+
+  BootMod <- (1:max(df$ID)) %>%
+  map(~{
+
+    ModData <- df %>%
+      filter(ID ==.x)
+
+  model <- glm(ModForm, 
+               family=binomial(link='logit'),
+               data = ModData[trainvect,])
+
+  }
+
+  )
+
+}
+
+#extract predictions
+MakeBootPreds <- function(df, BootMod, testvect){
+
+  Predsdf <- 1:length(BootMod) %>%
+  map(~{
+
+        ModData <- df %>%
+      filter(ID ==.x)
+
+    tibble(v1 =predict(BootMod[[.x]], ModData[testvect,], type = "response")>0.5) 
+  }) %>%
+  bind_cols() %>% set_names(make.names(1:length(BootMod)))# %>%
+ # mutate(BootResult =rowSums(.)/ncol(.)>0.5)
+
+  return(Predsdf)
+
+}
+
+#get the accuracy across all bootstraps
+MakeBootAccuracy <- function(Predsdf, df, testvect){
+
+    Accdf <- 1:ncol(Predsdf) %>%
+  map_df(~{
+
+    ModData <- df %>%
+      filter(ID ==.x)
+
+    Confmat <- confusionMatrix( Predsdf[,.x] %>% unlist,
+                              ModData$Reference[testvect])
+    # Confmat <- bind_cols(Predsdf %>% select(.x),
+    #                   as.data.frame(testvect) %>% select(Reference)) %>%
+    #   set_names(c("Predictions", "Reference")) %>%
+    #   mutate(Predictions = factor(Predictions,
+    #                     levels = as.factor(c("FALSE", "TRUE")))) %>%
+    #   conf_mat(truth = Reference, estimate = Predictions)
+
+  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = .x)
+
+  })
+
+}
+
+OpenFormula <- as.formula(Reference~ Extent + price)
+BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[1]]$train))
+Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[1]]$test))
+Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[1]]$test))
+
+bind_rows(Accdf %>%mutate(modelOpen = "V1"), 
+          Accdf2 %>%mutate(modelOpen = "V2")) %>%
+  ggplot(aes(x = modelOpen, y = AccuracyPValue)) + geom_boxplot()
+
+Confmat <- confusionMatrix(rowSums(Predsdf)/ncol(Predsdf)>0.5, as.data.frame(TestResample[[1]]$test)$Reference)
+  BootOut <- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = 1001)
+
+Coeffs1 <- 1:length(BootMod) %>%
+  map_df(~BootMod[[.x]] %>% tidy %>% mutate(ID = .x) ) %>%
+  mutate(model = "Open1")
+
+Coeffs1 %>%
+  filter(term != "VacantsPerc", term != "(Intercept)") %>%
+  ggplot(aes(x = term, y = p.value, fill = term)) + geom_boxplot() + 
+  coord_cartesian(y = c(0,0.12))
+
+Accdf <- bind_rows(Accdf, BootOut)
+
+set.seed(1983)
+TestResample <- 1:50 %>% map(~  resample_partition(ModelMe, c(test = 0.1, train = 0.9)))
+
+AccMega <- 50:1 %>%
+  map_df(~{
+    print(.x)
+    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train),ModForm =  as.formula(Reference~ + price))
+Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[.x]]$test))
+Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[.x]]$test))
+
+Confmat <- confusionMatrix(rowSums(Predsdf)/ncol(Predsdf)>0.5, as.data.frame(TestResample[[.x]]$test)$Reference)
+  BootOut <- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
+          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
+  mutate(ID = 1001)
+
+bind_rows(Accdf, BootOut) %>%
+  mutate(Sample = .x)
+  })
+
+CoeffsMega <- 50:1 %>%
+  map_df(~{
+    print(.x)
+    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train), ModForm =  as.formula(Reference~ + price))
+
+    #needs to be mapped again to extract every model not just the first 50!
+BootMod[[.x]] %>% tidy %>% mutate(ID = .x) %>%
+  mutate(Sample = .x)
+  })
+
+CoeffsMega <- CoeffsMega %>%
+  mutate(beats = p.value<0.05)
+
+CoeffsMega %>%
+  filter(term != "VacantsPerc", term != "(Intercept)") %>%
+  ggplot(aes(x = term, y = p.value, fill = term)) + geom_boxplot() + 
+  coord_cartesian(y = c(0,0.12))
+
+test<- CoeffsMega %>%
+  group_by(term) %>%
+  summarise_all(funs(mean, median))
+
+table((AccMega$Accuracy-AccMega$AccuracyNull)>0)/50050
+
+AccMega2 <- AccMega %>%
+  mutate(MajVote = ID == 1001)
+
+test <- AccMega2 %>%
+  group_by(MajVote) %>%
+  summarise_all(funs(mean, median))
+
+AccMega2 %>%
+  filter(ID == 1001) %>%
+  ggplot(aes(x = AccuracyPValue)) + geom_density()
+
+AccMega2 %>%
+  ggplot(aes(x = MajVote, y = Accuracy)) + geom_boxplot()
+
+median(AccMega$AccuracyPValue)
 
@@
 #All England Bootstrap
+
+Can't be used as there is not enough power
 
@@
 ```
+
+#Vancouver Tax
+
+```{r}
+setwd(DataFolder)
+QRC2017<- read_xlsx("QRC4-2017-2018.xlsx", sheet = 2, skip = 2) %>%
+  select(3:4) %>%
+  set_names("LAD11CD", "CouncilTax") %>%
+  mutate(CouncilTax = CouncilTax*1000)
+
+EmptyTax <- Combine1ExO %>%
+  left_join(., QRC2017) %>%
+  mutate(EmptyTax = MeanLUPs*LUPS*0.01,
+         EmptyOfCouncil = EmptyTax/CouncilTax)
+
+sum(EmptyTax$EmptyTax)/1e6
+mean(EmptyTax$EmptyOfCouncil, na.rm = T)
+median(EmptyTax$EmptyOfCouncil, na.rm = T)
+
+sum(EmptyTax$EmptyTax)/sum(EmptyTax$CouncilTax)
+
+EmptyTax %>%
+  ggplot(aes(x =EmptyOfCouncil)) + geom_density() +
+  coord_cartesian(x=c(0,0.7)) +
+  scale_x_continuous(labels = scales::percent) +
+  labs(title = "Distribution of value of Empty homes tax in terms of council tax by local authority", 
+       x = "Percent of council tax value")
+
+EmptyTax %>%
+  select(EmptyOfCouncil, LAD) %>%
+  arrange(EmptyOfCouncil) %>%
+  top_n(5,EmptyOfCouncil)
+
+```
+
+#Plot stuff
+```{r}
+x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet
+
+z<- MakeLeaflet(AllerdaleDATA)
+z
+# 
+setwd(basewd)
+ saveWidget(z, file=file.path(basewd, "Cumbria.html"), selfcontained = TRUE )
+
+#testSouth <- DistribCompareBootstrapper(SouthwarkLONDAls(pattern = "DATA")TA, 1652, 1000)
+testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
+  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
+  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
+
+ValueTtest(test)
+
+PlotMap(ConwyDATA)
+
+z <-ChelseaLONDATA %>% 
+  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
+  filter(LAD11NM =="Kensington and Chelsea") %>% 
+  MakeLeaflet()
+
+mapshot(z, file = file.path(Figures, "Chelsea.pdf"))
+
+CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
+  map_df(~get(.x)) %>%
+   group_by(LSOA_CODE) %>%
+   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
+  CalcLowUse()
+
+z<- MakeLeaflet(CumbriaPlot)
+
+mapshot(z, file = file.path(Figures, "Cumbria.pdf"))
+
+z<- MakeLeaflet(CornwallDATA)
+mapshot(z, file = file.path(Figures, "Cornwall.pdf"))
+
+z<- MakeLeaflet(BarrowCUMBRIADATA)
+mapshot(z, file = file.path(Figures, "Barrow.pdf"))
+
+MakeLeaflet(ConwyDATA)
+
+```

### 2018-07-31 Functions/SubsetPrice.R

@@ -1,5 +1,4 @@
-
-SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, PriceCuts = NULL){
+SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, Quantiles = NULL){
   #Subsets the price frame to be just for the specific LAD
   #Takes either the DATA dataframe or the character string LAD11CD
   #this allows the subsetting of the price list without looking up the LAD code
@@ -12,30 +11,35 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, PriceCuts = NULL)
     Code <- names(table(df$LAD11CD))[which.max(table(df$LAD11CD) %>% as.matrix)] 
   }
   
+  #filter prices to only relevant rows
+  pricesTemp <- prices %>%
+  filter(., grepl(Code, Admin_district_code)) 
+  
   if(!is.null(type)){
-    prices <- prices %>%
+    pricesTemp <- pricesTemp %>%
       filter(X15 == type)
   }
-
+  
   #Removes all unwanted property types, useful for removing Other type
   if(!is.null(PropertyTypes)){
-    prices <- prices %>%
+    pricesTemp <- pricesTemp %>%
       filter(X5 %in% PropertyTypes)
   }
   
-  if(is.null(PriceCuts)){
-    PriceCuts<-c(0,  490,      750,   2000, 12000, Inf)*10^3
+  if(is.null(Quantiles)){
+    Quantiles<-c(0, quantile(pricesTemp$X2)[2:4], Inf)
   }
-  
+
   #The  model used to take multiple councils if there was overlap, but this caused some strange
   #Problems So I removed it. The current version only takes a single LAD
-  prices %>%
-  filter(., grepl(Code, Admin_district_code)) %>%
-    select(Admin_ward_code, lsoa11cd, Price =X2, X15, PropType = X5) %>%
-    mutate(class = cut(Price, PriceCuts, 
-                       labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
-                       right = F),
+  pricesTemp %>%
+    select(Admin_ward_code, lsoa11cd, Price =X2, X15, PropType = X5, CountryClass, MSOA11CD) %>%
+    mutate(class = cut(Price, Quantiles, 
+                       labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
+                       right = F) %>% fct_relevel(., "Upper", after = 3),
+           classVal = cut(Price, Quantiles, 
[…]

### 2018-07-31 SubCode/AuxdataLoad.R

@@ -10,7 +10,7 @@ CTtaxstock<- read_csv("Table_CTSOP1.1_2016.csv")
 pop <- read_csv("SAPE2.csv")
 
 EW <- inner_join(select(CTtaxstock, ECODE, ALL_PROPERTIES),select(pop, `Area Codes`, `All Ages`),
-                 by=c("ECODE" = "Area Codes")) %>% setNames(c("ECODE", "Homes", "Pop")) 
+                 by=c("ECODE" = "Area Codes")) %>% setNames(c("ECODE", "Homes", "Pop"))
 
 
 #Load the LSOA shape data for EW 
@@ -72,7 +72,8 @@ EW2 <- inner_join(EW, lsoa, by = c("ECODE" = "LSOA11CD") ) %>%
   left_join(., select(wardnames, Admin_ward_code, WD16NM), by = "Admin_ward_code") %>%
   group_by(Admin_ward_code) %>%
   mutate(WardHomes = sum(Homes),  WardPop = sum(Pop)) %>% 
-  ungroup
+  ungroup %>%
+  filter(grepl("E", ECODE))
 rm(wardlsoa)
 rm(wardnames)
 
@@ -106,10 +107,23 @@ saveRDS(AG, file.path(DataFolder,"shapeframe.rds"))
 setwd(DataFolder)
 
 prices <-read_csv("pp-2016.csv", col_names = FALSE ) %>% 
-mutate(X4 = gsub(" ", "", X4)) %>% 
-left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)), 
-by = c("X4"="Postcode")) %>% 
-filter(!is.na(lsoa11cd)) %>% mutate(Prime = X2>1e6, SuperPrime = X2>1e7)
+  mutate(X4 = gsub(" ", "", X4)) %>%
+  left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)),
+            by = c("X4"="Postcode")) %>%
+  filter(!is.na(lsoa11cd)) %>% 
+  left_join(select(EW2, ECODE, MSOA11CD), by =c("lsoa11cd"="ECODE")) %>% #Add in the MSOA code
+  filter(Country_code == "E92000001") %>%
+  mutate(Prime = X2>1e6, SuperPrime = X2>1e7) #is this line necessary
+
+
+Quantiles <-c( 0, quantile(prices$X2)[2:4], Inf)
+
+prices <- prices %>%
[…]

### 2018-07-31 MSOAmodel.Rmd
Get back MSOA model
I made an MSOA model that worked really well. Sadly I crashed the computer and lost all the code. The re-written code produces a rubbish model, I don't know why. Maybe turning it off and on will help...

---
title: "Untitled"
author: "Jonathan Bourne"
date: "31 July 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

Use the MSOA to make a model it has many examples and maps perfectly to the income estimates

Number of MSOA per LAD
```{r}

testMSOA <- EW2 %>%
  group_by(LAD11CD, MSOA11CD) %>%
  summarise(counts = n()) %>%
  group_by(LAD11CD) %>%
  summarise(counts = n())

testWard <- EW2 %>%
  group_by(LAD11CD, Admin_ward_code) %>%
  summarise(counts = n()) %>%
  group_by(LAD11CD) %>%
  summarise(counts = n())

```

```{r}

test <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes )
test1 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes )

test2 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )

```

```{r}
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")

#Find what needs to be bootstrapped
BootStrapFiles <- list.files(getwd()) %>% gsub("DATA.rds", "",.)
  newLADsnames <- sub("DATA", "", ls(pattern = "DATA", envir = globalenv())) %>% 
    .[!(. %in% BootStrapFiles)] 
  newLADs <- paste0(newLADsnames, "DATA")

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD" )%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

  #once all Bootratps complete load them all into a list
 BootStrapRES <- list.files(getwd()) %>%
   map(~readRDS(.x))

 #name the list
 names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)
```

#Make modelling dataframe

The variables are

mean deprivation decile
Affordability

```{r}

MSOAdep <- LSOADep %>%
  select(LSOA_CODE, Rank = Rank..where.1.is.most.deprived., Decile = Decile..where.1.is.most.deprived.10..of.LSOAs.) %>%
  left_join(select(EW2, MSOA11CD, ECODE), by = c("LSOA_CODE"="ECODE")) %>%
  select(-LSOA_CODE) %>%
  group_by(MSOA11CD) %>%
  summarise_all(mean)

BootDeets <- BootStrapRES %>% 
  map_df(~.x %>%
           mutate(Reference = MedianHomes < MedianLUPs,
                  MeanPropPrice = (HomesValue+LowUseValue)/(Homes+LowUse)) %>%
           select(MSOA11CD, MeanPropPrice, Reference, ID)) %>%
  left_join(select(IncomeEst, MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
  left_join(MSOAdep, by = "MSOA11CD") %>%
  mutate(AffordRatio  = MeanPropPrice/Yearly.income,
         AffordRatio2 = AffordRatio^2,
         AffordRatio3 = AffordRatio^3)

rm(MSOAdep)

#Why do some have 2000?
test <- BootDeets %>%
  group_by(MSOA11CD) %>%
  summarise(Majority = sum(Reference, na.rm = T)/1000,
            Total = n())

BootDeetsMean <- BootDeets %>%
  select(MSOA11CD, Reference, Decile, AffordRatio) %>%
  group_by(MSOA11CD) %>%
  summarise_all(mean) %>%
  mutate(Reference = Reference>0.5)

set.seed(1983)
TestResample <- 1:50 %>% map(~  resample_partition(BootDeetsMean, c(test = 0.1, train = 0.9)))

OpenFormula <- as.formula(Reference~ AffordRatio+ Decile)

BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[1]]$train))
Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[1]]$test))
Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[1]]$test))

sum(Accdf$Accuracy>Accdf$AccuracyNull)

mean(Accdf$Accuracy)

CoeffsMega <- 1 %>%
  map_df(~{
    print(.x)
    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train), ModForm =  OpenFormula)

    #needs to be mapped again to extract every model not just the first 50!
    Out <- 1:length(BootMod) %>% map_df(~
                          BootMod[[.x]] %>% tidy %>% mutate(ID = .x)               
                                        )%>%
      mutate(Sample = .x)
  })

```

### 2018-07-31 PaperCode.Rmd
Get back MSOA model
I made an MSOA model that worked really well. Sadly I crashed the computer and lost all the code. The re-written code produces a rubbish model, I don't know why. Maybe turning it off and on will help...

@@
 #Saleries
+
+Problem here with the MSOA/LSOA code in the IncomeEst
+
 ```{r}
@@
   }) %>%
-  bind_cols() %>% set_names(make.names(1:length(BootMod)))# %>%
- # mutate(BootResult =rowSums(.)/ncol(.)>0.5)
+  bind_cols() %>% set_names(make.names(1:length(BootMod)))
 

### 2018-07-31 Functions/DistribCompareBootstrapper.R

@@ -1,4 +1,4 @@
-DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL){
+DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("class", "classVal", "CountryClass")){
   #df:data frame of processed area/s data
   #LADCD: The LAD code to fetch the correct price data
   # Random seed
@@ -17,10 +17,10 @@ DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, Prope
     group_by(LAD11CD) %>%
     mutate(LADCount = n()) %>% ungroup %>%
     filter(!is.na(Admin_ward_code), LADCount == max(LADCount)) %>% #filter out any stray areas that are classed as a different authority
-  select(-LADCount)  
-    
+    select(-LADCount)  
+  
   #Function generated within the function to make sure both Homes and LUPs are calculated the same way.
-  StrappedLowUse <- function(WhichLowUse, HighValue = NA){
+  StrappedLowUse <- function(WhichLowUse, HighValue = NA, Grouping){
     test<- 1:samples %>%
       map_df(~{
         
@@ -41,7 +41,7 @@ DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, Prope
           )  %>% mutate(HighVal = Price>HighValue[.x],
                         LADmedian = median(Price, na.rm = T),
                         LADmean = mean(Price, na.rm = T)) %>%
-          group_by(class, classVal, CountryClass) %>%
+          group_by_(.dots = Grouping) %>%
           summarise(Counts = n(),
                     Value = sum(Price),
                     HighVal = sum(HighVal),
@@ -59,10 +59,10 @@ DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, Prope
   
   
   print("Start Bootstrapping Homes distribution")
-  #bootrapps LAD housing stock.
+  #bootstraps LAD housing stock.
   set.seed(seed)
-  dfWardHomesStrap1 <- StrappedLowUse("WardHomes") %>%
-    select(-HighVal, -classVal)
+  dfWardHomesStrap1 <- StrappedLowUse("WardHomes", Grouping = GroupVars) %>%
+    select(-HighVal)
   
   print("Start LUP distribution")
   
[…]

### 2018-08-02 MSOAModelORIGINALLLLLLL.Rmd
Update distrib compare
Trying to make the generation of random bootstraps faster and prevent crashing

---
title: "MSOA affordability model"
author: "Jonathan Bourne"
date: "30 July 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

I realised that If I am not using vacants which has no statistical significance, Then I can change my model and use MSOA. This is becuase deprivation is at LSOA level and area income statistics are at MSOA level and price works down to ward level.

In fact even ward level might be ok if we use MSOA level income stats.

```{r}

test <- DistribCompareBootstrapper(ChelseaLONDATA, 1652, 100, type=NULL, PropertyTypes)

test2 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1652, 100, type=NULL, PropertyTypes, GroupVars = "MSOA11CD")

test3 <- test2 %>%
         group_by(ID, Admin_ward_code) %>%
         summarise(Homes = sum(Homes),
                   HomesValue = sum(HomesValue),
                   LowUse = sum(LowUse),
                   LowUseValue = sum(LowUseValue),
                   HighVal = sum(HighVal)) %>%
         mutate(HomesPrice = HomesValue/Homes,
                LowUsePrice = LowUseValue/LowUse)

# %>%
#   group_by(Admin_ward_code, ID) %>%
#   summarise(Homes = sum(Homes),
#             LowUse = sum(LowUse),
#             HighVal = sum(HighVal)) %>%
#   mutate(ratio = HighVal/LowUse)

test4 <- test3 %>%
  group_by(Admin_ward_code) %>%
  summarise_all(mean, rm.na = T)

test5 <- test2 %>%
  filter(Admin_ward_code == "E05009394")

```

```{r}
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")

#Find what needs to be bootstrapped
BootStrapFiles <- list.files(getwd()) %>% gsub("DATA.rds", "",.)
  newLADsnames <- sub("DATA", "", ls(pattern = "DATA", envir = globalenv())) %>% 
    .[!(. %in% BootStrapFiles)] 
  newLADs <- paste0(newLADsnames, "DATA")

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper2(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD")%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

    #once all Bootratps complete load them all into a list
 BootStrapRES <- list.files(getwd()) %>%
   map(~readRDS(.x))

 #name the list
 names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)

```

To get the modelling variables

HighVal, Mean property Price, Deprivation

```{r}

#Get MSOA deprivation
MSOAdep <- LSOADep %>%
  select(LSOA_CODE, Rank = Rank..where.1.is.most.deprived., Decile = Decile..where.1.is.most.deprived.10..of.LSOAs.) %>%
  left_join(select(EW2, ECODE, MSOA11CD), by= c("LSOA_CODE"= "ECODE")) %>%
  select(-LSOA_CODE) %>%
  group_by(MSOA11CD) %>%
  summarise_all(mean)

BootDeets <- BootStrapRES %>%
  map_df(~ .x %>% 
  mutate(Reference = HighVal>(LowUse-HighVal),
         Reference2 = MedianHomes<MedianLUPs,
         AllProps = Homes+LowUse,
         prices = (HomesValue+LowUseValue)/AllProps,  #this creates the average price for the MSOA as if mean price had been bootstrapped
         LowUsePerc = LowUse/AllProps) %>%
  select(Reference, Reference2, MSOA11CD, prices, ID, LowUsePerc) ) %>%
   left_join(IncomeEst %>%
              select( MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
  mutate(Affordratio = prices/Yearly.income,
         Affordratio2 = Affordratio^2,
         Affordratio3 = Affordratio^3)%>%
  left_join(MSOAdep)

```

```{r}

MeanOut <- BootDeets %>%
  group_by(MSOA11CD) %>%
  summarise(Mean = mean(Reference),
            Reference = Mean>0.5)

#Mean percentage of MSOA that are investment is about 50% on partial bootstrap
test <-BootDeets %>%
  group_by(ID) %>%
  summarise(Total = sum(Reference)/n())
test %>% ggplot(aes(x = Total)) + geom_density()

#create sample
set.seed(1983)
TestResample <- 1:50 %>% map(~  resample_partition(MeanOut, c(test = 0.1, train = 0.9)))

#set formula
OpenFormula <- as.formula(Reference~Affordratio + Decile)

BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[1]]$train), ModForm = OpenFormula)
Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[1]]$test))
Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[1]]$test))

#Beats Null 100% of the time
sum(Accdf$Accuracy>Accdf$AccuracyNull)

median(Accdf$Accuracy-Accdf$AccuracyNull)

#Average accuracy
mean(Accdf$Accuracy)

set.seed(4622)
Modeldf <- BootDeets  %>%
  vfold_cv(., V = 5, repeats = 5) %>%
  mutate(LogisticOpen = splits %>%
  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  ForestOpen = splits %>% 
    map(., ~{rpart(OpenFormula, data=analysis(.x))})
  ) %>%
  mutate(LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"),
         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))

```

```{r}
CoeffsMega <- 1 %>%
  map_df(~{
    print(.x)
    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train), ModForm =  OpenFormula )

    #needs to be mapped again to extract every model not just the first 50!
Out <- 1:length(BootMod) %>% map_df( ~BootMod[[.x]] %>% tidy %>% mutate(ID = .x)
  )

Out  %>%
  mutate(Sample = .x) 
  })

CoeffsMega %>%
  filter(term !="(Intercept)") %>%
  ggplot(aes(x = term, y = estimate, fill = term)) + geom_boxplot()
```

#Terrible Regression
```{r}

BootModReg <- MakeBootModelsReg(BootDeets, as.integer(TestResample[[1]]$train), 
                                ModForm = as.formula(LowUsePerc~Affordratio + Affordratio2+ Affordratio3+ Decile))
PredsdfReg <- MakeBootPredsReg(BootDeets, BootModReg, as.integer(TestResample[[1]]$test))
AccdfReg   <- MakeBootAccuracyReg(PredsdfReg, BootDeets, as.integer(TestResample[[1]]$test))

MakeBootModelsReg <- function(df, trainvect, ModForm = OpenFormula){

  BootMod <- (1:max(df$ID)) %>%
  map(~{

    ModData <- df %>%
      filter(ID ==.x)

  model <- lm(ModForm,
               data = ModData[trainvect,])

  }

  )

}

MakeBootPredsReg <- function(df, BootMod, testvect){

  Predsdf <- 1:length(BootMod) %>%
  map(~{

        ModData <- df %>%
      filter(ID ==.x)

    tibble(v1 =predict(BootMod[[.x]], ModData[testvect,])) 
  }) %>%
  bind_cols() %>% set_names(make.names(1:length(BootMod)))

  return(Predsdf)

}

MakeBootAccuracyReg <- function(Predsdf, df, testvect){

    Accdf <- 1:ncol(Predsdf) %>%
  map_df(~{

    ModData <- df %>%
      filter(ID ==.x)

    Confmat <- postResample( Predsdf[,.x] %>% unlist,
                              ModData$LowUsePerc[testvect])

  Out<- bind_cols(Confmat %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x) %>% as.tibble

  })

}

```

### 2018-08-02 MSOAmodel.Rmd
Update distrib compare
Trying to make the generation of random bootstraps faster and prevent crashing

@@
 
-test2 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )
+test2 <- DistribCompareBootstrapper(BirminghamDATA, 1983, 100, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )
 
@@
 ```{r}
+PropertyTypes <- c("D", "S", "T", "F")
 setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")
@@
       saveRDS(., file = paste0(.x, ".rds"))
+      gc()
       }) 
+  }
+
+    if(length(newLADsnames)>0){
+    for (.x in newLADs) {print(.x)
+      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD" )%>%
+      saveRDS(., file = paste0(.x, ".rds"))
+      gc()
+      } 
   }
@@
   map_df(~.x %>%
-           mutate(Reference = MedianHomes < MedianLUPs,
+           mutate(Reference = HighVal>(LowUse-HighVal),
                   MeanPropPrice = (HomesValue+LowUseValue)/(Homes+LowUse)) %>%
@@
 
+CoeffsMega %>%
+  ggplot(aes(x = term))
+
 ```
+
+Need to find MSOA that contain 100% of the LSOA of a ward
+
+```{r}
+
+  StrappedLowUse <- function(WhichLowUse, Grouping){
+    Tempdf<- unique(dfWard$LSOA11CD) %>%
+          map_df(~{
+            #print(.x)
+            PriceData <- dfPrice %>% 
+              filter(LSOA11CD == .x)
+            #Sometimes an LSOA will have no sales in that year. In these thankfully rare cases the entire LAD is used.
+            if(nrow(PriceData)==0){
+              PriceData<-dfPrice
+            }
+            LowUseCounts <- sum(filter(dfWard, LSOA11CD == .x) %>% select_(WhichLowUse)) #sample rows from LSOA
+
+            SampledData <-sample_n(PriceData, LowUseCounts*samples, replace = TRUE) %>%
+              mutate(ID = rep(1:samples, nrow(.)/samples))
+
+            SampledData
+          }
+          )
+
+    Tempdf %>% 
+      group_by(ID) %>%
+      mutate(LADmedian = median(Price, na.rm = T),
+             LADmean = mean(Price, na.rm = T)) %>%
+      group_by_(.dots = c("ID", Grouping)) %>%
+      summarise(Counts = n(),
+                Value = sum(Price),
+                GeogMedian = median(Price),
+                GeogMean = mean(Price),
+                LADmedian = first(LADmedian),
+                LADmean = first(LADmean)) %>%
+      ungroup
+
+  }
+
+dfWardHomesStrap1 <- StrappedLowUse("LowUse", Grouping = "MSOA11CD")
+
+```

### 2018-08-02 PaperCode.Rmd
Update distrib compare
Trying to make the generation of random bootstraps faster and prevent crashing

@@
 ---
+
+Do the CalcLowUse and ProcessDataMeanPrice functions need to be changed from LSOA to MSOA?
 
@@
 ```{r}
-list.files()
 
@@
 ```{r}
-#ward folder
-setwd(SemiLondon)
-
-wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)
-
-#TowerHamlets
-TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
-  filter(!is.na(DiscClass)) %>%
-  group_by(Ward, DiscClass) %>%
-  summarise(count = n()) %>% ungroup %>%
-  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
-  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
-  slice(c(1:13, 15:17, 14, 18:20)) %>%
-   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
-  SemiDataStructure
-
-HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
-  rename(DiscClass = X__1) %>%
-  select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
-  gather(key = "ward", value = "counts", -DiscClass) %>%
-  spread(key= DiscClass, value = counts, fill = 0) %>%
-  mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
-  bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
-  SemiDataStructure
+# #ward folder
+# setwd(SemiLondon)
+# 
+# 
+# wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)
+
+#These don't work now the LSOA are being used directly
+# 
+# #TowerHamlets
+# TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
+#   filter(!is.na(DiscClass)) %>%
+#   group_by(Ward, DiscClass) %>%
+#   summarise(count = n()) %>% ungroup %>%
+#   spread(., key =DiscClass, value = count, fill = 0 ) %>% 
+#   mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
+#   slice(c(1:13, 15:17, 14, 18:20)) %>%
+#    bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
+#   SemiDataStructure
+# 
+# 
+# HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
+#   rename(DiscClass = X__1) %>%
+#   select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
+#   gather(key = "ward", value = "counts", -DiscClass) %>%
+#   spread(key= DiscClass, value = counts, fill = 0) %>%
+#   mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
+#   bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
+#   SemiDataStructure
 

### 2018-08-02 BOOTSTRAPPEREXP.R

@@ -1,0 +1,114 @@
+DistribCompareBootstrapper2 <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("class", "classVal", "CountryClass")){
+  #df:data frame of processed area/s data
+  #LADCD: The LAD code to fetch the correct price data
+  # Random seed
+  #Number of Bootstrap samples.
+  #type: whether all purchese or only classes A or b are taken, enter a character "A" or "B" or leave NULL for all
+  #PriceCuts: the cut points for the different classes of housing, used only occaisionally has to start with 0 and end with Inf
+  #and in total have 6 elements
+  
+  dfPrice <- df %>%
+    filter(!is.na(Admin_ward_code)) %>%#filter(!is.na(Pop)) %>%#removes any NA rows which cause a crash
+    SubsetPrice(., type, PropertyTypes)
+  
+  dfWard <- df %>% 
+    group_by(Admin_ward_code) %>%
+    summarise_all(funs(first)) %>% 
+    group_by(LAD11CD) %>%
+    mutate(LADCount = n()) %>% ungroup %>%
+    filter(!is.na(Admin_ward_code), LADCount == max(LADCount)) %>% #filter out any stray areas that are classed as a different authority
+    select(-LADCount)  
+  
+  #Function generated within the function to make sure both Homes and LUPs are calculated the same way.
+  StrappedLowUse <- function(WhichLowUse, HighValue = NA, GroupVar= GroupVars){
+    test<- 1:samples %>%
+      map_df(~{
+        
+        Out <- unique(dfWard$Admin_ward_code) %>%
+          map_df(~{
+            #print(.x)
+            PriceData <- dfPrice %>% 
+              filter(Admin_ward_code == .x)
+            #Sometimes a ward will have no sales in that year. In these thankfully rare cases the entire LAD is used.
+            if(nrow(PriceData)==0){
+              PriceData<-dfPrice
+            }
+            LowUseCounts <- sum(filter(dfWard, Admin_ward_code == .x) %>% select_(WhichLowUse)) #sample rows from ward
+            
+            sample_n(PriceData, LowUseCounts, replace = TRUE)
+            
+          }
+          )  %>% mutate(HighVal = Price>HighValue[.x],
+                        LADmedian = median(Price, na.rm = T),
[…]

### 2018-08-02 Functions/CalcLowUse.R

@@ -1,15 +1,17 @@
 CalcLowUse<- function(df){
   #This function calculates all the low use data etc in the processing step.
   #It is a separate function as it allows the selection of what data to include
-  #from the Structuredata function. ALtherantively it can be used to clean up
+  #from the Structuredata function. Alterantively it can be used to clean up
   #LSOA codes that overlap between LAD's due to postcode matching.
   
   df %>%
     left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
-    group_by(Admin_ward_code)  %>%
-    mutate(LowUsePerc = round(LowUse/Homes *100), 
-           WardLowUse = sum(LowUse) ,
-           WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
+    rename(LSOA11CD = LSOA_CODE) %>%
+    group_by(MSOA11CD)  %>%
+    mutate(MSOAHomes = sum(Homes),
+           LowUsePerc = round(LowUse/Homes *100), 
+           MSOALowUse = sum(LowUse) ,
+           MSOALowUsePerc = round(MSOALowUse/sum(Homes)*100)) %>% 
     ungroup %>%  
     ProcessDataMeanPrice(.)
 }      

### 2018-08-02 Functions/ProcessDataMeanPrice.R

@@ -1,9 +1,9 @@
 ProcessDataMeanPrice <- function(df) {
-  df %>% left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
+  df %>% left_join(., MeanWardPrice, by = "LSOA11CD") %>% 
     mutate(ValLow = LowUse*MeanPrice,
-           PercTurnover = counts/WardHomes,
+           PercTurnover = counts/MSOAHomes,
            LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
                              labels =  c("0-10","11-20","21-30", "30+")),
-           WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
+           MSOALowuseClass = cut(MSOALowUsePerc, c(0,10,20, 30, 100), 
                                  labels = c("0-10","11-20","21-30", "30+")) ) 
 }

### 2018-08-02 Functions/SubsetPrice.R

@@ -7,13 +7,13 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, Quantiles = NULL)
   if(is.character(df)){
     Code <- df
   } else{
-    #Som LADS have bits of other LADS mixed in this removes those
+    #Some LADS have bits of other LADS mixed in this removes those
     Code <- names(table(df$LAD11CD))[which.max(table(df$LAD11CD) %>% as.matrix)] 
   }
   
   #filter prices to only relevant rows
   pricesTemp <- prices %>%
-  filter(., grepl(Code, Admin_district_code)) 
+  filter(., grepl(Code, LAD11CD)) 
   
   if(!is.null(type)){
     pricesTemp <- pricesTemp %>%
@@ -33,7 +33,7 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, Quantiles = NULL)
   #The  model used to take multiple councils if there was overlap, but this caused some strange
   #Problems So I removed it. The current version only takes a single LAD
   pricesTemp %>%
-    select(Admin_ward_code, lsoa11cd, Price =X2, X15, PropType = X5, CountryClass, MSOA11CD) %>%
+    select(Admin_ward_code, LSOA11CD, Price =X2, X15, PropType = X5, CountryClass, MSOA11CD) %>%
     mutate(class = cut(Price, Quantiles, 
                        labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
                        right = F) %>% fct_relevel(., "Upper", after = 3),

### 2018-08-02 SubCode/AuxdataLoad.R

@@ -106,37 +106,58 @@ saveRDS(AG, file.path(DataFolder,"shapeframe.rds"))
 #
 setwd(DataFolder)
 
-prices <-read_csv("pp-2016.csv", col_names = FALSE ) %>% 
-  mutate(X4 = gsub(" ", "", X4)) %>%
-  left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)),
-            by = c("X4"="Postcode")) %>%
-  filter(!is.na(lsoa11cd)) %>% 
-  left_join(select(EW2, ECODE, MSOA11CD), by =c("lsoa11cd"="ECODE")) %>% #Add in the MSOA code
-  filter(Country_code == "E92000001") %>%
-  mutate(Prime = X2>1e6, SuperPrime = X2>1e7) #is this line necessary
+#Need to replace the prices file with the new larger prices file
 
 
-Quantiles <-c( 0, quantile(prices$X2)[2:4], Inf)
 
-prices <- prices %>%
-  mutate(CountryClass = cut(X2, Quantiles, 
-                   labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
-                   right = F) %>% fct_relevel(., "Upper", after = 3))
+if(file.exists("prices.rds")){
+  
+  prices <- readRDS("prices.rds")
+} else {
+  #if you don't have enough ram this might crash your computer.
+  prices <- read_csv("pp-complete.csv", col_names = FALSE )
+  
+  prices <- prices %>%
+    filter(year(X3)>2012,year(X3)<2018) %>%
+    mutate(X4 = gsub(" ", "", X4)) %>%
+    left_join(., PstCdLSOA.raw %>% mutate(Postcode = gsub(" ", "", Postcode)),
+              by = c("X4"="Postcode")) %>%
+    filter(!is.na(lsoa11cd)) %>%
+    left_join(select(EW2, ECODE, MSOA11CD, LAD11CD), by =c("lsoa11cd"="ECODE")) %>% #Add in the MSOA code
+    filter(Country_code == "E92000001") %>%
+    select(X2, X5, X3, X15, X16, Admin_ward_code, lsoa11cd, MSOA11CD, LAD11CD) %>%
+    rename(LSOA11CD = lsoa11cd)
+  
+  Quantiles <-c( 0, quantile(prices$X2)[2:4], Inf)
+  
+  prices <- prices %>%
+    mutate(CountryClass = cut(X2, Quantiles, 
[…]

### 2018-08-02 SubCode/Setup.R

@@ -1,7 +1,7 @@
 ##This code is used to setup the project it is common to both the empty homes doc and also the template creation doc.
 
 
-packages <- c("tidyverse", "spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
+packages <- c("tidyverse", "lubridate","spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
               "forcats", "e1071", "htmlwidgets", "stringr", "modelr", "caret", "xtable", "rpart", "broom", "yardstick", "rsample")
 
 #, "mapview"

### 2018-08-09 MSOAmodel.Rmd
Complete re-factor
The code was turning into a complete mess and it wasn't clear what was happening at all and definitely not reproducible. I rewrote everything to simply the code and reduce the complexity of the workspace. I focussed on getting a few key model types and showing how they work and how they don't. The new code is much easier to understand and run.

--- 2018-07-31 MSOAmodel.Rmd
@@
 
+#LAD quartiles are wrong
+
 ```{r}
 
-test <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes )
-test1 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes )
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")
+test <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 501, type = NULL, PropertyTypes, GroupVars = "class"  )
 
-test2 <- DistribCompareBootstrapper2(ChelseaLONDATA, 1983, 100, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )
+ChelTest1 <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 501, type = NULL, PropertyTypes, GroupVars = "MSOA11CD" )
+
+test2 <- DistribCompareBootstrapper(ChelseaLONDATA, 1983, 501, type = NULL, PropertyTypes, GroupVars = c("MSOA11CD", "class"))
+
+MSOAList <- unique(test2$MSOA11CD) %>%
+  map(~{
+test2 %>%
+  filter(MSOA11CD == .x)
+})
+
+test3 <- MSOAList[[21]] %>%
+  CleanForPlotClassDiff
+
+MSOAList[[21]] %>%
+CleanForPlotClassDiff()  %>%
+PlotClassDiff(., "Kensington and Chelsea by MSOA")
+
+test %>%
+  mutate(LowUse = Homes) %>%
+  CleanForPlotClassDiff()  %>%
+  PlotClassDiff(., "Kensington and Chelsea full borough")
+
+test %>%
+#  mutate(LowUse = Homes) %>%
+  CleanForPlotClassDiff2()  %>%
+  PlotClassDiff(., "Kensington and Chelsea full borough")
+
+CleanForPlotClassDiff2 <- function(df){ #relative to the homes distrib
+  df %>% 
+  group_by(ID, class) %>%
+  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
+  group_by(ID)%>%
+  mutate(RatioExvsAct = LowUse/sum(LowUse),
+         HomesRatio = Homes/sum(Homes),
+         RatioExvsAct = (RatioExvsAct/HomesRatio)-1)
+}
 
@@
 ```{r}
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities2")
+
+PropertyTypes <- c("D", "S", "T", "F")
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")
 
@@
 
+  test <- ls(pattern = "DATA") %>% map_df(~
+ data.frame(LAD = .x, LSOA = get(.x) %>% nrow(),Homes = sum(get(.x)$Homes, na.rm = T))) %>%
+    arrange(Homes)
+
+  newLADs <- newLADs[match(test$LAD, newLADs)] %>% .[!is.na(.)]
+
   #only bootstrap if there is something to add.
@@
     newLADs  %>% walk(~{print(.x)
-      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes, GroupVars = "MSOA11CD" )%>%
+      DistribCompareBootstrapper(get(.x), 1652, 501, type=NULL, PropertyTypes, GroupVars = "MSOA11CD", Limit =1.3e5  )%>%
       saveRDS(., file = paste0(.x, ".rds"))
+      gc()
       }) 
@@
  names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)
+
 ```
-
-#Make modelling dataframe
-
-The variables are
-
-mean deprivation decile
-Affordability
 
@@
 
-MSOAdep <- LSOADep %>%
-  select(LSOA_CODE, Rank = Rank..where.1.is.most.deprived., Decile = Decile..where.1.is.most.deprived.10..of.LSOAs.) %>%
-  left_join(select(EW2, MSOA11CD, ECODE), by = c("LSOA_CODE"="ECODE")) %>%
-  select(-LSOA_CODE) %>%
+library(Rtsne)
+
+# dfmat <- BootDeetsMean %>%
+#   select(AffordDiff, Decile, AffordRatio, AffordRatio2, DecileDiff) %>%
+#   as.matrix()
+
+dfmat <- ModelMSOAdf %>%
+  select( Tourism, AffordRatio, AffordRatio2) %>%
+  as.matrix()
+
+set.seed(12358)
+TsnecorOut1 <-dfmat  %>%
+  Rtsne(verbose = TRUE, eta = 1, max_iter = 5000, perplexity = 50, check_duplicates = FALSE)
+
+# tsne_corplot <- data.frame(x1 = TsnecorOut1$Y[,1],
+#                         y1 = TsnecorOut1$Y[,2]) %>%
+#   bind_cols(BootDeetsMean) %>%
+#   mutate(MedianCheck = MSOAHomesMedian<MSOALowUseMedian)
+
+tsne_corplot <- data.frame(x1 = TsnecorOut1$Y[,1],
+                        y1 = TsnecorOut1$Y[,2]) %>%
+  bind_cols(ModelMSOAdf)
+
+tsne_corplot %>%
+    ggplot() +
+  geom_point(aes(x=x1, y=y1, color= TourDepCat==1|TourDepCat==2))
+
+BootDeetsMean %>%
+  ggplot(aes(x = LowUseConc, y = AffordDiff, colour = Reference)) + geom_point()
+
+BootDeetsMean %>%
+  filter(sales <1) %>%
+  ggplot(aes(x = sales, y = LowUse, colour = Reference)) + geom_point()
+
+```
+
+#Sample quantiles
+
+```{r}
+PriceCounts <-prices %>%
+  filter(X5 %in% c("D", "S", "T", "F")) %>%
+  group_by(LSOA11CD) %>%
+  summarise(counts = n()) %>%
+  arrange(counts)
+
+PriceCounts<- EW2 %>%
+  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
+  left_join(.,PriceCounts, by = "LSOA11CD") %>%
+  mutate(counts = ifelse(is.na(counts), 0, counts),
+         Homes2 = Homes/10) %>%
+  filter(counts!=0)
+
+#Create a list of vectors by LSOA
+setwd(basewd)
+ LSOAPriceList <- 1:nrow(PriceCounts) %>% map(~{
+   print(.x)
+    prices %>%
+      filter(LSOA11CD==PriceCounts$LSOA11CD[.x], 
+             X5 %in% c("D", "S", "T", "F")) %>%
+      pull(X2)
+ })
+
+ names(LSOAPriceList) <- PriceCounts$LSOA11CD
+saveRDS(LSOAPriceList, "LSOAPriceList2.rds")
+
+LSOAPriceList <- readRDS("LSOAPriceList2.rds")
+
+```
+
+```{r}
+
+StratifiedBoot <- function(dataList, LSOAcode, SamplesVect, samples = 1000){
+  #datadf
+ 1: samples %>% map_df(~{
+   print(.x)
+  SubData <- 1:length(LSOAcode) %>% map(~{
+    #print(.x)
+    dataList[[LSOAcode[.x]]] %>%
+      sample(., SamplesVect[.x], replace = TRUE)
+
+    }) %>% unlist
+
+  SubData%>%
+       quantile(.) %>% t %>% as.data.frame %>% setNames(names(.) %>% make.names) %>%
+      mutate(mean = mean(SubData),
+             ID = .x)
+ }) 
+}
+
+#Subset list to only the LADs used in analyis
+LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
+PriceCounts2 <- PriceCounts %>%
+  filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))
+
+AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)
+
+test <- LSOAPriceList %>% map_int(length(.x))
+
+```
+
+#MSOA Quartiles
+
+I'm not sure this is useful
+
+```{r}
+#Create a list of vectors where each element of the list is an MSOA and the vector elements are its LSOA
+ LSOAinMSOA <- unique(PriceCounts$MSOA11CD) %>% map(~{
+   print(.x)
+    PriceCounts %>%
+      filter(MSOA11CD==.x) %>%
+      pull(LSOA11CD)
+ })
+ #name the elements of the list
+ names(LSOAinMSOA) <- unique(PriceCounts$MSOA11CD)
+
+ #Create a bootstrap for each of the MSOA
+
+ MSOABootQuartiles <- unique(PriceCounts$MSOA11CD) %>% map_df(~{
+   print(.x)
+   PriceCounts2 <- PriceCounts %>%
+     filter(MSOA11CD == .x)
+
+   LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% PriceCounts2$LSOA11CD]
+
+   StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 100) %>%
+     mutate(MSOA11CD=.x)
+
+ })
+
+ saveRDS(MSOABootQuartiles, "MSOABootQuartiles.rds")
+
+ MSOABootQuartiles2 <- MSOABootQuartiles %>%
+   select(-X0.,-X100.) %>%
    group_by(MSOA11CD) %>%
-  summarise_all(mean)
+   summarise_all(funs(mean, sd)) %>%
+   mutate(X25Perc = X25._sd/X25._mean,
+          X50Perc = X50._sd/X50._mean,
+          X75Perc = X75._sd/X75._mean)  %>%
+   left_join(., EW2%>%
+               select(MSOA11CD, LAD11CD, LAD11NM) %>% distinct()) %>%
+   left_join(., IncomeEst) %>%
+   select(MedianPrice=X50._mean, Yearly.income, MSOA11CD, LAD11CD, LAD11NM) %>%
+   mutate(AffordRatio = MedianPrice/Yearly.income,
+          AffordRank = percent_rank(AffordRatio))
+```
 
-BootDeets <- BootStrapRES %>% 
-  map_df(~.x %>%
-           mutate(Reference = MedianHomes < MedianLUPs,
-                  MeanPropPrice = (HomesValue+LowUseValue)/(Homes+LowUse)) %>%
-           select(MSOA11CD, MeanPropPrice, Reference, ID)) %>%
-  left_join(select(IncomeEst, MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
-  left_join(MSOAdep, by = "MSOA11CD") %>%
-  mutate(AffordRatio  = MeanPropPrice/Yearly.income,
-         AffordRatio2 = AffordRatio^2,
-         AffordRatio3 = AffordRatio^3)
+#Local value
 
-rm(MSOAdep)
+Here I create a graph of the MSOA. 
+I calculate the avereage distance by LAD.
+I then use that distance to find all the MSOA within that jump distance.
+I then calculate the mean and quartiles of the local area for each MSOA
+From there I can calculate the local area affordability and thus the relative local area affordability
 
-#Why do some have 2000?
-test <- BootDeets %>%
-  group_by(MSOA11CD) %>%
-  summarise(Majority = sum(Reference, na.rm = T)/1000,
-            Total = n())
+```{r}
 
-BootDeetsMean <- BootDeets %>%
-  select(MSOA11CD, Reference, Decile, AffordRatio) %>%
-  group_by(MSOA11CD) %>%
-  summarise_all(mean) %>%
-  mutate(Reference = Reference>0.5)
+ MSOAAdjacency <- readShapeSpatial(file.path("/home/jonno/Dropbox/SSE/Empty Homes/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
+                                             "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp"))
 
-set.seed(1983)
-TestResample <- 1:50 %>% map(~  resample_partition(BootDeetsMean, c(test = 0.1, train = 0.9)))
+ test <- poly2nb(MSOAAdjacency)
 
-OpenFormula <- as.formula(Reference~ AffordRatio+ Decile)
+ MSOAAdjMat = nb2mat(test, style="B",zero.policy=T)
 
-BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[1]]$train))
-Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[1]]$test))
-Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[1]]$test))
+#Add MSOA codes so that they are added as the vertex names
+colnames(MSOAAdjMat) <- MSOAAdjacency$msoa11cd
 
-sum(Accdf$Accuracy>Accdf$AccuracyNull)
+MSOAgraph <- graph.adjacency(MSOAAdjMat, mode = "undirected")
 
-mean(Accdf$Accuracy)
+#Add in Lad
 
-CoeffsMega <- 1 %>%
-  map_df(~{
+MSOAgraph <- set_vertex_attr(MSOAgraph, 
+                name = "LAD11CD", 
+                value = MSOAtoLAD$LAD11CD[match(get.vertex.attribute(MSOAgraph, "name"),
+                                          MSOAtoLAD$MSOA11CD)]
+                )
+
+#Subset by LAD into a list of graphs
+
+Subgraph <- function(g, KeepNodes){
+
+  VertexNames <-get.vertex.attribute(g, "name")
+  VertexNames<- VertexNames[!(VertexNames %in% KeepNodes)]
+
+g2 <- delete_vertices(g, VertexNames)
+
+g2
+}
+
+AllLADsGraph <- unique(MSOAtoLAD$LAD11CD) %>% map(~{
+  KeepNodes <-MSOAtoLAD %>%
+  filter(LAD11CD ==.x)
+KeepNodes2 <- KeepNodes$MSOA11CD
+
+  Subgraph(MSOAgraph, KeepNodes2)
+})
+
+#name the elements by the LAD represented
+names(AllLADsGraph) <- unique(MSOAtoLAD$LAD11CD)
+
+#calculate mean distance and diameter of each lad
+MSOAconnections <- AllLADsGraph %>% map_df(~{
+
+  tibble(distance = mean_distance(.x), diameter = diameter(.x), MSOA = vcount(.x))
+
+}) %>%
+  mutate(LAD11CD = names(AllLADsGraph)) %>%
+  filter(MSOA !=1) #removes city of london which only has a single MSOA and so can't be included in the calc
+
+MSOAconnections %>%
+  ggplot(aes(x=diameter )) + geom_density()
+
+#Using mean distance is best
+summary(MSOAconnections$distance)
+summary(MSOAconnections$diameter)
+
+# find names of local MSOA using an x jump distance
+EgoSize <- tibble(ego_size = ego_size(MSOAgraph, 2), MSOA11CD = get.vertex.attribute(MSOAgraph, "name")) %>%
+  left_join(MSOAtoLAD)
+##Ego size of jump two has a mean almost identical to the mean number of MSOA in a LAD. However the Ego size is less skewed.
+mean(EgoSize$ego_size)
+
+MSOAtoLAD %>%
+  group_by(LAD11CD) %>%
+  summarise(counts = n(),
+            LAD11NM = first(LAD11NM)) %>%
+  pull(counts) %>% mean
+
+test <-  tibble(MSOA11CD = ego(MSOAgraph, 1, nodes = "E02000001")[[1]] %>% names) %>%
+  left_join(MSOAtoLAD)
+
+##names of the MSOA in each area.
+MSOAEgoList <- ego(MSOAgraph, 2) %>%map(~names(.x))
+names(MSOAEgoList) <- get.vertex.attribute(MSOAgraph, "name")
+
+```
+
+```{r}
+#Create a list of vectors where each element of the list is an MSOA and the vector elements are its LSOA
+ LSOAinMSOAEgo <- MSOAEgoList %>% map(~{
+   #print(.x)
+    PriceCounts %>%
+      filter(MSOA11CD %in% .x) %>%
+      pull(LSOA11CD)
+ })
+
+ ##name the elements of the list
+ names(LSOAinMSOAEgo) <- names(MSOAEgoList)
+
+ ##Create a bootstrap for the ego of each MSOA
+ NeighbourhoodQuartiles <- names(MSOAEgoList) %>% map_df(~{
+
    print(.x)
-    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train), ModForm =  OpenFormula)
+   target <- MSOAEgoList[[.x]]
+   PriceCounts2 <- PriceCounts %>%
+     filter(MSOA11CD %in% target)
 
-    #needs to be mapped again to extract every model not just the first 50!
-    Out <- 1:length(BootMod) %>% map_df(~
-                          BootMod[[.x]] %>% tidy %>% mutate(ID = .x)               
-                                        )%>%
-      mutate(Sample = .x)
+   LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% PriceCounts2$LSOA11CD]
+
+   Out <-StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 10) %>%
+     mutate(MSOA11CD=.x)
+
+   Out
+
  })
@@
 ```
+
+Do westminster and lambeth fall into each others local area?
+need to check and make sure they do!
+```{r}
+#Calculate mean local income
+LocalIncome <- names(MSOAEgoList) %>% map(~{
+  print(.x)
+#.x <- "E02000001"
+Group <-MSOAEgoList[[.x]]
+
+Incomest2 <- IncomeEst %>%
+  left_join(select(MSOAtoLAD, MSOA11CD, Homes),  by="MSOA11CD")
+
+Out <- Incomest2 %>%
+  filter(MSOA11CD %in% .x) %>%
+  summarise(LocalIncome =sum(Yearly.income* Homes)/sum(Homes)) %>% pull()
+
+Out
+}) %>% unlist %>%
+  tibble(MSOA11CD = names(MSOAEgoList), LocalIncome = .)
+
+LocalAfford <-NeighbourhoodQuartiles %>%
+  select(-ID,-X0., -X100.) %>%
+    group_by(MSOA11CD) %>%
+  summarise_all(funs(mean, sd, min, max)) %>%
+  mutate(perc = X50._sd/X50._mean) %>%
+  left_join(LocalIncome, by = "MSOA11CD") %>%
+  mutate(LocalAfford = X50._mean/LocalIncome) %>%
+  select(MSOA11CD, MedianLocalHomesPrice = X50._mean, LocalAfford)
+
+```
+
+```{r}
+LupPerc <- ls(pattern= "DATA") %>% map_df(~{
+  get(.x) %>% select(MSOA11CD, LowUse, Homes)
+
+}) %>%
+  group_by(MSOA11CD) %>%
+  summarise_all(sum) %>%
+  mutate(LowUsePerc = LowUse/(LowUse+Homes),
+         Q1 = LowUsePerc>0.033,
+         Q2 = LowUsePerc>0.02,
+         Top90 = LowUsePerc>0.058)
+
+#Top quartile of LUPS
+quantile(LupPerc$LowUsePerc)
+quantile(LupPerc$LowUsePerc, prob = seq(0, 1, length = 11))
+
+MSOABootQuartiles2 <- MSOABootQuartiles %>%
+   select(-X0.,-X100.) %>%
+   group_by(MSOA11CD) %>%
+   summarise_all(funs(mean, sd)) %>%
+   mutate(X25Perc = X25._sd/X25._mean,
+          X50Perc = X50._sd/X50._mean,
+          X75Perc = X75._sd/X75._mean)  %>%
+   left_join(., EW2%>%
+               select(MSOA11CD, LAD11CD, LAD11NM) %>% distinct()) %>%
+   left_join(., IncomeEst) %>%
+   select(MedianPrice=X50._mean, Yearly.income, MSOA11CD, LAD11CD, LAD11NM)  %>%
+  left_join(LocalAfford, by = "MSOA11CD") %>%
+  left_join(LupPerc, by = "MSOA11CD")%>%
+  filter(!is.na(LowUse)) %>%
+   mutate(AffordRatio = MedianPrice/Yearly.income,
+          AffordLocalRatio = AffordRatio/LocalAfford,
+          AffordRank = percent_rank(AffordRatio),
+          AffordLocalRank = percent_rank(AffordLocalRatio),
+          LowUseRank = percent_rank(LowUse)>0.75)
+
+MSOABootQuartiles2 %>%
+  ggplot(aes(x= AffordRatio , y = AffordLocalRatio, colour = LowUseRank)) + geom_point()
+
+```
+
+#Quadrant
+
+```{r}
+  BootDeets <- BootStrapRES %>% map_df(~.x %>% group_by(ID) %>%
+                                    summarise(MedianHomes = first(MedianHomes),
+                                              MeanHomes = first(MeanHomes),
+                                              MedianLUPs = first(MedianLUPs),
+                                              MeanLUPs = first(MeanLUPs),
+                                              LAD11CD= first(LAD11CD),
+                                              HighVal = sum(HighVal),
+                                              Homes = sum(Homes),
+                                              LowUse = sum(LowUse)) %>%
+                                    group_by(LAD11CD) %>%
+                                    summarise_all(., mean, na.rm = TRUE) %>%
+                                      select(-ID)
+  )
+
+BootDeets2 <- BootDeets %>%
+  mutate(MedianPercDiff = (MedianLUPs-MedianHomes)/MedianHomes,
+         PercLowUse = LowUse/Homes,
+         RankLowUse = percent_rank(PercLowUse),
+         RankMedianDiff = percent_rank(MedianPercDiff),
+         Catagory = case_when( 
+           RankLowUse>=0.5 & RankMedianDiff>=0.5 ~ 1, #High low use and High price difference
+           RankLowUse>=0.5 & RankMedianDiff<0.5 ~ 2, #High low Use and Low rank price difference
+           RankLowUse<0.5 & RankMedianDiff>=0.5 ~3, # Low low use and high price difference
+           TRUE ~ 4 #Low low use low price difference
+         ) %>% as.factor)%>%
+  left_join(EW2 %>%
+  group_by(LAD11CD, LAD11NM) %>%
+  summarise(TotMSOA = n(),
+         Homes = sum(Homes)) %>%
+  arrange(-TotMSOA) %>%
+  summarise(TotMSOA = first(TotMSOA),
+            LAD11NM = first(LAD11NM)), by = "LAD11CD")
+
+BootDeets2 %>%
+  ggplot(aes(x= RankLowUse, y = RankMedianDiff, colour = Catagory)) + geom_point()
+
+test <- MSOABootQuartiles2 %>%
+  left_join(select(BootDeets2, LAD11CD, Catagory), by = "LAD11CD")
+
+ %>%
+  ggplot(aes(x= AffordRank , y = AffordLocalRank, colour = Catagory)) + geom_point()
+
+```

### 2018-08-09 OldCode.Rmd
Complete re-factor
The code was turning into a complete mess and it wasn't clear what was happening at all and definitely not reproducible. I rewrote everything to simply the code and reduce the complexity of the workspace. I focussed on getting a few key model types and showing how they work and how they don't. The new code is much easier to understand and run.

--- 2018-08-02 PaperCode.Rmd
@@
   They are more concentrated than homes in general
+  Spatial Auto-Correlation?
 Are LUPs more or less expensive?
@@
 ```{r}
-# 
-# setwd(file.path(RegionsComp, "Region Wales"))
-# list.files()
-# 
-# #Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
-# 
-# CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
-#   StructureData(lowuse =c(8:13,15))
-# 
-# MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
-#   StructureData(lowuse = c(4:8))
-# 
-# 
-# #includes the zero class which is descibeed as 
-# #ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
-#   CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
-#     StructureData()
-# 
-# #Strangely low numbers checking
-# # PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
-# #   StructureData(lowuse = c(3,5:6))
-# 
-# #It seems Conwy really is this short on the discounts  
-# ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
-#   rename(Postcode = geo_postcode) %>%
-#   mutate(Postcode = sub(" ", "", Postcode)) %>%
-#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
-#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
-#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
-#   StructureData(lowuse = c(2,4))
-# 
-# DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
-#     StructureData(c(8:9,11,13))
-# 
-# WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
-#     StructureData(2:5)
-# 
-# #Pembrokeshire didn't send all the data
-# PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
-#     StructureData(3)
-# 
-# FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
-#     StructureData()
+
+setwd(file.path(RegionsComp, "Region Wales"))
+list.files()
+
+#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
+
+CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
+  StructureData(lowuse =c(8:13,15))
+
+MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
+  StructureData(lowuse = c(4:8))
+
+#includes the zero class which is descibeed as
+#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
+  CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
+    StructureData()
+
+#Strangely low numbers checking
+# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
+#   StructureData(lowuse = c(3,5:6))
+
+#It seems Conwy really is this short on the discounts
+ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
+  rename(Postcode = geo_postcode) %>%
+  mutate(Postcode = sub(" ", "", Postcode)) %>%
+  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
+  StructureData(lowuse = c(2,4))
+
+DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
+    StructureData(c(8:9,11,13))
+
+WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
+    StructureData(2:5)
+
+#Pembrokeshire didn't send all the data
+PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
+    StructureData(3)
+
+FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
+    StructureData()
 
@@
 
+#Scrub the names
+
+Remove LSOA that belong to another LAD
+
+```{r}
+
+for(i in ls(pattern = "DATA")){
+
+  Temp <-get(i) %>% 
+    group_by(LSOA11CD) %>%  #Remove double LSOA that may have sneaked in
+    summarise_all(funs(first)) %>% 
+    group_by(LAD11CD) %>% #Remove LAD data that is not from this lad. Occaisonly a few lsoa from other LADs get in and cause problems
+    mutate(LADCount = n()) %>% ungroup %>%
+    filter(!is.na(Admin_ward_code), LADCount == max(LADCount)) %>% #filter out any stray areas that are classed as a different authority
+    select(-LADCount)
+
+  assign(i, Temp)
+
+  }
+
+```
+
 General Stats
@@
 unafford <- ls(pattern = "DATA") %>%
-  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
+  map_df(~get(.x) %>% select(LowUse:MSOALowuseClass)) %>%
   group_by(MSOA11CD) %>% # ward code is used for consistency
@@
   left_join(IncomeEst, by = "MSOA11CD") %>%
-  mutate(decile = ntile(ratio, 20))
+  mutate(decile = ntile(ratio, 50))
 
@@
 
+#Is n
 unaffordLAD <- unafford %>%
@@
   group_by(LAD11CD) %>%
-  mutate(TotInc = Yearly.income*Pop) %>%
+  mutate(TotInc = Yearly.income*Homes) %>%
   summarise(TotInc = sum(TotInc),
-            Pop = sum(Pop)) %>%
-  mutate(meanInc = TotInc/Pop)
+            Homes = sum(Homes)) %>%
+  mutate(meanInc = TotInc/Homes)
 
@@
   map_df(~get(.x)) %>%
-   group_by(LSOA_CODE) %>%
+   group_by(LSOA11CD) %>%
    summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
@@
 
-MakeLeaflet(ConwyDATA)
-
-```
+MakeLeaflet(WestminsterLONDATA)
+
+#MSOA version
+
+NorthDevonDATA %>%
+ # left_join(select(BootDeetsMean, MSOA11CD, AffordRatio)) %>%
+ # mutate(LowUsePerc = AffordRatio/mean(AffordRatio)) %>% 
+  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
+  filter(LAD11NM =="Kensington and Chelsea") %>% 
+  MakeLeaflet()
+
+  MakeLeaflet(NorthDevonDATA)
+
+```

### 2018-08-09 PaperCode.Rmd
Complete re-factor
The code was turning into a complete mess and it wasn't clear what was happening at all and definitely not reproducible. I rewrote everything to simply the code and reduce the complexity of the workspace. I focussed on getting a few key model types and showing how they work and how they don't. The new code is much easier to understand and run.

--- 2018-07-31 PaperCode.Rmd
@@
 author: "Jonathan Bourne"
-date: "5 July 2017"
+date: "9 August 2018"
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
 
-Are LUPS concentrated in specific areas?
-  They are more concentrated than homes in general
-Are LUPs more or less expensive?
-  They tend to be concentrated in more expensive areas
-Are High value LUP LADS predictable?
-   They are predictable using number of vacants deprivation and price
-What is the relationship between LUPs and affordability?
-   A bath Tub curve
-What would the revenue from an empty homes tax be in the current situation?
-  A lot
-
-What do I conclude?
-  That there is a clear relationship between LUPs and price/unnafordability with the theorized curve being observed.
-  That areas with high prices tend to have more LUPs
-  That these areas may not have the space to build new property
-That building property in areas of high value LUPs means more LUPs as buyers invest in property, thus negating the purpose of the buidling.
-
-new article and paper on airbnb effecr
-https://www.citylab.com/equity/2018/03/what-airbnb-did-to-new-york-city/552749/?utm_source=atlfb
-
-Islington should be removed and put back in when they send the correct data, it is giving a false negative
-
-#this uses rank for distance from LAD I think it should be dist check this
-
-Intellectual property rights and
-disclosures under the Freedom of
-Information Act
-
-16. It may not be apparent to recipients that the information is
-protected by copyright. Therefore when a public authority
-wishes to protect its own copyright, or the copyright is owned
-by a third party, it should advise the applicant that the
-information remains copyright protected.
-
-Please can you provide excel the file sent to Jonathan Bourne on xxx
-
-The reference number for this case is xxx.
-
-Yours faithfully,
-
-Jonathan Bourne
-
-#ico complaint ref
-fs-506-897-47
-
-#OGL licence claim
-
-All data used in this paper is covered by the Open Government Licence.
-
-The Data meets all 4 criteria described in section 56 of "Datasets (sections 11, 19 & 45)" FOI guidance document.
-These criteria are that the data is held by the authority, The data is part of a relveant copyright work (The data is held in a databse), the authority holds the copyright to the data (The information in the database is owned by the local council).
-As local authorities are public sector bodies (shown in the public sector classification guide) and that council tax is a core task, normally the data would be covered by the RPSI.
-However, following section 5 of the Re use of public sector infrmation regulations 2015.
-
-"5.—(1) These Regulations do not apply to a document where—
-
-(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review"
-
-As the document the councils needed to complete is custom made and not part of the public task, the RPSI does not cover the resultant work and licencing reverts to the FOIA. 
-The FOIA states that a specific licence must be given for all datasets released under the act.
-As no charge has been levied against the use of the data then the default Open government licence is applied following section 69 of the "Datasets (sections 11, 19 & 45)" FOI guidance document.
-
-#Setup
-
-```{r setup}
-setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
+```{r}
+SubCode <- "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode"
+setwd(SubCode)
 source("Setup.R")
@@
 source(file.path(CommonCode, "AuxdataLoad.R"))
+```
+
+#Process all areas
+
+This chunk processes all the areas and combines into a single dataframe
+It also cleans all postcodes that are in other LADs out... should it just combine them into the other LADs LSOA?
+```{r}
+#creates a data frame called DATAdf
+source(file.path(SubCode, "LOADandProcessLADData.R"))
 
@@
 
-#Cumbria
+#MSOA to LAD
 ```{r}
-setwd(file.path(RegionsComp, "Region North West"))
-
-BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
-  StructureData(.,lowuse = c(2:6,8))
-
-SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
-    StructureData(., lowuse=2:9)
-
-#only inlcudes postcodes so the mergeing needs to be done manually
-CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
-  mutate(Postcode = sub(" ", "", Postcode)) %>%
-  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
-  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
-  StructureData()
-
-EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
-  StructureData(.,lowuse = c(2:6,8))
-
-CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
-  StructureData(.)
-
-AllerdaleCUMBRIADATA <- read_excel("F17.132_Copy of Allerdale discounts LSOA_170815.xlsx"  , sheet=1)[1:4] %>%  
-  StructureData(c(4:10))
-
+MSOAtoLAD <- EW2 %>%
+  group_by(MSOA11CD, LAD11CD, LAD11NM) %>%
+  summarise(TotMSOA = n(),
+         Homes = sum(Homes),
+         Region = first(Region)) %>%
+  arrange(-TotMSOA) %>%
+  group_by(MSOA11CD) %>%
+  mutate(counts = n()) %>%
+  summarise(LAD11CD = first(LAD11CD),
+            TotMSOA = first(TotMSOA),
+            counts = first(counts),
+            LAD11NM = first(LAD11NM),
+            Homes = first(Homes),
+            Region = first(Region))
 ```
 
-#Manchester
+#Get Population Statistics
+
+This chunk calculates how much data cover I have using several metrics
 
 ```{r}
-list.files()
-
-OldhamMANCDATA <- read_excel("FOI 10635 OldhamDiscounts LSOA.xlsx", sheet = 1 )[c(1,4:6)] %>%  
-  StructureData(., c(5:6,8:11))
-
-ManchesterMANCDATA <- read_excel("ManchesterDiscountsLSOA.xlsx", sheet = 1 )[1:4] %>%  
-  StructureData(. )
-
-RochdaleMANCDATA <- read_excel("Rochdale Both.xlsx" , sheet = 1 )[1:4] %>%  
-  StructureData(., c(5,6,14,15,20:22))
-
-TamesideMANCDATA <- read_excel("Tameside FOI 6257A2.xlsx", sheet = 1 )[1:4] %>%  
-  StructureData(. )
-
-TraffordMANCDATA <- read_excel("Trafford Exemption and Levy.xlsx" , sheet = 1 )[1:4] %>%
-  filter(Exemption_type =="LEVY") %>% 
-  bind_rows(.,read_excel("TraffordDiscountsLSOA.XLSX", sheet = 1 )[1:4] %>% rename(Exemption_type = Class)) %>%
-  StructureData()
-
-WiganMANCDATA <- read_excel("Wigan 5528 DISCOUNTS.xlsx", sheet = 1 )[1:4] %>%  
-  StructureData(., lowuse = c(2:3, 5:9) )
-
-#hide plot
-#ls(pattern = "MANC") %>% map_df(~eval(parse(text=.x))) %>% PlotMap(., AG)
-
-```
-
-#West Midlands Brum
-```{r}
-
-setwd(file.path(RegionsComp, "Region West Midlands"))
-
-SandWellDATA <- read_excel("FOI - SandwellDiscountsLSOA - FS57000079 Disc.xlsx" )[1:4] %>%  
-  StructureData(2:6)
-
-WolverhamptonDATA <- read_excel("WolverhamptonDiscountsLSOA.XLSX"  )[1:4] %>%  
-  StructureData(c(2:5,7))
-
-WalsallDATA <- read_excel("WalsallDiscountsLSOA.XLSX" )[1:4] %>%  
-  StructureData(c(4:5,7:8))
-
-BirminghamDATA <-  read_excel("Birmingham CT EMPTIES.xlsx" )%>%
-mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
- left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
-  rename(Exemption.type=`Current Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
-  StructureData(c(2,4:9))
-
-DudleyDATA <- read_excel("Completed DudleyDiscountsLSOA.xlsx"  )[1:4] %>%  
-  StructureData()
-
-```
-
-#SouthWest
-
-##Cornwall
-
-```{r}
-
-setwd(file.path(RegionsComp, "Region South West"))
-
-CornwallDATA <- read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
-  StructureData(lowuse = c(2,23:28))
-```
-
-##Devon
-
-```{r}
-
-NorthDevonDATA <- read_excel("North DevonDiscountsLSOA.XLSX", sheet=1)[1:4] %>%
-  StructureData
-
-PlymouthDATA <- read_excel("PlymouthDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
-  StructureData(lowuse = 4:8)
-
-TorbayDATA <- read_excel("Torbay_discounts 1718551.xlsx"  , sheet=1)[1:4] %>%
-  StructureData()
-
-MidDevonDATA <- read_excel("MidDevon FOI04942Information 3.xlsx" , sheet=1)[1:4] %>%
-  StructureData(c(7,10:11,20:22,26,28))
-
-TorridgeDATA <- read_excel("FOI_TorridgeDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
-  StructureData(c(4:5,7:10,13))
-
-```
-
-##Somerset
-
-```{r}
-NorthSomsertDATA <- read_excel("1501796 North SomersetDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
-  StructureData(lowuse= 2:6)
-
-MendipDATA <- read_excel("Mendip 356 20170706 Response.xlsx" , sheet=1)[1:4] %>%
-  StructureData(lowuse= c(37:39,52:54,65:66,69))
-
-#Bristol appears to have not included second homes
-#BristolDATA <- read_excel("Bristol%2c City ofDiscountsLSOA_as at 110817.xlsx")[c(1:4)] %>%
-#  StructureData()
-
-```
-
-##Dorset
-
-```{r}
-BournemouthDATA <- read_excel("BournemouthDiscountsLSOA_R.xlsx" )[1:4] %>%
-  StructureData(c(6,8,9:13))
-
-PooleDATA <- read_excel("Copy of FOI - 265 - Bourne - PooleDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
-  StructureData(lowuse = c(5,11:14,18))
-
-ChristchurchDATA <- read_excel("Christchurch FOI17 - 0312 - Bourne - Ctax Discounts and Exemptions.xls",
-                               sheet=1)[1:4] %>%
-  StructureData(lowuse = c(6,12:17,20))
-
-WeymouthDATA <-  read_excel("63687 Weymouth and PortlandDiscountsLSOA - 010817.xlsx"    ,
-                               sheet=1)[1:4] %>%
-  StructureData()
-
-WestDorsetDATA <-  read_excel("47019 West DorsetDiscountsLSOA - 010817.xlsx"     ,
-                               sheet=1)[1:4] %>%
-  StructureData()
-
-PurbeckDATA <-  read_excel("PurbeckDiscountsLSOA - 010817.xlsx"      ,
-                               sheet=1)[1:4] %>%
-  StructureData()
-
-```
-
-##Wiltshire
-
-```{r}
-#Wiltshire have not included everything
-WiltshireDATA <- read_excel("Wiltshire ENQ07536 - Council tax discounts 2.xlsx",
-                               sheet=1)[1:4] %>%
-  StructureData(lowuse = 3:8)
-
-SwindonDATA <- read_excel("Swindon - 7th July 2017 - Part 2 (Discounts).xlsx" ,
-                               sheet=1)[1:4] %>%
-  StructureData(2:6)
-```
-
-#East of England
-
-##Suffolk
-
-```{r}
-setwd(file.path(RegionsComp, "Region East of England"))
-list.files()
-
-#Serparete in to the two LADS
-# CoastWaveDATA <- bind_rows(read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] , read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4]) %>% setNames(make.names(names(.))) %>%
-#   mutate(Exemption.type = Exemption.type %>% trimws %>%
-#            make.names %>% 
-#            gsub("\\.{2,}" , ".", .))  %>%
-#   StructureData(., lowuse = c(5,6,13,14,16:18))
-
-CoastSUFFDATA <- read.xlsx("FOI IMT178324 SuffolkCoastal.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
-  mutate(Exemption.type = Exemption.type %>% trimws %>%
-           make.names %>% 
-           gsub("\\.{2,}" , ".", .))  %>%
-  StructureData(.,c(5,6,11,12,14:16))
-
-WaveneySUFFDATA <- read.xlsx("FOI IMT178324 Waveney.xlsx")[1:4] %>% setNames(make.names(names(.))) %>%
-  mutate(Exemption.type = Exemption.type %>% trimws %>%
-           make.names %>% 
-           gsub("\\.{2,}" , ".", .))  %>%
-  StructureData(., lowuse = c(5,6,13,14,16:18))
-
-StEdmundsDATA <- read.xlsx("se FOI 146  3948502_Copy+of+St+EdmundsburyDiscountsLSOA.xlsx")[1:4] %>%
-  StructureData()
-
-ForestHeathDATA <- read.xlsx("FH FOI 146 Discounts.xlsx")[1:4] %>%
-  StructureData()
-
-IpswichDATA <- read_xlsx("IpswichDiscountsLSOA.xlsx")[1:4] %>%
-   StructureData(c(2:4,6:11,13:15))
-
-#Mid Suffolk and Babergh
-#These have been combined and are just the postcodes so need to be fixed
-#Missing loads of postcodes
-MidSuffolkDATA <- read_excel("MidSuffolk FOI MF379 1718 Discount.xlsx") %>%
-mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
- left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
-  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
-  StructureData(c(2:12,14:15))
-
-BaberghDATA <- read_excel("Babergh FOI BF378 1718 Discount.xlsx")%>%
-mutate(Postcode = gsub(" ", "", `Post Code`)) %>%
- left_join(.,PstCdLSOA.raw,  by=c("Postcode") ) %>%
-  rename(Exemption.type=`Discount Type Description`, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Country_code, Admin_district_code) %>%
-  StructureData(c(2:6,8:11,13:15))
-
-```
-
-##Norfolk
-```{r}
-#This is being checked
-BroadlandsDATA <- read_excel("BroadlandDiscountsLSOA.xlsx", sheet=1)[1:4] %>%
-  StructureData(4:9)
-
-KingsLynnDATA <- read_excel("197782 - King s Lynn and West NorfolkDiscountsLSOA (2).xlsx" , sheet=1)[1:4] %>%
-  StructureData(2:11)
-
-NorthNorfolkDATA <- read_excel("North NorfolkDiscountsLSOA.XLSX" , sheet=1)[1:4] %>%
-  StructureData()
-
-BrecklandsDATA <- read_excel("BFOI-003031 BrecklandDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
-  StructureData()
-
-SNorfolkDATA <- read_excel("SNorfolk 17-307 Discounts.xlsx"  , sheet=1)[1:4] %>%
-  StructureData()
-
-NorwichDATA <- read_excel("Norwich Discounts FINAL.xlsx"  , sheet=1)[1:4] %>%
-  StructureData(2:8)
-
-```
-
-##Cambridge
-```{r}
-EastCambsDATA <- read_excel("EC FOI 130 - DISC_FOI_0_3944413b.xlsx", sheet=1)[1:4] %>%
-  StructureData()
-
-FenlandDATA <- read_excel("FL FOI 4544 DISCOUNTS.XLSX" , sheet=1)[1:4] %>%
-  StructureData()
-
-HuntingdonDATA <- read_excel("Huntingdonshire  FOI 568discounts.xlsx" , sheet=1)[1:4] %>%
-  StructureData(lowuse = 2:8)
-
-PeterboroughDATA <- read_excel("Peterborough 1707267585 completed.xlsx" , sheet=1)[1:4] %>%
-  StructureData(lowuse = c(4,6:7,11))
-
-CambridgeDATA <- read_excel("566 - Copy of Copy of CambridgeDiscountsLSOA .xlsx" , sheet=1)[1:4] %>%
-  StructureData(2:5)
-
-```
-
-#South East
-
-```{r}
-
-setwd(file.path(RegionsComp, "Region South East"))
-list.files()
-
-BrightonDATA <- read_excel("Copy of Brighton and HoveDiscountsLSOA (4).xlsx", sheet=1)%>% .[,c(2,3:5)] %>%
-  StructureData(lowuse = 2:8)
-#MakeLeaflet(BournemouthDATA)
-
-ValeWhiteDATA <- read_excel("Vale of White HorseDiscountsLSOA (00000002).xlsx" , sheet=1)[1:4] %>%
-  StructureData(c(5,7,8,9,10,14))
-
-SouthOxfordDATA <- read_excel("South OxfordshireDiscountsLSOA.xlsx" , sheet=1)[1:4] %>%
-  StructureData(c(5,7,8,9,10,14))
-
-```
-
-#Yorkshire and the Humber
-```{r}
-setwd(file.path(RegionsComp, "Region Yorkshire and The Humber"))
-
-#Hull
-
-HullDATA <-read_excel("KINGSTON UPON HULL%2c CITY OFDISCOUNTSLSOA.XLSX")[-c(c(1:6)),1:4] %>%
-  StructureData(.)
-
-#Harrowgate
-
-HarrogateDATA <-read_excel("Harrogate DiscountsExemptionsLSOA.xlsx" )[,1:4] %>%
-  StructureData(.,3:10)
-
-#Selby
-SelbyDATA <-read_excel("SelbyExemptionsLSOA.xlsx" )[,1:4]%>%
-  StructureData(20:27)
-
-# HambletonDATA <- read_excel("HDC1088.xlsx")[,1:4] %>%
-#  StructureData()
-
-ScarboroughDATA <- read_excel("FOIA 5156 Scarborough Discounts LSOA.xlsx"  )[,1:4]%>%
-  StructureData(2:8)
-
-# Middlesbrough sent the wrong data
-# MiddlesbroughDATA <- read_excel( "Middlesbrough FOI RES - 011397 Discounts.xlsx"   )[,1:4]%>%
-#   StructureData()
-
-#Ryedale
-RyedaleDATA <-  read_excel("Ryedale FOI 4597.xlsx")[,1:4]%>%
-  StructureData(2:6)
-
-#Crave they sent full addresses by mistake I'll do a temporary fix
-CravenDATA <- read_excel("Craven Discounts.xlsx" ) %>%
-  setNames(make.names(names(.))) %>%
-  mutate(Postcode = str_split(Full.Property.Address, "(,)(?!.*,)", simplify = T)[,2] %>% 
-           gsub(" ", "", .)) %>%
-  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
-  rename(Exemption.type=Discount.Type.Description, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
-  StructureData(c(2:5,7))
-
-#Redcar and cleveland
-
-RedcarDATA <-  read_excel("Redcar 0614 attachment 1.xlsx")[,1:4]%>%
-  StructureData(2:10)
-
-CalderdaleDATA <- read_excel("Copy of CalderdaleDiscountsLSOA.xlsx" )[,1:4]%>%
-  StructureData(c(7,10,22:25))
-
-BradfordDATA <- read_excel("Copy of BradfordDiscountsLSOA.xlsx")[1:4] %>%
-  StructureData(c(2:7))
-
-RichmondshireDATA <- read_excel("Richmondshire FOI 4960.xls", col_names = FALSE)[1:2] %>%
-    setNames(c("Exemption.type", "Postcode")) %>%
-  mutate(Postcode = sub(" ", "", Postcode)) %>%
-  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
-  rename(LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
-  StructureData(lowuse = c(2:7))
-
-KirkleesDATA <- read_excel("Jonathan Bourne KirkleesDiscountsLSOA Complete.xlsx" )[1:4] %>%
-  StructureData(2:5)
-
-WakefieldData <-  read_excel("WakefieldDiscountsLSOA.xlsx" )[1:4] %>%
-  StructureData(2:7)
-
-```
-
-#North East
-
-##Tyneside
-
-```{r}
-
-setwd(file.path(RegionsComp, "Region North East"))
-list.files()
-#Not sure all are there ask for confirmation
- SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
-   StructureData(lowuse = c(2:4,6,8:10))
-
-NewcastleDATA <- read_excel("Newcastle upon TyneDiscountsLSOA.xlsx", sheet=1)%>% .[,c(1,3:5)] %>%
-    StructureData(lowuse = 2:7)
-
-#FOr some reason Gateshead has the wrong LAD11CD I don't know why. I have changed it to the right one but feel that perhaps I should check them all, but how?
-GatesheadDATA <- read_excel("Copy of GatesheadExemptionsLSOA.XLSX"   , sheet=1)%>% .[,1:4] %>%
-   StructureData(lowuse = c(2:3, 20,22:25)) %>%
-  mutate(LAD11CD = ifelse(is.na(LAD11CD), NA, "E08000037"))
-
-STynesideDATA <- read_excel("FOI 17.18456 - South Tyneside Discounts.xlsx", sheet=1)[,c(1,4:6)] %>%
-    StructureData(c(32:35,38))
-
-```
-
-##Northumberland
-
-```{r}
-NorthumberlandDATA <- read_excel("FOI 2762 data NorthumberlandDiscounts.xlsx", sheet=1)%>% .[,1:4] %>%
-    StructureData(2:7) %>%
-  #The LAD code is wrong for some reason
-  mutate(LAD11CD = "E06000057")
-
-```
-
-##Durham
-```{r}
-
-DurhamDATA <- read_excel("County DurhamDiscountsLSOA.XLSX" , sheet=1) %>% .[,c(1,4:6)] %>%
-    StructureData()
-
-  DarlingtonDATA <- read_excel("Darlington DBC-0809-17.xlsx" , sheet=1) %>% .[,1:4] %>%
-    StructureData()
-
-  HartlepoolDATA <- read_csv("FOI 7942 HartlepoolDiscountsLSOA.csv") %>% .[,1:4] %>%
-    StructureData(2:7)
-
-```
-
-#Wales
-
-Wales is removed to simplify the process.
-As the deprivation scales are separate for all countries this means wales cannot be included in the predictive model later. Also the council tax is seperate.
-
-```{r}
-# 
-# setwd(file.path(RegionsComp, "Region Wales"))
-# list.files()
-# 
-# #Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
-# 
-# CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
-#   StructureData(lowuse =c(8:13,15))
-# 
-# MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
-#   StructureData(lowuse = c(4:8))
-# 
-# 
-# #includes the zero class which is descibeed as 
-# #ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
-#   CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
-#     StructureData()
-# 
-# #Strangely low numbers checking
-# # PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
-# #   StructureData(lowuse = c(3,5:6))
-# 
-# #It seems Conwy really is this short on the discounts  
-# ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
-#   rename(Postcode = geo_postcode) %>%
-#   mutate(Postcode = sub(" ", "", Postcode)) %>%
-#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
-#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
-#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
-#   StructureData(lowuse = c(2,4))
-# 
-# DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
-#     StructureData(c(8:9,11,13))
-# 
-# WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
-#     StructureData(2:5)
-# 
-# #Pembrokeshire didn't send all the data
-# PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
-#     StructureData(3)
-# 
-# FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
-#     StructureData()
-
-```
-
-# London using the full data
-
-```{r}
-#Source the code from another file as it is very long
-source(file.path(CommonCode, "LondonFullProcesss.R"))
-
-#MakeLeaflet(NewhamLONDATA)
-
-```
-
-#Semi data
-
-The LSOA will be assigned empty and low use homes by percentage
-
-```{r}
-#ward folder
-setwd(SemiLondon)
-
-wardnames <- EW2 %>% group_by(Admin_ward_code, WD16NM) %>% summarise(counts = n(), LAD11NM = first(LAD11NM), LAD11CD = first(LAD11CD)) %>% arrange(WD16NM)
-
-#TowerHamlets
-TowerLONDATA <- read_excel("Towerhamlets.xlsx")[,c(1,3)] %>% 
-  filter(!is.na(DiscClass)) %>%
-  group_by(Ward, DiscClass) %>%
-  summarise(count = n()) %>% ungroup %>%
-  spread(., key =DiscClass, value = count, fill = 0 ) %>% 
-  mutate(Empty = rowSums(.[,4:8]), LowUse = B+BE+Empty) %>% 
-  slice(c(1:13, 15:17, 14, 18:20)) %>%
-   bind_cols(., wardnames %>% filter(grepl("Tower", LAD11NM))) %>%
-  SemiDataStructure
-
-HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
-  rename(DiscClass = X__1) %>%
-  select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
-  gather(key = "ward", value = "counts", -DiscClass) %>%
-  spread(key= DiscClass, value = counts, fill = 0) %>%
-  mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
-  bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
-  SemiDataStructure
-
-```
-
-General Stats
-#UK population
-
-```{r}
-
-#number of LUPS and Total Homes
-DataCover <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x))) %>% 
-  filter(!is.na(LAD11NM)) %>%
+DataCover <-DATAdf  %>%
+                #filter(!is.na(LAD11NM)) %>%
   summarise(
-           'LADs' = length(ls(pattern = "DATA", envir = globalenv())), #bits of other LADS cause the number to be higher than reality so the ls function is used again
-           '% of all LADs' = length(ls(pattern = "DATA", envir = globalenv()))/(EW2$LAD11NM %>% unique %>% length())*100,
+           'LADs' = length(unique(DATAdf$LAD11CD)), 
+           '% of all LADs' = length(unique(DATAdf$LAD11CD))/length(unique(EW2$LAD11CD))*100,
            LUPs = sum(LowUse, na.rm = T),
@@
 
-#Percentage of EW LADS
-length(ls(pattern = "DATA"))/(EW2$LAD11NM %>% unique %>% length())
+```
 
-#check which lads are present even though I don't have data due to postcode matching
-#test <- ls(pattern = "DATA") %>% map_df(~eval(parse(text=.x)))  %>% arrange(LAD11NM)
-#unique(test$LAD11NM)
+#BootStrap
+
+This section bootstraps the price classes for each property then aggregates it by quartiles per LAD
+From this we can find out if the majority of a LADs Low Use properties are investment or not by comparing the median values.
+
+The same can be done at MSOA level but the areas are so small that you don't get enough variation in the house price levels to get a meaningful result.
+A better way to do this would be to use the ego network of MSOA around a target to find the "Neighbourhood LAD" and see if that is investment.
+However as I don't have the the low use property data for all adjoining MSOA this is not possible.
+
+##Quartiles Bootstrap
+
+Needed for creating the skew plots
+```{r}
+
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapQuartiles")
+BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501)
+BootStrapRes <- LoadBootstrapData()
 
@@
 
-#Saleries
+##MSOA Bootstrap
+Used for most of the analysis
+```{r}
 
-Problem here with the MSOA/LSOA code in the IncomeEst
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
+BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501, GroupingVars = "MSOA11CD")
+
+#Temporay untill the proper one is complete
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
+BootStrapRes <- LoadBootstrapData()
+
+```
+
+#Low Use quartile plot
+
+This chunk plots which of the LADs affordability quartiles the LUPs fall into.
+
+##This will need to be re-worked when the quartiles are put in and the data is re bootstrapped
+
+```{r}
+CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
+  df %>% 
+  group_by(ID, class) %>%
+  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
+  group_by(ID)%>%
+  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
+  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
+}
+
+#I think I should have 1 plot with high value skew, one plot with low value skew and 1 plot for all data
+#These three plots should be shown as a panel of data
+
+CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
+PlotClassDiff(., "Kensington and Chelsea")
+SaveFig("ClassdiffChelsea.pdf")
+
+CleanForPlotClassDiff(BootStrapRES$BarrowCUMBRIA) %>% #maybe choose a better place than barrow?
+PlotClassDiff(., "Barrow")
+SaveFig("ClassdiffBarrow.pdf")
+
+#Plot for all data
+All_data_class <- BootStrapRES %>% 
+  bind_rows %>%
+  select(CountryClass, ID, LowUse, Homes) %>%
+  rename(class = CountryClass)%>%
+  CleanForPlotClassDiff
+
+All_data_class %>% group_by(class) %>%
+  summarise_all(mean)
+
+PlotClassDiff(All_data_class)
+SaveFig("ClassdiffAllData.pdf")
+
+```
+
+#Tourism data
+This section Loads and processes tourism Data
 
@@
 
-unafford <- ls(pattern = "DATA") %>%
-  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
-  group_by(MSOA11CD) %>% # ward code is used for consistency
-  summarise(
-    #MSOA11CD = first(MSOA11CD), #MSOA is kept to allow joining of income
-    LowUse = sum(LowUse, na.rm = T),
-            Homes = sum(Homes, na.rm = T),
-            Pop = sum(Pop, na.rm = T)) %>%
-  mutate(LowUsePerc = LowUse/Homes) %>%
-  left_join(IncomeEst, by = "MSOA11CD") %>%
-  mutate(decile = ntile(ratio, 20))
+CorePstCd <- PstCdLSOA.raw %>%
+  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
+  select(Postcode,LSOA11CD= lsoa11cd, LAD11CD, LAD11NM, MSOA11CD, Pop)
 
-unaffordExLon <- unafford %>%
-  filter(Region.name != "London") %>%
-  mutate(decile = ntile(ratio, 50))
+setwd(file.path(basewd, "VOA data"))
 
-#London follows the same pattern it just happens further up the scale
-unaffordLon <- unafford %>%
-  filter(Region.name == "London") %>%
-  mutate(decile = ntile(ratio, 50))
+#Creates Tourism dataframe at LSOA level
+Tourism <- read_delim("uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv", 
+                          delim = "*", col_names = F) %>%
+  mutate(X15 = gsub(" ", "", X15)) %>%
+  left_join(., CorePstCd, by = c("X15" = "Postcode")) %>%
+  filter(!is.na(LAD11CD)) %>%
+  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
+  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
+         Hotel = grepl("(HOTEL)|(HOSTEL)",X6)) %>%
+   group_by(LSOA11CD, X6) %>%
+  summarise(Tourism = n(),
+            LAD11CD = first(LAD11CD),
+            LAD11NM = first(LAD11NM),
+            MSOA11CD = first(MSOA11CD),
+            Pop = first(Pop),
+            Guest = sum(Guest),
+            Hotel = sum(Hotel))
 
-decile <- bind_rows(mutate(unaffordExLon, type = "Excluding London"), 
-                    mutate(unafford, type = "Including London"),
-                    mutate(unaffordLon, type = "Only London")) %>%
+```
+
+#Create LAD and MSOA DATA frames
+
+This chunk creates useful data frames for the rest of the analysis
+
+##LAD Data
+
+HArtlePool E06000001
+COl E02000001
+```{r}
+LADModelData <-CreateGeogModelData("LAD", "/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")
+LADMean<- MeanModelData(LADModelData, "LAD") %>%
+  mutate(AffordRank2 = scale(AffordRank)^2,
+         TourismDensityRank = rank(TourismDensity, ties.method = "max"))
+
+  LADMean %>%
+  ggplot(aes(x= AffordRank, y = TourismDensityRank, colour = HighVal)) + geom_point()
+
+  LADMean %>%
+  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = HighVal)) + geom_point()
+
+```
+
+##MSOA Data
+
+```{r}
+
+MSOAModelData <-CreateGeogModelData("MSOA", "/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA") 
+MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
+  left_join(select(MSOAtoLAD, MSOA11CD, LAD11CD)) %>%
+  mutate(AffordRank2 = scale(AffordRank)^2,
+         TourismDensityRank = rank(TourismDensity, ties.method = "max"))
+
+ MSOAMean %>%
+  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point()
+
+  MSOAMean %>%
+  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = HighVal)) + geom_point()
+
+  #Great results for the MSOA model predicting High LUP numbers
+  ModelFormula <- as.formula(Reference ~ TourismRank+ AffordRank+ AffordRank2)
+
+```
+
+#Price affordability correlation
+
+Why is there such a large difference between price and affordability at lad level and MSOA level  is this a mistake?
+```{r}
+
+cor(LADMean$AffordRatio, LADMean$HomesMedian)
+cor(MSOAMean$AffordRatio, MSOAMean$HomesMedian)
+```
+
+#Affordability
+
+This chunk includes affordability and plots the theoretical and observed curves.
+Uses the Bootstrapped values to calculate the affordability
+
+```{r}
+MSOAAffordRatio <- MSOAMean %>%
+  left_join(select(MSOAtoLAD, MSOA11CD, Region), by ="MSOA11CD")
+
+MSOAAffordRatio  <- bind_rows(MSOAAffordRatio %>% filter(Region != "London") %>% mutate(type = "Excluding London"), 
+                    MSOAAffordRatio %>% mutate( type = "Including London"),
+                    MSOAAffordRatio %>% filter(Region == "London") %>% mutate( type = "Only London")) %>%
     group_by(type) %>%
-    mutate(decile = ntile(ratio, 50)) %>%
+    mutate(
+      decile = ntile(AffordRatio, 100)) %>%
       group_by(decile, type) %>%
@@
               counts = n(),
-              ratio= mean(ratio)
-              ) %>%
-  mutate(decile2 = decile^2,
-         ratio2 = ratio^2,
-         logval = log(decile),
-         expval = exp(decile),
-         expvalneg = exp(-decile)) %>%
-  filter(!is.na(decile))
+              AffordRatio= mean(AffordRatio)
+              )
 
-cor(unafford$Yearly.income, unafford$ratio, "complete.obs")
-cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
-cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")
-lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford) %>% summary
-
-rm(unafford); rm(unaffordExLon); rm(unaffordLon)
-
-#Looking at the relationship between unaffordability and LUP percentage
-
-decile %>% 
+MSOAAffordRatio %>% 
   #filter(type == "Excluding London") %>% 
@@
   geom_smooth(method="loess",se=FALSE, colour = "black") +
- coord_cartesian(ylim = c(0.01, 0.05)) +
+ #coord_cartesian(ylim = c(0.01, 0.05)) +
    scale_y_continuous(labels = scales::percent)
@@
 
-#make nonlinear  model
-mod <- decile %>% 
-    filter(type == "Excluding London") %>% 
-  nls(median ~ exp(a + b*decile)+  exp(d + c*decile), data = ., 
-      start = list(a = 0, b = -3, c = 0, d = 0))
-
-summary(mod)
-
-decile %>%
-      filter(type == "Excluding London") %>% 
-  ggplot(aes(x = decile, y = median))+
-  geom_point() +
-  geom_line(aes(y = predict(mod, list(x = decile))))
-
-#Example of the theoretical relationship
-
+#The plot of the theoretical curves
 data_frame(Index = 1:100) %>%
@@
 
-unaffordLAD <- unafford %>%
-  rename(LAD11CD = Local.authority.code) %>%
-  group_by(LAD11CD) %>%
-  mutate(TotInc = Yearly.income*Pop) %>%
-  summarise(TotInc = sum(TotInc),
-            Pop = sum(Pop)) %>%
-  mutate(meanInc = TotInc/Pop)
+```
+
+#Models
+
+The models that will be made are all binary logistic regression
+
+Are the majority of the of the LUPS above the LAD price? 
+  this uses the variables Affordability Rank (normalised), the square of the affordability rank and tourism
+Are there more than the average LUPS in the LAD
+
+Are there more than average LUPS in the LSOA/MSOA
+
+Both models can be bootstrapped as the investment number relies on the inferred value of Homes and LUPs and the affordability relies on the bootstrapped Homes price...
+only question is is there enough variation in the median homes price for it to be worth it.
+
+#LAD Model
+
+works well at predicting high numbers of LUPs
+ ModelFormula <- as.formula(Reference ~ TourismDensityRank + AffordRank)
+
+```{r}
+
+set.seed(1983)
+TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))
+
+#Make a lot of models
+
+Combos<-expand.grid(1:2,1:2)
+
+LADModels <- map2_df(.x = c("HighVal", "HighLUP")[Combos[,1]], .y = c(as.formula(Reference ~ HomesMedianRank+ AffordRank), 
+                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank))[Combos[,2]],
+        ~{
+          print(paste(.x,.y))
+          LADMean %>% #LADMean %>%
+    rename_(Reference = .x ) %>%
+  ResampledModelPerf(., TestResample,  .y) %>%
+            mutate(Dependent = .x,
+                   Formula = toString(.y))
+
+        } ) %>%
+  mutate(Formula = ifelse(grepl("Tourism", Formula), "Tourism", "Price"))
+
+MODOut <- 1:length(TestResample) %>% map_df(~{
+  Mod2 <- LADMean  %>%
+    rename(Reference = HighVal) %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$train)) %>%
+  glm(formula = as.formula(Reference ~ TourismDensityRank+ AffordRank), data = ., family=binomial(link='logit'))%>%
+    tidy
+
+})
+
+ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+
+LADModels %>%
+  group_by(Dependent, Formula) %>%
+  summarise(BeatNull = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            meanAcc = mean(Accuracy), #What was the mean accuracy
+            NULLMod = mean(AccuracyNull),
+            DiffNull = mean(Accuracy-AccuracyNull), #Mean difference relative to NULL
+            StatistSignif = t.test(Accuracy,AccuracyNull, alternative = "greater", paired = T)$p.value) #Was Beat NUll statis
 
@@
 
-#Bootstrap
-
-Now all the data is loaded each LAD needs to be bootstrapped
-
-```{r}
-PropertyTypes <- c("D", "S", "T", "F")
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities")
-
-#Find what needs to be bootstrapped
-BootStrapFiles <- list.files(getwd()) %>% gsub("DATA.rds", "",.)
-  newLADsnames <- sub("DATA", "", ls(pattern = "DATA", envir = globalenv())) %>% 
-    .[!(. %in% BootStrapFiles)] 
-  newLADs <- paste0(newLADsnames, "DATA")
-
-   #only bootstrap if there is something to add.
-  #Save each boostrap as you go along to avoid losing it all in a crash
-  if(length(newLADsnames)>0){
-    newLADs  %>% walk(~{print(.x)
-      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes)%>%
-      saveRDS(., file = paste0(.x, ".rds"))
-      }) 
-  }
-
-  #once all Bootratps complete load them all into a list
- BootStrapRES <- list.files(getwd()) %>%
-   map(~readRDS(.x))
-
- #name the list
- names(BootStrapRES) <- list.files(getwd()) %>% gsub(".rds", "",.)
-
-#Make a summary dataframe
-Combine1ExO <- BootResSummaryData(BootStrapRES)
-
-```
-
-#Analyse Bootstrap
-
-```{r}
-#99% of the LADs are significantly different from 0 at the 95% level
-sum(Combine1ExO$Ttest.p.value>0.975 |Combine1ExO$Ttest.p.value<0.025)/nrow(Combine1ExO)
-
-CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
-  df %>% 
-  group_by(ID, class) %>%
-  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
-  group_by(ID)%>%
-  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
-  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
-}
-
-CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
-PlotClassDiff(., "Kensington and Chelsea")
-SaveFig("ClassdiffChelsea.pdf")
-
-CleanForPlotClassDiff(BootStrapRES$Cornwall)  %>%
-PlotClassDiff(., "Cornwall")
-SaveFig("ClassdiffCornwall.pdf")
-
-CleanForPlotClassDiff(BootStrapRES$BarrowCUMBRIA) %>%
-PlotClassDiff(., "Barrow")
-SaveFig("ClassdiffBarrow.pdf")
-
-#Plot for all data
-All_data_class <- BootStrapRES %>% 
-  bind_rows %>%
-  select(CountryClass, ID, LowUse, Homes) %>%
-  rename(class = CountryClass)%>%
-  CleanForPlotClassDiff
-
-All_data_class %>% group_by(class) %>%
-  summarise_all(mean)
-
-PlotClassDiff(All_data_class)
-SaveFig("ClassdiffAllData.pdf")
-
-#Total value of homes and LUPS
-
-#LADnames <- names(BootStrapRES)
-
-LUPval <-   map2(.x =BootStrapRES, .y =   names(BootStrapRES),~ {.x %>% mutate(LAD  = .y)}) %>%
-  bind_rows %>%
-  select(-class, -LAD11CD, -CountryClass,-classVal) %>%
-  group_by(LAD, ID) %>%
-  summarise_all(sum) %>%
-  group_by(LAD) %>%
-  summarise_all(mean) %>%
-  ungroup %>%
-  mutate(HomesPrice = HomesValue/Homes,
-         LowUsePrice = LowUseValue/LowUse,         
-         ratio = LowUse/Homes,
-         HomesPerc = Homes/sum(Homes, rm.na = T),
-         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
-         ClassPerc = LowUse/Homes,
-         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
-         RatioExvsAct = LowUse/ExpectedHomes
-         ) %>%
-  mutate(VancouverTax = LowUseValue*0.01/1000)
-
-#value is billions of pounds of a vancouver tax in England and wales.
-LUPval$VancouverTax %>% sum(.)/1000
-
-```
-
-#Explore results
-
+#MSOA Model
 ```{r}
 
-LADNMs <- EW2 %>% group_by(LAD11CD) %>%
-  summarise(LAD11NM = first(LAD11NM))
-
-#calulcate the number of properties sold and the mean price
-ABratio <- prices %>% 
-  filter(X5 %in% PropertyTypes) %>%
-  group_by(Admin_district_code, X15) %>%
-  summarise(count = n(), 
-            mean = mean(X2)) %>%
-  rename(LAD11CD = Admin_district_code)
-
-ABratio2 <- ABratio%>%
-  select(-mean) %>%
-spread(key = X15, value = count) %>%
-  mutate(Countratio = B/(A+B)) %>%
-  rename(CountofA = A, CountofB = B)
-
-ABratio3 <- ABratio%>%
-  select(-count) %>%
-spread(key = X15, value = mean) %>%
-  mutate(Valueratio = B/(A)) %>%
-  rename(MeanofA= A, MeanofB = B)
-
-CombineAB <-left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
-  left_join(Combine1ExO, ., by = "LAD11CD")
-
-rm(ABratio); rm(ABratio2); rm(ABratio3)
-
-CombineAB %>%
-  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, colour = Valueratio>1)) + geom_point()
-
-```
-
-#Overall Concentration plot
-
-This chunk makes a plot that shows that LUPs are more heavily concentrated than Homes
-
-```{r}
-   test <- ls(pattern = "DATA") %>%
-  map_df( ~get(.x) %>%
-            select(LSOA_CODE, Admin_ward_code, LowUse, Homes))%>%
-  group_by(Admin_ward_code) %>%
-  summarise(LowUse = sum(LowUse),
-            Homes = sum(Homes)) %>%
-  filter(!is.na(Homes))
-
-%>%
-  arrange(-LowUse) %>%
-  mutate(
-    CumsumLUP = cumsum(LowUse),
-    CumsumLUPPerc = CumsumLUP/sum(LowUse),
-    CumsumHomes = cumsum(Homes),
-    CumsumHomesPerc = CumsumHomes/max(CumsumHomes),
-    CumsumNumber = 1:nrow(.),
-    CumsumPercNumber = CumsumNumber/max(CumsumNumber))
-
-test2 <- test %>%
-  gather(key = Type, value = value, -Admin_ward_code) %>%
-  group_by(Type) %>%
-  arrange(-value) %>%
-  mutate(
-    Cumsum = cumsum(value),
-    CumPerc = Cumsum/sum(value),
-    CumsumNumber = 1:n(),
-    CumsumPercNumber = CumsumNumber/max(CumsumNumber))
-
-test2%>%
-  ggplot(aes(x = CumsumPercNumber, y = CumPerc, colour = Type)) + geom_line() +
-  labs(
-    title= "Comparison of LUP vs Home concentration", 
-       y= "Percent of total property type", 
-    x= "Cumulative percent of administrative wards") +
-  scale_color_discrete(labels = c("Homes", "LUPs"))+
-   scale_y_continuous(labels = scales::percent)+
-  scale_x_continuous(labels = scales::percent)
-SaveFig("LUPConcentration.pdf")
-
-test3 <-test2 %>%
-  select(Type, CumPerc, CumsumPercNumber) %>%
-  spread(key = "Type", value = "CumPerc") %>%
-  mutate(ratio = LowUse/Homes-1)
-
-test3 %>%
-  ggplot(aes(x= CumsumPercNumber, y = ratio)) + geom_line()
-
-```
-
-#Inlcuding deprivation
-```{r}
-
-#creating the empty deprivation extent
-maxLSOA <- max(LSOADep$Rank..where.1.is.most.deprived.)
-
-ExtentWeight <- LSOADep%>%
-  mutate(percentile = (Rank..where.1.is.most.deprived./maxLSOA),
-         perc2 = percentile-0.11,
-         weight = ifelse(percentile<.11|percentile>.3,0, 0.95 - (0.95/.20)*perc2 ),
-         weight = ifelse(percentile<0.11, 1, weight)) %>%
-  select(LSOA_CODE, weight)
-
-#Create the extent of deprivation of the LUPs
-LUPdepExt <- ls(pattern = "DATA") %>% map_dbl(~{
-df <- get(.x)
-test <- df %>% 
-  left_join(., ExtentWeight, by= "LSOA_CODE")  %>%
-  mutate(WeightedLUP = (LowUse*weight)/sum(LowUse))
-
-sum(test$WeightedLUP, na.rm = TRUE)
-})
-
-#Add in deprivation
-Combine1ExO <- select(LADDep, LAD11CD ,Extent) %>% 
-  left_join(CombineAB, ., by = "LAD11CD") %>%
-  mutate(LUPdepExt)
-
-Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
-  geom_jitter()
-
-```
-
-#Model
-
-##Create modelling dataframe
-
-```{r}
-LADincome <- EW2 %>%
-  group_by(MSOA11CD) %>%
-  summarise(Pop = sum(Pop),
-            LAD11CD = first(LAD11CD)) %>%
-  ungroup %>%
-  select(LAD11CD,MSOA11CD, Pop)%>%
- left_join(IncomeEst %>%
-              select( MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
-  mutate(TotalIncome = Pop*Yearly.income) %>%
-  group_by(LAD11CD) %>%
-  summarise(Pop = sum(Pop),
-            income = sum(TotalIncome)) %>%
-   mutate(income = income/Pop)
-
-LADprice <- prices %>%
-  filter(X5!= "O") %>%
-  group_by(Admin_district_code) %>%
-summarise(price = mean(X2)) %>%
-  mutate(pricepercent = percent_rank(price)) %>%
-  ungroup
-
-ModelMe <- Combine1ExO %>%
-  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
-  left_join(Vacants, by = "LAD11CD") %>%  
-  left_join(LADincome %>%
-              select(LAD11CD, income ), by = "LAD11CD") %>%
-  mutate(VacantsPerc = Vacants/Homes,
-         LTVPerc = Vacants/Homes,
-         afford = price/income) %>%
-  #filter out wales
-  filter(!grepl("W", LAD11CD)) %>%
-  mutate(Reference = as.factor(absdiff>0) ) %>%
-  #scaled so that the binomial can be interpreted
-  mutate(pricepercent = scale(pricepercent) %>% as.numeric,
-         LUPdepExt = scale(LUPdepExt) %>% as.numeric,
-         maxPerc = scale(maxPerc) %>% as.numeric,
-         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
-         price = price %>% scale %>% as.numeric,
-         Extent = scale(Extent) %>% as.numeric) #%>%
- # mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)
-
-ModelMe %>% ggplot(aes(x = afford, y = (LUPS/(Homes+LUPS)), colour = Reference)) + geom_point()
-
-#57% of LADs have mostly high value properties
-table(ModelMe$Reference)
-
-rm(LADincome)
-
-```
-
-##create functions to get out model preds
-
-```{r}
- GetAccuracy <- function(df, splits , Var ) {
-  select_(df,splits) %>% flatten %>%
-           map2_dbl(select_(df,Var) %>% flatten, ., ~{ augment(.x, newdata = assessment(.y)) %>%
-               mutate(.fitted = factor(.fitted > 0,
-                        levels = as.factor(c("FALSE", "TRUE"))))  %>%
-              accuracy(., Reference, .fitted)} ) }
-
-#If this one is used on the logistic regression I get an "incorrect number of dimensions error"
-GetAccuracyForest <- function(df, splits , Var ) {
-   select_(df,splits) %>% flatten %>%
-map2_dbl( select_(df,Var) %>% flatten, ~{assessment(.x) %>%
-   mutate(fitted = predict(.y, .) %>% .[,colnames(.)=="TRUE"],
-          fitted = factor(fitted > 0,
-                        levels = as.factor(c("FALSE", "TRUE")))) %>%
-              accuracy(., Reference, fitted) 
-}) }
-
-```
-
-#Create Models
-```{r}
-
-FOIFormula <- as.formula(Reference~ LUPdepExt + price + VacantsPerc)
-OpenFormula <- as.formula(Reference~ Extent + price + VacantsPerc)
-OpenFormula2 <- as.formula(Reference~ Extent + price)
-
-set.seed(4622)
-Modeldf <- ModelMe  %>%
-  vfold_cv(., V = 5, repeats = 200) %>%
-  mutate(LogisticFOI = splits %>%
-  map(.,~{ glm(FOIFormula, data = analysis(.x),binomial(link='logit'))}
-        ),
-  LogisticOpen = splits %>%
-  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
-        ),
-  LogisticOpen2 = splits %>%
-  map(.,~{ glm(OpenFormula2, data = analysis(.x),binomial(link='logit'))}
-        ),
-  ForestOpen = splits %>% 
-    map(., ~{rpart(OpenFormula2, data=analysis(.x))})
-  ) %>%
-  mutate(LogFoiAcc = GetAccuracy(., "splits", "LogisticFOI"),
-         LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"),
-         LogOpenAcc2 = GetAccuracy(., "splits", "LogisticOpen2"),
-         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))
-
-Modeldf$LogisticOpen %>%
-   map_df(., ~coefficients(.x) %>%
-            as.data.frame(.) %>% rownames_to_column()) %>%
-   setNames(c("key", "value")) %>%
-  ggplot(aes(x= key, y = value, fill = key)) +geom_boxplot() +
-  labs(title = "Coefficient values across 100 samples of 10 fold cross validation")
-SaveFig("ModelCoeffs.pdf")
-
-ModComp <- Modeldf %>%
-  select(LogFoiAcc, LogOpenAcc, ForestOpenAcc, LogOpenAcc2) %>%
-  gather
-
-  ModComp %>%
-  ggplot(aes(x=model, y = statistic, fill = model)) + 
-  geom_boxplot()
-
-  ModComp %>%
-  group_by(model) %>%
-  summarise(mean =mean(statistic),
-            median = median(statistic))
-
-   test <- select_(Modeldf, "splits") %>% 
-     flatten %>%
-     map2(select_(Modeldf,"LogisticFOI") %>% flatten, ., ~{ augment(.x, newdata = assessment(.y)) %>%
-               mutate(.fitted = factor(.fitted > 0,
-                        levels = as.factor(c("FALSE", "TRUE"))))
-     })
-
-```
-
-#Model two
-
-Older modelling style as I am not sure what is happening with the current method.
-```{r}
-reps <- 1000
+    #as.formula(Reference ~ AffordRank+ AffordRank2+ TourismDensityRank)
 
 set.seed(1983)
-TestResample <- 1:reps %>% map(~  resample_partition(ModelMe, c(test = 0.2, train = 0.8)))
+TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean , c(test = 0.2, train = 0.8)))
 
-LogFOI <- 1:reps %>% map_df(~{
-  train<- TestResample[[.x]]$train %>% as.data.frame
-  test <- TestResample[[.x]]$test %>% as.data.frame
-  ;
-  model <- glm(FOIFormula, 
-               family=binomial(link='logit'),
-               train)
+#Make a lot of models
 
-  Confmat <- confusionMatrix( predict(model, test, type = "response")>0.5,
-                              test$Reference)
+Combos <- expand.grid(1:2,1:3)
 
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
-          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
+MSOAModels <- map2_df(.x = c("HighVal", "HighLUP")[Combos[,1]], .y = c(as.formula(Reference ~ HomesMedian+ AffordRank), 
+                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank),
+                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank+ AffordRank2))[Combos[,2]],
+        ~{
+          print(paste(.x,.y))
+          MSOAMean %>% #LADMean %>%
+    rename_(Reference = .x ) %>%
+  ResampledModelPerf(., TestResample,  .y) %>%
+            mutate(Dependent = .x,
+                   Formula = toString(.y))
 
-}
+        } ) %>%
+  mutate(type = ifelse(grepl("2", Formula), "2", "1"),
+          Formula = ifelse(grepl("Tourism", Formula), "Tourism", "Price")
          )
 
-LogOpen<- 1:reps %>% map_df(~{
-  TestResample<- TestResample[[.x]]
-
-  model <- glm(OpenFormula, 
-               family=binomial(link='logit'),
-               as.data.frame(TestResample$train))
-
-  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
-                              as.data.frame(TestResample$test)$Reference)
-
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
-          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
-
-}
-)
-
-ForestOpen<- 1:reps %>% map_df(~{
-  TestResample<- TestResample[[.x]]
-
-  model <- rpart(OpenFormula, data = as.data.frame(TestResample$train))
-
-  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "prob")[,2]>0.5,
-                              as.data.frame(TestResample$test)$Reference)
-
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
-
-}
-)
-
-ModRes <- bind_rows(LogFOI, LogOpen, ForestOpen) %>%
-  mutate(Model = rep(c("LogFOI", "LogOpen", "ForestOpen"), each = reps))
-
-ModRes %>%
-  ggplot(aes(x= Model, y = Accuracy)) +
-  geom_boxplot()
-
-ModRes %>%
-  group_by(Model) %>%
-  summarise(mean = mean(Accuracy),
-            median = median(Accuracy),
-            above = sum(Accuracy>AccuracyNull)/reps,
-            above2 = median(Accuracy-AccuracyNull),
-            NullMean = mean(AccuracyNull),
-            NullMedian = median(AccuracyNull))
-
-```
-
-```{r}
-
-  BootDeets <- BootStrapRES %>% map_df(~.x %>% group_by(ID) %>%
-                                    summarise(HighVal = sum(HighVal, na.rm = T),
-                                              LAD11CD= first(LAD11CD),) 
-  ) %>% 
-  left_join(., Combine1ExO %>% select(LAD11CD, LUPS)) %>%
-  mutate(Majority = HighVal>=(LUPS/2)) %>%
-  left_join(., select(ModelMe, LAD11CD, Extent, price, VacantsPerc), by = "LAD11CD") %>%
-  mutate(Reference = HighVal>(LUPS/2))
-
-#There is in fact boostrap variation on which LADS are majority
-test <- BootDeets %>%
-  group_by(LAD11CD) %>%
-  summarise(Majority = sum(Majority, na.rm = T)/1000,
-            Total = n(),
-            t2 = abs(Majority-0.5)+0.5)
-
-test %>%
-  ggplot(aes(x = Majority)) + geom_density()
-
-test2 <- BootStrapRES$IslingtonLONDATA %>%
-  group_by( ID) %>%
-  summarise(HighVal = sum(HighVal),
-            LowUse = sum(LowUse))
-
-median(test$t2)
-
-BootModData <- select(BootDeets, ID, LAD11CD, Majority) %>%
-  left_join(., select(ModelMe, LAD11CD, Reference,LUPdepExt, price, VacantsPerc, Extent))
-
-#make list of bootstrap models
-MakeBootModels <- function(df, trainvect, ModForm = OpenFormula){
-
-  BootMod <- (1:max(df$ID)) %>%
-  map(~{
-
-    ModData <- df %>%
-      filter(ID ==.x)
-
-  model <- glm(ModForm, 
-               family=binomial(link='logit'),
-               data = ModData[trainvect,])
-
-  }
-
-  )
-
-}
-
-#extract predictions
-MakeBootPreds <- function(df, BootMod, testvect){
-
-  Predsdf <- 1:length(BootMod) %>%
-  map(~{
-
-        ModData <- df %>%
-      filter(ID ==.x)
-
-    tibble(v1 =predict(BootMod[[.x]], ModData[testvect,], type = "response")>0.5) 
-  }) %>%
-  bind_cols() %>% set_names(make.names(1:length(BootMod)))
-
-  return(Predsdf)
-
-}
-
-#get the accuracy across all bootstraps
-MakeBootAccuracy <- function(Predsdf, df, testvect){
-
-    Accdf <- 1:ncol(Predsdf) %>%
-  map_df(~{
-
-    ModData <- df %>%
-      filter(ID ==.x)
-
-    Confmat <- confusionMatrix( Predsdf[,.x] %>% unlist,
-                              ModData$Reference[testvect])
-    # Confmat <- bind_cols(Predsdf %>% select(.x),
-    #                   as.data.frame(testvect) %>% select(Reference)) %>%
-    #   set_names(c("Predictions", "Reference")) %>%
-    #   mutate(Predictions = factor(Predictions,
-    #                     levels = as.factor(c("FALSE", "TRUE")))) %>%
-    #   conf_mat(truth = Reference, estimate = Predictions)
-
-  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = .x)
+MODOut <- 1:length(TestResample) %>% map_df(~{
+  Mod2 <- LADMean  %>%
+    rename(Reference = HighVal) %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$train)) %>%
+  glm(formula = as.formula(Reference ~ TourismDensityRank+ AffordRank), data = ., family=binomial(link='logit')) %>%
+    tidy
 
@@
 
-}
+ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot()
 
-OpenFormula <- as.formula(Reference~ Extent + price)
-BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[1]]$train))
-Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[1]]$test))
-Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[1]]$test))
-
-bind_rows(Accdf %>%mutate(modelOpen = "V1"), 
-          Accdf2 %>%mutate(modelOpen = "V2")) %>%
-  ggplot(aes(x = modelOpen, y = AccuracyPValue)) + geom_boxplot()
-
-Confmat <- confusionMatrix(rowSums(Predsdf)/ncol(Predsdf)>0.5, as.data.frame(TestResample[[1]]$test)$Reference)
-  BootOut <- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = 1001)
-
-Coeffs1 <- 1:length(BootMod) %>%
-  map_df(~BootMod[[.x]] %>% tidy %>% mutate(ID = .x) ) %>%
-  mutate(model = "Open1")
-
-Coeffs1 %>%
-  filter(term != "VacantsPerc", term != "(Intercept)") %>%
-  ggplot(aes(x = term, y = p.value, fill = term)) + geom_boxplot() + 
-  coord_cartesian(y = c(0,0.12))
-
-Accdf <- bind_rows(Accdf, BootOut)
-
-set.seed(1983)
-TestResample <- 1:50 %>% map(~  resample_partition(ModelMe, c(test = 0.1, train = 0.9)))
-
-AccMega <- 50:1 %>%
-  map_df(~{
-    print(.x)
-    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train),ModForm =  as.formula(Reference~ + price))
-Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[.x]]$test))
-Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[.x]]$test))
-
-Confmat <- confusionMatrix(rowSums(Predsdf)/ncol(Predsdf)>0.5, as.data.frame(TestResample[[.x]]$test)$Reference)
-  BootOut <- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
-          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
-  mutate(ID = 1001)
-
-bind_rows(Accdf, BootOut) %>%
-  mutate(Sample = .x)
-  })
-
-CoeffsMega <- 50:1 %>%
-  map_df(~{
-    print(.x)
-    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train), ModForm =  as.formula(Reference~ + price))
-
-    #needs to be mapped again to extract every model not just the first 50!
-BootMod[[.x]] %>% tidy %>% mutate(ID = .x) %>%
-  mutate(Sample = .x)
-  })
-
-CoeffsMega <- CoeffsMega %>%
-  mutate(beats = p.value<0.05)
-
-CoeffsMega %>%
-  filter(term != "VacantsPerc", term != "(Intercept)") %>%
-  ggplot(aes(x = term, y = p.value, fill = term)) + geom_boxplot() + 
-  coord_cartesian(y = c(0,0.12))
-
-test<- CoeffsMega %>%
-  group_by(term) %>%
-  summarise_all(funs(mean, median))
-
-table((AccMega$Accuracy-AccMega$AccuracyNull)>0)/50050
-
-AccMega2 <- AccMega %>%
-  mutate(MajVote = ID == 1001)
-
-test <- AccMega2 %>%
-  group_by(MajVote) %>%
-  summarise_all(funs(mean, median))
-
-AccMega2 %>%
-  filter(ID == 1001) %>%
-  ggplot(aes(x = AccuracyPValue)) + geom_density()
-
-AccMega2 %>%
-  ggplot(aes(x = MajVote, y = Accuracy)) + geom_boxplot()
-
-median(AccMega$AccuracyPValue)
+MSOAModelSumm <- MSOAModels %>%
+  group_by(Dependent, Formula, type) %>%
+  summarise(BeatNull = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            meanAcc = mean(Accuracy), #What was the mean accuracy
+            NULLmod = mean(AccuracyNull),
+            DiffNull = mean(Accuracy-AccuracyNull), #Mean difference relative to NULL
+            StatistSignif = t.test(Accuracy,AccuracyNull, alternative = "greater", paired = T)$p.value) #Was Beat NUll statis
 
 ```
-
-#All England Bootstrap
-
-Can't be used as there is not enough power
-
-```{r}
-#Create model using all data
-Mod <- ModelMe %>% 
-  glm(OpenFormula, data = ., binomial(link='logit'))
-
-LadHomes <-  EW2 %>%
-  group_by(LAD11CD) %>%
-  summarise(Homes = sum(Homes, na.rm = TRUE),
-            Pop = sum(Pop, na.rm = TRUE))
-
-EnglandComp <- LADDep %>% 
-  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
-  left_join(., Vacants, by = "LAD11CD") %>%
-  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
-  left_join( LadHomes, by = "LAD11CD") %>%
-  ungroup %>%
-  #left_join(Rural, by = "LAD11CD") %>%
-  as.data.frame() %>%
-  mutate(VacantsPerc = Vacants/Homes,
-  #scaled so that the binomial can be interpreted
-  pricepercent = pricepercent %>% scale %>% as.numeric,
-         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
-         price = scale(price) %>% as.numeric,
-         Extent = scale(Extent) %>% as.numeric) %>%
-  mutate(Prob = predict(Mod, newdata = ., type ="response")) %>%
-  #merge on the truth
-  left_join(ModelMe %>% select(LAD11CD, Reference), by = "LAD11CD") %>%
-  mutate(BootCol = case_when(Reference == TRUE ~1,
-                             Reference == FALSE ~ 0,
-                             TRUE ~ Prob),
-         Comp.Type = Prob>0.5)
-
-BootPopHigh <-map2(EnglandComp$Pop, EnglandComp$BootCol, 
-            ~sample(c(.x, 0), size = 1000, 
-                    replace = TRUE,
-                    prob = c(.y, 1-.y)) %>%
-              as.tibble) %>%
-  bind_cols() %>%
-  rowSums() %>%
-  tibble(Pop=.) %>%
-  mutate(PercPop = Pop/sum(EnglandComp$Pop))
-
-BootPopHigh %>%
-  ggplot(aes(x = PercPop)) +
-  geom_density()
-
-#The 95 percent confidence interval of the mean
-QuantInfo<-quantile(BootPopHigh$Pop, probs = c(0.05, 0.5 ,0.95))
-quantile(BootPopHigh$PercPop, probs = c(0.05, 0.5 ,0.95))
-#diff is 3.6M
-QuantInfo[3]-QuantInfo[1]
-
-```
-
-#Vancouver Tax
-
-```{r}
-setwd(DataFolder)
-QRC2017<- read_xlsx("QRC4-2017-2018.xlsx", sheet = 2, skip = 2) %>%
-  select(3:4) %>%
-  set_names("LAD11CD", "CouncilTax") %>%
-  mutate(CouncilTax = CouncilTax*1000)
-
-EmptyTax <- Combine1ExO %>%
-  left_join(., QRC2017) %>%
-  mutate(EmptyTax = MeanLUPs*LUPS*0.01,
-         EmptyOfCouncil = EmptyTax/CouncilTax)
-
-sum(EmptyTax$EmptyTax)/1e6
-mean(EmptyTax$EmptyOfCouncil, na.rm = T)
-median(EmptyTax$EmptyOfCouncil, na.rm = T)
-
-sum(EmptyTax$EmptyTax)/sum(EmptyTax$CouncilTax)
-
-EmptyTax %>%
-  ggplot(aes(x =EmptyOfCouncil)) + geom_density() +
-  coord_cartesian(x=c(0,0.7)) +
-  scale_x_continuous(labels = scales::percent) +
-  labs(title = "Distribution of value of Empty homes tax in terms of council tax by local authority", 
-       x = "Percent of council tax value")
-
-EmptyTax %>%
-  select(EmptyOfCouncil, LAD) %>%
-  arrange(EmptyOfCouncil) %>%
-  top_n(5,EmptyOfCouncil)
-
-```
-
-#Plot stuff
-```{r}
-x <-bind_rows(SouthwarkLONDATA, TowerDATA, LambethLONDATA, CoLLONDATA, NewhamLONDATA) %>% MakeLeaflet
-
-z<- MakeLeaflet(AllerdaleDATA)
-z
-# 
-setwd(basewd)
- saveWidget(z, file=file.path(basewd, "Cumbria.html"), selfcontained = TRUE )
-
-#testSouth <- DistribCompareBootstrapper(SouthwarkLONDAls(pattern = "DATA")TA, 1652, 1000)
-testSouth %>% mutate(RatioExvsAct = (RatioExvsAct-1)*100) %>% 
-  ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + geom_boxplot() + 
-  labs(title = "Bootstrapped difference from expected number of low-use homes", y = "% difference from expected")
-
-ValueTtest(test)
-
-PlotMap(ConwyDATA)
-
-z <-ChelseaLONDATA %>% 
-  mutate(LAD11CD = ifelse(LAD11CD  == "E09000005", "E05009388" ,LAD11CD)) %>% #kept adding in Barnet
-  filter(LAD11NM =="Kensington and Chelsea") %>% 
-  MakeLeaflet()
-
-mapshot(z, file = file.path(Figures, "Chelsea.pdf"))
-
-CumbriaPlot <- ls(pattern = "CUMBRIA") %>% 
-  map_df(~get(.x)) %>%
-   group_by(LSOA_CODE) %>%
-   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
-  CalcLowUse()
-
-z<- MakeLeaflet(CumbriaPlot)
-
-mapshot(z, file = file.path(Figures, "Cumbria.pdf"))
-
-z<- MakeLeaflet(CornwallDATA)
-mapshot(z, file = file.path(Figures, "Cornwall.pdf"))
-
-z<- MakeLeaflet(BarrowCUMBRIADATA)
-mapshot(z, file = file.path(Figures, "Barrow.pdf"))
-
-MakeLeaflet(ConwyDATA)
-
-```

### 2018-08-09 Functions/BootstrapAllData.R

@@ -1,0 +1,29 @@
+BootstrapAllData <- function(DATAdf, GroupingVars = c("class", "classVal", "CountryClass"), Reps=501, LimitValue, RandomSeed = 1652){
+  PropertyTypes <- c("D", "S", "T", "F")  
+  #Find the length of each vector so that it can be sampled as quickly as possible
+  LADBootInfo <- DATAdf %>%
+    group_by(LAD11CD) %>%
+    summarise(LAD11NM = first(LAD11NM),
+              LSOA = n(),
+              Homes = sum(Homes),
+              LowUse = sum(LowUse)) %>%
+    arrange(Homes)
+  
+  #Find what needs to be bootstrapped
+  #The data is saved using LAD codes, this means it is not particularly Human readable but is more reliable.
+  newLADsnames <-  unique(DATAdf$LAD11CD)[!(unique(DATAdf$LAD11CD) %in% gsub(".rds", "",list.files(getwd())))] #finds the LAD codes I have and compares them to the LAD codes that are already completed
+  
+  #only bootstrap if there is something to add.
+  #Save each boostrap as you go along to avoid losing it all in a crash
+  if(length(newLADsnames)>0){
+    newLADsnames  %>% walk(~{print(.x)
+      DATAdf %>% 
+        filter(LAD11CD == .x) %>%
+        DistribCompareBootstrapper(., RandomSeed, Reps, type=NULL, PropertyTypes, Limit = LimitValue, GroupVars = GroupingVars ) %>%
+        saveRDS(., file = paste0(.x, ".rds"))
+      gc()
+    }) 
+  }
+  
+  
+}

### 2018-08-09 Functions/DistribCompareBootstrapper.R

@@ -1,4 +1,4 @@
-DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("class", "classVal", "CountryClass")){
+DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("class", "classVal", "CountryClass"), Limit = Inf){
   #df:data frame of processed area/s data
   #LADCD: The LAD code to fetch the correct price data
   # Random seed
@@ -6,65 +6,40 @@ DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, Prope
   #type: whether all purchese or only classes A or b are taken, enter a character "A" or "B" or leave NULL for all
   #GroupVars: the variables that will be used to summarise by group
   
-  dfPrice <- df %>%
-    filter(!is.na(Admin_ward_code)) %>%#filter(!is.na(Pop)) %>%#removes any NA rows which cause a crash
-    SubsetPrice(., type, PropertyTypes)
-  
+  #The function saves the sample of each LSOA to the working directory. This stops the computer crashing on large LADS All files are deleted aftwords. 
   
   dfWard <- df %>% 
-    group_by(LSOA11CD) %>%
+    group_by(LSOA11CD) %>%  #Remove double LSOA that may have sneaked in
     summarise_all(funs(first)) %>% 
-    group_by(LAD11CD) %>%
+    group_by(LAD11CD) %>% #Remove LAD data that is not from this lad. Occaisonly a few lsoa from other LADs get in and cause problems
     mutate(LADCount = n()) %>% ungroup %>%
     filter(!is.na(Admin_ward_code), LADCount == max(LADCount)) %>% #filter out any stray areas that are classed as a different authority
     select(-LADCount)  
   
-  #Function generated within the function to make sure both Homes and LUPs are calculated the same way.
-  StrappedLowUse <- function(WhichLowUse, Grouping){
-    Tempdf<- unique(dfWard$LSOA11CD) %>%
-      map_df(~{
-        #print(.x)
-        PriceData <- dfPrice %>% 
-          filter(LSOA11CD == .x)
-        #Sometimes an LSOA will have no sales in that year. In these thankfully rare cases the entire LAD is used.
-        if(nrow(PriceData)==0){
[…]

### 2018-08-09 Functions/DistribCompareBootstrapperSave.R

@@ -1,4 +1,5 @@
-DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("class", "classVal", "CountryClass")){
+DistribCompareBootstrapperSave <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("class", "classVal", "CountryClass")){
+  #This version is used for big files such as Birmingham. It is really slow but the computer doesn't crash
   #df:data frame of processed area/s data
   #LADCD: The LAD code to fetch the correct price data
   # Random seed
@@ -8,45 +9,57 @@ DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, Prope
   
   #The function saves the sample of each LSOA to the working directory. This stops the computer crashing on large LADS All files are deleted aftwords. 
   
-  dfPrice <- df %>%
-    filter(!is.na(Admin_ward_code)) %>%#filter(!is.na(Pop)) %>%#removes any NA rows which cause a crash
-    SubsetPrice(., type, PropertyTypes)
-  
-  
   dfWard <- df %>% 
-    group_by(LSOA11CD) %>%
+    group_by(LSOA11CD) %>%  #Remove double LSOA that may have sneaked in
     summarise_all(funs(first)) %>% 
-    group_by(LAD11CD) %>%
+    group_by(LAD11CD) %>% #Remove LAD data that is not from this lad. Occaisonly a few lsoa from other LADs get in and cause problems
     mutate(LADCount = n()) %>% ungroup %>%
     filter(!is.na(Admin_ward_code), LADCount == max(LADCount)) %>% #filter out any stray areas that are classed as a different authority
     select(-LADCount)  
   
+  
+  dfPrice <- dfWard %>%
+    filter(!is.na(Admin_ward_code)) %>%#filter(!is.na(Pop)) %>%#removes any NA rows which cause a crash
+    SubsetPrice(., type, PropertyTypes)
+  
   #Function generated within the function to make sure both Homes and LUPs are calculated the same way.
-  StrappedLowUse <-  function(WhichLowUse, Grouping){
-    Out <- 1:samples %>%
-      map_df(~{
-        print(.x)
-        Temp <- 1:length(unique(dfWard$LSOA11CD)) %>%
+  StrappedLowUse <- function(WhichLowUse, Grouping){
+    1:length(unique(dfWard$LSOA11CD)) %>%
+      walk(~{
[…]

### 2018-08-09 Functions/LoadBootstrapData.R

@@ -1,0 +1,11 @@
+LoadBootstrapData <-function(path= getwd()){
+  #Loads all the Bootrapped files into a named list
+  #Once all Bootratps complete load them all into a list
+  BootStrapRES <- list.files(path) %>%
+    map(~readRDS(.x))
+  
+  #Name the list by the LAD code
+  names(BootStrapRES) <- list.files(path) %>% gsub(".rds", "",.)
+  
+  return(BootStrapRES)
+}

### 2018-08-09 SubCode/AuxdataLoad.R

@@ -69,11 +69,11 @@ select(lsoa11cd, Admin_ward_code)
 
 EW2 <- inner_join(EW, lsoa, by = c("ECODE" = "LSOA11CD") ) %>%
   left_join(., wardlsoa, by = c("ECODE"="lsoa11cd") ) %>% 
-  left_join(., select(wardnames, Admin_ward_code, WD16NM), by = "Admin_ward_code") %>%
+  left_join(., select(wardnames, Admin_ward_code, WD16NM, Region = GOR10NM), by = "Admin_ward_code") %>%
   group_by(Admin_ward_code) %>%
   mutate(WardHomes = sum(Homes),  WardPop = sum(Pop)) %>% 
-  ungroup %>%
-  filter(grepl("E", ECODE))
+  ungroup #%>%
+ # filter(grepl("E", ECODE)) don't filter wales
 rm(wardlsoa)
 rm(wardnames)
 
@@ -124,7 +124,7 @@ if(file.exists("prices.rds")){
               by = c("X4"="Postcode")) %>%
     filter(!is.na(lsoa11cd)) %>%
     left_join(select(EW2, ECODE, MSOA11CD, LAD11CD), by =c("lsoa11cd"="ECODE")) %>% #Add in the MSOA code
-    filter(Country_code == "E92000001") %>%
+    #filter(Country_code == "E92000001") %>% keep in wales
     select(X2, X5, X3, X15, X16, Admin_ward_code, lsoa11cd, MSOA11CD, LAD11CD) %>%
     rename(LSOA11CD = lsoa11cd)
   
@@ -172,57 +172,62 @@ setwd(DataFolder)
 #is mean income estimates
 IncomeEst <- read_excel("1smallareaincomeestimatesdataupdate.xls", sheet = 4, skip = 4) %>%
 setNames(make.names(names(.)) %>% 
-gsub("\\.(?=\\.*$)", "", ., perl=TRUE)) #removes trailing full stop.
+gsub("\\.(?=\\.*$)", "", ., perl=TRUE)) %>% #removes trailing full stop
+  rename(LAD11CD = Local.authority.code,
+         LAD11NM = Local.authority.name,
+         MSOA11CD = MSOA.code,
+         MSOA11NM = MSOA.name) %>%
+  mutate(Yearly.income= 52 * Total.weekly.income)
 
-IncomeEst <- prices %>% 
-  filter(X5 %in% c("D", "S", "T", "F")) %>%
[…]

### 2018-08-09 SubCode/LOADandProcessLADData.R

@@ -1,0 +1,486 @@
+
+#This script cleans and processes all the Local authorities into a single data frame
+#loading is by region and county but they are not in alphabetical order... sorry
+
+
+setwd(file.path(RegionsComp, "Region North West"))
+
+#Cumbria
+
+print("Region North-west")
+
+BarrowCUMBRIADATA <- read_excel("Barrow-in-FurnessExemptionsLSOA.xlsx", sheet=1)[1:4]%>%  
+  StructureData(.,lowuse = c(2:6,8))
+
+SLakelandCUMBRIADATA <- read_excel("South LakelandExemptionsLSOA.XLSX", sheet=1)[,1:4] %>%
+  StructureData(., lowuse=2:9)
+
+#only inlcudes postcodes so the mergeing needs to be done manually
+CopelandCUMBRIADATA <- read_excel("CopelandFOI 5778 data 100517 CBC.XLSX", sheet=1) %>% 
+  mutate(Postcode = sub(" ", "", Postcode)) %>%
+  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
+  rename(Exemption.type=`Disc Type Ind`, LSOA_CODE = lsoa11cd) %>%
+  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
+  StructureData()
+
+
+EdenCUMBRIADATA <- read_excel("EdenDiscountsLSOA.xlsx"  , sheet=1)[1:4] %>%  
+  StructureData(.,lowuse = c(2:6,8))
+
+CarliseCUMBRIADATA <- read_excel("FOI 5846 5983-CarlisleDiscountsLSOA June 2017.xlsx"  , sheet=1)[1:4] %>%  
+  StructureData(.)
+
+AllerdaleCUMBRIADATA <- read_excel("F17.132_Copy of Allerdale discounts LSOA_170815.xlsx"  , sheet=1)[1:4] %>%  
+  StructureData(c(4:10))
+
+
+#Manchester
+
+OldhamMANCDATA <- read_excel("FOI 10635 OldhamDiscounts LSOA.xlsx", sheet = 1 )[c(1,4:6)] %>%  
+  StructureData(., c(5:6,8:11))
+
+ManchesterMANCDATA <- read_excel("ManchesterDiscountsLSOA.xlsx", sheet = 1 )[1:4] %>%  
+  StructureData(. )
+
[…]

### 2018-08-10 MSOAmodel.Rmd
Subset Bootstrapping
The previous bootstrap functions didn't have the LowUse homes as a subset of the regular homes. I have now chnaged the Strapped functions so that this is the case. Previously this meant that the LowUse and Homes were actually independent, this caused side effects especially on smaller geographys

@@
 
-```{r}
+#Calc Real Quantiles for all data
+
+This takes ages and gives an almost identical number to simple running quantiles on the whole dataset
+
+```{r Real Quantile Chunk}
 
@@
 AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)
+setwd(basewd)
 
-test <- LSOAPriceList %>% map_int(length(.x))
+saveRDS(AllDataQuartiles, "AllDataQuartiles.rds")
+
+test <-  AllDataQuartiles %>%
+   select(-X0.,-X100.) %>%
+   summarise_all(funs(mean, sd)) %>%
+   mutate(X25Perc = X25._sd/X25._mean,
+          X50Perc = X50._sd/X50._mean,
+          X75Perc = X75._sd/X75._mean)
+
+prices %>%
+   filter(X5 %in% c("D", "S", "T", "F")) %>%
+  pull(X2) %>% quantile()
 

### 2018-08-10 PaperCode.Rmd
Subset Bootstrapping
The previous bootstrap functions didn't have the LowUse homes as a subset of the regular homes. I have now chnaged the Strapped functions so that this is the case. Previously this meant that the LowUse and Homes were actually independent, this caused side effects especially on smaller geographys

@@
 source(file.path(SubCode, "LOADandProcessLADData.R"))
+
+#This is no longer needed
+rm(PstCdLSOA.raw)
 
@@
 
+#Calculate Quantiles
+
+ This is not the right way to do it but give almost identical values to the weighted sampled quantiles. 
+ if you don't believe me see "MSOAmodel.Rmd" section "Calc Real Quantiles for all data". It takes ages and you regret everything
+
+```{r}
+
+ PropertyTypes <- c("D", "S", "T", "F")   #I need to specify this is what is being included in write up
+
+  #Adds in Quantiles based on the LADs we have data for
+  prices <- prices %>%
+    mutate(CountryClass = cut(X2, 
+                              X2 %>% .[LAD11CD %in% unique(DATAdf$LAD11CD)] %>% quantile(.) %>%
+                                .[2:4] %>% c(0,., Inf), 
+                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
+                              right = F) %>% fct_relevel(., "Upper", after = 3))
+
+```
+
 ##Quartiles Bootstrap
@@
 BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501)
-BootStrapRes <- LoadBootstrapData()
+BootStrapQuartiles <- LoadBootstrapData()
 
@@
 setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
-BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501, GroupingVars = "MSOA11CD")
+BootstrapAllData(DATAdf, LimitValue = 2e5, Reps = 501, GroupingVars = "MSOA11CD")
 
-#Temporay untill the proper one is complete
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
-BootStrapRes <- LoadBootstrapData()
+BootStrapMSOA <- LoadBootstrapData()
 
@@
   df %>% 
-  group_by(ID, class) %>%
+  group_by(ID, Class) %>%
   summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
@@
   mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
-  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
+  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1) %>%
+    ungroup
 }
+
+test1 <- system.time(result <-  StrappedLowMem(dfPrice, dfWard, samples, Grouping = GroupVars))
+test2 <- system.time(result <-  StrappedHighMem(dfPrice, dfWard, samples, Grouping = GroupVars))
+
+LADS<-DATAdf%>%
+  group_by(LAD11CD) %>%
+  summarise(LAD11NM = first(LAD11NM)) %>%
+  arrange(LAD11NM)
 
@@
 
-CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
+test <- BootStrapQuartiles$E09000020
+
+test <-DistribCompareBootstrapper(DATAdf%>%filter(LAD11CD == "E09000020"), samples = 100)
+
+test2 <- test %>% 
+  mutate(LowUse = Homes) %>%
+  CleanForPlotClassDiff()
+
+test3 <-test%>%
+  group_by(ID)%>%
+  mutate(RatioExvsAct = Homes/sum(Homes)) %>%
+  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1) %>%
+    ungroup
+
+test2 %>% PlotClassDiff()
+
+CleanForPlotClassDiff(BootStrapQuartiles$E09000020)  %>%
   PlotClassDiff(., "Kensington and Chelsea")
@@
 #Plot for all data
-All_data_class <- BootStrapRES %>% 
+All_data_class <- BootStrapQuartiles %>% 
   bind_rows %>%
   select(CountryClass, ID, LowUse, Homes) %>%
-  rename(class = CountryClass)%>%
+  rename(class = CountryClass) %>%
   CleanForPlotClassDiff
+
+BootStrapQuartiles %>% 
+  bind_rows %>%
+  select(CountryClass, ID, LowUse, Homes) %>%
+  rename(class = CountryClass) %>%
+  #mutate(LowUse = Homes) %>%
+  CleanForPlotClassDiff %>% 
+  group_by(class) %>%
+  summarise_all(mean)
 

### 2018-08-10 Functions/BootstrapAllData.R

@@ -1,5 +1,5 @@
-BootstrapAllData <- function(DATAdf, GroupingVars = c("class", "classVal", "CountryClass"), Reps=501, LimitValue, RandomSeed = 1652){
-  PropertyTypes <- c("D", "S", "T", "F")  
+BootstrapAllData <- function(DATAdf, GroupingVars = c("class", "classVal", "CountryClass"), Reps=501, LimitValue, RandomSeed = 1652, PropertyTypes= c("D", "S", "T", "F") ){
+  
   #Find the length of each vector so that it can be sampled as quickly as possible
   LADBootInfo <- DATAdf %>%
     group_by(LAD11CD) %>%
@@ -16,11 +16,12 @@ BootstrapAllData <- function(DATAdf, GroupingVars = c("class", "classVal", "Coun
   #only bootstrap if there is something to add.
   #Save each boostrap as you go along to avoid losing it all in a crash
   if(length(newLADsnames)>0){
-    newLADsnames  %>% walk(~{print(.x)
+    1:length(newLADsnames)  %>% walk(~{
+      print(paste0("Bootstrapping ", LADBootInfo$LAD11NM[LADBootInfo$LAD11CD==newLADsnames[.x]],". LADs remaining ", length(newLADsnames)-.x))
       DATAdf %>% 
-        filter(LAD11CD == .x) %>%
+        filter(LAD11CD == newLADsnames[.x]) %>%
         DistribCompareBootstrapper(., RandomSeed, Reps, type=NULL, PropertyTypes, Limit = LimitValue, GroupVars = GroupingVars ) %>%
-        saveRDS(., file = paste0(.x, ".rds"))
+        saveRDS(., file = paste0( newLADsnames[.x], ".rds"))
       gc()
     }) 
   }

### 2018-08-10 Functions/DistribCompareBootstrapper.R

@@ -1,4 +1,4 @@
-DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("class", "classVal", "CountryClass"), Limit = Inf){
+DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, PropertyTypes = NULL, GroupVars = c("Class","CountryClass"), Limit = Inf){
   #df:data frame of processed area/s data
   #LADCD: The LAD code to fetch the correct price data
   # Random seed
@@ -18,51 +18,25 @@ DistribCompareBootstrapper <- function(df, seed, samples=100, type = NULL, Prope
   
   
   dfPrice <- dfWard %>%
-    filter(!is.na(Admin_ward_code)) %>%#filter(!is.na(Pop)) %>%#removes any NA rows which cause a crash
+    #filter(!is.na(Admin_ward_code)) %>%#filter(!is.na(Pop)) %>%#removes any NA rows which cause a crash
     SubsetPrice(., type, PropertyTypes)
 
+  #Not much difference in them poss around 17% (not tested a lot), which isn't the 10x speed up I'd hoped for
   if(sum(dfWard$Homes, na.rm = T)>Limit){
-    Strapped<- StrappedLowMem
-    print("Low Mem Mode, Go and make a cup of tea...maybe go to bed")
+    print("Low Mem Mode")
+    StrappedData <- StrappedLowMem(dfPrice, dfWard, samples, Grouping = GroupVars) 
+    
   }  else {
-    Strapped <- StrappedHighMem
     print("High memory usage Mode. can use lots of ram")
+    
+    StrappedData <- StrappedHighMem(dfPrice, dfWard, samples, Grouping = GroupVars)
+    
   }
 
-  
-  print("Start Bootstrapping Homes distribution")
-  #bootstraps LAD housing stock.
-  set.seed(seed)
-  dfWardHomesStrap1 <- Strapped(dfPrice, dfWard, samples, "Homes", Grouping = GroupVars)
-  
-  print("Start LUP distribution")
-  
-  #bootstraps LAD housing stock.
-  set.seed(seed)
-  dfWardLowUseStrap1 <- Strapped(dfPrice, dfWard, samples, "LowUse", Grouping = GroupVars)
-  
-  print("LUP distribution Complete")
-  
-  test1 <- dfWardHomesStrap1  %>%
[…]

### 2018-08-10 Functions/MatchPostCodes2LSOA.R

@@ -1,6 +1,6 @@
 MatchPostCode2LSOA<-function(ONSpostcodes, ONSpostcodeMeta){
   #Matches all postcodes to the relevant LSOA
-  #The function uses the ONS code point postcode data which can be found at
+  #The function uses the ONS code to point to postcode data which can be found at
   #https://www.ordnancesurvey.co.uk/business-and-government/products/code-point-open.html
   #This data set is updated regularly
   #ONSpostcodes: the path of the ONS postcodes CSVs

### 2018-08-10 Functions/PlotClassDiff.R

@@ -14,7 +14,7 @@ PlotClassDiff <-function(df, LAD = NULL){
                    "Upper" = "#00B0F6")
   
   df %>% 
-     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
+      ggplot(., aes(x= Class, y = RatioExvsAct, fill = Class)) + 
      geom_boxplot() + 
      labs(title = titlewords, 
           y = "% difference from expected", x= "Price Quartile") +

### 2018-08-10 Functions/StrappedHighMem.R

@@ -1,11 +1,14 @@
-StrappedHighMem <- function(dfPrice, dfWard, samples, WhichLowUse, Grouping){
+StrappedHighMem <- function(dfPrice, dfWard, samples, Grouping){
   #Is fast but uses a lot of memory
   #dfPrice: the prices for the local authority
   #dfWard the data for the local authority
   #samples: the number of bootstraps to be taken. This causes a crash when large due to lack of memory
   #WhichLowUse: The varaiable that will be used to get the number of bootstrap samples to draw.
   #Grouping: the variables that will be used for aggregating the resulting dataframe.
-  Temp <-  1:length(unique(dfWard$LSOA11CD)) %>%
+  
+  print("Start Bootstrapping Homes distribution")
+  
+  HomesTemp <-  1:length(unique(dfWard$LSOA11CD)) %>%
     map_df(~{
       LSOA <- unique(dfWard$LSOA11CD)[.x]
       
@@ -16,16 +19,41 @@ StrappedHighMem <- function(dfPrice, dfWard, samples, WhichLowUse, Grouping){
       if(nrow(PriceData)==0){
         PriceData<-dfPrice
       }
-      LowUseCounts <- sum(filter(dfWard, LSOA11CD == LSOA) %>% select_(WhichLowUse)) #sample rows from LSOA
+      Counts <- filter(dfWard, LSOA11CD == LSOA) %>% pull(Homes) #sample rows from LSOA
       
-      SampledData <-sample_n(PriceData, LowUseCounts*samples, replace = TRUE) %>%
+      SampledData <-sample_n(PriceData, Counts*samples, replace = TRUE) %>%
         mutate(ID = rep(1:samples, nrow(.)/samples))
       
     }
-    ) 
+    ) %>%
+    group_by(ID) %>%
+    mutate(Class = cut(Price, 
+                       Price %>% quantile(.) %>%
+                         .[2:4] %>% c(0,., Inf), 
+                       labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
+                       right = F) %>% fct_relevel(., "Upper", after = 3))
+  
+  print("Start LUP distribution")
+  
+  #This is annyngky slow as it has to sample from a large number of specific sets.
+  #Using a different numbe each time making it difficult to vectorise.
+  LowUseTemp <- 1:length(unique(dfWard$LSOA11CD)) %>% map_df(~{
[…]

### 2018-08-10 Functions/StrappedLowMem.R

@@ -8,7 +8,7 @@ StrappedLowMem <-  function(dfPrice, dfWard, samples, WhichLowUse, Grouping){
   Out <- 1:samples %>%
     map_df(~{
       print(.x)
-      Temp <- 1:length(unique(dfWard$LSOA11CD)) %>%
+      HomesTemp <- 1:length(unique(dfWard$LSOA11CD)) %>%
         map_df(~{
           LSOA <- unique(dfWard$LSOA11CD)[.x]
           
@@ -19,17 +19,36 @@ StrappedLowMem <-  function(dfPrice, dfWard, samples, WhichLowUse, Grouping){
           if(nrow(PriceData)==0){
             PriceData<-dfPrice
           }
-          LowUseCounts <- sum(filter(dfWard, LSOA11CD == LSOA) %>% select_(WhichLowUse)) #sample rows from LSOA
+          LowUseCounts <- filter(dfWard, LSOA11CD == LSOA) %>% pull(Homes) #sample rows from LSOA
           
           SampledData <-sample_n(PriceData, LowUseCounts, replace = TRUE)
           
           SampledData  
         }
-        ) %>% 
-        mutate(ID = .x,
-               LADmedian = median(Price, na.rm = T),
+        ) %>%
+        mutate(Class = cut(Price, 
+                           Price %>% quantile(.) %>%
+                             .[2:4] %>% c(0,., Inf), 
+                           labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
+                           right = F) %>% fct_relevel(., "Upper", after = 3))
+      
+      
+      LowUseTemp <-  1:length(unique(dfWard$LSOA11CD)) %>% map_df(~{
+        
+        
+        LSOA <- unique(dfWard$LSOA11CD)[.x]
+        CurrentHomes <- HomesTemp %>% filter(LSOA11CD == LSOA) 
+        Counts <- filter(dfWard, LSOA11CD == LSOA) %>% pull(LowUse)
+        
+        SampledData <-CurrentHomes %>%
+          sample_n( Counts, replace = FALSE) #This is a strict subset of the Homes data not a bootstrap!
+        
+      })
+      
+      HomesTemp <- HomesTemp %>% 
+        mutate(LADmedian = median(Price, na.rm = T),
                LADmean = mean(Price, na.rm = T))   %>%
-        group_by_(.dots = c("ID", Grouping)) %>%
+        group_by_(.dots = c(Grouping)) %>%
         summarise(Counts = n(),
                   Value = sum(Price),
[…]

### 2018-08-10 Functions/SubsetPrice.R

@@ -1,4 +1,4 @@
-SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, Quantiles = NULL){
+SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL){
   #Subsets the price frame to be just for the specific LAD
   #Takes either the DATA dataframe or the character string LAD11CD
   #this allows the subsetting of the price list without looking up the LAD code
@@ -25,21 +25,12 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL, Quantiles = NULL)
     pricesTemp <- pricesTemp %>%
       filter(X5 %in% PropertyTypes)
   }
-  
-  if(is.null(Quantiles)){
-    Quantiles<-c(0, quantile(pricesTemp$X2)[2:4], Inf)
-  }
+
 
   #The  model used to take multiple councils if there was overlap, but this caused some strange
   #Problems So I removed it. The current version only takes a single LAD
   pricesTemp %>%
-    select(Admin_ward_code, LSOA11CD, Price =X2, X15, PropType = X5, CountryClass, MSOA11CD) %>%
-    mutate(class = cut(Price, Quantiles, 
-                       labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
-                       right = F) %>% fct_relevel(., "Upper", after = 3),
-           classVal = cut(Price, Quantiles, 
-                          labels =     c(Quantiles[2:4], paste0("x>", Quantiles[5])), 
-                          right = F),
-           Price = as.numeric(Price)) #there was some number overflow thing changing to numeric solves this
+    select( LSOA11CD, Price =X2, X15, PropType = X5, CountryClass, MSOA11CD) %>%
+    mutate(Price = as.numeric(Price)) #there was some number overflow thing changing to numeric solves this
   
 }

### 2018-08-12 MSOAmodel.Rmd
Simplify Bootstrapping
I refactored the code for bootstrapping and sampling. This made it easier to understand and allowed me to have a single strapping function that can be modified for high or low memory usage.
I also fine tuned the quantiles

@@
 ```{r}
+
+#Create a data frame of LSO
 PriceCounts <-prices %>%
@@
   arrange(counts)
-
+##The subsampling is 1/10 of the number of homes in each LSOA, this stops crashes
 PriceCounts<- EW2 %>%
@@
 
-#Create a list of vectors by LSOA
+#Create a list of price vectors by LSOA
+#This process can take a while
 setwd(basewd)
+if(file.exists("LSOAPriceList2.rds")){
+
+  LSOAPriceList <- readRDS("LSOAPriceList2.rds")
+
+}else{
+
   LSOAPriceList <- 1:nrow(PriceCounts) %>% map(~{
@@
     })
-
   names(LSOAPriceList) <- PriceCounts$LSOA11CD
@@
 
-LSOAPriceList <- readRDS("LSOAPriceList2.rds")
+}
+
+if(file.exists("AllDataQuartiles.rds")){
+
+  AllDataQuartiles <- readRDS("AllDataQuartiles.rds")
+
+}else{
+  #Subset list to only the LADs used in analyis
+  LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
+  PriceCounts2 <- PriceCounts %>%
+    filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))
+
+  AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)
+
+  saveRDS(AllDataQuartiles, "AllDataQuartiles.rds")
+
+  rm(list = c("LSOAPriceList2", "PriceCounts2"))
+
+}
+
+rm(LSOAPriceList)
+
+AllDataQuartilesSummary <- AllDataQuartiles %>%
+  summarise_all(funs(mean, sd))
+
+BasicQuartiles <- prices$X2 %>% .[prices$LAD11CD %in% unique(DATAdf$LAD11CD)] %>% quantile(.)
+
+#difference between the two up to 8% this has knock on effects later in the analysis if the quartiles are not calculated correctly
+AllDataQuartilesSummary[2:4]/BasicQuartiles[2:4]
+
+prices <- prices %>%
+  mutate(CountryClass = cut(X2, AllDataQuartilesSummary[2:4] %>% c(0,., Inf), 
+                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
+                              right = F) %>% fct_relevel(., "Upper", after = 3))
+
+rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary)
 
@@
 ```{r Real Quantile Chunk}
-
-StratifiedBoot <- function(dataList, LSOAcode, SamplesVect, samples = 1000){
-  #datadf
- 1: samples %>% map_df(~{
-   print(.x)
-  SubData <- 1:length(LSOAcode) %>% map(~{
-    #print(.x)
-    dataList[[LSOAcode[.x]]] %>%
-      sample(., SamplesVect[.x], replace = TRUE)
-
-    }) %>% unlist
-
-  SubData%>%
-       quantile(.) %>% t %>% as.data.frame %>% setNames(names(.) %>% make.names) %>%
-      mutate(mean = mean(SubData),
-             ID = .x)
- }) 
-}
-
-#Subset list to only the LADs used in analyis
-LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
-PriceCounts2 <- PriceCounts %>%
-  filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))
-
-AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, PriceCounts2$LSOA11CD, PriceCounts2$Homes2, samples = 501)
-setwd(basewd)
-
-saveRDS(AllDataQuartiles, "AllDataQuartiles.rds")
 
@@
 
+#Complex models
+
+These models work at MSOA level only and include data from the LAD level
+Tehy are rubbish so aren't included in the main work. Just kept here so I don't forget I have already checked.
+
 ```{r}
-LupPerc <- ls(pattern= "DATA") %>% map_df(~{
-  get(.x) %>% select(MSOA11CD, LowUse, Homes)
 
-}) %>%
-  group_by(MSOA11CD) %>%
-  summarise_all(sum) %>%
-  mutate(LowUsePerc = LowUse/(LowUse+Homes),
-         Q1 = LowUsePerc>0.033,
-         Q2 = LowUsePerc>0.02,
-         Top90 = LowUsePerc>0.058)
+DATAdf %>%
+  arrange(LAD11NM) %>% pull(LAD11NM) %>% unique
 
-#Top quartile of LUPS
-quantile(LupPerc$LowUsePerc)
-quantile(LupPerc$LowUsePerc, prob = seq(0, 1, length = 11))
+MSOAMean2 <-MSOAMean %>%
+  mutate(RelativeAfford = AffordRatio/LADAffordRatio,
+         RelativeTourismDens = TourismDensity/LADTourismDensity,
+         RelativeTourismDens = ifelse(is.finite(RelativeTourismDens), RelativeTourismDens, 100)) %>%
+  filter(!is.na(HighVal)) #Temporary  until I work out how to get rid of those weird MSOA
 
-MSOABootQuartiles2 <- MSOABootQuartiles %>%
-   select(-X0.,-X100.) %>%
-   group_by(MSOA11CD) %>%
-   summarise_all(funs(mean, sd)) %>%
-   mutate(X25Perc = X25._sd/X25._mean,
-          X50Perc = X50._sd/X50._mean,
-          X75Perc = X75._sd/X75._mean)  %>%
-   left_join(., EW2%>%
-               select(MSOA11CD, LAD11CD, LAD11NM) %>% distinct()) %>%
-   left_join(., IncomeEst) %>%
-   select(MedianPrice=X50._mean, Yearly.income, MSOA11CD, LAD11CD, LAD11NM)  %>%
-  left_join(LocalAfford, by = "MSOA11CD") %>%
-  left_join(LupPerc, by = "MSOA11CD")%>%
-  filter(!is.na(LowUse)) %>%
-   mutate(AffordRatio = MedianPrice/Yearly.income,
-          AffordLocalRatio = AffordRatio/LocalAfford,
-          AffordRank = percent_rank(AffordRatio),
-          AffordLocalRank = percent_rank(AffordLocalRatio),
-          LowUseRank = percent_rank(LowUse)>0.75)
+KitchenSink <- as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2+ RelativeAfford +RelativeTourismDens+
+                            LADTourismDensity+ LADAffordRatio+ LADAffordRatio2)
 
-MSOABootQuartiles2 %>%
-  ggplot(aes(x= AffordRatio , y = AffordLocalRatio, colour = LowUseRank)) + geom_point()
+KitchenSink2 <- as.formula(Reference ~RelativeAfford +RelativeTourismDens+
+                            LADTourismDensity+ LADAffordRatio)
+Formulas2 <- c(as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2),
+               KitchenSink)
+
+set.seed(1983)
+TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean2 , c(test = 0.2, train = 0.8)))
+
+MSOAModels2 <-LinearClassifierCombiner(MSOAMean2,  Outcomes, Formulas2, TestResample) %>%
+  mutate(IncAfford2 = grepl("2", Formula),
+           LAD = grepl("LAD", Formula)
+         )
+
+#No difference
+MSOAModels2 %>%
+  group_by(Dependent, IncAfford2, LAD) %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            ) %>%
+  ungroup %>%
+   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value"))
+
+library(ranger)
+
+#Just under 78% better than all other models
+ResOut <- MSOAMean2 %>%
+  mutate(Reference = HighLUP) %>% 
+  TreeResampledModelPerf(., TestResample, KitchenSink)
+
+ResOut2 <- MSOAMean2 %>%
+  mutate(Reference = HighLUP) %>%
+  TreeResampledModelPerf(., TestResample, KitchenSink2)
+
+ResOut %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            )
+
+ResOut2 %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            )
 
@@
 
-#Quadrant
+```{r}
+#This model uses information from the over all LUP as a result I need to subset the data by lups then train on the MSOA
+set.seed(1983)
+TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))
 
-```{r}
-  BootDeets <- BootStrapRES %>% map_df(~.x %>% group_by(ID) %>%
-                                    summarise(MedianHomes = first(MedianHomes),
-                                              MeanHomes = first(MeanHomes),
-                                              MedianLUPs = first(MedianLUPs),
-                                              MeanLUPs = first(MeanLUPs),
-                                              LAD11CD= first(LAD11CD),
-                                              HighVal = sum(HighVal),
-                                              Homes = sum(Homes),
-                                              LowUse = sum(LowUse)) %>%
-                                    group_by(LAD11CD) %>%
-                                    summarise_all(., mean, na.rm = TRUE) %>%
-                                      select(-ID)
+ComplexModels <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
+  map_df(~{
+    print(.x)
+    ResOut2 <- MSOAMean2 %>%
+      rename_(Reference = .x) %>%
+      TreeResampledModelPerf(., TestResample, KitchenSink, CombineData = TRUE) %>%
+      mutate(Dependent = .x)
+})
+
+ComplexModels %>%
+  group_by(Dependent) %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
             )
 
-BootDeets2 <- BootDeets %>%
-  mutate(MedianPercDiff = (MedianLUPs-MedianHomes)/MedianHomes,
-         PercLowUse = LowUse/Homes,
-         RankLowUse = percent_rank(PercLowUse),
-         RankMedianDiff = percent_rank(MedianPercDiff),
-         Catagory = case_when( 
-           RankLowUse>=0.5 & RankMedianDiff>=0.5 ~ 1, #High low use and High price difference
-           RankLowUse>=0.5 & RankMedianDiff<0.5 ~ 2, #High low Use and Low rank price difference
-           RankLowUse<0.5 & RankMedianDiff>=0.5 ~3, # Low low use and high price difference
-           TRUE ~ 4 #Low low use low price difference
-         ) %>% as.factor)%>%
-  left_join(EW2 %>%
-  group_by(LAD11CD, LAD11NM) %>%
-  summarise(TotMSOA = n(),
-         Homes = sum(Homes)) %>%
-  arrange(-TotMSOA) %>%
-  summarise(TotMSOA = first(TotMSOA),
-            LAD11NM = first(LAD11NM)), by = "LAD11CD")
+KitchenSink2 <- as.formula(Reference ~RelativeAfford +RelativeTourismDens+
+                            LADTourismDensity+ LADAffordRatio)
 
-BootDeets2 %>%
-  ggplot(aes(x= RankLowUse, y = RankMedianDiff, colour = Catagory)) + geom_point()
+ComplexModels2 <- c("BothHighLUP", "BothHighVal", "MSOALUPLADVal", "LADHighLUP", "HighLUP", "LADHighVal") %>%
+  map_df(~{
+    print(.x)
+    ResOut2 <- MSOAMean2 %>%
+      rename_(Reference = .x) %>%
+      TreeResampledModelPerf(., TestResample, KitchenSink2, CombineData = TRUE) %>%
+      mutate(Dependent = .x)
+})
 
-test <- MSOABootQuartiles2 %>%
-  left_join(select(BootDeets2, LAD11CD, Catagory), by = "LAD11CD")
+ComplexModels2 %>%
+  group_by(Dependent) %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            )
 
- %>%
-  ggplot(aes(x= AffordRank , y = AffordLocalRank, colour = Catagory)) + geom_point()
+Modeldf <-MSOAMean2 %>%
+      rename_(Reference = "LADHighLUP")
 
 ```
+
+#Collaspy tree voting
+```{r}
+
+test <- MSOAMean2 %>%
+      rename_(Reference = "LADHighLUP") %>%
+MSOATreeVoting(., TestResample, KitchenSink )
+
+test %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            )
+
+```

### 2018-08-12 PaperCode.Rmd
Simplify Bootstrapping
I refactored the code for bootstrapping and sampling. This made it easier to understand and allowed me to have a single strapping function that can be modified for high or low memory usage.
I also fine tuned the quantiles

--- 2018-08-09 PaperCode.Rmd
@@
 ---
+Mang en natt har jeg sittet opp og skrevet dype romaner paa dette skrivebordet.
+Det er pent brukt, men har gitt meg graa haar.
+Det er som min Moby Dick, jeg har aldri helt klart aa temme det, boken er halvskrevet, hodet fult, hjertet tomt.
+Derfor maa det bort, kona orker ikke at jeg sitter oppe og stirrer paa uskrevne linjer i min moleskinen mer.
 
@@
 TexTables <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Empty Homes Write up 2/Tables"
-source(file.path(CommonCode, "AuxdataLoad.R"))
+suppressMessages(source(file.path(CommonCode, "AuxdataLoad.R")))
 ```
@@
 #creates a data frame called DATAdf
-source(file.path(SubCode, "LOADandProcessLADData.R"))
+suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))
 
+rm(PstCdLSOA.raw)
 ```
@@
 
+rm(DataCover)
+
+```
+
+#Calculate Quantiles
+
+This rather long winded way of getting the quartiles is important as it weights the sampling by Homes in an area.
+Relative proportion of sales in an area is not the same as homes.
+Some areas have higher turnover other lower.
+This means the quartiles need to be repeatedly sampled to get the right quartiles for the whole dataset.
+
+In the below chunk I have sampled the data 501 times, however it is only necessary to sample one the quartiles don't change.
+
+```{r}
+
+#Create a data frame of LSO
+PriceCounts <-prices %>%
+  filter(X5 %in% c("D", "S", "T", "F")) %>%
+  group_by(LSOA11CD) %>%
+  summarise(counts = n()) %>%
+  arrange(counts)
+##The subsampling is 1/10 of the number of homes in each LSOA, this stops crashes
+PriceCounts<- EW2 %>%
+  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
+  left_join(.,PriceCounts, by = "LSOA11CD") %>%
+  mutate(counts = ifelse(is.na(counts), 0, counts),
+         Homes2 = Homes/10) %>%
+  filter(counts!=0)
+
+#Create a list of price vectors by LSOA
+#This process can take a while
+setwd(basewd)
+if(file.exists("LSOAPriceList2.rds")){
+
+  LSOAPriceList <- readRDS("LSOAPriceList2.rds")
+
+}else{
+
+  LSOAPriceList <- 1:nrow(PriceCounts) %>% map(~{
+   print(.x)
+    prices %>%
+      filter(LSOA11CD==PriceCounts$LSOA11CD[.x], 
+             X5 %in% c("D", "S", "T", "F")) %>%
+      pull(X2)
+    })
+  names(LSOAPriceList) <- PriceCounts$LSOA11CD
+  saveRDS(LSOAPriceList, "LSOAPriceList2.rds")
+
+}
+
+if(file.exists("AllDataQuartiles.rds")){
+
+  AllDataQuartiles <- readRDS("AllDataQuartiles.rds")
+
+}else{
+  #Subset list to only the LADs used in analyis
+  LSOAPriceList2 <- LSOAPriceList[names(LSOAPriceList) %in% unique(DATAdf$LSOA11CD)]
+  PriceCounts2 <- PriceCounts %>%
+    filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))
+
+  AllDataQuartiles <- StratifiedBoot(LSOAPriceList2, 
+                                     PriceCounts2$LSOA11CD, 
+                                     PriceCounts2$Homes2, 
+                                     samples = 501) #change to 1 for a quicker solution has no effect on outcome
+
+  saveRDS(AllDataQuartiles, "AllDataQuartiles.rds")
+
+  rm(list = c("LSOAPriceList2", "PriceCounts2"))
+
+}
+
+AllDataQuartilesSummary <- AllDataQuartiles %>%
+  summarise_all(funs(mean, sd))
+
+BasicQuartiles <- prices$X2 %>% .[prices$LAD11CD %in% unique(DATAdf$LAD11CD)] %>% quantile(.)
+
+#difference between the two up to 8% this has knock on effects later in the analysis if the quartiles are not calculated correctly
+AllDataQuartilesSummary[2:4]/BasicQuartiles[2:4]
+
+#Add the balanced quartiles on to the prices.
+prices <- prices %>%
+  mutate(CountryClass = cut(X2, AllDataQuartilesSummary[2:4] %>% c(0,., Inf), 
+                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
+                              right = F) %>% fct_relevel(., "Upper", after = 3))
+
+rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary);rm(LSOAPriceList)
+
 ```
@@
 ```{r}
-
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapQuartiles")
-BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501)
-BootStrapRes <- LoadBootstrapData()
+setwd(file.path(basewd, "BootstrapQuartiles"))
+BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501)
+BootStrapQuartiles <- LoadBootstrapData()
 
@@
 ```{r}
-
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
-BootstrapAllData(DATAdf, LimitValue = 1.3e5, Reps = 501, GroupingVars = "MSOA11CD")
-
-#Temporay untill the proper one is complete
-setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA2")
-BootStrapRes <- LoadBootstrapData()
+setwd(file.path(basewd, "BootstrapMSOA"))
+BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")
+BootStrapMSOA <- LoadBootstrapData()
 
@@
 
-##This will need to be re-worked when the quartiles are put in and the data is re bootstrapped
-
 ```{r}
@@
   df %>%  
-  group_by(ID, class) %>%
-  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
+  group_by(ID, Class) %>%
+  summarise(Homes = sum(Homes), 
+            LowUse = sum(LowUse)) %>%
   group_by(ID)%>%
-  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
-  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
+  mutate(LowUseDistrib = LowUse/sum(LowUse),
+         HomesDistrib = Homes/sum(Homes)) %>%
+  mutate(LowUseRatio1 = (LowUseDistrib/0.25)-1,
+         HomesRatio1 = (HomesDistrib/0.25)-1,
+         LowUseRatio2 = (LowUseDistrib-HomesDistrib)/HomesDistrib) %>%
+    ungroup
 }
 
-#I think I should have 1 plot with high value skew, one plot with low value skew and 1 plot for all data
-#These three plots should be shown as a panel of data
-
-CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
-PlotClassDiff(., "Kensington and Chelsea")
-SaveFig("ClassdiffChelsea.pdf")
-
-CleanForPlotClassDiff(BootStrapRES$BarrowCUMBRIA) %>% #maybe choose a better place than barrow?
-PlotClassDiff(., "Barrow")
-SaveFig("ClassdiffBarrow.pdf")
+LADS<-DATAdf%>%
+  group_by(LAD11CD) %>%
+  summarise(LAD11NM = first(LAD11NM)) %>%
+  arrange(LAD11NM)
 
 #Plot for all data
-All_data_class <- BootStrapRES %>% 
+All_data_class <- BootStrapQuartiles %>% 
   bind_rows %>%
   select(CountryClass, ID, LowUse, Homes) %>%
-  rename(class = CountryClass)%>%
-  CleanForPlotClassDiff
+  rename(Class = CountryClass)
 
-All_data_class %>% group_by(class) %>%
-  summarise_all(mean)
+BootStrapQuartiles$E09000020  %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
+BootStrapQuartiles$E08000032 %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
+All_data_class %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "LowUseRatio2")
 
-PlotClassDiff(All_data_class)
+#All data summary
+All_data_class %>% 
+  group_by(Class,ID) %>%
+  summarise_all(sum) %>%
+  group_by(Class) %>%
+  summarise_all(mean) %>%
+  CleanForPlotClassDiff()
+
+#Create multi panel plot for two areas and all data
+bind_rows(
+CleanForPlotClassDiff(BootStrapQuartiles$E09000020) %>% mutate(Area = "Kensington and Chelsea"),
+CleanForPlotClassDiff(BootStrapQuartiles$E08000032) %>% mutate(Area = "Bradford"),
+CleanForPlotClassDiff(All_data_class) %>% mutate(Area = "All Data")
+) %>%
+  mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
+  PlotClassDiff(Var = "LowUseRatio1") +
+    facet_wrap(.~Area) +
+  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
 SaveFig("ClassdiffAllData.pdf")
 
+rm(BootStrapQuartiles);rm(All_data_class)
 ```
@@
 ```{r}
-
-CorePstCd <- PstCdLSOA.raw %>%
-  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
-  select(Postcode,LSOA11CD= lsoa11cd, LAD11CD, LAD11NM, MSOA11CD, Pop)
-
 setwd(file.path(basewd, "VOA data"))
@@
 
-HArtlePool E06000001
-COl E02000001
 ```{r}
-LADModelData <-CreateGeogModelData("LAD", "/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")
-LADMean<- MeanModelData(LADModelData, "LAD") %>%
+LADModelData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapMSOA"))
+LADMean <- MeanModelData(LADModelData, "LAD") %>%
   mutate(AffordRank2 = scale(AffordRank)^2,
-         TourismDensityRank = rank(TourismDensity, ties.method = "max"))
+           AffordRatio2 = scale(AffordRatio)^2,
+         TourismDensityRank = rank(TourismDensity, ties.method = "max"),
+         LowUseType =case_when(
+    "TRUE"==HighLUP & "TRUE" ==HighVal ~ 1, # All high
+    "TRUE" == HighLUP & "FALSE" ==HighVal ~ 2, #High LUP in MSOA but not in LAD
+    "FALSE"==HighLUP & "TRUE" ==HighVal ~ 3, #High LUP in LAD but not MSOA
+    "FALSE"==HighLUP & "FALSE"==HighVal ~ 4 #LOW LUP in both LAD and MSOA
+  ) %>% as.factor,
+  LowUseAfford =case_when(
+    "TRUE"==HighLUP & AffordRank>=0.5 ~ 1, # All high
+    "TRUE" == HighLUP & AffordRank<0.5 ~ 2, #High LUP in MSOA but not in LAD
+    "FALSE"==HighLUP & AffordRank>=0.5 ~ 3, #High LUP in LAD but not MSOA
+    "FALSE"==HighLUP & AffordRank<0.5 ~ 4 #LOW LUP in both LAD and MSOA
+  ) %>% as.factor)  %>%
+  left_join(MSOAtoLAD %>%
+              group_by(LAD11CD) %>%
+              summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")
 
   LADMean %>%
-  ggplot(aes(x= AffordRank, y = TourismDensityRank, colour = HighVal)) + geom_point()
-
-  LADMean %>%
-  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = HighVal)) + geom_point()
+  ggplot(aes(x= AffordRank, y = LowUseRank, colour = LowUseAfford)) + geom_point() +
+    geom_vline(xintercept  = 0.5)+
+    geom_hline(yintercept = 0.5) +
+    labs(title = "Seperating Low-Use type  by affordability", x = "Affordability percentage rank", y = "Low-Use percentile rank")
+  SaveFig("LowUseAffordcolour.pdf")
 
@@
 ```{r}
-
-MSOAModelData <-CreateGeogModelData("MSOA", "/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA") 
+MSOAModelData <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapMSOA")) 
 MSOAMean <- MeanModelData(MSOAModelData, "MSOA") %>%
@@
   mutate(AffordRank2 = scale(AffordRank)^2,
-         TourismDensityRank = rank(TourismDensity, ties.method = "max"))
+         AffordRatio2 = scale(AffordRatio)^2,
+         TourismDensityRank = rank(TourismDensity, ties.method = "max")) %>%
+  left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
+                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatio2,
+                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff), by = "LAD11CD") %>%
+  mutate(BothHighLUP =case_when(
+    "TRUE"==HighLUP & "TRUE" ==LADHighLUP ~ 1, # all high
+    "TRUE" == HighLUP & "FALSE" ==LADHighLUP ~ 2, #High LUP in MSOA but not in LAD
+    "FALSE"==HighLUP & "TRUE" ==LADHighLUP ~ 3, #High LUP in LAD but not MSOA
+    "FALSE"==HighLUP & "FALSE"==LADHighLUP ~ 4 #LOW LUP in both LAD and MSOA
+  ) %>% as.factor,
+  BothHighVal =case_when(
+    "TRUE" ==HighVal & "TRUE" ==LADHighVal ~ 1, # all high
+   "TRUE" == HighVal & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
+    "FALSE"==HighVal & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
+    "FALSE"==HighVal & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
+  ) %>% as.factor,
+  MSOALUPLADVal =case_when(
+    "TRUE" ==HighLUP & "TRUE" ==LADHighVal ~ 1, # all high
+   "TRUE" == HighLUP & "FALSE"==LADHighVal ~ 2, #High LUP in MSOA but not in LAD
+    "FALSE"==HighLUP & "TRUE" ==LADHighVal ~ 3, #High LUP in LAD but not MSOA
+    "FALSE"==HighLUP & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
+  ) %>% as.factor
+           )
 
  MSOAMean %>%
+   #filter(TourismDensity!= 0) %>%
+  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point()
+
+  MSOAMean %>%
+   #filter(TourismDensity!= 0) %>%
+  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighLUP)) + geom_point()
+
+   MSOAMean %>%
+   filter(TourismDensity!= 0) %>%
   ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point()
@@
       MSOAMean %>%
-  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = HighVal)) + geom_point()
+   filter(TourismDensity!= 0) %>%
+  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighVal)) + geom_point()
 
-  #Great results for the MSOA model predicting High LUP numbers
-  ModelFormula <- as.formula(Reference ~ TourismRank+ AffordRank+ AffordRank2)
+  MSOAMean %>%
+  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = BothHighVal)) + geom_point()
 
@@
 
-#Price affordability correlation
+Plots that help explain the data seperation
+```{r}
+bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
+  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point() +
+  facet_wrap(~type) + 
+  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Density") +
+  guides(fill=guide_legend(title="Above Median"))
+SaveFig("HighLUP.pdf")
 
-Why is there such a large difference between price and affordability at lad level and MSOA level  is this a mistake?
-```{r}
+bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
+  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point() +
+  facet_wrap(~type) + 
+  labs(title = "Is the median LUP price higher than the Median price of all properties", x = "Affordability Rank", y = "Tourism Density") +
+  guides(fill=guide_legend(title="Above Median"))
+SaveFig("HighVal.pdf")
 
-cor(LADMean$AffordRatio, LADMean$HomesMedian)
-cor(MSOAMean$AffordRatio, MSOAMean$HomesMedian)
 ```
@@
 
-#LAD Model
+#Model Combinations
 
-works well at predicting high numbers of LUPs
- ModelFormula <- as.formula(Reference ~ TourismDensityRank + AffordRank)
+The below are the combinations of formula and outcome variable
 
@@
 
+Outcomes <- c("HighVal", "HighLUP")
+OutcomesLinear <- c("LowUsePerc", "MedianDiff")
+
+Formulas <- c(as.formula(Reference ~ AffordRatio),
+   as.formula(Reference ~ TourismDensity + AffordRatio),
+      as.formula(Reference ~ AffordRatio + AffordRatio2),
+   as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatio2))
+
+```
+
+#LAD Model
+
+```{r}
+
+cv <- tidy(vfold_cv(mtcars, v = 5))
+
+cv <- tidy(vfold_cv(mtcars, v = 5, repeats = 2))
+
+#Create sample
 set.seed(1983)
@@
 
-#Make a lot of models
+#Create a load of classifiers
+LADModels <- LinearClassifierCombiner(LADMean,  Outcomes, Formulas, TestResample) %>%
+  mutate(IncAfford2 = grepl("2", Formula),
+           IncTourism = grepl("Tourism", Formula)
+         )
 
-Combos<-expand.grid(1:2,1:2)
-
-LADModels <- map2_df(.x = c("HighVal", "HighLUP")[Combos[,1]], .y = c(as.formula(Reference ~ HomesMedianRank+ AffordRank), 
-                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank))[Combos[,2]],
-        ~{
-          print(paste(.x,.y))
-          LADMean %>% #LADMean %>%
-    rename_(Reference = .x ) %>%
-  ResampledModelPerf(., TestResample,  .y) %>%
-            mutate(Dependent = .x,
-                   Formula = toString(.y))
-
-        } ) %>%
-  mutate(Formula = ifelse(grepl("Tourism", Formula), "Tourism", "Price"))
-
-MODOut <- 1:length(TestResample) %>% map_df(~{
-  Mod2 <- LADMean  %>%
-    rename(Reference = HighVal) %>%
-  mutate(Reference = as.factor(Reference)) %>%
-  slice(as.integer(TestResample[[.x]]$train)) %>%
-  glm(formula = as.formula(Reference ~ TourismDensityRank+ AffordRank), data = ., family=binomial(link='logit'))%>%
-    tidy
-
-})
-
-ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+#Create a load of linear models
+LADModelsLin <- LinearClassifierCombiner(LADMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
+  mutate(IncAfford2 = grepl("2", Formula),
+           IncTourism = grepl("Tourism", Formula)
+         )
 
 LADModels %>%
-  group_by(Dependent, Formula) %>%
-  summarise(BeatNull = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
-            meanAcc = mean(Accuracy), #What was the mean accuracy
-            NULLMod = mean(AccuracyNull),
-            DiffNull = mean(Accuracy-AccuracyNull), #Mean difference relative to NULL
-            StatistSignif = t.test(Accuracy,AccuracyNull, alternative = "greater", paired = T)$p.value) #Was Beat NUll statis
+  group_by(Dependent, IncAfford2, IncTourism) %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            ) %>%
+  ungroup %>%
+   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
+  rename(Afford2 = IncAfford2,
+         Tourism = IncTourism) %>% mutate(ModelID = rep(1:4,2))
+
+#Linear models are rubbish
+LADModelsLin %>%
+  select(-sample) %>%
+  group_by(Dependent, IncAfford2, IncTourism) %>%
+  summarise_if(is.numeric, funs(mean))
+
+#Explore the best classifier
+#There is no structure which adequately models whether A LAD will have more than the median LUP percentage
+LADMODOut2 <- ExtractClassCoeffs(LADMean, "HighLUP", TestResample, Formulas[[1]])
+LADMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+LADMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
+
+#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
+LADMODOut <- ExtractClassCoeffs(LADMean, "HighVal", TestResample, Formulas[[2]])
+LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
+
+LADMODOut %>%
+  select(-statistic, -std.error) %>%
+  group_by(term) %>%
+  summarise_all(funs(mean, median))
 
@@
 ```{r}
-
-    #as.formula(Reference ~ AffordRank+ AffordRank2+ TourismDensityRank)
-
 set.seed(1983)
@@
 
-#Make a lot of models
-
-Combos <- expand.grid(1:2,1:3)
-
-MSOAModels <- map2_df(.x = c("HighVal", "HighLUP")[Combos[,1]], .y = c(as.formula(Reference ~ HomesMedian+ AffordRank), 
-                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank),
-                                                         as.formula(Reference ~ TourismDensityRank+ AffordRank+ AffordRank2))[Combos[,2]],
-        ~{
-          print(paste(.x,.y))
-          MSOAMean %>% #LADMean %>%
-    rename_(Reference = .x ) %>%
-  ResampledModelPerf(., TestResample,  .y) %>%
-            mutate(Dependent = .x,
-                   Formula = toString(.y))
-
-        } ) %>%
-  mutate(type = ifelse(grepl("2", Formula), "2", "1"),
-          Formula = ifelse(grepl("Tourism", Formula), "Tourism", "Price")
+MSOAModels <-LinearClassifierCombiner(MSOAMean,  Outcomes, Formulas, TestResample) %>%
+  mutate(IncAfford2 = grepl("2", Formula),
+           IncTourism = grepl("Tourism", Formula)
          )
 
-MODOut <- 1:length(TestResample) %>% map_df(~{
-  Mod2 <- LADMean  %>%
-    rename(Reference = HighVal) %>%
-  mutate(Reference = as.factor(Reference)) %>%
-  slice(as.integer(TestResample[[.x]]$train)) %>%
-  glm(formula = as.formula(Reference ~ TourismDensityRank+ AffordRank), data = ., family=binomial(link='logit')) %>%
-    tidy
+MSOAModelsLin <- LinearClassifierCombiner(MSOAMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
+  mutate(IncAfford2 = grepl("2", Formula),
+           IncTourism = grepl("Tourism", Formula)
+         )
 
-})
+MSOAModels %>%
+  group_by(Dependent, IncAfford2, IncTourism) %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            ) %>%
+  ungroup %>%
+   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
+  rename(Afford2 = IncAfford2,
+         Tourism = IncTourism)
 
-ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot()
+#Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
+LADMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", TestResample, Formulas[[4]])
+LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
 
-MSOAModelSumm <- MSOAModels %>%
-  group_by(Dependent, Formula, type) %>%
-  summarise(BeatNull = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
-            meanAcc = mean(Accuracy), #What was the mean accuracy
-            NULLmod = mean(AccuracyNull),
-            DiffNull = mean(Accuracy-AccuracyNull), #Mean difference relative to NULL
-            StatistSignif = t.test(Accuracy,AccuracyNull, alternative = "greater", paired = T)$p.value) #Was Beat NUll statis
+#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
+MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", TestResample, Formulas[[1]])
+MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
+
+MSOAMODOut %>%
+  select(-statistic, -std.error) %>%
+  group_by(term) %>%
+  summarise_all(funs(mean, median))
+
+#Rubbish
+MSOAModelsLin %>%
+  select(-sample) %>%
+  group_by(Dependent, IncAfford2, IncTourism) %>%
+  summarise_if(is.numeric, mean, na.rm = T)
 
 ```
+
+Take away message is that the LAD model cannot predict LUP% whilst the MSOA model cannot predict High LUP Value

### 2018-08-12 Functions/LinearResampledModelPerf.R

@@ -1,4 +1,4 @@
-ResampledModelPerf <- function(Modeldf, TestResample, ModelFormula){
+LinearResampledModelPerf <- function(Modeldf, TestResample, ModelFormula){
   #Cretes a dataframe with the Classification performance of many resampled models.
   #This allows the same resample set to be used across multiple model builds
   
@@ -16,20 +16,18 @@ ResampledModelPerf <- function(Modeldf, TestResample, ModelFormula){
     
     Mod2 <- Modeldf  %>%
       slice(trainrows) %>%
-      glm(formula = ModelFormula, data = ., family=binomial(link='logit'))
-
-    preds2<- Modeldf  %>%
+      lm(formula = ModelFormula, data = .)
+    
+    preds2 <- Modeldf  %>%
       slice(testrows) %>%
-      predict(Mod2, newdata = ., type = "response" ) 
+      predict(Mod2, newdata = . ) 
     
     Refs <- Modeldf  %>%
       slice(testrows) %>%
       pull(Reference)
     
-    ConfOut <-Refs %>%
-      confusionMatrix( data =factor(preds2>0.5, levels = c("FALSE", "TRUE")), reference = .)
-
-    ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
+    ConfOut <-preds2 %>%
+      postResample(pred = ., Refs) %>% t %>% data.frame() %>% as.tibble %>%
       mutate(sample = .x)
     
     

### 2018-08-12 Functions/MSOATreeVoting.R

@@ -1,0 +1,52 @@
+MSOATreeVoting <- function(Modeldf, TestResample, ModelFormula){
+  #This model predicts a LAD outcome at MSOA level, It then uses majority vote to 
+  #choos the class of the over all LAD
+  #Cretes a dataframe with the Classification performance of many resampled models.
+  #This allows the same resample set to be used across multiple model builds
+  
+  #The Outcome variable HAS TO BE CALLED REFERENCE!
+  
+  #Modeldf: the dataframe that will be used as the data set of the model
+  #TestResample, a list of esample_partition objects based on Modeldf
+  #ModelFormula the formula used for the model. created using as.formula()
+
+  
+  ResOut <- 1:length(TestResample) %>% map_df(~{
+    
+
+      LADS <- TestResample[[.x]]$train %>% as.data.frame() %>% pull(LAD11CD) %>% unique
+      trainrows <-(1:nrow(Modeldf))[Modeldf$LAD11CD %in% LADS]
+      LADS <- TestResample[[.x]]$test %>% as.data.frame() %>% pull(LAD11CD) %>% unique
+      testrows <-(1:nrow(Modeldf))[Modeldf$LAD11CD %in% LADS]
+
+    
+    
+    print(.x)
+    Mod2 <- Modeldf %>%
+      slice(trainrows) %>%
+      ranger(formula = ModelFormula , data = . )
+    
+    
+    preds2<- Modeldf  %>%
+      slice(testrows) %>%
+      predict(Mod2, ., type = "response")
+    
+    preds2 <- Modeldf  %>%
+      slice(testrows) %>% 
+      select(Reference, LAD11CD) %>%
+      mutate(Predictions = ifelse(preds2$predictions=="TRUE",1,0),
+             Reference = ifelse(Reference=="TRUE",1,0)) %>%
+      group_by(LAD11CD) %>%
+      summarise(Predictions = mean(Predictions)>0.5,
+                Reference = mean(Reference)>0.5)
+    
+    ConfOut <-confusionMatrix( data =preds2$Predictions, reference = preds2$Reference)
+    
+    ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
+      mutate(sample = .x)
+    
+    
+  })
+  return(ResOut)
+  
+}

### 2018-08-12 Functions/StrappedHighMem.R

@@ -1,100 +1,0 @@
-StrappedHighMem <- function(dfPrice, dfWard, samples, Grouping){
-  #Is fast but uses a lot of memory
-  #dfPrice: the prices for the local authority
-  #dfWard the data for the local authority
-  #samples: the number of bootstraps to be taken. This causes a crash when large due to lack of memory
-  #WhichLowUse: The varaiable that will be used to get the number of bootstrap samples to draw.
-  #Grouping: the variables that will be used for aggregating the resulting dataframe.
-  
-  print("Start Bootstrapping Homes distribution")
-  
-  HomesTemp <-  1:length(unique(dfWard$LSOA11CD)) %>%
-    map_df(~{
-      LSOA <- unique(dfWard$LSOA11CD)[.x]
-      
-      print(paste("LSOA",.x, "of",length(dfWard$LSOA11CD)))
-      PriceData <- dfPrice %>% 
-        filter(LSOA11CD == LSOA)
-      #Sometimes an LSOA will have no sales in that year. In these thankfully rare cases the entire LAD is used.
-      if(nrow(PriceData)==0){
-        PriceData<-dfPrice
-      }
-      Counts <- filter(dfWard, LSOA11CD == LSOA) %>% pull(Homes) #sample rows from LSOA
-      
-      SampledData <-sample_n(PriceData, Counts*samples, replace = TRUE) %>%
-        mutate(ID = rep(1:samples, nrow(.)/samples))
-      
-    }
-    ) %>%
-    group_by(ID) %>%
-    mutate(Class = cut(Price, 
-                       Price %>% quantile(.) %>%
-                         .[2:4] %>% c(0,., Inf), 
-                       labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
-                       right = F) %>% fct_relevel(., "Upper", after = 3))
-  
-  print("Start LUP distribution")
-  
-  #This is annyngky slow as it has to sample from a large number of specific sets.
-  #Using a different numbe each time making it difficult to vectorise.
-  LowUseTemp <- 1:length(unique(dfWard$LSOA11CD)) %>% map_df(~{
-    print(paste("LSOA",.x, "of",length(dfWard$LSOA11CD)))
-    
-    LSOA <- unique(dfWard$LSOA11CD)[.x]
-    CurrentHomes <- HomesTemp %>% filter(LSOA11CD == LSOA) 
[…]

### 2018-08-12 Functions/StrappedLowMem.R

@@ -1,97 +1,0 @@
-StrappedLowMem <-  function(dfPrice, dfWard, samples, WhichLowUse, Grouping){
-  #Is slow but avoids crashes due to large values of "sample"
-  #dfPrice: the prices for the local authority
-  #dfWard the data for the local authority
-  #samples: the number of bootstraps to be taken. This causes a crash when large due to lack of memory
-  #WhichLowUse: The varaiable that will be used to get the number of bootstrap samples to draw.
-  #Grouping: the variables that will be used for aggregating the resulting dataframe.
-  Out <- 1:samples %>%
-    map_df(~{
-      print(.x)
-      HomesTemp <- 1:length(unique(dfWard$LSOA11CD)) %>%
-        map_df(~{
-          LSOA <- unique(dfWard$LSOA11CD)[.x]
-          
-          #print(paste(.x, "of",length(dfWard$LSOA11CD)))
-          PriceData <- dfPrice %>% 
-            filter(LSOA11CD == LSOA)
-          #Sometimes an LSOA will have no sales in that year. In these thankfully rare cases the entire LAD is used.
-          if(nrow(PriceData)==0){
-            PriceData<-dfPrice
-          }
-          LowUseCounts <- filter(dfWard, LSOA11CD == LSOA) %>% pull(Homes) #sample rows from LSOA
-          
-          SampledData <-sample_n(PriceData, LowUseCounts, replace = TRUE)
-          
-          SampledData  
-        }
-        ) %>%
-        mutate(Class = cut(Price, 
-                           Price %>% quantile(.) %>%
-                             .[2:4] %>% c(0,., Inf), 
-                           labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
-                           right = F) %>% fct_relevel(., "Upper", after = 3))
-      
-      
-      LowUseTemp <-  1:length(unique(dfWard$LSOA11CD)) %>% map_df(~{
-        
-        
-        LSOA <- unique(dfWard$LSOA11CD)[.x]
-        CurrentHomes <- HomesTemp %>% filter(LSOA11CD == LSOA) 
-        Counts <- filter(dfWard, LSOA11CD == LSOA) %>% pull(LowUse)
-        
-        SampledData <-CurrentHomes %>%
-          sample_n( Counts, replace = FALSE) #This is a strict subset of the Homes data not a bootstrap!
-        
-      })
-      
-      HomesTemp <- HomesTemp %>% 
-        mutate(LADmedian = median(Price, na.rm = T),
[…]

### 2018-08-12 Functions/TreeResampledModelPerf.R

@@ -1,0 +1,54 @@
+TreeResampledModelPerf <- function(Modeldf, TestResample, ModelFormula, CombineData = FALSE){
+  #Cretes a dataframe with the Classification performance of many resampled models.
+  #This allows the same resample set to be used across multiple model builds
+  
+  #The Outcome variable HAS TO BE CALLED REFERENCE!
+  
+  #Modeldf: the dataframe that will be used as the data set of the model
+  #TestResample, a list of esample_partition objects based on Modeldf
+  #ModelFormula the formula used for the model. created using as.formula()
+  #CombineData: the data set includes outcome variables for LADs and MSOA meaning the subsetting has to be by LAD
+  
+  ResOut <- 1:length(TestResample) %>% map_df(~{
+    
+    if(CombineData){
+      
+      LADS <- TestResample[[.x]]$train %>% as.data.frame() %>% pull(LAD11CD) %>% unique
+      trainrows <-(1:nrow(Modeldf))[Modeldf$LAD11CD %in% LADS]
+      LADS <- TestResample[[.x]]$test %>% as.data.frame() %>% pull(LAD11CD) %>% unique
+      testrows <-(1:nrow(Modeldf))[Modeldf$LAD11CD %in% LADS]
+      
+    }else{
+    
+      trainrows <- as.integer(TestResample[[.x]]$train)
+      testrows <- as.integer(TestResample[[.x]]$test)  
+      
+    }
+    
+    
+    print(.x)
+    Mod2 <- Modeldf %>%
+      slice(trainrows) %>%
+      ranger(formula = ModelFormula , data = . )
+    
+    
+    preds2<- Modeldf  %>%
+      slice(testrows) %>%
+      predict(Mod2, ., type = "response")
+    
+    preds2 <- preds2$predictions
+    
+    Refs <- Modeldf  %>%
+      slice(testrows) %>%
+      pull(Reference)
+    
+    ConfOut <-confusionMatrix( data =preds2, reference = Refs)
+    
+    ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
+      mutate(sample = .x)
+    
+    
+  })
+  return(ResOut)
+  
+}

### 2018-08-12 SubCode/LOADandProcessLADData.R

@@ -343,7 +343,7 @@ RichmondshireDATA <- read_excel("Richmondshire FOI 4960.xls", col_names = FALSE)
 KirkleesDATA <- read_excel("Jonathan Bourne KirkleesDiscountsLSOA Complete.xlsx" )[1:4] %>%
   StructureData(2:5)
 
-WakefieldData <-  read_excel("WakefieldDiscountsLSOA.xlsx" )[1:4] %>%
+WakefieldDATA <-  read_excel("WakefieldDiscountsLSOA.xlsx" )[1:4] %>%
   StructureData(2:7)
 
 
@@ -454,22 +454,6 @@ source(file.path(CommonCode, "LondonFullProcesss.R"))
 # Scrub the data to remove Cross overs with other LADs
 #
 
-print("Scrubbing loose ends")
-
-for(i in ls(pattern = "DATA$")){
-  
-  Temp <-get(i) %>% 
-    group_by(LSOA11CD) %>%  #Remove double LSOA that may have sneaked in
-    summarise_all(funs(first)) %>% 
-    group_by(LAD11CD) %>% #Remove LAD data that is not from this lad. Occaisonly a few lsoa from other LADs get in and cause problems
-    mutate(LADCount = n()) %>% ungroup %>%
-    filter(!is.na(Admin_ward_code), LADCount == max(LADCount)) %>% #filter out any stray areas that are classed as a different authority
-    select(-LADCount)  
-  
-  assign(i, Temp)
-  
-} 
-
 
 #
 #
@@ -484,3 +468,20 @@ DATAdf <- ls(pattern = "DATA$") %>%
   })
 
 rm(list = ls(pattern = "DATA$"))
+
+print("Scrubbing loose ends")
+
+
+DATAdf <-DATAdf %>% 
+    group_by(LSOA11CD) %>%  #Remove double LSOA that may have sneaked in
+    summarise_all(funs(first)) %>%
+    group_by(LAD11CD, LAD11NM) %>%
+    mutate(LSOACounts = n()) %>%
+    filter(LSOACounts>5)  %>% #remove any odd bits that have mixed up LAD code and name
+    ungroup %>%
+    select(-LSOACounts)
+
+
+
+
+

### 2018-08-17 MSOAmodel.Rmd
Cleaning and don't ruin postocdes

@@
 
-MSOAtoLAD %>%
-  group_by(LAD11CD) %>%
-  summarise(counts = n(),
-            LAD11NM = first(LAD11NM)) %>%
-  pull(counts) %>% mean
-
 test <-  tibble(MSOA11CD = ego(MSOAgraph, 1, nodes = "E02000001")[[1]] %>% names) %>%
@@
  })
+
+MSOAEgoList1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
+names(MSOAEgoList1) <- get.vertex.attribute(MSOAgraph, "name")
+
+MSOAEgoList2 <- ego(MSOAgraph, 2) %>%map(~names(.x))
+names(MSOAEgoList2) <- get.vertex.attribute(MSOAgraph, "name")
+
+ TourismMSOAEgo2 <- MSOAEgoList %>% map_dbl(~{
+   print(.x)
+    Tourism %>%
+      filter(MSOA11CD %in% .x) %>%
+      pull(Tourism) %>% sum
+ }) %>%
+   tibble(Ego2Tourism = .,
+          MSOA = names(MSOAEgoList))
+
+  TourismMSOAEgo1 <- MSOAEgoList1 %>% map_dbl(~{
+   print(.x)
+    Tourism %>%
+      filter(MSOA11CD %in% .x) %>%
+      pull(Tourism) %>% sum
+ }) %>%
+   tibble(Ego1Tourism = .,
+          MSOA = names(MSOAEgoList1))
 
@@
 These models work at MSOA level only and include data from the LAD level
-Tehy are rubbish so aren't included in the main work. Just kept here so I don't forget I have already checked.
+They don't really add anything extra so aren't included in the main work. Just kept here so I don't forget I have already checked.
 
 ```{r}
-
-DATAdf %>%
-  arrange(LAD11NM) %>% pull(LAD11NM) %>% unique
-
 MSOAMean2 <-MSOAMean %>%
@@
          RelativeTourismDens = TourismDensity/LADTourismDensity,
-         RelativeTourismDens = ifelse(is.finite(RelativeTourismDens), RelativeTourismDens, 100)) %>%
+         RelativeTourismDens = ifelse(is.finite(RelativeTourismDens), RelativeTourismDens, 100),
+         HighFinance = factor("TRUE"==LADHighVal & "TRUE"==HighLUP, levels = c("TRUE", "FALSE"))) %>%
   filter(!is.na(HighVal)) #Temporary  until I work out how to get rid of those weird MSOA
@@
 KitchenSink <- as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2+ RelativeAfford +RelativeTourismDens+
-                            LADTourismDensity+ LADAffordRatio+ LADAffordRatio2)
+                            LADTourismDensity+ LADAffordRatio+ LADAffordRatio2+ LADMeanMedianRatio)
 
-KitchenSink2 <- as.formula(Reference ~RelativeAfford +RelativeTourismDens+
-                            LADTourismDensity+ LADAffordRatio)
+KitchenSink2 <- as.formula(Reference ~RelativeAfford + RelativeTourismDens +
+                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio)
+
 Formulas2 <- c(as.formula(Reference ~ TourismDensity+ AffordRatio+ AffordRatio2),
@@
 
-set.seed(1983)
-TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean2 , c(test = 0.2, train = 0.8)))
-
+####Needs updating
 MSOAModels2 <-LinearClassifierCombiner(MSOAMean2,  Outcomes, Formulas2, TestResample) %>%
@@
 
-library(ranger)
-
-#Just under 78% better than all other models
+#Just under 76%. Better than all other models...but is it?
+#The more LAD variables that are included the better the model gets... Until you find out that this is becuase the model uses the lad data to predict the results of other MSOA in the same lad.
 ResOut <- MSOAMean2 %>%
   mutate(Reference = HighLUP) %>% 
-  TreeResampledModelPerf(., TestResample, KitchenSink)
+  TreeResampledModelPerf(., MSOAHighLUPResample, KitchenSink2)
+
+#Data contains LAD information I account for that here
 
@@
   mutate(Reference = HighLUP) %>%
-  TreeResampledModelPerf(., TestResample, KitchenSink2)
+  TreeResampledModelPerf(., LADHighLUPResample, KitchenSink2, LADData = LADMean )
 
-ResOut %>%
-  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
-            Accuracy = mean(Accuracy), #What was the mean accuracy
-            'NULL Model' = mean(AccuracyNull),
-           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
-            )
-
-ResOut2 %>%
-  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
-            Accuracy = mean(Accuracy), #What was the mean accuracy
-            'NULL Model' = mean(AccuracyNull),
-           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
-            )
+#The model was getting information from the shared LAD data so making it appear much better than it really is
+ResOut %>% SummariseModels()
+ResOut2 %>% SummariseModels()
 
@@
 set.seed(1983)
-TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))
+TestResample <- vfold_cv(LADMean, v = 5, repeats = 20)
 
@@
       rename_(Reference = .x) %>%
-      TreeResampledModelPerf(., TestResample, KitchenSink, CombineData = TRUE) %>%
+      TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean) %>%
       mutate(Dependent = .x)
 })
+
+#the data from the Lup is increasing the accuracy of the model
+ResOut2 <- MSOAMean2 %>%
+  mutate(Reference = HighLUP) %>%
+  TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean)
 
@@
       rename_(Reference = .x) %>%
-      TreeResampledModelPerf(., TestResample, KitchenSink2, CombineData = TRUE) %>%
+      TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean) %>%
       mutate(Dependent = .x)
@@
 
-Modeldf <-MSOAMean2 %>%
-      rename_(Reference = "LADHighLUP")
+```
 
+Highly financialized
+
+```{r}
+KitchenSink2 <- as.formula(Reference ~RelativeAfford + RelativeTourismDens +
+                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio, Ego2TourismDens2+Ego2TourismDens)
+
+test <- MSOAMean2 %>%
+  select(HighFinance, LADHighVal, HighLUP)
+
+ComplexModels2 <- c("HighFinance", "HighLUP", "LADHighVal") %>%
+  map_df(~{
+    print(.x)
+    ResOut2 <- MSOAMean2 %>%
+      rename_(Reference = .x) %>%
+      TreeResampledModelPerf(., TestResample, KitchenSink2, LADData = LADMean) %>%
+      mutate(Dependent = .x)
+})
+
+ComplexModels2 %>%
+  group_by(Dependent) %>%
+  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
+            Accuracy = mean(Accuracy), #What was the mean accuracy
+            'NULL Model' = mean(AccuracyNull),
+           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+            )
 ```
@@
 
-test <- MSOAMean2 %>%
+test <- MSOAMean2 %>% left_join(MSOAtoLAD) %>%
       rename_(Reference = "LADHighLUP") %>%
-MSOATreeVoting(., TestResample, KitchenSink )
+MSOATreeVoting(., TestResample, KitchenSink2 )
 
-test %>%
-  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
-            Accuracy = mean(Accuracy), #What was the mean accuracy
-            'NULL Model' = mean(AccuracyNull),
-           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
-            )
+test %>% SummariseModels()
 

### 2018-08-17 PaperCode.Rmd
Cleaning and don't ruin postocdes

@@
 suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))
-
-rm(PstCdLSOA.raw)
+rm(OAandPstCd)
 ```
@@
          Homes = sum(Homes),
+         Pop = sum(Pop),
          Region = first(Region)) %>%
@@
             Homes = first(Homes),
-            Region = first(Region))
+            Pop = first(Pop),
+            Region = first(Region)) %>%
+  mutate(Region = ifelse(is.na(Region), "Wales", Region))
 ```
@@
 ##MSOA Bootstrap
-Used for most of the analysis
+Used for most of the analysis, doesn't need to be loaded as it is loaded by other functions
 ```{r}
@@
 BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")
-BootStrapMSOA <- LoadBootstrapData()
+
+```
+
+##Non-Dataset LADs
+This bootstrapping is done to get the data needed to predict across the whole of Wngland and Wales
+```{r}
+#Filter out all the LADs for the data we have, ake dataframe that can be sampled
+AllOtherLADsdf <- EW2 %>% rename(LSOA11CD = ECODE) %>%
+  filter(!(LAD11CD %in% DATAdf$LAD11CD)) %>%
+  select(LSOA11CD:Pop, MSOA11CD, LAD11CD, LAD11NM)%>%
+  mutate(LowUse = 0) 
+#Bootstrap
+setwd(file.path(basewd, "BootstrapAllLADs"))
+BootstrapAllData(AllOtherLADsdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")
+
+#Not needed again
+rm(AllOtherLADsdf)
 
@@
 ```{r}
-CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
-  df %>%  
-  group_by(ID, Class) %>%
-  summarise(Homes = sum(Homes), 
-            LowUse = sum(LowUse)) %>%
-  group_by(ID)%>%
-  mutate(LowUseDistrib = LowUse/sum(LowUse),
-         HomesDistrib = Homes/sum(Homes)) %>%
-  mutate(LowUseRatio1 = (LowUseDistrib/0.25)-1,
-         HomesRatio1 = (HomesDistrib/0.25)-1,
-         LowUseRatio2 = (LowUseDistrib-HomesDistrib)/HomesDistrib) %>%
-    ungroup
-}
-
-LADS<-DATAdf%>%
-  group_by(LAD11CD) %>%
-  summarise(LAD11NM = first(LAD11NM)) %>%
-  arrange(LAD11NM)
-
 #Plot for all data
@@
   rename(Class = CountryClass)
-
-BootStrapQuartiles$E09000020  %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
-BootStrapQuartiles$E08000032 %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "HomesRatio1")
-All_data_class %>% CleanForPlotClassDiff()  %>%PlotClassDiff(Var = "LowUseRatio2")
 
@@
   mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
-  PlotClassDiff(Var = "LowUseRatio1") +
+  PlotClassDiff(Var = "LowUseRatio2") +
     facet_wrap(.~Area) +
@@
 ```{r}
+
 setwd(file.path(basewd, "VOA data"))
@@
   left_join(., CorePstCd, by = c("X15" = "Postcode")) %>%
-  filter(!is.na(LAD11CD)) %>%
+  #filter(!is.na(LAD11CD)) %>%
   filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
@@
          Hotel = grepl("(HOTEL)|(HOSTEL)",X6)) %>%
-   group_by(LSOA11CD, X6) %>%
+   group_by(MSOA11CD) %>% #Have X6 as a grouping variable to 
   summarise(Tourism = n(),
-            LAD11CD = first(LAD11CD),
-            LAD11NM = first(LAD11NM),
-            MSOA11CD = first(MSOA11CD),
-            Pop = first(Pop),
             Guest = sum(Guest),
-            Hotel = sum(Hotel))
+            Hotel = sum(Hotel))  %>%
+  left_join(., MSOAtoLAD, by="MSOA11CD")
+
+ MSOAAdjacency <- readShapeSpatial(file.path(basewd,"/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
+                                             "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp"))
+
+ test <- poly2nb(MSOAAdjacency)
+
+ MSOAAdjMat = nb2mat(test, style="B",zero.policy=T)
+
+#Add MSOA codes so that they are added as the vertex names
+colnames(MSOAAdjMat) <- MSOAAdjacency$msoa11cd
+
+MSOAgraph <- graph.adjacency(MSOAAdjMat, mode = "undirected")
+
+MSOAEgoList1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
+names(MSOAEgoList1) <- get.vertex.attribute(MSOAgraph, "name")
+
+MSOAEgoList2 <- ego(MSOAgraph, 2) %>%map(~names(.x))
+names(MSOAEgoList2) <- get.vertex.attribute(MSOAgraph, "name")
+
+ TourismMSOAEgo2 <- MSOAEgoList2 %>% map_df(~{
+    Tourism %>%
+      filter(MSOA11CD %in% .x) %>%
+      summarise(Ego2Tourism = sum(Tourism),
+                Ego2Guest = sum(Guest),
+                Ego2Hotel = sum(Hotel),
+                Ego2Homes = sum(Homes))
+ }) %>% mutate(Ego2TourismDens = Ego2Tourism/Ego2Homes,
+               Ego2GuestDens = Ego2Guest/Ego2Homes,
+               Ego2HotelDens = Ego2Hotel/Ego2Homes,
+               MSOA11CD = names(MSOAEgoList1))
+
+ TourismMSOAEgo1 <- MSOAEgoList1 %>% map_df(~{
+    Tourism %>%
+      filter(MSOA11CD %in% .x) %>%
+      summarise(Ego1Tourism = sum(Tourism),
+                Ego1Guest = sum(Guest),
+                Ego1Hotel = sum(Hotel),
+                Ego1Homes = sum(Homes))
+ }) %>% mutate(Ego1TourismDens = Ego1Tourism/Ego1Homes,
+               Ego1GuestDens = Ego1Guest/Ego1Homes,
+               Ego1HotelDens = Ego1Hotel/Ego1Homes,
+               MSOA11CD = names(MSOAEgoList1))
+
+Tourism <- Tourism %>%
+  left_join(TourismMSOAEgo1, ., by = "MSOA11CD") %>%
+  left_join(., TourismMSOAEgo2, by = "MSOA11CD") %>%
+  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
+         Hotel = ifelse(is.na(Hotel), 0, Hotel),
+         Guest = ifelse(is.na(Guest), 0, Guest))
+
+rm(MSOAAdjacency);rm(test);rm(MSOAAdjMat); rm(MSOAgraph); rm(MSOAEgoList1);rm(MSOAEgoList2); rm(TourismMSOAEgo1);rm(TourismMSOAEgo2)
 
@@
 LADMean <- MeanModelData(LADModelData, "LAD") %>%
-  mutate(AffordRank2 = scale(AffordRank)^2,
-           AffordRatio2 = scale(AffordRatio)^2,
-         TourismDensityRank = rank(TourismDensity, ties.method = "max"),
+  mutate(TourismDensityRank = rank(TourismDensity, ties.method = "max"),
          LowUseType =case_when(
@@
               summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")
+
+#Amount of variance in the bootstrap samples 
+#HighVal varies whilst HighLUP is fixed. However, in both of them the variables change as the affordability ratio varies. Not sure if it varies enough to change much though!
+LADRefAverages <- LADModelData %>%
+  group_by(LAD11CD) %>%
+  summarise(HighVal = mean(ifelse(HighVal==TRUE,1,0)),
+            HighLUP = mean(ifelse(HighLUP==TRUE,1,0)),
+            Afford = mean(AffordRatio),
+            Affordsd = sd(AffordRatio)) %>%
+  left_join(., MSOAtoLAD %>% select(LAD11CD, LAD11NM)%>% distinct)
+
+#example Affordatio bootstrap data for Chelsea. Variaince is very low
+LADModelData %>% filter(LAD11CD=="E09000020") %>% ggplot(aes(x = AffordRatio)) + geom_density()
 
@@
   left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
-                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatio2,
-                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff), by = "LAD11CD") %>%
+                   LADAffordRatio = AffordRatio, LADAffordRatio2 = AffordRatioScale2,
+                   LADTourismDensity = TourismDensity, LADMedianDiff = MedianDiff, LADMeanMedianRatio = MeanMedianRatio,
+                   LowUseType), by = "LAD11CD") %>%
   mutate(BothHighLUP =case_when(
@@
 
- MSOAMean %>%
-   #filter(TourismDensity!= 0) %>%
-  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point()
-
-  MSOAMean %>%
-   #filter(TourismDensity!= 0) %>%
-  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighLUP)) + geom_point()
-
-   MSOAMean %>%
-   filter(TourismDensity!= 0) %>%
-  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point()
-
-      MSOAMean %>%
-   filter(TourismDensity!= 0) %>%
-  ggplot(aes(x= AffordRank, y = TourismDensity, colour = BothHighVal)) + geom_point()
-
-  MSOAMean %>%
-  ggplot(aes(x= MedianDiffRank, y = LowUseRank, colour = BothHighVal)) + geom_point()
-
 ```
@@
 ```{r}
-bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
-  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighLUP)) + geom_point() +
+bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD"))  %>%group_by(type)%>% mutate(Eg2 = percent_rank(Ego2TourismDens)) %>% ungroup %>%
+  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighLUP)) + geom_point() +
   facet_wrap(~type) + 
-  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Density") +
+  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Rank") +
   guides(fill=guide_legend(title="Above Median"))
@@
 
+quantile(MSOAMean$LowUsePerc)
+
+```
+
+#Rural Analysis
+
+The rural areas seem to be much less likely to had a negative mean difference,  but there is not enough data for the data to be used for moddelling
+```{r}
+LADrural <- rural %>% group_by(LAD11CD, Urban) %>%
+  summarise(count = n()) %>%
+  spread(key = Urban, value = count, fill = 0) %>%
+  mutate(UrbanPerc = Urban/(Urban+Rural),
+         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
+  left_join(LADMean,.)
+
+MSOArural <- rural %>% group_by(MSOA11CD, Urban) %>%
+  summarise(count = n()) %>%
+  spread(key = Urban, value = count, fill = 0) %>%
+  mutate(UrbanPerc = Urban/(Urban+Rural),
+         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
+  left_join(MSOAMean,.)
+
+#Almost no rural areas are classified as having a negative median difference
+table(LADrural$Class,LADrural$MedianDiff>0.5)
+table(LADrural$Class,LADrural$LowUseType)
+2/26
+42/86
+
+table(ifelse(percent_rank(LADrural$TourismDensity)>0.5, "HighTour", "LowTour"),LADrural$HighLUP,LADrural$Class)
+
+LADrural  %>%
+  ggplot(aes(x = log(LowUsePerc), y =  log(TourismDensity), colour = Class)) + geom_point()
+
+rm(LADrural);rm(MSOArural);rm(rural)
 ```
@@
   left_join(select(MSOAtoLAD, MSOA11CD, Region), by ="MSOA11CD")
+
+cor(MSOAMea)
 
@@
 
-#Model Combinations
+##Model Parameters
 
@@
 
+Including Mean Median is useful for LADs where the intra lad variance is large but not for MSOA where the whole area can have a high number of LUPs not just a part which occurs in lads.
+The effect on the lad model is to increase accuracy by only 1%
+
 ```{r}
-
-Outcomes <- c("HighVal", "HighLUP")
-OutcomesLinear <- c("LowUsePerc", "MedianDiff")
-
 Formulas <- c(as.formula(Reference ~ AffordRatio),
               as.formula(Reference ~ TourismDensity + AffordRatio),
-      as.formula(Reference ~ AffordRatio + AffordRatio2),
-   as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatio2))
+              as.formula(Reference ~ AffordRatio + AffordRatioScale2),
+              as.formula(Reference ~ TourismDensity+ AffordRatio + AffordRatioScale2))
+
+#the below function is used to clearly mark the model summaries with the formular type
+MarkModels <- function(df){
+  df %>%
+  mutate(IncAfford2 = grepl("AffordRatioScale2", Formula),
+        # IncAfford3 = grepl("3", Formula),
+           IncTourism = grepl("Tourism", Formula)
+         )
+
+}
 
@@
 
-#LAD Model
+##LAD Model
 
 ```{r}
-
-cv <- tidy(vfold_cv(mtcars, v = 5))
-
-cv <- tidy(vfold_cv(mtcars, v = 5, repeats = 2))
-
 #Create sample
-set.seed(1983)
-TestResample <- 1:100 %>% map(~  resample_partition(LADMean , c(test = 0.2, train = 0.8)))
+set.seed(1235)
+LADHighValResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")
+set.seed(1235)
+LADHighLUPResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighLUP")
 
 #Create a load of classifiers
-LADModels <- LinearClassifierCombiner(LADMean,  Outcomes, Formulas, TestResample) %>%
-  mutate(IncAfford2 = grepl("2", Formula),
-           IncTourism = grepl("Tourism", Formula)
-         )
+LADModels <- bind_rows(LinearClassifierCombiner(LADMean,  "HighVal", Formulas, LADHighValResample),
+                       LinearClassifierCombiner(LADMean,  "HighLUP", Formulas, LADHighLUPResample)) %>%
+MarkModels
 
 #Create a load of linear models
-LADModelsLin <- LinearClassifierCombiner(LADMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
-  mutate(IncAfford2 = grepl("2", Formula),
-           IncTourism = grepl("Tourism", Formula)
-         )
+LADModelsLin <- bind_rows(LinearClassifierCombiner(LADMean,  "LowUsePerc", Formulas, LADHighValResample, Classifier = FALSE),
+                       LinearClassifierCombiner(LADMean,  "MedianDiff", Formulas, LADHighValResample, Classifier = FALSE)) %>%
+MarkModels()
 
-LADModels %>%
-  group_by(Dependent, IncAfford2, IncTourism) %>%
-  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
-            Accuracy = mean(Accuracy), #What was the mean accuracy
-            'NULL Model' = mean(AccuracyNull),
-           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
-            ) %>%
-  ungroup %>%
+LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
-  rename(Afford2 = IncAfford2,
-         Tourism = IncTourism) %>% mutate(ModelID = rep(1:4,2))
+  mutate(ModelID = rep(1:4,2))
 
@@
 
+#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have high value LUPs
+LADMODOut <- ExtractClassCoeffs(LADMean, "HighVal", LADHighValResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
+LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
+
 #Explore the best classifier
-#There is no structure which adequately models whether A LAD will have more than the median LUP percentage
-LADMODOut2 <- ExtractClassCoeffs(LADMean, "HighLUP", TestResample, Formulas[[1]])
+#There The quadtratic relationship is accurately covered using this formula 
+LADMODOut2 <- ExtractClassCoeffs(LADMean, "HighLUP", LADHighLUPResample, Formulas[[4]]) %>% filter(term !="(Intercept)")
 LADMODOut2 %>%  ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
@@
 
-#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
-LADMODOut <- ExtractClassCoeffs(LADMean, "HighVal", TestResample, Formulas[[2]])
-LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
-LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
-
-LADMODOut %>%
-  select(-statistic, -std.error) %>%
-  group_by(term) %>%
-  summarise_all(funs(mean, median))
+LADMODOut %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))
+LADMODOut2 %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))
 
@@
 
-#MSOA Model
+##MSOA Model
 ```{r}
-set.seed(1983)
-TestResample <- 1:100 %>% map(~  resample_partition(MSOAMean , c(test = 0.2, train = 0.8)))
 
-MSOAModels <-LinearClassifierCombiner(MSOAMean,  Outcomes, Formulas, TestResample) %>%
-  mutate(IncAfford2 = grepl("2", Formula),
-           IncTourism = grepl("Tourism", Formula)
-         )
+set.seed(1235)
+MSOAHighValResample <- vfold_cv(MSOAMean, v = 5, repeats = 20, strata = "HighVal")
+set.seed(1235)
+MSOAHighLUPResample <- vfold_cv(MSOAMean, v = 5, repeats = 20, strata = "HighLUP")
 
-MSOAModelsLin <- LinearClassifierCombiner(MSOAMean,  OutcomesLinear, Formulas, TestResample, Classifier = FALSE) %>%
-  mutate(IncAfford2 = grepl("2", Formula),
-           IncTourism = grepl("Tourism", Formula)
-         )
+MSOAModels <-bind_rows(LinearClassifierCombiner(MSOAMean,  "HighVal", Formulas, MSOAHighValResample),
+                       LinearClassifierCombiner(MSOAMean,  "HighLUP", Formulas, MSOAHighLUPResample))  %>%
+  MarkModels()
 
-MSOAModels %>%
-  group_by(Dependent, IncAfford2, IncTourism) %>%
-  summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
-            Accuracy = mean(Accuracy), #What was the mean accuracy
-            'NULL Model' = mean(AccuracyNull),
-           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
-            ) %>%
-  ungroup %>%
+LADModelsLin <- bind_rows(LinearClassifierCombiner(MSOAMean,  "LowUsePerc", Formulas, MSOAHighValResample, Classifier = FALSE),
+                       LinearClassifierCombiner(MSOAMean,  "MedianDiff", Formulas, MSOAHighValResample, Classifier = FALSE)) %>%
+  MarkModels
+
+MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
-  rename(Afford2 = IncAfford2,
-         Tourism = IncTourism)
+  mutate(ModelID = rep(1:4,2))
+
+#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
+MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", HighValResample, Formulas[[4]])  %>% filter(term !="(Intercept)")
+MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
 
 #Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
-LADMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", TestResample, Formulas[[4]])
-LADMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
-LADMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
-
-#Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
-MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", TestResample, Formulas[[1]])
-MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
-MSOAMODOut2 %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
+MSOAMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", MSOAHighLUPResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
+MSOAMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+MSOAMODOut %>% ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
 
@@
 Take away message is that the LAD model cannot predict LUP% whilst the MSOA model cannot predict High LUP Value
+
+#Model Bootstrap results
+
+using the most sucessful model formula I then use the Bootstrap data to create 501 models then majority vote the response variable.
+This creates a model with an overall lower accuracy but also a smaller standard deviation
+
+```{r}
+
+set.seed(1235)
+LADHighValResample200 <- vfold_cv(LADMean, v = 5, repeats = 200, strata = "HighVal")
+test <- LADMean %>% mutate(Reference = HighVal) %>%
+  ResampledModelPerf(., LADHighValResample200, Formulas[[2]])
+
+set.seed(1235)
+
+TestResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")
+
+TestResample <- vfold_cv(LADMean, v = 5, repeats = 100, strata = "HighVal")
+LADModelData2 <- LADModelData %>%
+  filter(ID<102)
+
+setwd(basewd)
+if(file.exists("LADBootVoteModel.rds")){
+
+  LADBootVoteModel <- readRDS("LADBootVoteModel.rds")
+
+  }else{
+    LADBootVoteModel <- 1:100 %>% map_df(~{ 
+       print(.x)
+        trainrows <- rsample2caret(TestResample)$index[[.x]]
+        testrows <-  rsample2caret(TestResample)$indexOut[[.x]]
+
+        test <- LADModelData %>% 
+          mutate(Reference = as.factor(HomesMedian < LowUseMedian)) %>% 
+          BootstrapResampledModelPerf(., trainrows, 
+                                      testrows, 
+                                      as.formula(Reference ~ TourismDensity + AffordRatio)) # creates a dataframe out predictions
+
+      ConfOut <- LADMean %>% mutate(Reference = factor(HomesMedian < LowUseMedian, levels = c("FALSE", "TRUE")))  %>% 
+        slice(testrows) %>% pull(Reference) %>%
+        confusionMatrix( data =factor( rowMeans(test) >0.5, levels = c("FALSE", "TRUE")), reference = .)
+
+          ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
+          mutate(sample = .x)
+
+    })
+
+}
+
+#has a lower mean but a much small standard deviation
+LADBootVoteModel %>% SummariseModels()
+
+bind_rows(LADModels %>% 
+            filter(IncAfford2 == FALSE,  IncTourism == TRUE, Dependent=="HighVal") %>% 
+            select(Accuracy) %>% mutate(type = "Basic"),
+          #select(test, Accuracy) %>% mutate(type = "big repeats"),
+          select(LADBootVoteModel, Accuracy) %>% mutate(type = "Boot")) %>%
+  ggplot(aes(x = Accuracy, colour = type)) + geom_density() +
+  ggtitle("Distribution of model results. Bootstrap has much tighter distribution")
+
+LADModels %>% 
+            filter(IncAfford2 == FALSE, IncTourism == TRUE) %>% 
+            select(Accuracy) %>% mutate(type = "Basic") %>% pull(Accuracy) %>%
+quantile(.,  probs = c(5, 50, 95)/100)
+quantile(LADBootVoteModel$Accuracy,  probs = c(5, 50, 95)/100)
+
+#Creates a boots model which can be analysed more
+
+set.seed(1235)
+LADHighValResample200 <- vfold_cv(LADMean, v = 5, repeats = 200, strata = "HighVal")
+
+if(file.exists("LADBootVoteModelBig.rds")){
+
+    LADBootVoteModelBig <- readRDS("LADBootVoteModelBig.rds")
+
+}else{
+
+        ModKlar <- LADModelData %>% 
+          mutate(Reference = as.factor(HomesMedian < LowUseMedian))
+
+ LADBootVoteModel <- (1:nrow(LADHighValResample200)) %>% map_df(~{ 
+       print(.x)
+        trainrows <- rsample2caret(LADHighValResample200)$index[[.x]]
+        testrows <-  rsample2caret(LADHighValResample200)$indexOut[[.x]]
+
+        test <- ModKlar %>% 
+          BootstrapResampledModelPerf(., trainrows, 
+                                      testrows, 
+                                      as.formula(Reference ~ TourismDensity + AffordRatio)) # creates a dataframe out predictions
+
+          Refs <- LADMean %>% 
+          mutate(Reference = as.factor(HomesMedian < LowUseMedian)) %>%
+              slice(testrows) %>%
+              select(Reference, LAD11CD)
+
+    tibble(Preds = rowSums(test>0.5), PredProbs = rowMeans(test), ID = .x) %>%
+      bind_cols(Refs)
+
+ })
+
+ LADBootVoteModelBig<- LADBootVoteModel %>%
+   mutate(Predres = (PredProbs>0.5)==Reference
+          ) %>%
+   left_join(LADRefAverages %>% select(-Afford, -Affordsd, -HighLUP)) %>%
+   group_by(LAD11CD)
+
+ saveRDS(LADBootVoteModelBig, "LADBootVoteModelBig.rds")
+
+ rm(LADBootVoteModel);rm(ModKlar);rm(test)
+}
+
+ LADBootVoteModelBig %>% ggplot(aes(x = PredProbs, y = HighVal, colour= Predres)) + geom_point()
+
+ test <- LADBootVoteModelBig %>%
+   group_by(LAD11CD, Predres) %>%
+   mutate(counts = n()) %>%
+   summarise_all(mean) %>%
+   select(-ID, -LAD11NM)
+
+ test2 <- test %>%
+   select(LAD11CD, Predres, counts) %>%
+   spread(key = Predres, value = counts, fill = 0)%>%
+   mutate(FractCorrect = `TRUE`/200) %>%
+   left_join(LADRefAverages %>% select(-Afford, -Affordsd, -HighLUP)) %>%
+   left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
+   mutate(PercDiff = (MedianDiff-HomesMedian)/HomesMedian)
+
+ test2 %>% ggplot(aes(y = FractCorrect, x = HighVal)) + geom_jitter()
+
+  test2 %>% ggplot(aes(y = FractCorrect, x = PercDiff, colour = is.na(Ego1TourismDens))) + geom_jitter()
+
+ table(test2$FractCorrect>0.5)
+
+ is.na(test2$Ego1TourismDens) %>% table
+
+```
+
+Boot MSOA
+
+```{r}
+FormulaMSOA <- as.formula(Reference ~ TourismDensity + AffordRatio)
+
+set.seed(1983)
+TestResample <- vfold_cv(MSOAMean, v = 5, repeats = 20, strata = "HighLUP")
+
+BootVoteModel <- 1:100 %>% map(~{ 
+   print(.x)
+    trainrows <- rsample2caret(TestResample)$index[[.x]]
+    testrows <-  rsample2caret(TestResample)$indexOut[[.x]]
+
+    test <- MSOAModelData %>% 
+      mutate(Reference = HighLUP) %>% 
+      BootstrapResampledModelPerf(., trainrows, testrows, FormulaMSOA ) # creates a dataframe out predictions
+
+    PredVect <- factor( rowMeans(test) >0.5, levels = c("FALSE", "TRUE"))
+
+  ConfOut <- MSOAMean %>% mutate(Reference = factor(HighLUP, levels = c("FALSE", "TRUE")))  %>% 
+    slice(testrows) %>% pull(Reference) %>%
+    confusionMatrix( data = PredVect, reference = .)
+
+      ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
+      mutate(sample = .x)
+
+})
+
+rm(FormulaMSOA)
+
+test<- MSOAModelData %>% group_by(ID)%>% summarise(counts= n())
+
+```
+
+##Create predictive dataset
+
+Create the predictive data set for the local authorities in England and wales for which we do not hold data
+
+#Create adjustment probability
+
+```{r}
+#calculate the minimum number of net swaps to move from majority to minority
+CalcZ <- function(Tot,M){
+
+  (2*M-Tot+1)/2
+
+}
+
+#Majority class probability function
+PiGreaterXZ <- function(x,z,M, p){
+
+  sum(dbinom((x+z):M, M, p))
+
+}
+
+Tot <- 501
+H <-282
+error <- 0.26
+
+#Go through all vote values and calculate the probability
+AdjustmentProb <- 0:501 %>% map_dbl(~{
+
+M <-abs(Tot/2 -.x)+Tot/2
+z<- CalcZ(Tot, M)
+
+AllProb <- 0:(Tot-M)  %>% map_dbl(~{
+  PiGreaterXZ(.x, z, Tot, error)*dbinom(.x, Tot-M, error)
+  })
+
+sum(AllProb)
+}) %>% tibble(ConfProb = .) %>%
+  mutate(Votes = 0:501,
+         ConfProb = 1-ConfProb) #We are very certain these will stay as they are
+```
+
+#Predict LADs
+
+```{r}
+
+PredictData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapAllLADs") )%>%  
+  MeanModelData(., "LAD")
+
+FormulaBootLAD<- ModelFormula <- as.formula(Reference ~ TourismDensity + AffordRatio)
+
+trainrows <- 1:nrow(LADModelData)
+
+BootstrapLADModels <- LADModelData %>% 
+  mutate(Reference = as.factor(HighVal)) %>% 
+  BootstrapResampledModelPerf(., trainrows, 0 , FormulaBootLAD, ModsOut = TRUE ) # creates a list of models
+
+VoteResults<- BootstrapLADModels %>% map(~{
+ preds2 <- tibble(x = predict(.x, newdata = PredictData, type = "response" )>0.5)
+
+}) %>% bind_cols() %>% rowSums(.) %>%
+  tibble(Votes = .) %>%
+  mutate(Prob = Votes/length(BootstrapLADModels), 
+         Class = Prob>0.5,
+         LAD11CD = PredictData$LAD11CD) %>%
+  left_join(., AdjustmentProb, by = "Votes") %>%
+  mutate(AdjustedProb = (Prob-0.5)*ConfProb+0.5)
+
+WholeCountry <- LADMean %>% select(LAD11CD, Votes = HighValCount) %>%
+  mutate(Prob = Votes/max(Votes), #a bit dodgey to do that but I know there are 100% outcomes
+         AdjustedProb = Prob,
+         Class = Prob>0.5) %>% #The addujsted probability of the collected dataset is simply the probability that the medianHOMes<MedianLUPs so no change us needed
+  bind_rows(VoteResults) %>%
+  left_join(MSOAtoLAD %>% group_by(LAD11CD, LAD11NM) %>% summarise(Pop = sum(Pop))) %>%
+  mutate(Diff = Prob-AdjustedProb)
+
+NumberOfSamples <- 10000
+
+PopAffected <- matrix(runif(NumberOfSamples*nrow(WholeCountry)), ncol = NumberOfSamples)
+
+PopAffected <- ((PopAffected >WholeCountry$AdjustedProb)*WholeCountry$Pop) %>%  t %>% rowSums(.) %>%
+  tibble(InvestmentPop = .) %>%
+  mutate(PopPerc = InvestmentPop/ sum(WholeCountry$Pop))
+
+PopAffected %>% ggplot(aes(x = PopPerc)) + geom_density() +
+  labs(title ="Estimate percentage of the Population living in areas with high LUP values",
+       x = "Population percentage")
+SaveFig("PopulationHighLUP.pdf")
+
+```
+
+#Predict MSOA High LUP
+
+```{r}
+
+PredictDataMSOA <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapAllLADs") )%>%  
+  MeanModelData(., "MSOA")
+
+FormulaMSOAPredAll <- as.formula(Reference ~ TourismDensity+ AffordRatio + AffordRatioScale2)
+
+PredictAllMSOAMod <- MSOAMean %>% 
+  mutate(Reference = as.factor(HighLUP))  %>%
+      glm(formula =FormulaMSOAPredAll , data = ., family=binomial(link='logit'))
+
+summary(PredictAllMSOA)
+
+MSOAWholeCountry <- tibble(HighLUP = predict(PredictAllMSOAMod, newdata = PredictDataMSOA, type = "response" )>0.5,
+                  MSOA11CD = PredictDataMSOA$MSOA11CD) %>%
+  mutate(HighLUP = as.factor(HighLUP)) %>%
+  bind_rows(select(MSOAMean, MSOA11CD, HighLUP))
+
+```
+
+#Plot Model Outputs
+
+##LAD model
+```{r}
+LADshapfile <-file.path(basewd,"ShapeFiles", "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain",
+                        "Local_Authority_Districts_December_2014_Ultra_Generalised_Clipped_Boundaries_in_Great_Britain.shp")
+
+LADShape <- st_read(LADshapfile)
+
+LADShape2 <- LADShape %>% left_join(WholeCountry, by = c("lad14cd" = "LAD11CD")) %>%
+  filter(!is.na(Class))
+
+ggplot(LADShape2) +
+  geom_sf(aes(fill = Class)) + 
+  labs(title = "Local Authorities classified as having predominently high value LUPs")
+SaveFig("EWHighValMap.pdf")
+
+```
+
+#MSOA model
+
+```{r}
+
+MSOAshapefile <-file.path(basewd,
+                         "/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
+                         "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp")
+
+MSOAShape <- st_read(MSOAshapefile) %>% left_join(MSOAWholeCountry, by = c("msoa11cd" = "MSOA11CD")) %>%
+  filter(!is.na(HighLUP))
+
+ggplot(MSOAShape2) +
+  geom_sf(aes(fill = HighLUP, colour = HighLUP)) + 
+  labs(title = "Local Authorities classified as having above the median percentage of LUPs")
+SaveFig("EWHighLUPMap.pdf")
+
+```

### 2018-08-17 Functions/BootstrapResampledModelPerf.R

@@ -1,0 +1,52 @@
+BootstrapResampledModelPerf <- function(Modeldf, trainrows, testrows, ModelFormula, ModsOut =FALSE){
+  #Creates a dataframe with the Classification performance of many resampled models.
+  #This allows the same resample set to be used across multiple model builds
+  
+  #The Outcome variable HAS TO BE CALLED REFERENCE!
+  
+  #Modeldf: the dataframe that will be used as the data set of the model
+  #trainrows the rows to be used in training
+  #testrows the rows to be used in testing
+  #ModelFormula the formula used for the model. created using as.formula()
+  #ModsOut if the models will be returned or not
+  
+  #TestResample <- rsample2caret(TestResample)
+  
+  ResOut <- 1:max(Modeldf$ID) %>% map(~{
+    #print(.x)
+    #The vector of rows used in this model
+  #  trainrows <- TestResample$index
+  #  testrows <- TestResample$indexOut 
+    
+    Modeldf <- Modeldf %>%
+      filter(ID==.x)
+    
+    Mod2 <- Modeldf  %>%
+      slice(trainrows) %>%
+      glm(formula = ModelFormula, data = ., family=binomial(link='logit'))
+    
+      if(ModsOut){
+        
+        Mod2
+        
+      }else{
+        preds2 <- Modeldf  %>%
+        slice(testrows) %>%
+        predict(Mod2, newdata = ., type = "response" ) 
+    
+        data.frame(preds2) %>%
+          setNames(paste0("Sim", .x))
+        }
+    
+  }) 
+  
+  if(!ModsOut){
+    
+    ResOut <- ResOut %>%
+      bind_cols
+  }
+
+  
+  return(ResOut)
+  
+}

### 2018-08-17 Functions/CleanForPlotClassDiff .R

@@ -1,0 +1,13 @@
+CleanForPlotClassDiff <- function(df){
+  df %>%  
+    group_by(ID, Class) %>%
+    summarise(Homes = sum(Homes), 
+              LowUse = sum(LowUse)) %>%
+    group_by(ID)%>%
+    mutate(LowUseDistrib = LowUse/sum(LowUse),
+           HomesDistrib = Homes/sum(Homes)) %>%
+    mutate(LowUseRatio1 = (LowUseDistrib/0.25)-1,
+           HomesRatio1 = (HomesDistrib/0.25)-1,
+           LowUseRatio2 = (LowUseDistrib-HomesDistrib)/HomesDistrib) %>%
+    ungroup
+}

### 2018-08-17 Functions/CreateGeogModelData.R

@@ -31,6 +31,7 @@ CreateGeogModelData <- function(target, path){
                 LowUse = sum(LowUse),
                 Homes = sum(Homes), #sum(Yearly.income*Homes)/sum(Homes),
                 HomesMedian = first(HomesMedian),
+                HomesMean = first(HomesMean),
                 LowUseMedian = first(LowUseMedian)) 
   } else {
     Afford3 <- Afford2
@@ -39,17 +40,20 @@ CreateGeogModelData <- function(target, path){
   Afford3 <- Afford3 %>%
     mutate(LowUsePerc = LowUse/Homes,
            AffordRatio = HomesMedian/Yearly.income,
-           AfforRatioScale = scale(AffordRatio),
-           AffordRationScale2 = AfforRatioScale^2,
-           AffordRank = percent_rank(AffordRatio),
-           HighVal = HomesMedian < LowUseMedian, #Reference Variable
-           HighLUP = median(LowUsePerc) < LowUsePerc)  #Reference Variable
+           AffordRatioScale = scale(AffordRatio),
+           AffordRationScale2 = AffordRatioScale^2,
+           AffordRationScale3 = AffordRatioScale^3,
+           AffordRank = percent_rank(AffordRatio))  
   
-  LADModelData <- left_join(Afford3, 
+  Out <- left_join(Afford3, 
                             Tourism %>% #Add in the tourism designed for MSOA
                               group_by_(target2)  %>%
                               summarise(Guest = sum(Guest),
-                                        Hotel = sum(Hotel)), 
+                                        Hotel = sum(Hotel),
+                                        Ego1TourismDens = sum(Ego1TourismDens),
+                                        Ego2TourismDens = sum(Ego2TourismDens),
+                                        Region = first(Region)
+                                        ), 
                             by = target2) %>%
     mutate(Guest = ifelse(is.na(Guest), 0, Guest),
            Hotel = ifelse(is.na(Hotel), 0, Hotel),
@@ -57,7 +61,15 @@ CreateGeogModelData <- function(target, path){
            TourismDensity = Tourism/Homes,
            GuestDensity = Guest/Homes,
            HotelDensity = Hotel/Homes,
-           TourismDensityRank = rank(TourismDensity, ties.method = "max"))
+           TourismDensityRank = rank(TourismDensity, ties.method = "max"),
[…]

### 2018-08-17 Functions/MeanModelData.R

@@ -9,22 +9,34 @@ MeanModelData <- function(ModelData, target){
               LowUse = mean(LowUse),
               Guest = mean(Guest),
               Hotel = mean(Hotel),
+              Ego1TourismDens = mean(Ego1TourismDens),
+              Ego2TourismDens = mean(Ego2TourismDens),
               HomesMedian = mean(HomesMedian),
+              HomesMean = mean(HomesMean),
               LowUseMedian = mean(LowUseMedian),
-              Yearly.income = mean(Yearly.income)) %>%
+              Yearly.income = mean(Yearly.income),
+              Region = first(Region),
+              HighValCount =  sum(ifelse(HighVal==TRUE,1,0))) %>%
     mutate(AffordRatio = HomesMedian/Yearly.income,
+           AffordRatioScale2 = (scale(AffordRatio)^2),
+           AffordRatioScale3 = (scale(AffordRatio)^3),
+           AffordRatioScale = ((AffordRatio)),
+           Ego1TourismDens2 = (scale(Ego1TourismDens)^2),
+           Ego2TourismDens2 = (scale(Ego2TourismDens)^2),
            LowUsePerc = LowUse/Homes,
            LowUseRank = percent_rank(LowUsePerc),
            Tourism = Guest +Hotel,
+           MeanMedianRatio = HomesMean/HomesMedian,
            HomesMedianRank = percent_rank(HomesMedian),
            LowUseMedianRank = percent_rank(LowUseMedian),
            MedianDiff = LowUseMedian-HomesMedian,
            MedianDiffRatio = (LowUseMedian-HomesMedian)/HomesMedian,
            MedianDiffRank = percent_rank(MedianDiff),
            AffordRank = percent_rank(AffordRatio),
-           TourismDensity = percent_rank((Guest+Hotel)/Homes),
+           TourismDensity = (Guest+Hotel)/Homes,
            HighVal = as.factor(HomesMedian < LowUseMedian), #Reference Variable
-           HighLUP = as.factor(median(LowUsePerc) < LowUsePerc)) #Reference Variable
+           HighLUP = as.factor(median(LowUsePerc) < LowUsePerc),
+           HighLUP2 = as.factor(quantile(LowUsePerc, 0.75)< LowUsePerc)) #Reference Variable
   
   
 }

### 2018-08-17 Functions/TreeResampledModelPerf.R

@@ -1,30 +1,30 @@
-TreeResampledModelPerf <- function(Modeldf, TestResample, ModelFormula, CombineData = FALSE){
+TreeResampledModelPerf <- function(Modeldf, TestResample, ModelFormula, LADData = NULL){
   #Cretes a dataframe with the Classification performance of many resampled models.
   #This allows the same resample set to be used across multiple model builds
   
   #The Outcome variable HAS TO BE CALLED REFERENCE!
   
   #Modeldf: the dataframe that will be used as the data set of the model
-  #TestResample, a list of esample_partition objects based on Modeldf
+  #TestResample, a vfold_cv object
   #ModelFormula the formula used for the model. created using as.formula()
-  #CombineData: the data set includes outcome variables for LADs and MSOA meaning the subsetting has to be by LAD
+  #LADDaata a data frame of the LAD dataset. is used to identify which lads are included when using overall LAD data
   
-  ResOut <- 1:length(TestResample) %>% map_df(~{
+  TestResample <- rsample2caret(TestResample)
+  
+  ResOut <- 1:length(TestResample$index) %>% map_df(~{
     
-    if(CombineData){
-      
-      LADS <- TestResample[[.x]]$train %>% as.data.frame() %>% pull(LAD11CD) %>% unique
+    #The vector of rows used in this model
+    trainrows <- TestResample$index[[.x]]
+    testrows <- TestResample$indexOut[[.x]]  
+    
+    if(!is.null(LADData)){
+      #Include data by LAD
+      LADS <- LADData %>% slice(trainrows) %>% pull(LAD11CD) %>% unique
       trainrows <-(1:nrow(Modeldf))[Modeldf$LAD11CD %in% LADS]
-      LADS <- TestResample[[.x]]$test %>% as.data.frame() %>% pull(LAD11CD) %>% unique
+      LADS <- LADData %>% slice(testrows) %>% pull(LAD11CD) %>% unique
       testrows <-(1:nrow(Modeldf))[Modeldf$LAD11CD %in% LADS]
       
-    }else{
-    
-      trainrows <- as.integer(TestResample[[.x]]$train)
-      testrows <- as.integer(TestResample[[.x]]$test)  
-      
     }
-    
     
     print(.x)
     Mod2 <- Modeldf %>%

### 2018-08-17 SubCode/LondonFullProcesss.R

@@ -101,9 +101,9 @@ RedbridgeLONDATA <- read_excel("RedbridgeDiscountsLSOA.XLSX" )[1:4]  %>%
 BrentLONDATA <- read_excel("FOI  6900196 Brent empty domestic properties.xlsx", col_names = TRUE)[,c(1,5)] %>%
   setNames(c("X__1", "Postcode")) %>%
   mutate(Postcode = gsub(" ", "", Postcode)) %>%
-  left_join(., PstCdLSOA.raw,  by="Postcode" ) %>%
-  rename(Exemption.type=X__1, LSOA_CODE = lsoa11cd) %>%
-  select(Exemption.type, LSOA_CODE, Admin_ward_code, Country_code) %>%
+  left_join(., CorePstCd,  by="Postcode" ) %>%
+  rename(Exemption.type=X__1, LSOA_CODE = LSOA11CD) %>%
+  select(Exemption.type, LSOA_CODE, LAD11CD, Country_code) %>%
   StructureData(c(2,15:19))
 
 #Hammersmith and fulham
@@ -119,11 +119,11 @@ WalthamforestLONDATA <- read_excel("J Bourne Waltham ForestDiscountsLSOA 8.8.17.
 #Westminster
 #Holy SHIT!
 
-#They sent it in the wrong format becuase they are annoying
-LSOA2LSOA <- PstCdLSOA.raw %>% group_by(lsoa11cd) %>%
-  summarise(LSOA = first(lsoa11nm)) %>%
+#They sent it in the wrong format becuase they are annoying.
+LSOA2LSOA <- CorePstCd %>% group_by(LSOA11CD) %>%
+  summarise(LSOA = first(LSOA11NM)) %>%
   ungroup %>%
-  rename(LSOA_CODE = lsoa11cd)
+  rename(LSOA_CODE = LSOA11CD)
 
 #They have missed something out
 WestminsterLONDATA <- read_excel("Westminster 3123133  data Aug 2017.xlsx")[2:5] %>%
@@ -159,9 +159,9 @@ EnfieldLONDATA <- read_excel("EnfieldDiscountsLSOA.xlsx")[c(1,4:6)] %>%
  HounslowLONDATA <- read_excel("Hounslow - Bourne Info -210817.xls", sheet = 2)[c(1,4:5)] %>%
    setNames(c("Postcode","X__1","X__2")) %>%
    mutate(Postcode = gsub(" ", "", Postcode)) %>%
[…]

### 2018-08-17 SubCode/Setup.R

@@ -2,7 +2,7 @@
 
 
 packages <- c("tidyverse", "lubridate","spdep", "igraph", "maptools", "openxlsx", "readxl", "sp","rgdal", "rgeos", "raster", "broom", "leaflet",
-              "forcats", "e1071", "htmlwidgets", "stringr", "modelr", "caret", "xtable", "rpart", "broom", "yardstick", "rsample")
+              "forcats", "e1071", "htmlwidgets", "stringr", "modelr", "caret", "xtable", "rpart", "broom", "yardstick", "rsample", "ranger")
 
 #, "mapview"
 new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]

### 2018-08-17 PaperCode.Rmd
Don't destroy everything Postcodes
Going to change the postocde systme to one that is much simpler and uses a more easily maintainable dataset

@@
 DataCover <-DATAdf  %>%
-                #filter(!is.na(LAD11NM)) %>%
+                #filter(is.na(MSOA11CD)) %>%
   summarise(
@@
 rm(DataCover)
+
+#lost LUPS
+
+LostLowUse <- DATAdf %>%
+  filter(is.na(MSOA11CD)) %>%
+  group_by(LAD11CD) %>%
+  summarise(Lost = sum(LowUse)) %>%
+  arrange(-Lost) %>%
+  mutate(cumsum = cumsum(Lost),
+         cumperc = cumsum/sum(Lost))
+
+sum(LostLowUse$Lost)
+
+ONSPD <- read_csv(file.path("/home/jonno/Dropbox/SSE/Empty Homes/ONSPD",
+                            "ONS_Postcode_Directory_Latest_Centroids.csv"))
+
+LADconv <- read_csv(file.path(AddGeog, 
+                              "Local_Authority_Districts_December_2016_Names_and_Codes_in_the_United_Kingdom.csv")) %>%
+  select(LAD11CD=LAD16CD, LAD11NM = LAD16NM)
+
+test <- ONSPD %>%
+  select(Postcode = pcd, LSOA11CD = lsoa11, MSOA11CD = msoa11, LAD11CD = oslaua, OA11CD = oa11,Country_code = ctry, Region =  rgn) %>%
+  filter(grepl("(E92000001)|(W92000004)", Country_code)) %>%
+  left_join(LADconv) %>%
+  filter(!is.na(LSOA11CD))
+
+test2 <- test  %>%
+  filter(is.na(LSOA11CD))
+
+map_dbl(.x = 1:ncol(test), ~{
+
+  test %>% pull(.x) %>% is.na %>% sum
+
+})
 
@@
    select(LAD11CD, Predres, counts) %>%
-   spread(key = Predres, value = counts, fill = 0)%>%
+   spread(key = Predres, value = counts, fill = 0) %>%
    mutate(FractCorrect = `TRUE`/200) %>%
@@
    left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
-   mutate(PercDiff = (MedianDiff-HomesMedian)/HomesMedian)
+   mutate(PercDiff = (MedianDiff-HomesMedian)/HomesMedian) %>%
+   left_join(LostLowUse)
 

### 2018-08-20 PaperCode.Rmd
Remove Bootstrap
The bootstrap process does not create better models. As a result I am going to remove it from the final predictive model and just use the mean models method.

@@
 ---
-Mang en natt har jeg sittet opp og skrevet dype romaner paa dette skrivebordet.
-Det er pent brukt, men har gitt meg graa haar.
-Det er som min Moby Dick, jeg har aldri helt klart aa temme det, boken er halvskrevet, hodet fult, hjertet tomt.
-Derfor maa det bort, kona orker ikke at jeg sitter oppe og stirrer paa uskrevne linjer i min moleskinen mer.
+
+schedule 2 part 5 section
 
@@
 suppressMessages(source(file.path(SubCode, "LOADandProcessLADData.R")))
-rm(OAandPstCd)
+
 ```
@@
 sum(LostLowUse$Lost)
-
-ONSPD <- read_csv(file.path("/home/jonno/Dropbox/SSE/Empty Homes/ONSPD",
-                            "ONS_Postcode_Directory_Latest_Centroids.csv"))
-
-LADconv <- read_csv(file.path(AddGeog, 
-                              "Local_Authority_Districts_December_2016_Names_and_Codes_in_the_United_Kingdom.csv")) %>%
-  select(LAD11CD=LAD16CD, LAD11NM = LAD16NM)
-
-test <- ONSPD %>%
-  select(Postcode = pcd, LSOA11CD = lsoa11, MSOA11CD = msoa11, LAD11CD = oslaua, OA11CD = oa11,Country_code = ctry, Region =  rgn) %>%
-  filter(grepl("(E92000001)|(W92000004)", Country_code)) %>%
-  left_join(LADconv) %>%
-  filter(!is.na(LSOA11CD))
-
-test2 <- test  %>%
-  filter(is.na(LSOA11CD))
-
-map_dbl(.x = 1:ncol(test), ~{
-
-  test %>% pull(.x) %>% is.na %>% sum
-
-})
-
 ```
@@
 PriceCounts<- EW2 %>%
-  select(LSOA11CD = ECODE, Homes, Pop, LAD11CD, MSOA11CD) %>%
+  select(LSOA11CD, Homes, Pop, LAD11CD, MSOA11CD) %>%
   left_join(.,PriceCounts, by = "LSOA11CD") %>%
@@
          Homes2 = Homes/10) %>%
-  filter(counts!=0)
+  filter(counts!=0) %>%
+  left_join(IncomeEst %>% select(MSOA11CD, Yearly.income))
 
@@
 #This process can take a while
-setwd(basewd)
+setwd(DataFolder)
 if(file.exists("LSOAPriceList2.rds")){
@@
 
+ #Price Quartiles
  if(file.exists("AllDataQuartiles.rds")){
@@
                                      PriceCounts2$Homes2, 
-                                     samples = 501) #change to 1 for a quicker solution has no effect on outcome
+                                     samples = 100) #change to 1 for a quicker solution has no effect on outcome
 
@@
 
-rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary);rm(LSOAPriceList)
+#Affordability Quartiles
+
+if(file.exists("LSOAAffordList.rds")){
+
+  LSOAAffordList <- readRDS("LSOAAffordList.rds")
+
+}else{
+
+  LSOAAffordList<- 1:nrow(PriceCounts) %>%
+  map(~{
+    print(.x)
+    LSOAPriceList[[.x]]/PriceCounts$Yearly.income[.x]
+
+  })
+ names(LSOAAffordList) <- PriceCounts$LSOA11CD
+  saveRDS(LSOAAffordList, "LSOAAffordList.rds")
+
+}
+
+ #Price Quartiles
+ if(file.exists("AllDataAffordQuartiles.rds")){
+
+  AllDataAffordQuartiles <- readRDS("AllDataAffordQuartiles.rds")
+
+}else{
+  #Subset list to only the LADs used in analyis
+  LSOAAffordList2 <- LSOAAffordList[names(LSOAAffordList) %in% unique(DATAdf$LSOA11CD)]
+  PriceCounts2 <- PriceCounts %>%
+    filter(LSOA11CD %in% unique(DATAdf$LSOA11CD))
+
+   AllDataAffordQuartiles <- StratifiedBoot(LSOAAffordList2, 
+                                     PriceCounts2$LSOA11CD, 
+                                     PriceCounts2$Homes2, 
+                                     samples = 100) #change to 1 for a quicker solution has no effect on outcome
+
+  saveRDS(AllDataAffordQuartiles, "AllDataAffordQuartiles.rds")
+
+  rm(list = c("LSOAAffordList2", "PriceCounts2"))
+
+}
+
+AllDataAffordQuartilesSummary <-  AllDataAffordQuartiles %>%
+  summarise_all(funs(mean, sd))
+
+#Add the balanced quartiles on to the prices.
+prices <- prices %>%
+  left_join(select(PriceCounts, LSOA11CD, Yearly.income)) %>%
+  mutate(Affordability = X2/Yearly.income) %>%
+  select(-Yearly.income ) %>%
+  mutate(CountryAffordClass = cut(Affordability, AllDataAffordQuartilesSummary[2:4] %>% c(0,., Inf), 
+                              labels =     c("Lower", "Lower-Mid", "Upper-Mid", "Upper"), 
+                              right = F) %>% fct_relevel(., "Upper", after = 3))
+
+rm(BasicQuartiles);rm(AllDataQuartiles);rm(AllDataQuartilesSummary);rm(LSOAPriceList);rm(AllDataAffordQuartiles);rm(AllDataAffordQuartilesSummary);rm(LSOAAffordList)
 
@@
 
+Affordability Bootstrap
+```{r}
+setwd(file.path(basewd, "BootstrapAffordQuartiles"))
+BootstrapAllData(DATAdf, LimitValue = 1.4e5, Reps = 501, GroupingVars = c("AffordClass", "CountryAffordClass"))
+#BootStrapAffordQuartiles <- LoadBootstrapData()
+#BootStrapQuartiles2 <- BootStrapQuartiles
+
+BootStrapQuartiles<- BootStrapAffordQuartiles
+```
+
 ##MSOA Bootstrap
@@
 #Filter out all the LADs for the data we have, ake dataframe that can be sampled
-AllOtherLADsdf <- EW2 %>% rename(LSOA11CD = ECODE) %>%
+AllOtherLADsdf <- EW2 %>%
   filter(!(LAD11CD %in% DATAdf$LAD11CD)) %>%
@@
 
+##Old prices Bootstrap
+
+This is to calculate % change
+```{r}
+
+if(length(list.files(file.path(basewd, "BootstrapMSOAOldPrices")))==0){
+prices <- prices2
+DATAdf2 <- DATAdf %>% mutate(LowUse = 0)
+prices <- readRDS(file.path(DataFolder,"pricesOld.rds")) %>% mutate(CountryClass = 1, Affordability = 1, CountryAffordClass = 1)
+setwd(file.path(basewd, "BootstrapMSOAOldPrices"))
+BootstrapAllData(DATAdf2, LimitValue = 1.4e5, Reps = 501, GroupingVars = "MSOA11CD")
+rm(DATAdf2)
+prices<- prices2
+rm(prices2)
+}
+
+```
+
 #Low Use quartile plot
@@
   bind_rows %>%
-  select(CountryClass, ID, LowUse, Homes) %>%
-  rename(Class = CountryClass)
+  select(CountryClass = CountryAffordClass, ID, LowUse, Homes)
 
@@
 bind_rows(
-CleanForPlotClassDiff(BootStrapQuartiles$E09000020) %>% mutate(Area = "Kensington and Chelsea"),
-CleanForPlotClassDiff(BootStrapQuartiles$E08000032) %>% mutate(Area = "Bradford"),
-CleanForPlotClassDiff(All_data_class) %>% mutate(Area = "All Data")
+CleanForPlotClassDiff(BootStrapQuartiles$E09000020, AffordClass) %>% mutate(Area = "Kensington and Chelsea"),
+CleanForPlotClassDiff(BootStrapQuartiles$E08000032, AffordClass) %>% mutate(Area = "Bradford"),
+CleanForPlotClassDiff(All_data_class, CountryClass) %>% mutate(Area = "All Data")
 ) %>%
   mutate(Area = factor(Area, levels = c("Bradford", "All Data", "Kensington and Chelsea"))) %>%
-  PlotClassDiff(Var = "LowUseRatio2") +
+  PlotClassDiff(Var = "LowUseRatio1") +
     facet_wrap(.~Area) +
@@
 ```{r}
-
-setwd(file.path(basewd, "VOA data"))
-
-#Creates Tourism dataframe at LSOA level
-Tourism <- read_delim("uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv", 
-                          delim = "*", col_names = F) %>%
-  mutate(X15 = gsub(" ", "", X15)) %>%
-  left_join(., CorePstCd, by = c("X15" = "Postcode")) %>%
-  #filter(!is.na(LAD11CD)) %>%
-  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
-  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
-         Hotel = grepl("(HOTEL)|(HOSTEL)",X6)) %>%
-   group_by(MSOA11CD) %>% #Have X6 as a grouping variable to 
-  summarise(Tourism = n(),
-            Guest = sum(Guest),
-            Hotel = sum(Hotel))  %>%
-  left_join(., MSOAtoLAD, by="MSOA11CD")
-
- MSOAAdjacency <- readShapeSpatial(file.path(basewd,"/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
-                                             "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp"))
-
- test <- poly2nb(MSOAAdjacency)
-
- MSOAAdjMat = nb2mat(test, style="B",zero.policy=T)
-
-#Add MSOA codes so that they are added as the vertex names
-colnames(MSOAAdjMat) <- MSOAAdjacency$msoa11cd
-
-MSOAgraph <- graph.adjacency(MSOAAdjMat, mode = "undirected")
-
-MSOAEgoList1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
-names(MSOAEgoList1) <- get.vertex.attribute(MSOAgraph, "name")
-
-MSOAEgoList2 <- ego(MSOAgraph, 2) %>%map(~names(.x))
-names(MSOAEgoList2) <- get.vertex.attribute(MSOAgraph, "name")
-
- TourismMSOAEgo2 <- MSOAEgoList2 %>% map_df(~{
-    Tourism %>%
-      filter(MSOA11CD %in% .x) %>%
-      summarise(Ego2Tourism = sum(Tourism),
-                Ego2Guest = sum(Guest),
-                Ego2Hotel = sum(Hotel),
-                Ego2Homes = sum(Homes))
- }) %>% mutate(Ego2TourismDens = Ego2Tourism/Ego2Homes,
-               Ego2GuestDens = Ego2Guest/Ego2Homes,
-               Ego2HotelDens = Ego2Hotel/Ego2Homes,
-               MSOA11CD = names(MSOAEgoList1))
-
- TourismMSOAEgo1 <- MSOAEgoList1 %>% map_df(~{
-    Tourism %>%
-      filter(MSOA11CD %in% .x) %>%
-      summarise(Ego1Tourism = sum(Tourism),
-                Ego1Guest = sum(Guest),
-                Ego1Hotel = sum(Hotel),
-                Ego1Homes = sum(Homes))
- }) %>% mutate(Ego1TourismDens = Ego1Tourism/Ego1Homes,
-               Ego1GuestDens = Ego1Guest/Ego1Homes,
-               Ego1HotelDens = Ego1Hotel/Ego1Homes,
-               MSOA11CD = names(MSOAEgoList1))
-
-Tourism <- Tourism %>%
-  left_join(TourismMSOAEgo1, ., by = "MSOA11CD") %>%
-  left_join(., TourismMSOAEgo2, by = "MSOA11CD") %>%
-  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
-         Hotel = ifelse(is.na(Hotel), 0, Hotel),
-         Guest = ifelse(is.na(Guest), 0, Guest))
-
-rm(MSOAAdjacency);rm(test);rm(MSOAAdjMat); rm(MSOAgraph); rm(MSOAEgoList1);rm(MSOAEgoList2); rm(TourismMSOAEgo1);rm(TourismMSOAEgo2)
+if(file.exists(file.path(DataFolder, "Tourism.rds"))){
+
+  Tourism <- readRDS(file.path(DataFolder, "Tourism.rds"))
+}else{
+
+  suppressMessages(source(file.path(SubCode, "LoadProcessTourism.R")))
+
+}
+```
+
+```{r}
+test <- list.files(file.path(basewd, "BootstrapMSOAOldPrices"), full.names = TRUE) %>%
+    map_df(~readRDS(.x)) %>% select(MSOA11CD,LAD11CD, ID, MSOAHomesMedian:LADHomesMean) %>% 
+  set_names(c(names(.)[1:3], paste0(names(.)[-c(1:3)], "Old")))
+
+  group_by(LAD11CD) %>%
+      summarise(HomesMedian = first(LADHomesMedian),
+                HomesMean = first(LADHomesMean)) %>% 
+  rename(LADHomesMedianOld = HomesMedian,
+         LADHomesMeanOld = HomesMean)
+
+test2 <- left_join(LADMean, test) %>%
+  mutate(PercChange = (HomesMedian-LADHomesMedianOld)/LADHomesMedianOld,
+         PercChange = (HomesMean-HomesMeanOld)/HomesMeanOld)
+
+t.test(test2$LADHomesMedianOld, test2$HomesMedian, alternative = "less")
+
+test2 %>%
+  ggplot(aes(x = HomesMedian, y = LADHomesMedianOld))
+
+test2 %>%
+  ggplot(aes(x = PercChange)) + geom_density()
+
+test2%>%
+  ggplot(aes(x = PercChange, y = AffordRatio)) + geom_point()
+
+cor(test2$AffordRatio, test2$PercChangeMean)
+
+MSOAtest <- list.files(file.path(basewd, "BootstrapMSOAOldPrices"), full.names = TRUE) %>%
+    map_df(~readRDS(.x)) %>% select(MSOA11CD,LAD11CD, ID, MSOAHomesMedian:LADHomesMean) %>% 
+   group_by(MSOA11CD) %>%
+      summarise(HomesMedianOld = first(MSOAHomesMedian),
+                HomesMeanOld = first(MSOAHomesMean)) %>% 
+  left_join(MSOAMean, .) %>%
+  mutate(PercChange = (HomesMedian-HomesMedianOld)/HomesMedianOld,
+         PercChangeMean = (HomesMean-HomesMeanOld)/HomesMeanOld)
+
+cor(MSOAtest$AffordRatio, MSOAtest$PercChangeMean)
+
+MSOAtest %>%
+  ggplot(aes(x = PercChange)) + geom_density()
+
+MSOAtest%>%
+  ggplot(aes(x = log(TourismDensity+1), y = percent_rank(PercChange), colour = HighLUP)) + geom_point()
 
@@
   mutate(TourismDensityRank = rank(TourismDensity, ties.method = "max"),
+         TourismDensity = TourismDensity*1000, #Makes the coefficients easier
          LowUseType =case_when(
@@
     "FALSE"==HighLUP & AffordRank<0.5 ~ 4 #LOW LUP in both LAD and MSOA
-  ) %>% as.factor)  %>%
+  ) %>% as.factor,
+    HighFinance = factor("TRUE"==HighVal & "TRUE"==HighLUP, levels = c("FALSE", "TRUE"))   )  %>%
   left_join(MSOAtoLAD %>%
@@
               summarise(LAD11NM = first(LAD11NM)), by = "LAD11CD")
-
-#Amount of variance in the bootstrap samples 
-#HighVal varies whilst HighLUP is fixed. However, in both of them the variables change as the affordability ratio varies. Not sure if it varies enough to change much though!
-LADRefAverages <- LADModelData %>%
-  group_by(LAD11CD) %>%
-  summarise(HighVal = mean(ifelse(HighVal==TRUE,1,0)),
-            HighLUP = mean(ifelse(HighLUP==TRUE,1,0)),
-            Afford = mean(AffordRatio),
-            Affordsd = sd(AffordRatio)) %>%
-  left_join(., MSOAtoLAD %>% select(LAD11CD, LAD11NM)%>% distinct)
 
@@
 
+  #Relationship between Price change and affordability
+#From this we can see that areas with the most growth are the most unaffordable
+      cor(LADMean$PercChange, LADMean$AffordRatio)
+#However this only really tells us that the most expensive areas previously continue to be the most expensive  
+      cor(LADMean$HomesMeanOld, LADMean$HomesMean)
+
 ```
@@
          AffordRatio2 = scale(AffordRatio)^2,
-         TourismDensityRank = rank(TourismDensity, ties.method = "max")) %>%
+         TourismDensityRank = rank(TourismDensity, ties.method = "max"),
+         TourismDensity = TourismDensity*1000) %>% #Makes the coefficients easier
   left_join(select(LADMean, LAD11CD, LADHighLUP = HighLUP, LADHighVal = HighVal, #Add in Saucy LAD variables
@@
     "FALSE"==HighLUP & "FALSE"==LADHighVal ~ 4 #LOW LUP in both LAD and MSOA
-  ) %>% as.factor
-           )
+  ) %>% as.factor,
+       HighFinance = factor("TRUE"==LADHighVal & "TRUE"==HighLUP, levels = c("FALSE", "TRUE"))     )
+
+  #Relationship between Price change and affordability
+#From this we can see that areas with the most growth are the most unaffordable
+      cor(MSOAMean$PercChange, MSOAMean$AffordRatio)
+#However this only really tells us that the most expensive areas previously continue to be the most expensive  
+      cor(MSOAMean$HomesMeanOld, MSOAMean$HomesMean)
 
@@
 Plots that help explain the data seperation
+
 ```{r}
@@
 bind_rows(MSOAMean %>% mutate(type = "MSOA"), LADMean %>% mutate(type = "LAD")) %>%
-  ggplot(aes(x= AffordRank, y = TourismDensity, colour = HighVal)) + geom_point() +
+  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = HighVal)) + geom_point() +
   facet_wrap(~type) + 
@@
 LADHighLUPResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighLUP")
+set.seed(1235)
+LADHighFinanceResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighFinance")
 
@@
 LADModels <- bind_rows(LinearClassifierCombiner(LADMean,  "HighVal", Formulas, LADHighValResample),
-                       LinearClassifierCombiner(LADMean,  "HighLUP", Formulas, LADHighLUPResample)) %>%
+                       LinearClassifierCombiner(LADMean,  "HighLUP", Formulas, LADHighLUPResample),
+                       LinearClassifierCombiner(LADMean,  "HighFinance", Formulas, LADHighFinanceResample)) %>%
 MarkModels
@@
 LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
-  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
-  mutate(ModelID = rep(1:4,2))
+ # mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
+  mutate(ModelID = rep(1:4,3))
 
@@
 
-LADMODOut %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))
-LADMODOut2 %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median))
+LADMODOut %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median, sd))
+LADMODOut2 %>%  select(-statistic, -std.error) %>% group_by(term) %>% summarise_all(funs(mean, median, sd))
 
@@
 #Formula two provides the most accurate model without over fitting. Being a good model for identifying which LADs will have hhigh value LUPs
-MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", HighValResample, Formulas[[4]])  %>% filter(term !="(Intercept)")
+MSOAMODOut2 <- ExtractClassCoeffs(MSOAMean, "HighVal", MSOAHighValResample, Formulas[[2]])  %>% filter(term !="(Intercept)")
 MSOAMODOut2 %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
@@
 #Including both tourism and the quadratic affordability term produces the best model. Which makes sense given the plot earlier
-MSOAMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", MSOAHighLUPResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
+MSOAMODOut <- ExtractClassCoeffs(MSOAMean, "HighLUP", MSOAHighLUPResample, Formulas[[4]]) %>% filter(term !="(Intercept)")
 MSOAMODOut %>% ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
@@
   group_by(term) %>%
-  summarise_all(funs(mean, median))
+  summarise_all(funs(mean, median)) %>%
+  mutate(estimate = exp(estimate_mean))
 
@@
 using the most sucessful model formula I then use the Bootstrap data to create 501 models then majority vote the response variable.
-This creates a model with an overall lower accuracy but also a smaller standard deviation
-
-```{r}
+
+The Bootstrap model doesn't provide any more information.
+despite the pertubations it tends to always predict certain LADs incorrectly and others correctly.
+This means that the bootstrap predictions are not sufficiently independent to make the proocess worthwhile.
+
+```{r}
+#Creates a boots model which can be analysed
 
@@
 LADHighValResample200 <- vfold_cv(LADMean, v = 5, repeats = 200, strata = "HighVal")
-test <- LADMean %>% mutate(Reference = HighVal) %>%
-  ResampledModelPerf(., LADHighValResample200, Formulas[[2]])
-
-set.seed(1235)
-
-TestResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighVal")
-
-TestResample <- vfold_cv(LADMean, v = 5, repeats = 100, strata = "HighVal")
-LADModelData2 <- LADModelData %>%
-  filter(ID<102)
 
 setwd(basewd)
-if(file.exists("LADBootVoteModel.rds")){
-
-  LADBootVoteModel <- readRDS("LADBootVoteModel.rds")
-
-  }else{
-    LADBootVoteModel <- 1:100 %>% map_df(~{ 
-       print(.x)
-        trainrows <- rsample2caret(TestResample)$index[[.x]]
-        testrows <-  rsample2caret(TestResample)$indexOut[[.x]]
-
-        test <- LADModelData %>% 
-          mutate(Reference = as.factor(HomesMedian < LowUseMedian)) %>% 
-          BootstrapResampledModelPerf(., trainrows, 
-                                      testrows, 
-                                      as.formula(Reference ~ TourismDensity + AffordRatio)) # creates a dataframe out predictions
-
-      ConfOut <- LADMean %>% mutate(Reference = factor(HomesMedian < LowUseMedian, levels = c("FALSE", "TRUE")))  %>% 
-        slice(testrows) %>% pull(Reference) %>%
-        confusionMatrix( data =factor( rowMeans(test) >0.5, levels = c("FALSE", "TRUE")), reference = .)
-
-          ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
-          mutate(sample = .x)
-
-    })
-
-}
-
-#has a lower mean but a much small standard deviation
-LADBootVoteModel %>% SummariseModels()
-
-bind_rows(LADModels %>% 
-            filter(IncAfford2 == FALSE,  IncTourism == TRUE, Dependent=="HighVal") %>% 
-            select(Accuracy) %>% mutate(type = "Basic"),
-          #select(test, Accuracy) %>% mutate(type = "big repeats"),
-          select(LADBootVoteModel, Accuracy) %>% mutate(type = "Boot")) %>%
-  ggplot(aes(x = Accuracy, colour = type)) + geom_density() +
-  ggtitle("Distribution of model results. Bootstrap has much tighter distribution")
-
-LADModels %>% 
-            filter(IncAfford2 == FALSE, IncTourism == TRUE) %>% 
-            select(Accuracy) %>% mutate(type = "Basic") %>% pull(Accuracy) %>%
-quantile(.,  probs = c(5, 50, 95)/100)
-quantile(LADBootVoteModel$Accuracy,  probs = c(5, 50, 95)/100)
-
-#Creates a boots model which can be analysed more
-
-set.seed(1235)
-LADHighValResample200 <- vfold_cv(LADMean, v = 5, repeats = 200, strata = "HighVal")
-
 if(file.exists("LADBootVoteModelBig.rds")){
@@
 
+BootRes <- (1:nrow(LADHighValResample200)) %>%
+  map_df(~{
+
+    test <- LADBootVoteModelBig %>%
+      filter(ID==.x)
+
+      ConfOut <-  confusionMatrix( data =test$PredProbs>0.5, reference = test$Reference, positive = "TRUE")
+     #metrics(data = ., truth = Reference, estimate = factor(PredProbs>0.5, levels = "TRUTH", "FALSE"))
+
+       ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>% 
+      bind_cols(ConfOut$byClass %>% t %>% data.frame() %>% as.tibble) %>%
+      mutate(sample = .x)
+
+  })
+
+BootRes %>% SummariseModels()
+
  test <- LADBootVoteModelBig %>%
@@
    mutate(FractCorrect = `TRUE`/200) %>%
-   left_join(LADRefAverages %>% select(-Afford, -Affordsd, -HighLUP)) %>%
+   left_join(LADMean %>% select(LAD11CD, HighValCount, LAD11NM, AffordRank, LowUseRank, LowUseAfford, TourismDensity)) %>%
    left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
@@
 
- test2 %>% ggplot(aes(y = FractCorrect, x = HighVal)) + geom_jitter()
-
-  test2 %>% ggplot(aes(y = FractCorrect, x = PercDiff, colour = is.na(Ego1TourismDens))) + geom_jitter()
-
- table(test2$FractCorrect>0.5)
-
- is.na(test2$Ego1TourismDens) %>% table
+   test2 %>%
+  ggplot(aes(x= AffordRank, y = LowUseRank, colour = FractCorrect>.1)) + geom_point() +
+    geom_vline(xintercept  = 0.5)+
+    geom_hline(yintercept = 0.5) +
+    labs(title = "Seperating Low-Use type  by affordability", x = "Affordability percentage rank", y = "Low-Use percentile rank")
+
+  test2 %>%
+  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = FractCorrect>.1)) + geom_point()
 

### 2018-08-20 Functions/BootstrapAllData.R

@@ -5,8 +5,8 @@ BootstrapAllData <- function(DATAdf, GroupingVars = c("Class", "CountryClass"), 
     group_by(LAD11CD) %>%
     summarise(LAD11NM = first(LAD11NM),
               LSOA = n(),
-              Homes = sum(Homes),
-              LowUse = sum(LowUse)) %>%
+              Homes = sum(Homes, na.rm = TRUE),
+              LowUse = sum(LowUse, na.rm = TRUE)) %>%
     arrange(Homes)
   
   #Find what needs to be bootstrapped
@@ -19,7 +19,7 @@ BootstrapAllData <- function(DATAdf, GroupingVars = c("Class", "CountryClass"), 
     1:length(newLADsnames)  %>% walk(~{
       print(paste0("Bootstrapping ", LADBootInfo$LAD11NM[LADBootInfo$LAD11CD==newLADsnames[.x]],". LADs remaining ", length(newLADsnames)-.x))
       DATAdf %>% 
-        filter(LAD11CD == newLADsnames[.x]) %>%
+        filter(LAD11CD == newLADsnames[.x], !is.na(Homes)) %>% #removes errors caused by the unassigned empty homes
         DistribCompareBootstrapper(., RandomSeed, Reps, type=NULL, PropertyTypes, Limit = LimitValue, GroupVars = GroupingVars ) %>%
         saveRDS(., file = paste0( newLADsnames[.x], ".rds"))
       gc()

### 2018-08-20 Functions/CleanForPlotClassDiff .R

@@ -1,6 +1,11 @@
-CleanForPlotClassDiff <- function(df){
-  df %>%  
-    group_by(ID, Class) %>%
+CleanForPlotClassDiff <- function(df,...){
+  #df, the stacked output of a grouped bootstrap summary
+  #A single grouping variable is chosen in the ... argument. Any more and it will have an error
+  
+  group_var <- quos(...) 
+  
+  df%>%
+    group_by(ID, !!!group_var) %>%
     summarise(Homes = sum(Homes), 
               LowUse = sum(LowUse)) %>%
     group_by(ID)%>%
@@ -9,5 +14,6 @@ CleanForPlotClassDiff <- function(df){
     mutate(LowUseRatio1 = (LowUseDistrib/0.25)-1,
            HomesRatio1 = (HomesDistrib/0.25)-1,
            LowUseRatio2 = (LowUseDistrib-HomesDistrib)/HomesDistrib) %>%
-    ungroup
+    ungroup %>%
+    rename(Quartile = 2) #amazing!
 }

### 2018-08-20 Functions/CreateGeogModelData.R

@@ -6,7 +6,10 @@ CreateGeogModelData <- function(target, path){
   print("Load files")
   Afford <- list.files(path, full.names = TRUE) %>%
     map_df(~readRDS(.x)) %>%
-    left_join(select(IncomeEst, Yearly.income, MSOA11CD), by = "MSOA11CD") 
+    left_join(select(IncomeEst, Yearly.income, MSOA11CD), by = "MSOA11CD") %>%
+    left_join(., list.files(file.path(basewd, "BootstrapMSOAOldPrices"), full.names = TRUE) %>% # load the old prices
+                map_df(~readRDS(.x)) %>% select(MSOA11CD, ID, MSOAHomesMedian:LADHomesMean) %>% 
+                set_names(c(names(.)[1:3], paste0(names(.)[-c(1:3)], "Old"))), by = c("MSOA11CD", "ID"))
   
   #reverse the selection safely
   if(target=="LAD"){
@@ -32,14 +35,16 @@ CreateGeogModelData <- function(target, path){
                 Homes = sum(Homes), #sum(Yearly.income*Homes)/sum(Homes),
                 HomesMedian = first(HomesMedian),
                 HomesMean = first(HomesMean),
-                LowUseMedian = first(LowUseMedian)) 
+                LowUseMedian = first(LowUseMedian),
+                HomesMedianOld = first(HomesMedianOld),
+                HomesMeanOld = first(HomesMeanOld)) 
   } else {
     Afford3 <- Afford2
   }
   
   Afford3 <- Afford3 %>%
     mutate(LowUsePerc = LowUse/Homes,
-           AffordRatio = HomesMedian/Yearly.income,
+           AffordRatio = HomesMean/Yearly.income,
            AffordRatioScale = scale(AffordRatio),
            AffordRationScale2 = AffordRatioScale^2,
            AffordRationScale3 = AffordRatioScale^3,
@@ -63,6 +68,7 @@ CreateGeogModelData <- function(target, path){
            HotelDensity = Hotel/Homes,
            TourismDensityRank = rank(TourismDensity, ties.method = "max"),
            MeanMedianRatio = HomesMean/HomesMedian,  #Hindicates the skew of the area large skew could indicate LUP presence
+           PercChange = (HomesMean-HomesMeanOld)/HomesMeanOld,
            HighVal = as.factor(HomesMedian < LowUseMedian) #Reference Variable
            ) %>%
   group_by(ID) %>%

### 2018-08-20 Functions/PlotClassDiff.R

@@ -10,7 +10,7 @@ PlotClassDiff <-function(df, Var= "LowUseRatio1"){
   
   df %>% 
     rename_(Ratio = Var) %>%
-      ggplot(., aes(x= Class, y = Ratio, fill = Class)) + 
+      ggplot(., aes(x= Quartile, y = Ratio, fill = Quartile)) + 
      geom_boxplot() + 
      labs(y = "% difference from expected", x= "Price Quartile") +
     scale_fill_manual(values = colourTypes) +

### 2018-08-20 Functions/SubsetPrice.R

@@ -30,7 +30,7 @@ SubsetPrice <- function(df, type = NULL, PropertyTypes = NULL){
   #The  model used to take multiple councils if there was overlap, but this caused some strange
   #Problems So I removed it. The current version only takes a single LAD
   pricesTemp %>%
-    select( LSOA11CD, Price =X2, X15, PropType = X5, CountryClass, MSOA11CD) %>%
+    select( LSOA11CD, Price =X2, X15, PropType = X5, CountryClass, MSOA11CD, Affordability, CountryAffordClass) %>%
     mutate(Price = as.numeric(Price)) #there was some number overflow thing changing to numeric solves this
   
 }

### 2018-08-20 SubCode/AuxdataLoad.R

@@ -3,110 +3,62 @@
 #Council tax bands from VOA
 #https://www.gov.uk/government/statistics/council-tax-stock-of-properties-2016
 
-setwd(DataFolder)
-
-CTtaxstock<- read_csv("Table_CTSOP1.1_2016.csv")
-
-pop <- read_csv("SAPE2.csv")
-
-EW <- inner_join(select(CTtaxstock, ECODE, ALL_PROPERTIES),select(pop, `Area Codes`, `All Ages`),
-                 by=c("ECODE" = "Area Codes")) %>% setNames(c("ECODE", "Homes", "Pop"))
-
-
 #Load the LSOA shape data for EW 
 
 
 
 # Load Post code data
 
-#This chunk checks the exiatane of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup. Creating the lookup takes quite a lot of time so it is good to only have to do it once.
-
-
-if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
-PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
+#needed for the LAD names
+if(file.exists(file.path(DataFolder, "CorePstCd.rds"))){
+  
+  CorePstCd <- readRDS(file.path(DataFolder, "CorePstCd.rds"))
+  
 } else {
-  #shape file used in the Match2Postocde function
-  setwd(LSOAshapedata)
-  shape <- readOGR(dsn = list.files(pattern = "shp"))
-  
-  #this takes a while
-  PstCdLSOA.raw  <- MatchPostCode2LSOA(file.path(basewd, "ONS postcodes May17", "Data", "CSV"),
-                        file.path(basewd, "ONS postcodes May17", "Doc") )
   
   
+  print("Loading Postcode data")
+  LADconv <- read_csv(file.path(AddGeog, 
+                                "Local_Authority_Districts_December_2016_Names_and_Codes_in_the_United_Kingdom.csv")) %>%
+    select(LAD11CD=LAD16CD, LAD11NM = LAD16NM)
   
-  setwd(DataFolder)
-  saveRDS(PstCdLSOA.raw, "PstCdLSOA.rds")
-  rm(shape)
+  #This is used purely for westminster
[…]

### 2018-08-20 SubCode/LoadProcessTourism.R

@@ -1,0 +1,72 @@
+setwd(file.path(basewd, "VOA data"))
+
+#Creates Tourism dataframe at LSOA level
+Tourism <- read_delim("uk-englandwales-ndr-2017-listentries-compiled-epoch-0002-baseline-csv.csv", 
+                      delim = "*", col_names = F) %>%
+  mutate(X15 = gsub(" ", "", X15)) %>%
+  left_join(., CorePstCd, by = c("X15" = "Postcode")) %>%
+  #filter(!is.na(LAD11CD)) %>%
+  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
+  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
+         Hotel = grepl("(HOTEL)|(HOSTEL)",X6)) %>%
+  group_by(MSOA11CD) %>% #Have X6 as a grouping variable to 
+  summarise(Tourism = n(),
+            Guest = sum(Guest),
+            Hotel = sum(Hotel))  %>%
+  full_join(MSOAtoLAD,., by="MSOA11CD") %>%  #ensures all MSOA
+  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
+         Hotel = ifelse(is.na(Hotel), 0, Hotel),
+         Guest = ifelse(is.na(Guest), 0, Guest))
+
+MSOAAdjacency <- readShapeSpatial(file.path(basewd,"/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
+                                            "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp"))
+
+test <- poly2nb(MSOAAdjacency)
+
+MSOAAdjMat = nb2mat(test, style="B",zero.policy=T)
+
+#Add MSOA codes so that they are added as the vertex names
+colnames(MSOAAdjMat) <- MSOAAdjacency$msoa11cd
+
+MSOAgraph <- graph.adjacency(MSOAAdjMat, mode = "undirected")
+
+MSOAEgoList1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
[…]

### 2018-08-20 SubCode/Setup.R

@@ -20,8 +20,7 @@ DataFolder <- file.path(basewd, "Data")
 ShapeFiles <- file.path(basewd,"ShapeFiles/statistical-gis-boundaries-london/ESRI")
 PostcodeLookups <- file.path(DataFolder, "PostcodeLookups")
 ExcelLookups <- file.path(basewd, "ExcelLookups")
-ONSpostcodes <- file.path(basewd, "ONS postcodes May17", "Data", "CSV")
-ONSpostcodeMeta <- file.path(basewd, "ONS postcodes May17", "Doc")
+ONSpostcodes <- file.path(basewd, "ONSPD")
 LSOAshapedata <- file.path(basewd,"ShapeFiles",
                            "Lower_Layer_Super_Output_Areas_December_2011_Generalised_Clipped__Boundaries_in_England_and_Wales")
 AddGeog <- file.path(basewd, "AdditionalGeographies")

### 2018-08-20 PaperCode.Rmd
Triple prediction model
This update has no bootstrap model but uses a normal logistic regression, to predict three variables.

@@
 ```{r}
+
+setwd(file.path(basewd, "BootstrapAffordQuartiles"))
+BootStrapQuartiles <- LoadBootstrapData()
+
 #Plot for all data
@@
     labs(title = "Seperating Low-Use type  by affordability", x = "Affordability percentage rank", y = "Low-Use percentile rank")
-  SaveFig("LowUseAffordcolour.pdf")
+  #SaveFig("LowUseAffordcolour.pdf")
 
@@
 
+#Empty Homes tax
+
+Calculates the vancouver tax
+
+welsh data comes from 
+https://statswales.gov.wales/Catalogue/Local-Government/Finance/Council-Tax/Levels/counciltaxlevels-by-billingauthority-band
+
+```{r}
+setwd(DataFolder)
+WelshTax <- read_csv("WelshCTax.csv", skip = 6, n_max = 23) %>%
+  select(-X1) %>%
+  mutate(CouncilTax = rowSums(.[-1])*1000) %>%
+  rename(LAD11NM = X2) %>%
+  left_join(., MSOAtoLAD %>% 
+              select(LAD11CD, LAD11NM) %>%
+              distinct(LAD11NM, .keep_all = T)) %>%
+  filter(!is.na(LAD11CD)) %>%
+    select(LAD11CD, CouncilTax)
+
+QRC2017 <- read_xlsx("QRC4-2017-2018.xlsx", sheet = 2, skip = 2) %>%
+  select(3:4) %>%
+  set_names("LAD11CD", "CouncilTax") %>%
+  mutate(CouncilTax = CouncilTax*1000) %>%
+  bind_rows(WelshTax)
+
+EmptyTax <- LADMean %>% 
+  left_join(., QRC2017)%>%
+  left_join(MSOAtoLAD %>%
+              group_by(LAD11CD) %>%
+              summarise(Pop = sum(Pop))) %>%
+  mutate(EmptyTax = LowUse*LowUseMean*.01,
+         EmptyOfCouncil = EmptyTax/CouncilTax,
+         TaxPop = EmptyTax/Pop)
+
+sum(EmptyTax$EmptyTax)/1e6
+mean(EmptyTax$EmptyOfCouncil)
+median(EmptyTax$EmptyOfCouncil)
+
+mean(EmptyTax$EmptyTax)
+median(EmptyTax$EmptyTax)
+
+sum(EmptyTax$EmptyTax)/sum(EmptyTax$CouncilTax)
+
+EmptyTax %>%
+  ggplot(aes(x =EmptyOfCouncil)) + geom_density() +
+  coord_cartesian(x=c(0,0.7)) +
+  scale_x_continuous(labels = scales::percent) +
+  labs(title = "Distribution of value of Empty homes tax in terms of council tax by local authority", 
+       x = "Percent of council tax value")
+
+EmptyTax %>%
+  select(EmptyOfCouncil, LAD11NM) %>%
+  arrange(EmptyOfCouncil) %>%
+  top_n(5,EmptyOfCouncil)
+
+rm(WelshTax);rm(QRC2017)
+
+```
+
 #Rural Analysis
@@
 
-LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
+LADModTab <-LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
  # mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
   mutate(ModelID = rep(1:4,3))
+
+LADModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
+  slice(c(2,8,10)) %>%
+  xtable(., caption="Summary of viable Local authority models",
+       label = "tab:LADmodels") %>% 
+  print(., type="latex", file=file.path(TexTables,"LADmodels.tex"))
 
@@
 
+LADMODOut3 <- ExtractClassCoeffs(LADMean, "HighFinance", LADHighLUPResample, Formulas[[2]]) %>% filter(term !="(Intercept)")
+LADMODOut3 %>%  ggplot( aes(x = term, y = estimate)) + geom_boxplot() #Model Coefficients
+LADMODOut3 %>%  ggplot( aes(x = term, y = p.value)) + geom_boxplot() #Model p.values
+
 ```
@@
 
-MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
+MSOAModTab <- MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
   mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
   mutate(ModelID = rep(1:4,2))
+
+MSOAModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
+  slice(c(4)) %>%
+  xtable(., caption="Summary of viable MSOA authority models",
+       label = "tab:MSOAmodels") %>% 
+  print(., type="latex", file=file.path(TexTables,"MSOAmodels.tex"))
 
@@
 
+bind_rows(LADMODOut %>% mutate(type = "Financialised LAD"),
+          LADMODOut3 %>% mutate(type = "Highly Financialised LAD"),
+          LADMODOut2 %>% mutate(type = "High LUP % LAD"),
+          MSOAMODOut %>% mutate(type = "High LUP % MSOA")
+) %>%
+  ggplot( aes(x = term, y = estimate, fill = term)) + geom_boxplot()+
+  facet_wrap(~type)+
+    theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1))
+SaveFig("ModelCoeffs.pdf")
+
 ```
@@
    mutate(FractCorrect = `TRUE`/200) %>%
-   left_join(LADMean %>% select(LAD11CD, HighValCount, LAD11NM, AffordRank, LowUseRank, LowUseAfford, TourismDensity)) %>%
+   left_join(LADMean %>% select(LAD11CD, HighValCount, LAD11NM, AffordRank, 
+                                LowUseRank, LowUseAfford, TourismDensity,HighVal)) %>%
    left_join(select(LADMean,LAD11CD, HomesMedian, MedianDiff, Ego1TourismDens )) %>%
@@
 
-```
-
-Boot MSOA
-
-```{r}
-FormulaMSOA <- as.formula(Reference ~ TourismDensity + AffordRatio)
-
-set.seed(1983)
-TestResample <- vfold_cv(MSOAMean, v = 5, repeats = 20, strata = "HighLUP")
-
-BootVoteModel <- 1:100 %>% map(~{ 
-   print(.x)
-    trainrows <- rsample2caret(TestResample)$index[[.x]]
-    testrows <-  rsample2caret(TestResample)$indexOut[[.x]]
-
-    test <- MSOAModelData %>% 
-      mutate(Reference = HighLUP) %>% 
-      BootstrapResampledModelPerf(., trainrows, testrows, FormulaMSOA ) # creates a dataframe out predictions
-
-    PredVect <- factor( rowMeans(test) >0.5, levels = c("FALSE", "TRUE"))
-
-  ConfOut <- MSOAMean %>% mutate(Reference = factor(HighLUP, levels = c("FALSE", "TRUE")))  %>% 
-    slice(testrows) %>% pull(Reference) %>%
-    confusionMatrix( data = PredVect, reference = .)
-
-      ConfOut$overall %>% t %>% data.frame() %>% as.tibble %>%
-      mutate(sample = .x)
-
-})
-
-rm(FormulaMSOA)
-
-test<- MSOAModelData %>% group_by(ID)%>% summarise(counts= n())
+    test2 %>%
+  ggplot(aes(x= AffordRank, y = log(TourismDensity), colour = FractCorrect>.1)) + geom_point()
 
@@
 
-PredictData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapAllLADs") )%>%  
+PredictData <-CreateGeogModelData("LAD", file.path(basewd, "BootstrapAllLADs") ) %>%  
   MeanModelData(., "LAD")
 
-FormulaBootLAD<- ModelFormula <- as.formula(Reference ~ TourismDensity + AffordRatio)
-
-trainrows <- 1:nrow(LADModelData)
-
-BootstrapLADModels <- LADModelData %>% 
-  mutate(Reference = as.factor(HighVal)) %>% 
-  BootstrapResampledModelPerf(., trainrows, 0 , FormulaBootLAD, ModsOut = TRUE ) # creates a list of models
-
-VoteResults<- BootstrapLADModels %>% map(~{
- preds2 <- tibble(x = predict(.x, newdata = PredictData, type = "response" )>0.5)
-
-}) %>% bind_cols() %>% rowSums(.) %>%
-  tibble(Votes = .) %>%
-  mutate(Prob = Votes/length(BootstrapLADModels), 
-         Class = Prob>0.5,
-         LAD11CD = PredictData$LAD11CD) %>%
-  left_join(., AdjustmentProb, by = "Votes") %>%
-  mutate(AdjustedProb = (Prob-0.5)*ConfProb+0.5)
-
-WholeCountry <- LADMean %>% select(LAD11CD, Votes = HighValCount) %>%
-  mutate(Prob = Votes/max(Votes), #a bit dodgey to do that but I know there are 100% outcomes
-         AdjustedProb = Prob,
-         Class = Prob>0.5) %>% #The addujsted probability of the collected dataset is simply the probability that the medianHOMes<MedianLUPs so no change us needed
-  bind_rows(VoteResults) %>%
-  left_join(MSOAtoLAD %>% group_by(LAD11CD, LAD11NM) %>% summarise(Pop = sum(Pop))) %>%
-  mutate(Diff = Prob-AdjustedProb)
+FormulaBootLAD<-as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatioScale2)
+
+ModPreds <- c("HighVal", "HighLUP", "HighFinance") %>%
+  map(~{
+
+EWMod <- LADMean %>% 
+  rename_(Reference = .x )  %>% 
+  mutate(Reference = as.factor(Reference)) %>%
+      glm(formula = FormulaBootLAD, data = ., family=binomial(link='logit'))
+
+    PredictData  %>%
+      predict(EWMod, newdata = ., type = "response" ) %>%
+      as.tibble(.) %>% setNames(.x)
+
+}) %>% bind_cols()
+
+EWMod2<-ModPreds %>% mutate_all(funs((.>0.5)*1)) %>%
+  mutate_all(funs(ifelse(.==0, 0.2,0.8))) %>%
+               mutate(LAD11CD = PredictData$LAD11CD)
+
+WholeCountry <- LADMean %>% select(LAD11CD, HighVal = HighValCount, HighLUP ) %>%
+  mutate(HighVal = HighVal/max(HighVal), #a bit dodgey to do that but I know there are 100% outcomes
+         HighLUP = ifelse(HighLUP =="TRUE", 1, 0),
+                  HighFinance = HighVal*HighLUP) %>% #The addujsted probability of the collected dataset is simply the probability that the medianHOMes<MedianLUPs so no change us needed
+  bind_rows(EWMod2) %>%
+  left_join(EW2 %>% group_by(LAD11CD, LAD11NM) %>% summarise(Pop = sum(Pop)))
 
@@
 
-PopAffected <- ((PopAffected >WholeCountry$AdjustedProb)*WholeCountry$Pop) %>%  t %>% rowSums(.) %>%
-  tibble(InvestmentPop = .) %>%
-  mutate(PopPerc = InvestmentPop/ sum(WholeCountry$Pop))
-
-PopAffected %>% ggplot(aes(x = PopPerc)) + geom_density() +
+PopAffected <- tibble(HighValPop =  ((PopAffected <WholeCountry$HighVal)*WholeCountry$Pop) %>%  t %>% rowSums(.),
+         HighFinancePop =  ((PopAffected <WholeCountry$HighFinance)*WholeCountry$Pop) %>%  t %>% rowSums(.)) %>%
+  mutate(PopPerc = HighValPop/ sum(WholeCountry$Pop),
+         FinancePopPerc = HighFinancePop/ sum(WholeCountry$Pop))
+
+PopAffected %>% 
+  select(PopPerc, FinancePopPerc) %>%
+  gather(key, value) %>%
+  mutate(key = ifelse(key == "PopPerc", "Financialised", "Highly Financialised")) %>%
+  ggplot(aes(x = value)) + geom_density() +
+  facet_wrap(~key, scales = "free_x") +
   labs(title ="Estimate percentage of the Population living in areas with high LUP values",
@@
 
-```
-
-#Predict MSOA High LUP
-
-```{r}
-
-PredictDataMSOA <-CreateGeogModelData("MSOA", file.path(basewd, "BootstrapAllLADs") )%>%  
-  MeanModelData(., "MSOA")
-
-FormulaMSOAPredAll <- as.formula(Reference ~ TourismDensity+ AffordRatio + AffordRatioScale2)
-
-PredictAllMSOAMod <- MSOAMean %>% 
-  mutate(Reference = as.factor(HighLUP))  %>%
-      glm(formula =FormulaMSOAPredAll , data = ., family=binomial(link='logit'))
-
-summary(PredictAllMSOA)
-
-MSOAWholeCountry <- tibble(HighLUP = predict(PredictAllMSOAMod, newdata = PredictDataMSOA, type = "response" )>0.5,
-                  MSOA11CD = PredictDataMSOA$MSOA11CD) %>%
-  mutate(HighLUP = as.factor(HighLUP)) %>%
-  bind_rows(select(MSOAMean, MSOA11CD, HighLUP))
-
-```
-
-#Plot Model Outputs
-
-##LAD model
+quantile(PopAffected$PopPerc,  probs = c(2.5 ,97.5)/100)
+quantile(PopAffected$FinancePopPerc,  probs = c(2.5 ,97.5)/100)
+
+```
+
+#Plot maps
+
+##Model Outputs
 ```{r}
@@
 
-LADShape2 <- LADShape %>% left_join(WholeCountry, by = c("lad14cd" = "LAD11CD")) %>%
-  filter(!is.na(Class))
-
+LADShape2 <- WholeCountry %>%
+  mutate(HighVal = HighVal>0.5,
+         HighLUP = HighLUP>0.5,
+         HighFinance = HighFinance>0.5) %>% 
+  select(LAD11CD:HighFinance) %>%
+  gather(key = Type, value = Status, -LAD11CD) %>%
+  mutate(Type = case_when(
+    Type =="HighFinance" ~ "Highly Financialized",
+    Type == "HighLUP" ~"Large LUP percentage",
+    Type == "HighVal" ~"Some Financialization"
+  ) %>% as.factor(.) %>% fct_relevel("Highly Financialized", after = 2),
+  Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)) %>%
+  left_join(LADShape,., by = c("lad14cd" = "LAD11CD")
+            ) %>% # Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)
+  filter(!is.na(Status))
+
+#plot and save
 ggplot(LADShape2) +
-  geom_sf(aes(fill = Class)) + 
-  labs(title = "Local Authorities classified as having predominently high value LUPs")
+  geom_sf(aes(fill = Status)) + 
+  facet_wrap(~Type)+
+  labs(title = "LUP and financialization status in England and Wales") +
+   theme(axis.title.x=element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank(),
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())
 SaveFig("EWHighValMap.pdf")
@@
 
+#Plot LUP perc
+
+```{r}
+
+LSOAshape <- st_read(LSOAshapedata) %>%
+  left_join(DATAdf, by = c("lsoa11cd"="LSOA11CD")) %>% filter(grepl("Kensington and Chelsea",lsoa11nm)|  grepl("Bradford",lsoa11nm),
+                             LAD11CD=="E08000032"|LAD11CD=="E09000020")
+
+colourTypes <- c( "0-10" = "#F8766D", 
+                    "11-20" = "#A3A500", 
+                   "21-30" ="#00BF7D", 
+                   "30+" = "#00B0F6")
+
+LowUseColours <- gg_color_hue(4)
+names(LowUseColours) <- c( "0-10", "11-20","21-30","30+")
+
+gg_color_hue <- function(n) {
+  hues = seq(15, 375, length = n + 1)
+  hcl(h = hues, l = 65, c = 100)[1:n]
+}
+
+LSOAshape %>%
+  filter(LAD11CD=="E09000020")%>%
+ggplot(.)+  geom_sf(aes(fill = LowuseClass))  +
+   theme(axis.title.x=element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank(),
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())+
+  ggtitle("Low Use percentage by LSOA in Kensington and Chelsea")
+SaveFig("ChelseaMap.pdf")
+
+LSOAshape %>%
+  filter(LAD11CD=="E08000032")%>%
+ggplot(.)+  geom_sf(aes(fill = LowuseClass))  +
+      scale_fill_manual(values = LowUseColours) +
+   theme(axis.title.x=element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank(),
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())+
+  ggtitle("Low Use percentage by LSOA in Bradford")
+SaveFig("BradfordMap.pdf")
+
+```
+
 #MSOA model
 
-```{r}
-
-MSOAshapefile <-file.path(basewd,
-                         "/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
-                         "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp")
-
-MSOAShape <- st_read(MSOAshapefile) %>% left_join(MSOAWholeCountry, by = c("msoa11cd" = "MSOA11CD")) %>%
-  filter(!is.na(HighLUP))
-
-ggplot(MSOAShape2) +
-  geom_sf(aes(fill = HighLUP, colour = HighLUP)) + 
-  labs(title = "Local Authorities classified as having above the median percentage of LUPs")
-SaveFig("EWHighLUPMap.pdf")
-
-```
+Not Neccesary
+
+```{r}
+# 
+# MSOAshapefile <-file.path(basewd,
+#                          "/ShapeFiles/Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales",
+#                          "Middle_Layer_Super_Output_Areas_December_2011_Super_Generalised_Clipped_Boundaries_in_England_and_Wales.shp")
+# 
+# MSOAShape <- st_read(MSOAshapefile) %>% left_join(MSOAWholeCountry, by = c("msoa11cd" = "MSOA11CD")) %>%
+#   filter(!is.na(HighLUP))
+# 
+# 
+# ggplot(MSOAShape2) +
+#   geom_sf(aes(fill = HighLUP, colour = HighLUP)) + 
+#   labs(title = "Local Authorities classified as having above the median percentage of LUPs")
+# SaveFig("EWHighLUPMap.pdf")
+
+```

### 2018-08-20 Functions/CreateGeogModelData.R

@@ -36,6 +36,7 @@ CreateGeogModelData <- function(target, path){
                 HomesMedian = first(HomesMedian),
                 HomesMean = first(HomesMean),
                 LowUseMedian = first(LowUseMedian),
+                LowUseMean = first(LowUseMean),
                 HomesMedianOld = first(HomesMedianOld),
                 HomesMeanOld = first(HomesMeanOld)) 
   } else {

### 2018-08-20 Functions/MeanModelData.R

@@ -14,6 +14,7 @@ MeanModelData <- function(ModelData, target){
               HomesMedian = mean(HomesMedian),
               HomesMean = mean(HomesMean),
               LowUseMedian = mean(LowUseMedian),
+              LowUseMean = mean(LowUseMean),
               Yearly.income = mean(Yearly.income),
               Region = first(Region),
               HomesMedianOld = mean(HomesMedianOld),

### 2018-08-20 Functions/PlotClassDiff.R

@@ -3,17 +3,11 @@ PlotClassDiff <-function(df, Var= "LowUseRatio1"){
    #df: The dataframe of a specific LAD from BootStrapRES
    #Var the column name that you wish to be plotted
   
-   colourTypes <- c( "Lower" = "#F8766D", 
-                    "Lower-Mid" = "#A3A500", 
-                   "Upper-Mid" ="#00BF7D", 
-                   "Upper" = "#00B0F6")
-  
   df %>% 
     rename_(Ratio = Var) %>%
       ggplot(., aes(x= Quartile, y = Ratio, fill = Quartile)) + 
      geom_boxplot() + 
      labs(y = "% difference from expected", x= "Price Quartile") +
-    scale_fill_manual(values = colourTypes) +
     theme(legend.position = "none", axis.text.x = element_text(angle = 15, hjust = 1)) +
     scale_y_continuous(labels = scales::percent)
    

### 2018-09-27 PaperCode.Rmd
Pre-submission work
The changes made just before submission to the journel

@@
 
+install.packages("breakDown") provides a plot of the glm!
+
 schedule 2 part 5 section
+
+Palgrave nature inter-discplinary journel
+https://www.nature.com/palcomms/for-authors#edboard
+
+poss editors
+Dr Lei Wang, manchester Urban
+Tim Hall, university winchester
+
+maybe
+Trifon I Missov, Max planck demographics
+
+reviewr
+Glen Bramley at herriot watt
+
+ian caswell ucl mega journel
+Kathrine sharp
+
+Reviewers on plos
+
+search term: data mining
+César A Hidalgo
+Massachusetts Institute of tech
+
+search term: demography
+Celine Rozenblat
+University of Lausanne
+SWITZERLAND
+
+Heidi Harriman Ewen
+University of Georgia
+UNITED STATES
+
+The information provided in response to your request is copyright Gateshead Council unless otherwise endorsed.
+Granting access to this information under the Freedom of Information Act does not permit you to re-use the information provided for commercial purposes, for photocopying or reproduction in any form.
+If you wish to re-use the information you need to apply for a Licence.
+You can do this by writing to Tanya Rossington, Information Rights Officer, Corporate Services and Governance, 1st Floor, Civic Centre, Regent Street, Gateshead, NE8 1HH.
+You may be required to pay a fee or comply with conditions for permitted re-use.
 
@@
 ```{r}
-DataCover <-DATAdf  %>%
-                #filter(is.na(MSOA11CD)) %>%
+#Gives Region Data
+#Need to put in region names
+DataCover <-
+ DATAdf %>% 
+   filter(!is.na(MSOA11CD)) %>%
+  group_by(LAD11CD) %>%
+  summarise(Pop = sum(Pop),
+            Homes = sum(Homes),
+            LUPs = sum(LowUse),
+            LSOA = length(unique(LSOA11CD)),
+            MSOA = length(unique(MSOA11CD)),
+            Region = first(Region),
+            LAD = 1) %>%
+  select(-LAD11CD) %>%
+  group_by(Region) %>%
+  summarise_all(funs(sum)) %>%
+  left_join(.,
+            MSOAtoLAD %>%
+  select(LAD11CD, Region, LAD11NM) %>%
+  distinct(LAD11CD, .keep_all = T) %>%
+  group_by(Region) %>%
+  summarise(LADPerc = n())
+) %>% 
+  mutate(LADPerc = LAD/LADPerc,
+         Region2 = c("North East", "North West", "York and Humber", "West Midlands", "East England", "London", "South East", "South West", "Wales")) %>% 
+  arrange(Region)
+
+Total <- DataCover %>% summarise_if(is.numeric, sum) %>%
+  mutate(
+    Region = "Total",
+    LADPerc = LAD/348)
+
+DataCover <-bind_rows(DataCover, Total) %>%
+  mutate(LADPerc = round(LADPerc*100)) %>%
+  rename(`% of LADs` = LADPerc) %>%
+  mutate_if(is.numeric, as.integer)
+
+DataCover 
+DataCover %>% mutate(Perc = LUPs/Homes)
+
+xtable(DataCover, caption="Summary of collected dataset",
+       label = "tab:DataCover") %>% 
+  print(., type="latex", file=file.path(TexTables,"DataCover.tex"), include.rownames=FALSE)
+
+rm(DataCover);rm(Total)
+
+#lost LUPS
+
+LostLowUse <- DATAdf %>%
+  filter(is.na(MSOA11CD)) %>%
+  group_by(LAD11CD) %>%
+  summarise(Lost = sum(LowUse)) %>%
+  arrange(-Lost) %>%
+  mutate(cumsum = cumsum(Lost),
+         cumperc = cumsum/sum(Lost))
+
+sum(LostLowUse$Lost)
+
+  DATAdf  %>%
+                filter(!is.na(MSOA11CD)) %>%
   summarise(
@@
 
-DataCover
-
-xtable(DataCover, caption="Summary of collected data coverage",
-       label = "tab:DataCover") %>% 
-  print(., type="latex", file=file.path(TexTables,"DataCover.tex"))
-
-rm(DataCover)
-
-#lost LUPS
-
-LostLowUse <- DATAdf %>%
-  filter(is.na(MSOA11CD)) %>%
-  group_by(LAD11CD) %>%
-  summarise(Lost = sum(LowUse)) %>%
-  arrange(-Lost) %>%
-  mutate(cumsum = cumsum(Lost),
-         cumperc = cumsum/sum(Lost))
-
-sum(LostLowUse$Lost)
 ```
@@
     facet_wrap(.~Area) +
-  ggtitle("Difference in Low-Use Property distribution by Price Quartile")
+  ggtitle("Low-Use Property distribution by affordability Quartile")
 SaveFig("ClassdiffAllData.pdf")
@@
       cor(LADMean$HomesMeanOld, LADMean$HomesMean)
+
+#Compare the Long term vacants data with the collected data
+
+    test <-file.path(DataFolder, "LT_615.xls") %>%
+      read_xls(., sheet = 2, skip = 5) %>%
+      set_names(make.names(names(.))) %>%
+      select(LAD11CD = New.ONS.code, X2017) %>%
+      left_join(select(LADMean, LAD11CD, LowUse),.) %>%
+      filter(complete.cases(.))
+
+    cor(test$LowUse, test$X2017)
+
+    test <-file.path(DataFolder, "LT_615.xls") %>%
+      read_xls(., sheet = 3, skip = 5) %>%
+      set_names(make.names(names(.))) %>%
+      select(LAD11CD = New.ONS.code, X2017) %>%
+      left_join(select(LADMean, LAD11CD, LowUse),.) %>%
+      filter(complete.cases(.))
+
+     cor(test$LowUse, test$X2017)
 
@@
   facet_wrap(~type) + 
-  labs(title = "Does the geography have above the median LUPs", x = "Affordability Rank", y = "Tourism Rank") +
-  guides(fill=guide_legend(title="Above Median"))
+  labs(title = "Does the geography have above the median percent of LUPs", x = "Affordability Rank", y = "log Tourism Rank") +
+  guides(colour=guide_legend(title="Above Median"))+
+  theme(  legend.position="bottom")
 SaveFig("HighLUP.pdf")
@@
   facet_wrap(~type) + 
-  labs(title = "Is the median LUP price higher than the Median price of all properties", x = "Affordability Rank", y = "Tourism Density") +
-  guides(fill=guide_legend(title="Above Median"))
+  labs(title = "Are LUPs more expensive than homes?", x = "Affordability Rank", y = "log Tourism Density") +
+  guides(colour=guide_legend(title="More expensive"))+
+  theme(  legend.position="bottom")
 SaveFig("HighVal.pdf")
@@
 
-#Empty Homes tax
+# Tax on Empty Homes
 
@@
   mutate(EmptyTax = LowUse*LowUseMean*.01,
+         AllPropVal = Homes*HomesMean,
          EmptyOfCouncil = EmptyTax/CouncilTax,
@@
 median(EmptyTax$EmptyTax)
+
+sum(EmptyTax$EmptyTax*100)/sum(EmptyTax$LowUse)
+
+sum(EmptyTax$AllPropVal)/sum(EmptyTax$Homes)
+
+363/306
 
@@
 
-#Rural Analysis
-
-The rural areas seem to be much less likely to had a negative mean difference,  but there is not enough data for the data to be used for moddelling
-```{r}
-LADrural <- rural %>% group_by(LAD11CD, Urban) %>%
-  summarise(count = n()) %>%
-  spread(key = Urban, value = count, fill = 0) %>%
-  mutate(UrbanPerc = Urban/(Urban+Rural),
-         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
-  left_join(LADMean,.)
-
-MSOArural <- rural %>% group_by(MSOA11CD, Urban) %>%
-  summarise(count = n()) %>%
-  spread(key = Urban, value = count, fill = 0) %>%
-  mutate(UrbanPerc = Urban/(Urban+Rural),
-         Class = ifelse(UrbanPerc>0.5, "Urban", "Rural")) %>%
-  left_join(MSOAMean,.)
-
-#Almost no rural areas are classified as having a negative median difference
-table(LADrural$Class,LADrural$MedianDiff>0.5)
-table(LADrural$Class,LADrural$LowUseType)
-2/26
-42/86
-
-table(ifelse(percent_rank(LADrural$TourismDensity)>0.5, "HighTour", "LowTour"),LADrural$HighLUP,LADrural$Class)
-
-LADrural  %>%
-  ggplot(aes(x = log(LowUsePerc), y =  log(TourismDensity), colour = Class)) + geom_point()
-
-rm(LADrural);rm(MSOArural);rm(rural)
-```
-
 #Affordability
@@
 ```{r}
-MSOAAffordRatio <- MSOAMean %>%
-  left_join(select(MSOAtoLAD, MSOA11CD, Region), by ="MSOA11CD")
-
-cor(MSOAMea)
-
-MSOAAffordRatio  <- bind_rows(MSOAAffordRatio %>% filter(Region != "London") %>% mutate(type = "Excluding London"), 
+MSOAAffordRatio <- MSOAMean
+
+MSOAAffordRatio  <- bind_rows(MSOAAffordRatio %>% filter(Region != "E12000007") %>% mutate(type = "Excluding London"), 
                     MSOAAffordRatio %>% mutate( type = "Including London"),
-                    MSOAAffordRatio %>% filter(Region == "London") %>% mutate( type = "Only London")) %>%
+                    MSOAAffordRatio %>% filter(Region == "E12000007") %>% mutate( type = "Only London")) %>%
     group_by(type) %>%
@@
 data_frame(Index = 1:100) %>%
-  mutate(Primary = exp(-0.05*(Index))+0.05, 
-         Auxilary = (exp(Index/100)-1),
-    Total = Primary + Auxilary) %>%
+  mutate(`Low Value` = exp(-0.05*(Index))+0.05, 
+         `High Value` = (exp(Index/100)-1),
+    Total = `Low Value` + `High Value`) %>%
   gather(key = "Type", value = "value", -Index) %>%
@@
   geom_line() +
-  labs(title = "LUP percentage as a function of primary and Auxilary demand",
-       x = "Demand",
+  labs(title = "LUP percentage VS affordability ratio",
+       x = "Affordability ratio",
        y = "LUP percentage") +
@@
 LADModTab <-LADModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
- # mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
-  mutate(ModelID = rep(1:4,3))
-
-LADModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
+  mutate(Dependent = case_when(
+    Dependent=="HighVal"~ "High-Value",
+    Dependent == "HighLUP"~ "High-LUP %",
+    TRUE ~ "HVHL"
+  ) %>% as.factor) %>%
+  mutate(ModelID = rep(1:4,3)) %>%
+  arrange(Dependent)
+
+LADModTab %>% select(ID = ModelID, Dependent, `Beats Null`=`Beats NULL`, Accuracy=`Mean Accuracy`, PosPred, NegPred, Lift) %>%
   slice(c(2,8,10)) %>% 
-  xtable(., caption="Summary of viable Local authority models",
+  mutate(ID = ifelse(ID == 2, 3, ID))%>%
+  xtable(., caption="Summary of viable Local Authority models",
        label = "tab:LADmodels") %>% 
-  print(., type="latex", file=file.path(TexTables,"LADmodels.tex"))
+  print(., type="latex", file=file.path(TexTables,"LADmodels.tex"), include.rownames=FALSE)
 
@@
 MSOAModTab <- MSOAModels %>% SummariseModels(Dependent, IncAfford2,  IncTourism) %>%
-  mutate(Dependent = ifelse(Dependent=="HighLUP", "High LUP %", "High LUP value")) %>%
+  mutate(Dependent = ifelse(Dependent=="HighLUP", "High-LUP %", "High-Value")) %>%
   mutate(ModelID = rep(1:4,2))
 
-MSOAModTab %>% select(ID = ModelID, Dependent, `Beats NULL`, `Mean Accuracy`, PosPred, NegPred, `Null Difference`) %>%
+MSOAModTab %>% select(ID = ModelID, Dependent, `Beats Null`=`Beats NULL`, Accuracy=`Mean Accuracy`, PosPred, NegPred, Lift) %>%
   slice(c(4)) %>%
@@
        label = "tab:MSOAmodels") %>% 
-  print(., type="latex", file=file.path(TexTables,"MSOAmodels.tex"))
+  print(., type="latex", file=file.path(TexTables,"MSOAmodels.tex"), include.rownames=FALSE)
 
@@
 
-bind_rows(LADMODOut %>% mutate(type = "Financialised LAD"),
-          LADMODOut3 %>% mutate(type = "Highly Financialised LAD"),
-          LADMODOut2 %>% mutate(type = "High LUP % LAD"),
-          MSOAMODOut %>% mutate(type = "High LUP % MSOA")
+bind_rows(LADMODOut %>% mutate(type = "High-Value (LAD Level)"),
+          LADMODOut3 %>% mutate(type = "HVHL (LAD Level)"),
+          LADMODOut2 %>% mutate(type = "High-LUP % (LAD Level)"),
+          MSOAMODOut %>% mutate(type = "High-LUP % (MSOA Level)")
 ) %>%
@@
 
-FormulaBootLAD<-as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatioScale2)
-
-ModPreds <- c("HighVal", "HighLUP", "HighFinance") %>%
+FormulaBootLAD<-c(as.formula(Reference ~ TourismDensity + AffordRatio),
+  as.formula(Reference ~ TourismDensity + AffordRatio + AffordRatioScale2),
+                  as.formula(Reference ~ TourismDensity + AffordRatio))
+
+ModPreds <- 1:3 %>%
   map(~{
@@
 EWMod <- LADMean %>% 
-  rename_(Reference = .x )  %>% 
+  rename_(Reference = c("HighVal", "HighLUP", "HighFinance")[.x] )  %>% 
   mutate(Reference = as.factor(Reference)) %>%
-      glm(formula = FormulaBootLAD, data = ., family=binomial(link='logit'))
+      glm(formula = FormulaBootLAD[[.x]], data = ., family=binomial(link='logit'))
 
@@
       predict(EWMod, newdata = ., type = "response" ) %>%
-      as.tibble(.) %>% setNames(.x)
+      as.tibble(.) %>% setNames(c("HighVal", "HighLUP", "HighFinance")[.x])
 
@@
   gather(key, value) %>%
-  mutate(key = ifelse(key == "PopPerc", "Financialised", "Highly Financialised")) %>%
+  mutate(key = ifelse(key == "PopPerc", "High-Value", "High-Value High-LUP%")) %>%
   ggplot(aes(x = value)) + geom_density() +
@@
   mutate(Type = case_when(
-    Type =="HighFinance" ~ "Highly Financialized",
-    Type == "HighLUP" ~"Large LUP percentage",
-    Type == "HighVal" ~"Some Financialization"
-  ) %>% as.factor(.) %>% fct_relevel("Highly Financialized", after = 2),
+    Type =="HighFinance" ~ "High-Value High-LUP",
+    Type == "HighLUP" ~"High LUP percentage",
+    Type == "HighVal" ~"High-Value LUPs"
+  ) %>% as.factor(.) %>% fct_relevel("High-Value High-LUP", after = 2),
   Status = as.factor(Status) %>% fct_relevel(TRUE, after = 0)) %>%
@@
   facet_wrap(~Type)+
-  labs(title = "LUP and financialization status in England and Wales") +
+  labs(title = "Predicting LUP status across England and Wales") +
    theme(axis.title.x=element_blank(),
@@
           axis.text.y=element_blank(),
-          axis.ticks.y=element_blank())
+          axis.ticks.y=element_blank(),
+         legend.position="bottom")
 SaveFig("EWHighValMap.pdf")
@@
 ```
+
+#Miscellaneous
+
+```{r}
+
+#Gets the info on how conentrated the empty homes are
+test <- DATAdf %>%
+  arrange(-LowUsePerc) %>%
+  filter(!is.na(MSOA11CD)) %>%
+  mutate(CumsumLowUse = cumsum(LowUse),
+         CumsumHomes = cumsum(Homes),
+         CumsumLowUsePerc = CumsumLowUse/sum(LowUse),
+         CumsumHomesPerc = CumsumHomes/sum(Homes),
+         CumPerc = 1:nrow(.)/nrow(.) )
+
+median(test$LowUsePerc)
+mean(test$LowUsePerc)
+max(test$LowUsePerc)
+
+test[(c(0.5,2,5)/10) %>% map_dbl(~Position(function(fi) fi <= .x, test$CumPerc, right = TRUE)),] %>%
+  select(CumsumLowUsePerc, CumsumHomesPerc, CumPerc)
+
+#Dumps a CSV of all the LADs is not necessary for script and so is commented out, The csv can then be used to add the file names and FOI references
+# 
+# DATAdf %>%
+#   select(LAD11CD, LAD11NM, RGNCD = Region) %>%
+#   distinct(LAD11CD, .keep_all = TRUE) %>%
+#   left_join(data_frame(RGNCD = c("E12000001", "E12000002", "E12000003", 
+# "E12000005", "E12000006", "E12000007", "E12000008", "E12000009", 
+# "W99999999"), Region = c("North East", "North West", "York and Humber", 
+# "West Midlands", "East England", "London", "South East", "South West", 
+# "Wales"))) %>%
+#   write_csv(file.path(basewd,"LADsDataRaw.csv"))
+
+```

### 2018-09-27 Functions/CreateGeogModelData.R

@@ -9,7 +9,7 @@ CreateGeogModelData <- function(target, path){
     left_join(select(IncomeEst, Yearly.income, MSOA11CD), by = "MSOA11CD") %>%
     left_join(., list.files(file.path(basewd, "BootstrapMSOAOldPrices"), full.names = TRUE) %>% # load the old prices
                 map_df(~readRDS(.x)) %>% select(MSOA11CD, ID, MSOAHomesMedian:LADHomesMean) %>% 
-                set_names(c(names(.)[1:3], paste0(names(.)[-c(1:3)], "Old"))), by = c("MSOA11CD", "ID"))
+                set_names(c(names(.)[1:2], paste0(names(.)[-c(1:2)], "Old"))), by = c("MSOA11CD", "ID"))
   
   #reverse the selection safely
   if(target=="LAD"){

### 2018-09-27 Functions/SummariseModels.R

@@ -14,7 +14,8 @@ SummariseModels <- function(df,...){
               "PosPred" = mean(Pos.Pred.Value),
               "NegPred" = mean(Neg.Pred.Value),
               'NULL Model' = mean(AccuracyNull),
-              'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+              'Null Difference' = mean(Accuracy-AccuracyNull),#Mean difference relative to NULL
+              Lift = mean(Accuracy/AccuracyNull)
     ) %>% ungroup
   
   

### 2019-04-26 CreateExcelTemplates.Rmd
Major update to Excel script
This script has been totally changed making it much simpler and using the more reliable ONSP instead of the previous datasets. It also cuts out large amounts of superfluous code.

--- 2017-03-21 CreateExcelTemplates.Rmd
@@
 ---
+
+#references
+
+The key data is the ONS postcode directory. This data is released quarterly, and contains all the postcode past and present.
+This data set is great as it matches the postcodes to LSOA which makes the whole geospatial part much easier.
+
+The other two data sets are the regional code look up
+
+and the ward look up.
+Ward data can be found by searching the ONS open geograph portal.
+the name of the dataset is similar too "Lower Layer Super Output Area (2011) to Ward (2018) Lookup in England and Wales v3" this dataset is updated regulalry as well the most recent should be used.
+
+This code is greatly simplified from earlier versions due to switching to the ONSPD and removeing the mapping experiments.
 
@@
 
-```{r setup}
-setwd( "~/Dropbox/SSE/Empty Homes/EmptyHomesCode/SubCode")
-source("Setup.R")
-```
+```{r}
+basewd <-"~/Dropbox/SSE/Empty Homes"
+ONSpostcodes <- file.path(basewd, "ONSPD")
+AddGeog <- file.path(basewd, "AdditionalGeographies")
+wards_file <- "Lower_Layer_Super_Output_Area_2011_to_Ward_2018_Lookup_in_England_and_Wales_v3.csv"
+Regions <- file.path(basewd, "Regions")
 
-Postocode look up data found at
-http://ons.maps.arcgis.com/home/item.html?id=ef72efd6adf64b11a2228f7b3e95deea
+select <- dplyr::select
 
-Covered by open government licesence
-```{r}
+Wardnames <- read_csv(file.path(AddGeog, wards_file))
 
-setwd(PostcodeLookups)
+LADReg <- read.csv(file.path( AddGeog, "LAD15_RGN15_EN_LU.csv"), stringsAsFactors = FALSE   )
 
-PstCdLSOA.raw <- read.csv("PCD11_OA11_LSOA11_MSOA11_LAD11_EW_LU_aligned_v2.csv", stringsAsFactors = FALSE)
+CorePstCd  <- read_csv(file.path(ONSpostcodes, 
+                              "ONSPD_FEB_2019_UK.csv")) %>%
+  select(Postcode = pcd, LSOA11CD = lsoa11, 
+         MSOA11CD = msoa11, LAD11CD = oslaua, 
+         OA11CD = oa11, Country_code = ctry, 
+         Region =  rgn)
 
-templatefile<- "Convert Postcode to LSOA.xlsx"
+{
+PstCdLSOA <- CorePstCd %>% 
+  left_join(., LADReg, by = c("LAD11CD"="LAD15CD")) %>%
+  left_join(Wardnames, by = "LSOA11CD") %>%
+  #filter(Country_code == "W92000004")
+  select(Postcode, Country_code, Admin_district_code = LAD11CD, 
+         Admin_ward_code = WD18CD, lsoa11cd = LSOA11CD, LAD15NM = LAD18NM, 
+         RGN15CD, RGN15NM, WD16NM = WD18NM) %>%
+  mutate(
+    #Make sure Scotland and Wales have region names
+    RGN15CD = case_when(
+      grepl("W", Country_code) ~"Wales",
+      grepl("S", Country_code) ~"Scotland",
+      TRUE ~ RGN15CD),
+    RGN15NM = case_when(
+      grepl("W", Country_code) ~"Wales",
+      grepl("S", Country_code) ~"Scotland",
+      TRUE ~ RGN15NM
+    ),
+    Postcode = gsub(" ", "", Postcode)) %>% #remove spaces from postcodes
+filter(!is.na(RGN15NM),
+       LAD15NM != "NA",
+       RGN15CD !="Scotland")
+#This is a large dataframe so we want to remove it when possible to save memory
 
-lapply(unique(PstCdLSOA.raw$LAD1), function(LAD){ 
-   PstCdLSOA <- PstCdLSOA.raw[PstCdLSOA.raw$LAD11NM == LAD,]
+#region cleaning
+#some LSOA are in multiple regions and Adminwards this code fixes this by using a majority vote
 
-filename <- paste0(LAD,"LSOA.xlsx")
-setwd(basewd)
-wb <- loadWorkbook("Convert Postcode to LSOA.xlsx")
-#input the LSOA lookup table
-writeData(wb, sheet = "LSOAdata", PstCdLSOA, colNames = T)
-#add in randomly sampled postcodes as an example
-writeData(wb, sheet = "InpuNames and codes for administrative geographyt", sample(PstCdLSOA$PCD7, 6), 
-          startCol = 2, startRow = 2,
-          colNames = F)
-setwd(ExcelLookups)
-saveWorkbook(wb,filename ,overwrite = T)
-  })
+MajRegion <- PstCdLSOA  %>% group_by(lsoa11cd, RGN15CD) %>%
+  summarise(count = n(),
+            RGN15NM = first(RGN15NM)) %>%
+  group_by(lsoa11cd) %>%
+  arrange(-count) %>%
+  summarise_all(first) %>%
+  select(-count)
 
-```
+MajLAD <- PstCdLSOA  %>% group_by(lsoa11cd, Admin_district_code) %>%
+  summarise(count = n()) %>%
+  group_by(lsoa11cd) %>%
+  arrange(-count) %>%
+  summarise_all(first) %>%
+  select(-count)
 
-The data on ONS is old, so taking a current list of post codes is necessary.
-
-https://www.freemaptools.com/download/outcode-postcodes/postcode-outcodes.csv
-
-Need to check the lattitude and longitude and merge them with the LSOA they fall inside. to create a new list
-
-The England and wales shape files can be downloaded here
-http://geoportal.statistics.gov.uk/datasets/da831f80764346889837c72508f046fa_0
-
-```{r}
-
-setwd(ShapeFiles)
-list.files(pattern = ".shp")
-
-#load shape file
-shape <- readOGR(dsn = "LSOA_2004_London_Low_Resolution.shp")
-
-#Convert to Latitude and longitude
-shape <- spTransform(shape, CRS("+init=epsg:4326"))
-
-#read postcodes
-# setwd(basewd)
-# postcodes <-read.csv("ukpostcodes.csv")
-# 
-# #subset to souteast
-# p2 <- postcodes[grepl("^SE",postcodes$postcode),]
-
-#Plot using base this doesn't work I don't know why
-# coordinates(p2) <- ~ latitude + longitude  # pts needs to be a data.frame for this to work
-# proj4string(p2) <- proj4string(shape)
-# 
-# plot(shape)
-# plot(p2, col="red" , add=TRUE)
-
-#convert shape files to data frame
-AG <- tidy(shape)
-
-#Plot shape files as map of london with south east plotted over the top. this does work as expected.
-ggplot()+ geom_polygon(data=AG, aes(long, lat, group = group), 
-colour = alpha("darkred", 1/2), size = 0.7, fill = 'skyblue', alpha = .3) +geom_point(data= p2, aes(x = longitude, y= latitude))+
-  ggtitle("London With SE postcodes overplotted")
-
-#Subset map to a smaller area
-AG2 <- AG %>% filter(long>-0.2, long<0.1, lat<51.55, lat>51.45)
-#check that the points are aligned. They are.
-ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group), 
-colour = alpha("darkred", 1/2), size = 0.7, fill = 'skyblue', alpha = .3) + geom_point(data= p2, aes(x = longitude, y= latitude))
-
-```
-
-```{r}
-p3 <- postcodes %>% filter(latitude<65)
-#ensure that the points are converted to latitude and longitude
-coordinates(p3) <- ~longitude + latitude
-#set the projection of the data to longitude and latitude
-proj4string(p3) <- CRS("+proj=longlat")
-#I don't undertsand what is going on here
-p3 <- spTransform(p3, proj4string(shape))
-proj4string(p3) <- proj4string(shape)
-z <- over(p3, shape)
-
-PstCdLSOA.raw <- bind_cols(postcodes %>% filter(latitude<65), z)
-
-PstCdLSOA.raw <- PstCdLSOA.raw %>% filter(!is.na(PstCdLSOA.raw$LSOA_CODE))
-
-head(PstCdLSOA.raw,100)
-```
-
-```{r}
-lapply(unique(PstCdLSOA.raw$LA_NAME), function(LAD){ 
-   PstCdLSOA <- PstCdLSOA.raw[PstCdLSOA.raw$LA_NAME == LAD,]
-
-filename <- paste0(LAD,"LSOA.xlsx")
-setwd(basewd)
-wb <- loadWorkbook("Convert Postcode to LSOA.xlsx")
-#input the LSOA lookup table
-writeData(wb, sheet = "LSOAdata", PstCdLSOA, colNames = T)
-#add in randomly sampled postcodes as an example
-writeData(wb, sheet = "Input", sample(PstCdLSOA$postcode, 6), 
-          startCol = 2, startRow = 2,
-          colNames = F)
-setwd(ExcelLookups)
-saveWorkbook(wb,filename ,overwrite = T)
-  })
-```
-
-```{r}
-#Read postcodes from the ONS folder of codes
-setwd(ONSpostcodes)
-list.files()
-p2<- read.csv("se.csv", header = FALSE)
-setwd(ONSpostcodeMeta)
-names(p2) <- z <- read.csv("Code-Point_Open_Column_Headers.csv")[1,] %>%t
-
-#Check that the shapes are using the same coordinate system
-AG <- tidy(shape)
-#Subset map to a smaller area
-AG2 <- AG %>% filter(long>530000, long<550000, lat>170000, lat<185000)
-#check that the points are aligned. They are.
-ggplot()+ geom_polygon(data=AG2, aes(long, lat, group = group), 
-colour = alpha("darkred", 1/2), size = 0.7, fill = 'skyblue', alpha = .3)+ geom_point(data= p2, aes(x = Eastings, y= Northings))
-
-#set the Northings an eastings columns to be the coordinates
-coordinates(p2) <- ~Eastings + Northings
-#defines the coordinate system
-proj4string(p2) <- CRS("+init=epsg:27700")
-#converts the coordinate system from the one definded to the coordinate system of the shape file, this step is not neccesary in this case as both are using the Uk grid referencing system.
-p2 <- spTransform(p2, proj4string(shape))
-
-#check that the conversion has worked properly
-plot(shape)
-plot(p2, col="red" , add=TRUE)
-
-#Check which LSOA each postcode falls within and bind it to the postcode data
-PstCdLSOA.raw <- bind_cols(tidy(p2), over(p2, shape))
-
-#remove any NA values
-PstCdLSOA.raw <- PstCdLSOA.raw %>% filter(!is.na(PstCdLSOA.raw$LSOA_CODE))
-
-```
-
-This code block works smoothly using government data testing on the "se" postcodes. The next code chunk will perform the same operation for all postcodes. as a result it is computationally intense.
-
-#Using only ONS data
-
-Load the LSOA shape data for EW 
-```{r}
-setwd(LSOAshapedata)
-
-shape <- readOGR(dsn = list.files(pattern = "shp"))
-
-```
-
-# Load Post code data
-
-This chunk checks the exiatane of the postcode to lsoa lookup if it doesn't find it, the second part of the code is run that creates the lookup.
-Creating the lookup takes quite a lot of time so it is good to only have to do it once.
-```{r}
-
-if(file.exists(file.path(DataFolder,"PstCdLSOA.rds"))){
- PstCdLSOA.raw <- readRDS(file.path(DataFolder,"PstCdLSOA.rds"))
-} else {
-  source(file.path(CommonCode, "PostcodeLookup.R"))
+PstCdLSOA  <- PstCdLSOA %>%
+  select(-Admin_district_code,-RGN15CD, -RGN15NM) %>%
+  left_join(MajLAD) %>%
+  left_join(MajRegion)
 }
 
-```
-
-Add in LAD names and Region, remove non-essential columns
-```{r}
-setwd(AddGeog)
-list.files()
-
-LADReg <- read.csv("LAD15_RGN15_EN_LU.csv", stringsAsFactors = FALSE   )
-Wardnames <- read.csv("Ward_to_Local_Authority_District_to_County_to_Region_to_Country_December_2016_Lookup_in_United_Kingdom_V2.csv", stringsAsFactors = FALSE) %>%
-  select(WD16CD, WD16NM)
-
-PstCdLSOA <- PstCdLSOA.raw %>% mutate_if(., is.factor, as.character)
-
-#There are a couple of errors is the region LSOA look up these are manually corrected here.
-PstCdLSOA[PstCdLSOA$Postcode=="BN994AE", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="BN126BW", c(3,4,7)]
-
-PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BA", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)] 
-PstCdLSOA[PstCdLSOA$Postcode=="DY4 4BB", c(3,4,7)] <- PstCdLSOA[PstCdLSOA$Postcode=="DY4 0YX", c(3,4,7)]
-
-PstCdLSOA <- PstCdLSOA %>% left_join(., LADReg, by = c("Admin_district_code"="LAD15CD")) %>%
-  left_join(., Wardnames, c("Admin_ward_code" = "WD16CD")) %>% 
-  select(Postcode, Country_code, Admin_district_code, 
-                          Admin_ward_code, lsoa11cd, lsoa11nm, LAD15NM, 
-                          RGN15CD, RGN15NM, WD16NM)
-
-#Wales doesn't have any LAD for some reason, fix is to add in LSOA name subtracting the code
-
-PstCdLSOA$LAD15NM[grepl("W", PstCdLSOA$Country_code)] <- gsub(' .*', '' , PstCdLSOA$lsoa11nm[grepl("W", PstCdLSOA$Country_code)])
-
-#Make sure that Scotland and Wales are included in the regions.
-
-PstCdLSOA[grepl("W", PstCdLSOA$Country_code),c("RGN15CD" , "RGN15NM" )] <- c("Wales", "Wales")
-
-PstCdLSOA[grepl("S", PstCdLSOA$Country_code),c("RGN15CD" , "RGN15NM" )] <- c("Scotland", "Scotland")
-
-#remove spaces from the the Postcodes
-
-PstCdLSOA <- PstCdLSOA %>% mutate(Postcode = gsub(" ", "", Postcode))
+rm(CorePstCd)
 
@@
 
-lapply(unique(PstCdLSOA$RGN15NM), function(n){
-  title <- paste("Region", n)
+unique(PstCdLSOA$RGN15NM) %>%
+  walk(~{
+
+    title <- paste("Region", .x)
     dir.create(file.path(Regions, title ), showWarnings = FALSE)
     #The inner loop creates the excel files for each LAD within each region
-  PstCdLSOA.Reg <- PstCdLSOA %>% filter(RGN15NM == n)
+    PstCdLSOA.Reg <- PstCdLSOA %>% filter(RGN15NM == .x)
 
     print(title)
-  lapply(unique(PstCdLSOA.Reg$LAD15NM), function(LAD){
 
-    PstCdLSOA.filt <- PstCdLSOA.Reg %>% filter(LAD15NM == LAD)
-    print(paste(n, ":", LAD))
-      ExemptionsFile <- paste0(LAD,"ExemptionsLSOA.xlsx")
-      CTBandsFile <- paste0(LAD,"CTBandsLSOA.xlsx")
+    unique(PstCdLSOA.Reg$LAD15NM) %>%
+      walk(~{
+
+        PstCdLSOA.filt <- PstCdLSOA.Reg %>% filter(LAD15NM == .x)
+        print(paste(title, ":", .x))
+        ExemptionsFile <- paste0(.x,"ExemptionsLSOA.xlsx")
+        DiscountsFile <- paste0(.x,"DiscountsLSOA.xlsx")
         setwd(basewd)
@@
         saveWorkbook(wb,ExemptionsFile ,overwrite = T)
-      saveWorkbook(wb,CTBandsFile ,overwrite = T)
+        writeData(wb, "Input", "Discount_Class") #So that it says Discounts not exemptions, so nobody gets confused.
+        saveWorkbook(wb,DiscountsFile ,overwrite = T)
+
       })
+
   })

### 2020-11-11 MSOAmodel.Rmd

@@
             'NULL Model' = mean(AccuracyNull),
-           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+           'Null Difference' = mean(Accuracy-AccuracyNull),
+                                    Sens = mean(Sensitivity),
+           spec = mean(Specificity)#Mean difference relative to NULL
             )
@@
 KitchenSink2 <- as.formula(Reference ~RelativeAfford + RelativeTourismDens +
-                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio, Ego2TourismDens2+Ego2TourismDens)
+                            LADTourismDensity + AffordRatioScale + AffordRatioScale2 + LADMeanMedianRatio, Ego2TourismDens2+Ego2TourismDens + AffordRatioScale2*TourismDensity)
+
+Formulatest <-  as.formula(Reference ~ TourismDensity+ AffordRatio + AffordRatioScale2)
+
+set.seed(1983)
+TestResample <- vfold_cv(LADMean, v = 5, repeats = 20, strata = "HighFinance")
 
@@
 
+ComplexModels2 <- c("HighFinance", "HighLUP", "LADHighVal") %>%
+  map_df(~{
+    print(.x)
+    ResOut2 <- MSOAMean2 %>%
+      rename_(Reference = .x) %>%
+      ResampledModelPerf(., TestResample, Formulatest, LADData = LADMean) %>%
+      mutate(Dependent = .x)
+})
+
 ComplexModels2 %>%
-  group_by(Dependent) %>%
+  group_by(Dependent)%>%
   summarise('Beats NULL' = sum(Accuracy>AccuracyNull)/n(), #How many times did the models beat NULL
@@
             'NULL Model' = mean(AccuracyNull),
-           'Null Difference' = mean(Accuracy-AccuracyNull) #Mean difference relative to NULL
+           'Null Difference' = mean(Accuracy-AccuracyNull),
+                                    Sens = mean(Sensitivity),
+           spec = mean(Specificity)#Mean difference relative to NULL
             )
+
+AnalyzePreds <- c("HighFinance", "HighLUP", "LADHighVal") %>%
+  map_df(~{
+    print(.x)
+    ResOut2 <- MSOAMean2 %>%
+      rename_(Reference = .x) %>%
+      ResampledModelPerfPreds(., TestResample, Formulatest, LADData = LADMean) %>%
+      mutate(Dependent = .x,
+             row = 1:n())
+})
+
+test <- AnalyzePreds %>%
+  mutate(Predictions = Predictions>0.5) %>%
+  select(Predictions, Dependent, sample, row) %>%
+  spread(key = Dependent, value = Predictions)
+
+test2 <- AnalyzePreds %>%
+  mutate(Predictions = Predictions>0.5) %>%
+  select(Reference, Dependent, sample, row) %>%
+  spread(key = Dependent, value = Reference)
+
+confusionMatrix(data = test$HighLUP & test$LADHighVal, test2$HighFinance)
+
+confusionMatrix(test$HighFinance, test2$HighFinance)
+
+confusionMatrix(test$HighLUP, test2$HighLUP)
+
+confusionMatrix(test$LADHighVal, test2$LADHighVal)
+
 ```

### 2020-11-11 PaperCode.Rmd

@@
 install.packages("breakDown") provides a plot of the glm!
-
-schedule 2 part 5 section
-
-Palgrave nature inter-discplinary journel
-https://www.nature.com/palcomms/for-authors#edboard
-
-poss editors
-Dr Lei Wang, manchester Urban
-Tim Hall, university winchester
-
-maybe
-Trifon I Missov, Max planck demographics
-
-reviewr
-Glen Bramley at herriot watt
-
-ian caswell ucl mega journel
-Kathrine sharp
-
-Reviewers on plos
-
-search term: data mining
-César A Hidalgo
-Massachusetts Institute of tech
-
-search term: demography
-Celine Rozenblat
-University of Lausanne
-SWITZERLAND
-
-Heidi Harriman Ewen
-University of Georgia
-UNITED STATES
-
-The information provided in response to your request is copyright Gateshead Council unless otherwise endorsed.
-Granting access to this information under the Freedom of Information Act does not permit you to re-use the information provided for commercial purposes, for photocopying or reproduction in any form.
-If you wish to re-use the information you need to apply for a Licence.
-You can do this by writing to Tanya Rossington, Information Rights Officer, Corporate Services and Governance, 1st Floor, Civic Centre, Regent Street, Gateshead, NE8 1HH.
-You may be required to pay a fee or comply with conditions for permitted re-use.
 
@@
 #Need to put in region names
-DataCover <-
- DATAdf %>% 
+DataCover <- DATAdf %>% 
    filter(!is.na(MSOA11CD)) %>%
@@
 ##Non-Dataset LADs
-This bootstrapping is done to get the data needed to predict across the whole of Wngland and Wales
+This bootstrapping is done to get the data needed to predict across the whole of England and Wales
 ```{r}
@@
 }
+
 ```
@@
 
+```
+
+#2nd homes and Tourism
+```{r}
+
+TourismLAD <- Tourism %>%
+  group_by(LAD11CD) %>%
+  summarise_if(is.numeric, sum, na.rm = T) %>%
+  bind_cols(Tourism %>% group_by(LAD11CD) %>% summarise(LAD11NM =first(LAD11NM)),.) %>%
+  ungroup
+
+ScndhomesCensus <- read_xlsx(path = file.path(DataFolder, "Census2011secondHomes.xlsx"), sheet = 3, skip = 13)[,1:7] %>%
+  mutate(LAD11NM = ifelse(is.na(X__1), X__2, X__1)) %>%
+  select(LAD11CD = K04000001, LAD11NM, ScndHomes = X__5) %>% # Pop = X__4,
+  filter(!is.na(ScndHomes)) %>%
+  #Replace changed codes
+  mutate(LAD11CD = case_when(LAD11NM == "St Albans"~"E07000240",
+                             LAD11NM =="Welwyn Hatfield"~"E07000241",
+                             LAD11NM =="Northumberland UA 6"~"E06000057",
+                             LAD11NM =="East Hertfordshire"~"E07000242",
+                             LAD11NM =="Stevenage"~"E07000243",
+                             LAD11NM =="Gateshead"~"E08000037",
+                             TRUE~ LAD11CD)) %>%
+  select(-LAD11NM) %>%
+  left_join(TourismLAD, ., by = "LAD11CD") %>%
+  mutate(TourismDens = (Guest + Hotel)/Homes,
+         ScndHomesDens = ScndHomes/Homes) %>%
+  filter(!is.na(LAD11CD)) %>%
+  mutate(Perc2ndHomes = ScndHomes/sum(ScndHomes))
+
+#not a lot of corellation
+cor(ScndhomesCensus$TourismDens, ScndhomesCensus$ScndHomesDens)
+
+#no real pattern
+ScndhomesCensus %>%
+  filter(TourismDens<0.1) %>%
+ggplot(aes(x = TourismDens, ScndHomesDens)) + geom_point()
+
+test <- left_join(LADMean, ScndhomesCensus, by = "LAD11CD")
+
+sum(test$Perc2ndHomes)
+
+rm(TourismLAD);
 ```
@@
 setwd(DataFolder)
-WelshTax <- read_csv("WelshCTax.csv", skip = 6, n_max = 23) %>%
+
+WelshTax <- read_csv("WelshCTax.csv")
+
+WelshTax <- read_csv("WelshCTax.csv", skip = 4, n_max = 23) %>%
   select(-X1) %>%
@@
          TaxPop = EmptyTax/Pop)
+
+#For press office
+
+test <- EmptyTax %>%
+  select(LAD11CD, LAD11NM, Homes, LowUse, HomesMedian, LowUseMedian, LowUsePerc, MedianDiff, MedianDiffRatio, EmptyTax, EmptyOfCouncil, TaxPop)
+write_csv(test, file.path(basewd, "Key Figures by Council.csv"))
 
@@
 ```
+
+#Key figures
+```{r}
+
+#The top 3 LSOA for each LAD in terms of perc low use
+TopLSOA <- DATAdf %>% 
+  ungroup %>%
+  arrange(-LowUsePerc) %>%
+  group_by(LAD11CD) %>%
+  slice(1:3)
+  #top_n(., 3, LowUsePerc)
+
+#The value of the low use property
+TotalValueProperty <- DATAdf %>%
+  group_by(LAD11CD) %>%
+  summarise(LAD11NM = first(LAD11NM),
+            LUPSValue = sum(LowUse*MeanPrice, na.rm = T),
+            HomesValue = sum(Homes*MeanPrice, na.rm = T)) %>%
+  mutate(LUPofTotMarket = LUPSValue/HomesValue)
+
+Key_Areas <- read.csv(file.path("/home/jonno/Downloads", "LAs for Jonathan.csv")) %>% select(LAD11CD, news_area)
+
+TopLSOA <- Key_Areas %>%
+  left_join(TopLSOA, .) %>%
+  filter(!is.na(news_area))
+
+TotalValueProperty <- Key_Areas %>%
+  left_join(.,TotalValueProperty)
+
+test <-LADMean %>%
+ #filter(LAD11NM == "Barnet")
+  filter(Region == "E12000007") %>%
+  select(LAD11NM, LowUse, LowUseMean, HomesMean, AffordRatio, MedianDiff, MedianDiffRatio) %>%
+  mutate_if(is.numeric, signif, digits = 3)
+
+write.csv(test, file.path("/home/jonno", "LondonMSOA.csv"))
+
+test <- DATAdf %>%
+filter(LAD11CD == "E06000052") %>%
+  write.csv(file.path("/home/jonno/Downloads", "Brighton.csv"))
+
+write.csv(TopLSOA, file.path("/home/jonno/Downloads", "TopLSOA.csv"))
+write.csv(TotalValueProperty, file.path("/home/jonno/Downloads", "TotalValueProperty.csv"))
+
+LSOAshape <- st_read(LSOAshapedata) %>%
+  left_join(DATAdf, by = c("lsoa11cd"="LSOA11CD")) %>% filter(grepl("Bradford",LAD11NM)) #filter(grepl("E09000003",LAD11CD))
+
+colourTypes <- c( "0-10" = "#F8766D", 
+                    "11-20" = "#A3A500", 
+                   "21-30" ="#00BF7D", 
+                   "30+" = "#00B0F6")
+
+LowUseColours <- gg_color_hue(4)
+names(LowUseColours) <- c( "0-10", "11-20","21-30","30+")
+
+gg_color_hue <- function(n) {
+  hues = seq(15, 375, length = n + 1)
+  hcl(h = hues, l = 65, c = 100)[1:n]
+}
+
+LSOAshape %>%
+ggplot(.)+  geom_sf(aes(fill = LowUsePerc))  +
+   theme(axis.title.x=element_blank(),
+          axis.text.x=element_blank(),
+          axis.ticks.x=element_blank(),
+          axis.title.y=element_blank(),
+          axis.text.y=element_blank(),
+          axis.ticks.y=element_blank())+
+  ggtitle("Low use Percentage by lsoa in Trafford")+
+  scale_fill_viridis_c()
+
+test <- TotalValueProperty  %>%
+  filter(grepl("(Allerdale)|(Copeland)|(Carlisle)|(South Lake)|(Barrow)|(Eden)", LAD11NM))
+
+test <- MSOAMean %>%
+filter(LAD11CD == "E06000052")
+
+```
+
+```{r}
+CorePstCd %>%
+ filter(Region == "E12000007") %>%
+  distinct(LAD11CD, .keep_all = T) %>%
+  select(LAD11CD, LAD11NM) %>%
+  filter(!(LAD11CD %in% (LADMean %>%  filter(Region == "E12000007") %>% pull(LAD11CD))))
+
+```

### 2020-11-11 testCode.Rmd

@@
   left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
-  select(Postcode, lsoa11cd, LAD11CD, LAD11NM,Admin_ward_code = Admin_ward_code.x, WD16NM)
+  select(Postcode,LSOA11CD= lsoa11cd, LAD11CD, LAD11NM, MSOA11CD, Pop)
 
@@
 
+#How many of the postcodes are matched?
+sum(!is.na(CompanyData$LSOA11CD))/nrow(CompanyData) #this is a high number which is totally acceptable
+
 #X10 address
@@
 
+#Find each type of business
 LSOABiz <- CompanyData %>%
@@
          X6 = gsub("(AND PREMISES)|(& PREMISES)", "",X6)) %>%
-  group_by(lsoa11cd, X6) %>%
+  group_by(LSOA11CD, X6) %>%
   summarise(counts = n(),
@@
             LAD11NM = first(LAD11NM),
-            Admin_ward_code = first(Admin_ward_code),
-            WD16NM = first(WD16NM))
+            MSOA11CD = first(MSOA11CD))
 
@@
 
+Hotel <- FirmCounts %>%
+  filter(grepl("(HOTEL)|(HOSTEL)",X6))
+
+Guest <- FirmCounts %>%
+  filter(grepl("(GUEST)",X6))
+
+sum(Guest$counts)
+
 ```
 
-Look at Westminster
+#Tourism to Lups
+
+I want to be able to plot the tourism density to deprivation and overlay the catagories and see what happens
 
@@
 
-West <- LSOABiz %>%
+setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootstrapMSOA")
+
+ LADAfford2 <- list.files(getwd()) %>%
+   map_df(~readRDS(.x)) %>%
+   left_join(select(IncomeEst, Yearly.income, MSOA11CD), by = "MSOA11CD") %>%
+   ungroup %>%
+   mutate(MSOAAffordRatio = MSOAHomesMedian/Yearly.income,
+          MSOAHighVal = MSOAHomesMedian< MSOALowUseMedian, #Reference Variable
+          MOSAHighLUP = MSOALowUsePerc >median(MSOALowUsePerc))  #Reference Variable
+
+ %>%
+   group_by(LAD11CD, ID) %>%
+   summarise(LADHomesMedian = first(LADHomesMedian),
+             MedianLowUse = first(LADLowUseMedian)) %>%
+   group_by(LAD11CD) %>%
+   summarise(LADHomesMedian = mean(LADHomesMedian, na.rm = T),
+             MedianLowUse = mean(MedianLowUse, na.rm = T)) %>%
+   left_join(MSOAtoLAD,., by = "LAD11CD") %>%
+   filter(!is.na(LADHomesMedian)) %>% # keep only the LADs that I have data for
+   left_join(., IncomeEst, by = "MSOA11CD") %>%
+  group_by(LAD11CD) %>%
+  summarise(Yearly.income = weighted.mean(Yearly.income, Homes),
+            LADHomesMedian = weighted.mean(LADHomesMedian, Homes)) %>%
+   mutate(AffordRatio = LADHomesMedian/Yearly.income,
+          AffordRank = rank(AffordRatio),
+          AffordRank = scale(AffordRank),
+          AffordRank2 = AffordRank^2)
+
+Tourism <- CompanyData %>%
+  filter(!is.na(LAD11CD))%>%
+  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)|(GUEST)",X6))  %>%
+  mutate(Guest = grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6),
+         Hotel = grepl("(HOTEL)|(HOSTEL)",X6))
+   group_by(LSOA11CD, X6) %>%
+  summarise(counts = n(),
+            LAD11CD = first(LAD11CD),
+            LAD11NM = first(LAD11NM),
+            MSOA11CD = first(MSOA11CD),
+            Pop = first(Pop),
+            Guest = sum(Guest),
+            Hotel = sum(Hotel))
+
+Tourism2 <- Tourism %>%
+  group_by(LAD11CD, LAD11NM) %>%
+  summarise(Tourism = sum(counts),
+            Pop = sum(Pop))
+
+# Only used if bootdeets two exists, which is created in the MSOAmodel rmd
+testLAD <- Tourism2 %>% #
+  left_join(BootDeets2,.) %>% 
+  mutate(TourismDensity =Tourism/Homes,
+         TourismDensityRank = percent_rank(TourismDensity)) %>%
+  left_join(LADAfford2, by = "LAD11CD") %>%
+  #mutate(Extent = AffordRatio) %>%
+  left_join(select(LADDep, LAD11CD, Extent, Average.rank)) %>%
+  mutate(ExtentRank = percent_rank(-Extent),
+         ExtentRank2 = (Extent-0.5)^2,
+         TourDepCat = case_when( 
+           TourismDensityRank>=0.5 & ExtentRank>=0.5 ~ 1, #wealthly high tourism
+           TourismDensityRank>=0.5 & ExtentRank<0.5 ~ 2, #Wealthy Low tourism
+           TourismDensityRank<0.5 & ExtentRank>=0.5 ~3, #Poor High tourism
+           TRUE ~ 4                                          #Poor low tourism
+         ) %>% as.factor,
+         Reference = Catagory==1|Catagory==2)
+
+#This plot means we may be able to separate High low use from Low low use.
+testLAD  %>%
+  ggplot(aes(x= AffordRank2, y = TourismDensityRank, colour = Reference)) + geom_point()
++
+  geom_hline(yintercept = 0.5) +
+  geom_vline(xintercept = 0.5)
+
+testLAD %>%
+  filter(Catagory==1, TourDepCat==3) %>% select(Catagory, TourDepCat, LAD11NM)
+
+ testLAD %>%
+  filter(Catagory %in% c(3,4), TourDepCat==1) %>% select(Catagory, TourDepCat, LAD11NM)
+
+#
+#
+#This model is the best for predicting LADs with high value LUPs-- Can include wales!
+#
+  #OpenFormula <- as.formula(Reference ~ AffordRank+ AffordRank2+ TourismDensityRank)
+
+```
+
+#local tourism.
+number of hotels within 1 MSOA
+
+```{r}
+
+MSOAEgoListDist1 <- ego(MSOAgraph, 1) %>%map(~names(.x))
+names(MSOAEgoListDist1) <- get.vertex.attribute(MSOAgraph, "name")
+
+ NeighbourhoodQuartiles <- names(MSOAEgoListDist1) %>% map_df(~{
+
+   print(.x)
+   target <- MSOAEgoListDist1[[.x]]
+   test <- Tourism %>%
+     filter(MSOA11CD %in% target) %>%
+     ungroup %>%
+     summarise(
+               Hotel = sum(Hotel),
+               Guest = sum(Guest))
+
+ }) %>%
+  mutate(MSOA11CD =  names(MSOAEgoList))
+
+ test <- NeighbourhoodQuartiles %>%
+   left_join(MSOAtoLAD)
+
+```
+
+#How do I make an MSOA version? of tourism density?
+2654
+```{r}
+MSOAtest<- CompanyData %>%
+  filter(!is.na(LAD11CD))%>%
+  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)(GUEST)",X6))  %>%
+   group_by(LSOA11CD) %>%
+  summarise(counts = n(),
+            Guest = sum(grepl("(SELF CATER)|(HOLIDAY)|(GUEST)",X6)),
+            Hotel = sum(grepl("(HOTEL)|(HOSTEL)",X6)),
+            LAD11CD = first(LAD11CD),
+            LAD11NM = first(LAD11NM),
+            MSOA11CD = first(MSOA11CD),
+            Pop = first(Pop)) %>%
+  group_by(MSOA11CD) %>%
+  summarise(Tourism = sum(counts, na.rm = T),
+            Hotel= sum(Hotel, na.rm = T),
+            Guest = sum(Guest, na.rm = T),
+            Pop = sum(Pop),
+            LAD11CD = first(LAD11CD),
+            LAD11NM = first(LAD11NM)) %>% #
+  left_join(BootDeetsMean,., by = "MSOA11CD") %>%
+  mutate(Tourism = ifelse(is.na(Tourism), 0, Tourism),
+         Guest = ifelse(is.na(Guest), 0, Guest),
+         Hotel = ifelse(is.na(Hotel), 0, Hotel),
+         TourismDensity =scale(Tourism/Homes),
+         HotelDensity =scale(Hotel/Homes),
+         GuestDensity =scale(Guest/Homes),
+         TourismDensityRank = percent_rank(TourismDensity),
+         TourismDensityRankV2 = rank(TourismDensity, ties.method = "max"),
+         HotelDensityRank = percent_rank(HotelDensity),
+         GuestDensityRank = percent_rank(GuestDensity),
+         AffordRatio = scale(AffordRatio),
+         AffordRatio2 = AffordRatio^2)  %>% 
+  left_join(NeighbourhoodQuartiles %>% rename(Ego1Hotel= Hotel, Ego1Guest = Guest), by = "MSOA11CD") %>%
+  mutate(Ego1Guest = ifelse(is.na(Ego1Guest), 0, Ego1Guest),
+         Ego1Hotel = ifelse(is.na(Ego1Hotel), 0, Ego1Hotel))
+
+ModelMSOAdf <- MSOAtest %>%
+  mutate(ExtentRank = percent_rank(AffordRatio),
+         TourDepCat = case_when( 
+           TourismDensityRank>=0.5 & ExtentRank>=0.5 ~ 1, #wealthly high tourism
+           TourismDensityRank>=0.5 & ExtentRank<0.5 ~ 2, #Wealthy Low tourism
+           TourismDensityRank<0.5 & ExtentRank>=0.5 ~3, #Poor High tourism
+           TRUE ~ 4                                          #Poor low tourism
+         ) %>% as.factor)  %>%
+   mutate(MedianPercDiff = (MSOALowUseMedian-MSOAHomesMedian)/MSOAHomesMedian,
+         PercLowUse = LowUse/Homes,
+         RankLowUse = percent_rank(PercLowUse),
+         RankMedianDiff = percent_rank(MedianPercDiff),
+         Catagory = case_when( 
+           RankLowUse>=0.5 & RankMedianDiff>=0.5 ~ 1, #High low use and High price difference
+           RankLowUse>=0.5 & RankMedianDiff<0.5 ~ 2, #High low Use and Low rank price difference
+           RankLowUse<0.5 & RankMedianDiff>=0.5 ~3, # Low low use and high price difference
+           TRUE ~ 4 #Low low use low price difference
+         ) %>% as.factor,
+        Reference = RankLowUse>0.5, #Catagory==1|Catagory==2,
+         #Reference =MSOAHomesMedian<MSOALowUseMedian,
+         spare = 1)
+
+ModelMSOAdf   %>%
+  ggplot(aes(x= AffordRank, y = TourismDensityRankV2, colour = Reference)) + geom_point() 
++
+  geom_hline(yintercept = 0.5) +
+  geom_vline(xintercept = 0.5)
+
+ModelMSOAdf   %>%
+  filter(Tourism == 0) %>%
+  ggplot(aes(x= ExtentRank, y = LowUsePerc, colour = Catagory)) + geom_point()
++
+  geom_hline(yintercept = 0.5) +
+  geom_vline(xintercept = 0.5)
+
+ModelMSOAdf  %>%
+  ggplot(aes(x= RankLowUse, y = RankMedianDiff, colour = Guest>0)) + geom_point()
+
+table(ModelMSOAdf$Guest>0, ModelMSOAdf$RankLowUse>0.5)
+
+confusionMatrix(ModelMSOAdf$Tourism>0, ModelMSOAdf$RankLowUse>0.5)
+
+```
+
+#Model If a lot of LUPs
+
+```{r}
+
+Modeldf <- ModelMSOAdf #testLAD
+
+OpenFormula <- as.formula(Reference ~ Guest + Hotel + AffordRatio+ AffordRatio2)
+
+set.seed(1983)
+TestResample <- 1:100 %>% map(~  resample_partition(Modeldf , c(test = 0.2, train = 0.8)))
+
+#Make a lot of models
+
+ResOut <- 1:length(TestResample) %>% map_df(~{
+  Mod2 <- Modeldf  %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$train)) %>%
+  glm(formula = OpenFormula, data = ., family=binomial(link='logit'))
+
+preds2<- Modeldf  %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$test)) %>%
+predict(Mod2, ., type = "response")
+
+ConfOut<-Modeldf  %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$test)) %>%
+  pull(Reference) %>%
+confusionMatrix(.,preds2>0.5)
+
+ConfOut$overall %>% t %>% data.frame() %>% as.tibble
+
+})
+
+test <- tibble(truth = ConfOut, estimate = as.factor(preds2>0.5))
+conf_mat(test, truth, estimate) %>%summary(wide= T)
+
+MODOut <- 1:length(TestResample) %>% map_df(~{
+  Mod2 <- Modeldf  %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$train)) %>%
+  glm(formula = OpenFormula, data = ., family=binomial(link='logit'))%>%
+    tidy
+
+})
+
+ggplot(MODOut, aes(x = term, y = estimate)) + geom_boxplot()
+
+#
+#        TREEEEEEEEEEEEEEEEEE
+# 
+OpenFormula <- as.formula(Reference ~ TourismDensityRank + AffordRatio+ AffordRatio2)
+
+library(ranger)
+ResOut <- 1:length(TestResample) %>% map_df(~{
+  print(.x)
+  Mod2 <- Modeldf  %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$train)) %>%
+  ranger(formula = OpenFormula, data = . )
+
+preds2<- Modeldf  %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$test)) %>%
+predict(Mod2, ., type = "response")
+preds2 <- preds2$predictions
+
+ConfOut<-Modeldf  %>%
+  mutate(Reference = as.factor(Reference)) %>%
+  slice(as.integer(TestResample[[.x]]$test)) %>%
+  pull(Reference) %>%
+confusionMatrix(.,preds2)
+
+ConfOut$overall %>% t %>% data.frame() %>% as.tibble
+
+})
+
+sum(ResOut$Accuracy>ResOut$AccuracyNull)/nrow(ResOut)
+mean(ResOut$Accuracy)
+
+#The models are significantly greater than the null model when using a paired t-test.
+t.test(ResOut$Accuracy,ResOut$AccuracyNull, alternative = "greater", paired = T)
+
+ResOut %>%
+  ggplot(aes(x = (Accuracy - AccuracyNull))) + geom_density()
+
+```
+
+#Look at Westminster
+
+```{r}
+
+West <- LSOABiz %>5
   filter(LAD11CD=="E09000033")
@@
 Catering <- West %>%
-  filter(grepl("SELF CATER",X6))
+  filter(grepl("(SELF CATER)|(HOLIDAY)|(HOTEL)|(HOSTEL)(GUEST)",X6))
+
+sum(Catering$counts)
 
@@
 
-table(is.na(test$lsoa11cd))
+table(is.na(test$LSOA11CD))
 
 test2 <- test %>%
-  filter(!is.na(lsoa11cd)) %>%
-  group_by(lsoa11cd) %>%
+  filter(!is.na(LSOA11CD)) %>%
+  group_by(LSOA11CD) %>%
   summarise(counts = n(),
@@
 examin <- test %>% 
-  filter(lsoa11cd =="E01006854")
+  filter(LSOA11CD =="E01006854")
 
@@
 Flats3<- Flats %>% left_join(PstCdLSOA.raw)%>%
-   group_by(lsoa11cd) %>%
+   group_by(LSOA11CD) %>%
   summarise(Total = n()) %>%
-#  left_join(EW2, by = c("lsoa11cd" = "ECODE")) %>%
-  rename(LSOA_CODE = lsoa11cd)
+#  left_join(EW2, by = c("LSOA11CD" = "ECODE")) %>%
+  rename(LSOA_CODE = LSOA11CD)
 
